### 2014-12-04 wearables_survey.tex
Initial commit

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{Title Here}
%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}

%\subtitle{[Extended Abstract]
%\titlenote{Note
%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}

\numberofauthors{3}

\author{
% 1st. author
\alignauthor
Linda N. Lee
       \affaddr{University of California Berkeley}\\
       \email{lnl@berkeley.edu}
% 2nd. author
\alignauthor
Serge Egelman
       \affaddr{University of California Berkeley}\\
       \affaddr{International Computer Science Institute}\\
       \email{serge@cs.berkeley.edu}
% 3rd. author
\alignauthor David Wagner
       \affaddr{University of California Berkeley}\\
       \email{daw@cs.berkeley.edu}
}

\maketitle

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{Privacy, User Studies, Ubiquitous Computing,Internet of Things} % NOT required for Proceedings

\section{Introduction}

%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography

%  and remember to run:
% latex bibtex latex latex
% to resolve all references

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Appendix Title}

\balancecolumns

% That's all folks!
\end{document}

### 2014-12-04 wearables_survey.tex
Rough outline!

@@
 \alignauthor
-Linda N. Lee
-       \affaddr{University of California Berkeley}\\
+Linda N. Lee\\
+       \affaddr{UC Berkeley}\\
        \email{lnl@berkeley.edu}
@@
 \alignauthor
-Serge Egelman
-       \affaddr{University of California Berkeley}\\
-       \affaddr{International Computer Science Institute}\\
+Serge Egelman\\
+       \affaddr{UC Berkeley}\\
+       \affaddr{ICSI}\\
        \email{serge@cs.berkeley.edu}
 % 3rd. author
-\alignauthor David Wagner
-       \affaddr{University of California Berkeley}\\
+\alignauthor David Wagner\\
+       \affaddr{UC Berkeley}\\
        \email{daw@cs.berkeley.edu}
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
+Hello world.
 \end{abstract}
@@
 % A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
+\category{look it up}{keyword1}{keyword2}{keyword3}
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\terms{Theory}
+\terms{term1} {term2} {term3}
 
@@
 
+%%%%%%%%%%%%%%%%%%%
+%%%         PAPER BODY         %%%
+%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
+
+\section{Related Work}
+\subsection{Privacy for Wearables}
+\subsection{Privacy for Smartphones}
+\subsection{User Perception}
+\subsection{User Attitude}
+
+\section{Approach}
+\section{Scope}
+\section{Calibration}
+
+\section{Methodology}
+\subsection{Rationale}
+\subsection{Design}
+\subsubsection{Question Synthesis}
+\subsubsection{Validation}
+focus group here
+\subsection{Deployment}
+\subsection{Recruitment}
+
+\section{Survey}
+say numbers here
+\subsection{Format}
+\subsubsection{Cubetastic}
+\subsubsection{Tech Rankings}
+\subsubsection{Open-Ended Question}
+\subsubsection{Additional Questions}
+demographics and IUIPC
+
+\section{Results}
+takeaways
+\subsection{How Upset}
+\subsection{Tech Perceptions}
+\subsection{Risk Perceptions}
+
+\section{Discussion}
+\subsection{Limitations}
+\subsection{Future Research Directions}
+
+\section{Conclusion}
 
@@
 \section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
+NSF funding, SCRUB, BLUES. Also any people who helped.
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+%%%%%%%%%%%%%%%%%%%
+%%%            BIB & ACKS          %%%
+%%%%%%%%%%%%%%%%%%%
+
+% The following two commands are all you need in the initial runs of your .tex file to produce the bib
+%  and remember to run: latex bibtex latex latex to resolve all references
+
 \bibliographystyle{abbrv}
 \bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
 
@@
 %Appendix A
-\section{Appendix Title}
+\section{Full Survey}
+\section{Detailed Situation Rankings}
+\section{Detailed Tech Rankings}
+\section{Focus Group Script}
 

### 2014-12-20 wearables_survey.tex
rough rough draft

@@
 
-\title{Title Here}
+\title{Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices}
 %\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
@@
 \section{Introduction}
+Basically a longer version of the abstract, plus some additional motivational things thrown in here.
+
+2014 is year of wearables \cite{Forbes}.
+A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables \cite{Neilsen} says that most popular devices (61\%), followed by smart watches (45\%) and mHealth (mobile health) devices (17\%).
+It is estimated that ~15\% use it in daily life \cite{Nilsen}\cite{WearableStatNews}.
+
+End this section with an explicit list of contributions made by this paper.
+
+%%%%%%%%%%%%%%%%%%%
 
 \section{Related Work}
-\subsection{Privacy for Wearables}
-\subsection{Privacy for Smartphones}
+In this paper, we explore user perceptions of security threats for wearable devices.
+In this section, we discuss related works which explore threats for smartphones and wearable devices, discuss emerging challenges related to ubiquitous computing, and study user perceptions of threats and technologies.
+
+\subsection{Privacy for Smartphones and Wearables}
+Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.
+
+Mention any other privacy studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod. Also highlight how my study is different from previous studies.
+
+\subsection{Ubiquitous Computing}
+
 \subsection{User Perception}
-\subsection{User Attitude}
+Mention how people are generally really bad at estimating the likelihood of some threat or event occurring. And since
 
-\section{Approach}
-\section{Scope}
-\section{Calibration}
-
-\section{Methodology}
-\subsection{Rationale}
-\subsection{Design}
-\subsubsection{Question Synthesis}
-\subsubsection{Validation}
-focus group here
-\subsection{Deployment}
-\subsection{Recruitment}
+%%%%%%%%%%%%%%%%%%%
 
 \section{Survey}
-say numbers here
+The survey design process consisted of synthesizing a relevant and comprehensive set of questions, validating the relevance, clarity, and completeness of the questions, and concluded with finalizing distribution logistics.
+Details on the synthesis, validation, methodology, and data are below.
+
+\subsection{Synthesis} 
+Write about how I came up with the questions, what was considered (looking at many wearable devices and possible sensors, looking through previous works, just thinking of as many as possible), and the final list.
+
+\subsection{Validation}
+Talking about the focus group here. Does this even need to happen?
+
+\subsection{Methodology}
+CHANGE THISSSS !!!!!
+We recruited 500 participants on December 9th, 2013 via Amazon's Mechanical Turk.
+We restricted participants to those over 18 years old residing in the U.S.
+All participants stated that they owned a laptop or desktop computer with either an external or an internal webcam.
+We asked questions regarding participants' webcam use and their understanding of the purpose of the webcam LED.
+
+ %%%%%%%%%%%%%%%%%%%
+
+\section{Questions}
+The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (this was done to prevent any biases in answers from participants with respect to specific companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions.
+Details on the question ordering, question formatting, and sample questions are below.
+The full survey can be found at <LINK HERE>.
+
 \subsection{Format}
-\subsubsection{Cubetastic}
-\subsubsection{Tech Rankings}
-\subsubsection{Open-Ended Question}
+In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
+Out of the 27 seen by the participant, 10 of the questions are randomly selected from a particular set of questions (see below).
+\\[-.8cm]
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item 2 comprehension questions 
+\item 6/305 questions about various scenarios 
+\item 2/5 questions about smartphone scenarios 
+\item 1/20 benefit questions 
+\item 1/20 risk questions (same technology) 
+\item 4 demographics
+\item 1 open-ended question 
+\item 10 questions of IUIPC \\[-.8cm]
+\end{itemize}
+
+To mitigate any biases, we randomized the order in which users saw groups of questions.
+That is; the participant has an equal chance of seeing questions related to threat perceptions or questions related to risk and benefit assessment of technologies.
+Additionally, each question in the sections about various scenarios, questions about smartphone scenarios, and IUIPC questions were randomly selected.
+A participant was also equally likely to see the risk or benefit questions first when they got to the section pertaining to risk and benefit assessment of technologies.
+(Ugh this is bad, re-write later)
+
+\subsubsection{Threat Perceptions}
+Format of question explanation, list the edge case questions here. Show an example of the question.
+
+\subsubsection{Technology Perceptions}
+Format of the question explanation, list the technologies here (is this too many?). Show an example of the question.
+
+\subsubsection{User Concerns}
+This is an open-ended question. Show the question here. Say that the participants had as much space as they wanted, although they were shown a line.
+
 \subsubsection{Additional Questions}
-demographics and IUIPC
+demographics and IUIPC, explain why I used IUIPC instead of the Westin, just one or two sentences will do.
+
+%%%%%%%%%%%%%%%%%%%
 
 \section{Results}
-takeaways
-\subsection{How Upset}
-\subsection{Tech Perceptions}
-\subsection{Risk Perceptions}
+After removing X incomplete responses, our sample consisted of Y participants.
+Of these X, A\% were male, with a median age of B.
+Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+
+\subsection{Factors in Upsetting Users}
+We found that the data type and data recipient, respectively, are the most significant predictors of how upsetting or threatening a situation is perceived by a user.
+On the other hand, the device type does not significantly impact how users perceive a situation.
+
+\subsubsection{Data Type}
+blah blah here.
+
+%For all recipients \\[-.8cm]
+%
+%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+%  %\setcounter{enumi}{0}
+%  \item a video of you unclothed
+%  \item bank account information
+%  \item social security number
+%  \item video of you entering in your PIN
+%  \item a photo of you unclothed
+%  \item a photo of you that is incriminating or embarrassing
+%  \item username and password for websites
+%  \item credit card information
+%  \item a video of you that is incriminating or embarassing
+%  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
+%\end{enumerate}
+%
+%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+%  \setcounter{enumi}{63}
+%  \item eye movement patterns (for eye tracking)
+%  \item when and how much you exercise
+%  \item when you are happy or having fun
+%  \item which television shows you watch
+%  \item when you are busy or interruptible
+%  \item music from your device
+%  \item your heart rate
+%  \item your age 
+%  \item the language you speak
+%  \item your gender \\[-.8cm]
+%\end{enumerate}
+
+For shared only \\[-.8cm]
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  %\setcounter{enumi}{0}
+  \item social security number (98.04\%)
+  \item a video of you unclothed (97.44\%)
+  \item bank account information (97.10\%)
+  \item recordings of your work conversations (96.97\%)
+  \item a photo of you that is incriminating/embarrassing (96.36\%)
+  \item a photo of you unclothed (96.30\%)
+  \item credit card information (95.92\%)
+  \item username and password for websites (95.41\%)
+  \item a video of you entering in your PIN (93.91\%)
+  \item recordings of your phone conversations (93.88\%) \\[-.8cm]
+\end{enumerate}
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  \setcounter{enumi}{63}
+  \item your name (47.25\%)
+  \item when and how much you exercise (46.07\%)
+  \item when you were happy or having fun (38.10\%)
+  \item what television shows you watch (35.96\%)
+  \item when you are busy or interruptible (34.34\%)
+  \item your heart rate (32.28\%)
+  \item music from your device (31.87\%)
+  \item your age (29.67\%)
+  \item the language you speak (20.95\%)
+  \item your gender (16.81\%) \\[-.8cm]
+\end{enumerate}
+
+For appserver only  \\[-.8cm]
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  %\setcounter{enumi}{0}
+  \item bank account information (90.91\%)
+  \item a video of you unclothed (90.62\%)
+  \item social security number (88.68\%)
+  \item video of you entering your PIN (88.57\%)
+  \item a photo of you that is incriminating/embarrassing (78.05\%)
+  \item a photo of you unclothed (77.78\%)
+  \item a video of you entering a passcode to a door (75.00\%)
+  \item when and how much you have sex (73.08\%)
+  \item a video of you that is incriminating/embarassing (71.88\%)
+  \item a photo of you at home taken randomly by an inward-facing camera (66.67\%)  \\[-.8cm]
+\end{enumerate}
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  \setcounter{enumi}{63}
+  \item when and how much you exercise (16.67\%)
+  \item how much you use your phone (15.79\%)
+  \item your age (14.29\%)
+  \item how much you like the people you interact with (13.79\%)
+  \item when, what, and how much you ate (12.50\%)
+  \item which television shows you watch (11.43\%)
+  \item your gender (9.52\%)
+  \item your heart rate (9.09\%)
+  \item eye movement patterns (for eye tracking) (6.98\%)
+  \item the language you speak (2.50\%)\\[-.8cm]
+\end{enumerate}
+
+More text.
+
+\subsubsection{Data Recipient}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{recipient.png}
+	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
+\end{figure}
+
+\subsubsection{Device Type}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{device-type.png}
+	\caption{(This is a placeholder! TODO: generate a better version of this)}
+\end{figure}
+
+\subsection{A Bigger Picture}
+
+We asked users to rate how beneficial or risky a technology was, for all parties affected by the technology (including manufacturers, consumers, and bystanders), over a long period of time, with respect to other, well studied technologies.
+This gives us an interesting insight into how people perceive these new technologies.
+For instance, the capacity for facial detection on a wearable device is perceived to be as risky as interacting with a physical lawnmower.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{techplot.png}
+	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
+\end{figure}
+
+\subsubsection{Risk and Benefit Ranks} 
+\subsubsection{Lawnmower Ratios}
+
+\subsection{Perceived Concerns for Wearable Devices}
+
+Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices.
+Without any doubt, the most common concern for owning and interacting with wearable devices for the every day user is the \textit{loss of privacy}.
+
+Talk about the results of the open-ended answers here.
+
+%%%%%%%%%%%%%%%%%%%
 
 \section{Discussion}
+We take this section to discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
+
+\subsection{Future Research Directions}
+<ask David's/Serge's input for this section>
+
 \subsection{Limitations}
-\subsection{Future Research Directions}
+One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearable devices and their capabilities.
+83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen}\cite{WearableStatNews}, so our study is reflective of the status quo.
+We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables.
+However, that will also have its own bias and limitations as well, since they would not reflect the general population.
+We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
+
+Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}.
+While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S.
+population \cite{ross2010crowdworkers}\cite{kelley2010conducting}.
+Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S.
+public \cite{kang2014privacy}.
+
+The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
+For this reason, people were heavily primed for the open-ended question.
+However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
+The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
+
+I messed up that motorcycle question.
+
+%%%%%%%%%%%%%%%%%%%
 
 \section{Conclusion}
+END STRONG! Echo the conclusion a little, remind the people of the takeaways in a way that highlights the contribution of this paper.
 

### 2014-12-20 wearables_survey.tex
Filling in more writing.

@@
 
-\subsection{Synthesis} 
+\subsection{Threat Landscape Investigation} 
+(REDO) To generate the list of possible scenarios which can happen with a wearable device, we did three things.
+Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities.
+Secondly, we looked at past research in mobile devices, vision videos for wearables, and the news for possible concerns.
+
 Write about how I came up with the questions, what was considered (looking at many wearable devices and possible sensors, looking through previous works, just thinking of as many as possible), and the final list.
 
-\subsection{Validation}
 Talking about the focus group here. Does this even need to happen?
 
+\subsection{Calibrating with Existing Works}
+(REDO) We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices.
+Mobile devices threats are well studied and the closest well-researched thing to wearable device threats.
+
+We used a prompt similar to Fischoff's study so that we could compare our results to the ones that he got in his study, and to put more of the new technologies onto the risk/benefit map.
+This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies.
+
+\subsection{Validation}
+(REDO) We conducted a focus group to look over the list, brainstorm more scenarios, and clarify any scenarios which were unclear (we also used this time to time the survey and make sure the formatting was clear.
+
 \subsection{Methodology}
-CHANGE THISSSS !!!!!
-We recruited 500 participants on December 9th, 2013 via Amazon's Mechanical Turk.
-We restricted participants to those over 18 years old residing in the U.S.
-All participants stated that they owned a laptop or desktop computer with either an external or an internal webcam.
-We asked questions regarding participants' webcam use and their understanding of the purpose of the webcam LED.
+We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
+We restricted participants to those over 18 years old.
+No other restrictions on participation were applier.
+We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.
 

### 2014-12-20 wearables_survey.tex
Rough future directions done.

@@
 \subsection{Privacy for Smartphones and Wearables}
-Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.
+(REDO) Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.
 
@@
 \subsection{Ubiquitous Computing}
+(REDO) As technology becomes more and more ubiquitous, more sensors will record more things about more people more of the time.
+There are an endless amount of unique situations which can negatively impact a person's privacy or security.
+There is a clear need to better communicate these risks to people (cite webcam paper and other papers here?), but there are too many things to warn people about.
+Therefore, we need to know what are the most threatening and also most relevant situations to inform the users about, since we can't bug them all the time about everything.
 
 \subsection{User Perception}
-Mention how people are generally really bad at estimating the likelihood of some threat or event occurring. And since
+(REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people.
+We do this firstly because people are really bad at knowing the likelihood of something, especially a threat with respect to security or privacy, is going to happen (sources here).
+And while the most damaging situations should also be addressed, this is not yet possible since these technologies haven't been adopted and the damage hasn't happened, so we don't know yet.
+Additionally, since the number one concern that people had with these devices was privacy (can I say result here?
+I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.
 
@@
 Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities.
-Secondly, we looked at past research in mobile devices, vision videos for wearables, and the news for possible concerns.
+Secondly, we looked at past research in mobile devices and current wearable device considerations.
+Thirdly, we finished off brainstorming possible things yet to come by looking at vision videos for wearables, and the news for possible concerns.
 
-Write about how I came up with the questions, what was considered (looking at many wearable devices and possible sensors, looking through previous works, just thinking of as many as possible), and the final list.
-
-Talking about the focus group here. Does this even need to happen?
+Motivate the fact that this is important here! Mention ubiquitious computing, preventing security threats, etc.
 
@@
 \subsection{Future Research Directions}
-<ask David's/Serge's input for this section>
+(REDO, ask David's/Serge's input for this section) Additional future work is encouraged in the area of studying privacy with respect to ubiquitous computing, since we proved it was the number one concern of the users of wearable devices.
+Clearly, this is a hard question which has been worked on for a long time but not yet fully addressed.
+Even this survey just barely touched on the various factors which can influence privacy perceptions and how upset people would be.
+
+ Also, maybe some work with respect to security threats, and how feasible they might be, and some defenses against stopping wearables devices from getting sensitive information (like blocking text, detecting sensitive situations like the bathroom, etc.).
+Research which defends against false information, false positive commands, and just more safeguards against the new system for wearables, whatever that is, is also something to really look into.
+
+ Work making sure that people are aware of what is going on, using indicators, not-too-transparent interfaces, and maybe being polite (recording rules follow social rules--think polite glass talk from Jaeyeon at MSR) are going to be valuable as wearables get more sophisticated but also more adopted by people.
+Think about it--put people in control of the technology, not technology shifting the social norms (our survey says that one of the top concerns of people were about how wearables will change social norms).
 
@@
 
-I messed up that motorcycle question.
+(REDO, Should I even say this?) I messed up that motorcycle question.
+I wish I actually had a calibration point for high risk high benefit for the Fischoff technology assessment questions.
+But well, none of the new technologies fit that description so we didn't really need it critically.
 

### 2014-12-20 wearables_survey.tex
Rough and meta related work done.

@@
 
-\subsection{Privacy for Smartphones and Wearables}
-(REDO) Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.
+\subsection{Concerns for Smartphones and Wearables}
+(REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort.
+I will talk about how I model Adrienne's work in the next section, Survey, just give a nod to it here and go into it later.
+Since my results were that people care about privacy, security, health, and social change/social stigma, any phone studies which hint at any of those things will be good to put here.
+Be sure to go cite a fair number of them.
+Related work section is the part where it looks like I know stuff.
 
-Mention any other privacy studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod. Also highlight how my study is different from previous studies.
+Mention any studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod.
+Especially mention ones on privacy and perceptions, since I know those exist.
+I doubt there will be ones for social norm shifts/social stigma, or health concerns, but maybe I can at least include some security ones here too.
+Throughout mentioning all of these works, highlight how my study is different from previous studies.
 

### 2014-12-20 wearables_survey.tex
Rough of survey section done.

@@
 \begin{abstract}
-Hello world.
+(Okay, kind of intimidated with writing the abstract.
+My plan is to write intro/conclusion first and then condense it into here, while nodding off to the contributions that we made.) At the very least, I can say that we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices.
+Data type, data recipient, and device type all matter different amounts.
+All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies.
+Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma.
+Fantastic ending sentence here.
 \end{abstract}
@@
 
-\keywords{Privacy, User Studies, Ubiquitous Computing,Internet of Things} % NOT required for Proceedings
+\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearables} % NOT required for Proceedings
 
@@
 
+We need to investigate the threat landscape and people's privacy concerns now, before wearables are widely adopted, or designed without these considerations in mind.
+So although our research is at at time when things are rapidly changing and most people don't have wearables, it is crucial to do the research now so we can prevent badness later.
+
 \subsection{User Perception}
@@
 I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.
+
+We also study risk.
+Mention Fischoff here.
+This is a very seminal paper in risk perception and it also studies how safe enough something has to be before people can accept something.
+I will talk about how I model my work in the next section, Survey, just give it a nod here and go into it later.
+Also mention at least a couple more works related to risk perception here to round it off.
 
@@
 
-Motivate the fact that this is important here! Mention ubiquitious computing, preventing security threats, etc.
+We already motivated why ubiquitous computing is relevant and we need to do it, so no need to do it here.
+In the end, we ended up focusing questions on new capabilities that wearables have that smartphones and other devices do not, existing sensors, any concerns which might infringe on security and privacy, along with a couple investigative ones (like if someone recorded all your conversations but never shared it, are you going to be upset?
+that might be taken out of this paper, but still).
 
 \subsection{Calibrating with Existing Works}
-(REDO) We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices.
-Mobile devices threats are well studied and the closest well-researched thing to wearable device threats.
+(REDO) Mobile devices threats are well studied and the closest well-researched thing to wearable device threats.
+We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices.
+We purposed used the same scale and question format as she did in her study, but it's a pretty defensible scale to use anyway and the wording was about consistent with how we were going to do it anyway.
+Defend the likert scale use and the wording of the question a bit here.
+Because it is similar, and we also had calibrating questions, we can compare the threats with respect to existing threats studied.
+We're so relevant, yay.
 
@@
 This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies.
+This also makes the results that we have more accurate and tangible, since people have anchors to base their assessments off of, rather than comparing a bunch of things that seem nebulous to them.
 
 \subsection{Validation}
-(REDO) We conducted a focus group to look over the list, brainstorm more scenarios, and clarify any scenarios which were unclear (we also used this time to time the survey and make sure the formatting was clear.
+(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback.
+We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear.
+Logistically, we also used this time to time the survey, made sure the survey worked, and other things.
+Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.
 

### 2014-12-20 wearables_survey.tex
Rough of half of the question section done.

@@
 Details on the question ordering, question formatting, and sample questions are below.
-The full survey can be found at <LINK HERE>.
+The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
 
@@
 \subsubsection{Threat Perceptions}
-Format of question explanation, list the edge case questions here. Show an example of the question.
+Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000.
+people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants).
+These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc.
+\\[-.8cm]
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item Where and when would you wear the Cubetastic3000?
+\item What can the Cubetastic3000 do? \\[-.8cm]
+\end{itemize}
+
+The purpose of the 6/305 questions were to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not.
+These are word for word modeled after the mobile user study.
+You can see that in the first example question, these three controls are highlighted.
+Other questions were used for calibration with the smartphone study, where we literally ask the same questions as the study, but toggling the device type, to see if this plays a role in risk perception.
+\\[-.8cm]
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?
+\item How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first? \\[-.8cm]
+\end{itemize}
+
+Concluding blurb here about how we were actually able to tease those dimensions out and have a regression model in section <later section which doesn't exist yet>.
 
 \subsubsection{Technology Perceptions}
-Format of the question explanation, list the technologies here (is this too many?). Show an example of the question.
+The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
+We wanted to study personal but also broad perceptions of wearble risks.
+the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings.
+We did this so that we can calibrate the new technologies that we ask about with the existing seminal study.
+Prompt can be seen at <appendix something, add in soon>.
+
+After that prompt, users were given this question and asked to fill in the numbers according to the previous prompt’s instructions.
+Each person got the same four calibration questions (handguns, motorcycles, lawnmowers, electricity), and 1/20 randomized new technology.
+People rated the same randomized new technology for both benefit and risk.
+
+Fill in your benefit numbers for the following technologies:\\
+Fill in your risk numbers for the following technologies:
+
+Handguns: \_\_\_\_\_\_\_ \\
+Motorcycles: \_\_\_\_\_\_\_\\
+Lawnmowers: \_\_\_\_\_\_\_\\
+Voice-Based Emotion Detection: \_\_\_\_\_\_\_\\
+Electricity: \_\_\_\_\_\_\_\\
+
+The list of technologies included: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
+
+Note that some of these technologies were general technologies (internet), other were devices (smartphones), but most of them were new capabilities (facial detection).
+We were more interested in the capabilities, but found those other points to be useful for understanding where the risk/benefit of those capabilities stand respectively.
 

### 2014-12-20 wearables_survey.tex
rough of questions complete.

@@
 These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc.
-\\[-.8cm]
 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item Where and when would you wear the Cubetastic3000?
-\item What can the Cubetastic3000 do? \\[-.8cm]
-\end{itemize}
+\textit{Where and when would you wear the Cubetastic3000?}\\[-.5cm]
+
+\textit{What can the Cubetastic3000 do?}
 
@@
 Other questions were used for calibration with the smartphone study, where we literally ask the same questions as the study, but toggling the device type, to see if this plays a role in risk perception.
-\\[-.8cm]
 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?
-\item How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first? \\[-.8cm]
-\end{itemize}
+\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first}\\[-.5cm]
+
+\textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
 
@@
 
-Fill in your benefit numbers for the following technologies:\\
-Fill in your risk numbers for the following technologies:
+\textit{Fill in your benefit numbers for the following technologies:}\\
+\textit{Fill in your risk numbers for the following technologies:}
 
-Handguns: \_\_\_\_\_\_\_ \\
-Motorcycles: \_\_\_\_\_\_\_\\
-Lawnmowers: \_\_\_\_\_\_\_\\
-Voice-Based Emotion Detection: \_\_\_\_\_\_\_\\
-Electricity: \_\_\_\_\_\_\_\\
+\textit{Handguns}: \_\_\_\_\_\_\_ \\
+\textit{Motorcycles}: \_\_\_\_\_\_\_\\
+\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
+\textit{<New Tech Here>}: \_\_\_\_\_\_\_\\
+\textit{Electricity}: \_\_\_\_\_\_\_\\
 
@@
 \subsubsection{User Concerns}
-This is an open-ended question. Show the question here. Say that the participants had as much space as they wanted, although they were shown a line.
+Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.
+
+\textit{What do you think are the most likely risks associated with wearable devices?}
+
+Take this with a grain of salt since users are not the most accurate at determining which is the most likely, but we can really see what users care about.
+The participants had as much space as they wanted to write their reply.
+People were primed for this question because we asked it after the other two sets of questions, but this just means that people have been thinking about it for a while.
+We were not looking for hard results, but more of inspiration to direct future work and to just check if we were also asking the right questions which captured the people's concerns throughout the survey.
 
 \subsubsection{Additional Questions}
-demographics and IUIPC, explain why I used IUIPC instead of the Westin, just one or two sentences will do.
+During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not.
+We thought that would be important to know.
+Also, we imagined that privacy would be correlated to these results, which is why we made everyone take the IUIPC to see how much they cared about privacy.
+Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).
 

### 2014-12-20 wearables_survey.tex
rough intro done.

@@
 Basically a longer version of the abstract, plus some additional motivational things thrown in here.
+I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong.
+Hmm.
+Think about what to put here.
 
-2014 is year of wearables \cite{Forbes}.
+A huge paragraph or two on why wearables are important and how much they are in use.
+Basically, prove that the study is worth doing in the first place.
+Some sources to use: 2014 is year of wearables \cite{Forbes}.
 A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables \cite{Neilsen} says that most popular devices (61\%), followed by smart watches (45\%) and mHealth (mobile health) devices (17\%).
@@
 
-End this section with an explicit list of contributions made by this paper.
+People are getting upset and scared about the things that can happen with wearble devices.
+There was a scandal with fitbit where the 1) profiles were default public and 2) sex counted as an exercise (cite that), how google had to disable facial recognition for glass (cite) along with using voice commands rather than other commands for bystanders to be informed of what is going on (cite).
+We suspect that there will only be more and more situations like this to come, as wearables get increasingly powerful (cite) and are getting adopted by more people (cite), and across other demographics (cite).
+
+End this section with an explicit list of contributions made by this paper. \\[-.8cm]
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item we got people's perception on various new threats for wearable devices, a wide range of threats.
+\item we found out what matters in their perception of these things--data type, data recipient, and device type and how much each of those matter. We have a cool regression model for that. 
+\item we found out how people's perception of threats change when it is with respect to other people consuming the data, or just the device (data type analysis ranking with appserver only verse everyone else).
+\item we got people's risk and benefit assessment of new technologies and capabilities. Most new capabilities are seen as low risk low benefit, but we suspect it's because people aren't familiar. 
+\item we found out what people were, nebulously, most concerned with. Privacy, then security, health, finances, social norms. 
+\item we calibrate our work so it's relevant and understandable with smartphone research and risk perception research. We can even say that we extended those areas too, if I want to be bold. 
+\end{itemize}
 

### 2014-12-20 wearables_survey.tex
added some appendixes and references.

@@
        \affaddr{UC Berkeley}\\
-       \email{lnl@berkeley.edu}
+       \email{lnl@cs.berkeley.edu}
 % 2nd. author
@@
 \section{Introduction}
-Basically a longer version of the abstract, plus some additional motivational things thrown in here.
+(REDO) Basically a longer version of the abstract, plus some additional motivational things thrown in here.
 I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong.
@@
 Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.
+You can look at the focus group script in appendix \ref{sec:script}.
 
@@
 \subsection{Format}
-In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
+(REDO) In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
 Out of the 27 seen by the participant, 10 of the questions are randomly selected from a particular set of questions (see below).
@@
 A participant was also equally likely to see the risk or benefit questions first when they got to the section pertaining to risk and benefit assessment of technologies.
-(Ugh this is bad, re-write later)
 
 \subsubsection{Threat Perceptions}
-Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000.
+(REDO) Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000.
 people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants).
@@
 \subsubsection{Technology Perceptions}
-The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
+(REDO) The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
 We wanted to study personal but also broad perceptions of wearble risks.
@@
 We did this so that we can calibrate the new technologies that we ask about with the existing seminal study.
-Prompt can be seen at <appendix something, add in soon>.
+Prompt can be seen at appendix \ref{sec:prompt}.
 
@@
 \subsubsection{User Concerns}
-Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.
+(REDO) Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.
 
@@
 \subsubsection{Additional Questions}
-During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not.
+(REDO) During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not.
 We thought that would be important to know.
@@
 \subsubsection{Data Type}
-blah blah here.
+(REDO)
 
-%For all recipients \\[-.8cm]
-%
-%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-%  %\setcounter{enumi}{0}
-%  \item a video of you unclothed
-%  \item bank account information
-%  \item social security number
-%  \item video of you entering in your PIN
-%  \item a photo of you unclothed
-%  \item a photo of you that is incriminating or embarrassing
-%  \item username and password for websites
-%  \item credit card information
-%  \item a video of you that is incriminating or embarassing
-%  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
-%\end{enumerate}
-%
-%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-%  \setcounter{enumi}{63}
-%  \item eye movement patterns (for eye tracking)
-%  \item when and how much you exercise
-%  \item when you are happy or having fun
-%  \item which television shows you watch
-%  \item when you are busy or interruptible
-%  \item music from your device
-%  \item your heart rate
-%  \item your age 
-%  \item the language you speak
-%  \item your gender \\[-.8cm]
-%\end{enumerate}
+For all recipients \\[-.8cm]
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  %\setcounter{enumi}{0}
+  \item a video of you unclothed
+  \item bank account information
+  \item social security number
+  \item video of you entering in your PIN
+  \item a photo of you unclothed
+  \item a photo of you that is incriminating or embarrassing
+  \item username and password for websites
+  \item credit card information
+  \item a video of you that is incriminating or embarassing
+  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
+\end{enumerate}
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  \setcounter{enumi}{63}
+  \item eye movement patterns (for eye tracking)
+  \item when and how much you exercise
+  \item when you are happy or having fun
+  \item which television shows you watch
+  \item when you are busy or interruptible
+  \item music from your device
+  \item your heart rate
+  \item your age 
+  \item the language you speak
+  \item your gender \\[-.8cm]
+\end{enumerate}
 
@@
 \subsubsection{Data Recipient}
+(REDO)
 
@@
 \subsubsection{Risk and Benefit Ranks} 
+(REDO)
+
 \subsubsection{Lawnmower Ratios} 
+(REDO)
 
 \subsection{Perceived Concerns for Wearable Devices}
-
-Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices.
+(REDO) Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices.
 Without any doubt, the most common concern for owning and interacting with wearable devices for the every day user is the \textit{loss of privacy}.
 
-Talk about the results of the open-ended answers here.
+(I should probably make a table of the following. Ugh, but for now:)
+
+Privacy 				464 (25.99\%) \\
+Security 				94 (5.27\%)\\
+Hacking 				38 (2.13\%)\\
+Spying 				50 (2.80\%)\\ [-.5cm]
+
+Unaware Use 			167 (9.36\%)\\
+Accidental Sharing 		66 (3.70\%)\\
+Unaware Collection		64 (3.59\%)\\
+Unaware Access	 	44 (2.46\%)\\
+False Information 		33 (1.85\%)\\[-.5cm]
+
+Health Risk 			252 (14.12\%)\\
+Safety 				147 (8.24\%)\\
+Financial Cost	 		201 (11.26\%)\\[-.5cm]
+
+Social Impact 			135 (7.56\%)\\
+Social Stigma 			39 (2.18\%)\\
+Aesthetics 			19 (1.06\%)\\[-.5cm]
+
+Miscellaneous 		76 (4.26\%)\\
+None				51 (2.86\%)\\
+Don't know			 30 (1.68\%)\\
+Don't care 			6 (0.34\%)\\
+
+Talk about the coding labels and what they mean, in a very vague and compact way. Refer people to the appendix \ref{sec:coding} for what the coding means in detail.
+
+Takeaway is that people care about privacy, then security, health, social impact.
+Other interesting things to note are aesthetics, social stigma, and false information, which could be cool things to look into.
 
@@
 %Appendix A
-\section{Full Survey}
-\section{Detailed Situation Rankings}
-\section{Detailed Tech Rankings}
 \section{Focus Group Script}
+\label{sec:script}
+
+text text
+
+\section{Fischoff Prompts}
+\label{sec:prompt}
+
+text text
+
+\section{Coding Label Definitions}
+\label{sec:coding}
+
+text text
+%\section{Detailed Tech Rankings}
 

### 2014-12-20 wearables_survey.tex
rough conclusion done.

@@
 \section{Conclusion}
-END STRONG! Echo the conclusion a little, remind the people of the takeaways in a way that highlights the contribution of this paper.
+(REDO) END STRONG!
+Should I put this before the Discussion?
+Echo the introduction a little, remind the people of the takeaways in a way that highlights the contribution of this paper.
+Intro: ``we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices.
+Data type, data recipient, and device type all matter different amounts.
+All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies.
+Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma.
+Fantastic ending sentence here.''
+
+I can talk about the results a little bit more in depth because people have already supposedly read my whole paper now.
+Pull out the subtleties I couldn't have done in the introduction, and go into specific details, shooting out numbers and statistics.
+Then conclude the whole thing with an inspirational pitch on how there is much future work to be done in this area, how this area is exciting, and how I basically helped people see both of these things.
 

### 2014-12-20 wearables_survey.tex
half done roughing out the results section--last section to rough out!

@@
 
+\subsubsection{What Matters in Upsetting People}
+(REDO) Talk about the regression model here.
+Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.
+
+Also go into any correlations that I found with respect to demographics and the IUIPC index (I should do all of these things ASAP as soon as this paper is in good shape).
+There should be some interesting stuff there, whether there are specific correlations, or whether there is not.
+Both are good things to report and should be put here.
+
 \subsection{A Bigger Picture}
@@
 \subsubsection{Risk and Benefit Ranks} 
-(REDO)
+(REDO) Talk through the graph shown above.
+The basic takeaway is that all of the new technologies and capabilities are perceived to be low risk low benefit.
+We can see that for technologies that people are more familiar with, people rate it more beneficial and more risky (or is it because they are more relevant that they are more familiar to them?
+Can I make such a claim?).
+Interesting to note facial recognition versus detection, location tracking, and discrete camera.
+Refer to appendix \ref{sec:techrank} for the details (if I have space to include such a thing as the absolute benefit and risk ranking and quartiles in this paper..).
 
 \subsubsection{Lawnmower Ratios} 
-(REDO)
+(REDO) The basic idea for this is that I am going to compare all of the newly assessed technologies with respect to the well-studied technology generally considered to be low-risk and low-benefit, since all new technologies fit this mold.
+This can give a more accurate idea into how each person thought something was risky or not (twice as risky as the closest tech they know, or about equal, etc.).
+Do some fancy graphing stuff here.
+Maybe another scatter plot, or an overlay of various distributions of ratio of perceived lawnmower risk to technology risk.
+Hmm.
 
@@
 
+\section{Risk and Benefit Rankings}
+\label{sec:techrank}
+
+text text
+
 \section{Coding Label Definitions}

### 2014-12-20 wearables_survey.tex
Done with the rough draft. It is very rough, but also very done.

@@
 \subsubsection{Data Type}
-(REDO)
+(REDO) Okay, I list all of the top 10/bottom 10 lists I generated: the one for all recipients, one only with respect to friends, work, and public, and another for the app only.
+I think the interesting thing to do is to show the shared vs app only lists, and to highight what is different.
+If I could show the whole list of 70+ for both, that would be most insightful, but I don't have the place for it in this paper, so this will have to do.
+Maybe I can do a top/bottom 15 at the least, maybe that will be better?
 
@@
 
-More text.
+Results were that in the top 10, both app only and shared had: bank info, SSN, PIN, embarassing photo, naked photo, naked video.
+Write a sentence on why I think that is here.
+The differences were that the app had: door pw, sex freq, embarssing videos, and photos at home, while the shared had the differing top 5 to be work conversations, credit card, username and password,  and phone conversations.
+It's cool to see that it's like one is talking to a machine or a company and the other to a person, right?
+
+In the low 10, the common 6 were exercise details, age, tv shows, gender, heart rate, and language.
+For the 4 different low 10, the app only had: phone use, how much you like people, when and what you ate, and eye patterns for tracking.
+For shared, these 4 were name, having fun or happy, music, and if a person was busy or interruptible.
+Also, this is interesting.
+People don't want to share phone use, opinions on people, food habits, or eye patterns, but would find it useful to have for apps, and well, people don't care about observable things or happy/music with people.
+But maybe not apps since it seems creepy or will give them ads.
 
 \subsubsection{Data Recipient}
-(REDO)
+(REDO) Data recipient matters in how upset people get, or well, how much their privacy is invaded and even how secure their information is.
+What really matters is if it is shared to people or not.
+There isn't much difference between the friends, work, and public--they are all quite upsetting.
+Friends is a little lower, but not too significantly (do stats-y thing here).
+The difference between public being lower than work is probably due to the fact that people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+Basically, what matters is that there are guarantees that the information is bounded and used in a way that people would assume it would be used.
 
@@
 \subsubsection{Device Type}
+(REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not.
+In either case, this matters the least, and device type and data recipient are more influencing factors.
+This is just the result of biases in people we can't quite quantify.
 
@@
 \end{figure}
+
+with upset rates (cubetastic upset rate | smartphone upset rate)\\
+Q1: (14.81\% | 6.13\%)\\
+Q2: (44.11\% | 19.85\%)\\
+Q3: (87.09\% | 58.44\%)\\
+Q4: (52.77\% | 55.79\%)\\
+Q5: (86.49\% | 91.82\%)
+
+Exact question details here, and statistical stuff. Conclude with whatever conclusion I happen to come to after performing the statistical analysis.
 

### 2014-12-21 wearables_survey.tex
Added the appendixes

@@
 Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.
-You can look at the focus group script in appendix \ref{sec:script}.
+.
 
@@
 %Appendix A
-\section{Focus Group Script}
-\label{sec:script}
-
-text text
-
 \section{Fischoff Prompts}
@@
 
-text text
+BENEFIT:
+
+``We would like to ask you to rate the benefits associated with each of the following technologies.
+
+Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
+(e.g.
+for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.
+
+Do not consider the costs or risks associated with these items.
+It is true, for example, that sometimes swimmers can drown.
+But evaluating such risks is not your present job.
+Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.
+
+Please rate the following technologies below with a number.
+We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
+Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
+(For instance, a technology rated 34 is twice as beneficial as a technology rated 17)''
+
+RISK:
+
+``We would like to ask you to rate the risks associated with each of the following technologies.
+
+Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
+(e.g.
+for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.
+
+Do not consider the costs or benefits associated with these items.
+It is true, for example, that electricity also creates a market for home appliances.
+But evaluating such benefits is not your present job.
+Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.
+
+Please rate the following technologies below with a number.
+We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
+Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
+(For instance, a technology rated 14 is half as risky as a technology rated 28.)''
 
@@
 
-text text
+BENEFIT:
+
+technology 	median	25\%		75\% \\
+electricity	87	50	100\\
+internet	65	45	100\\
+laptops	60	40	80\\
+email	50	30	75\\
+smartphones	50	32.5	75\\
+location tracking	40	20	67.5\\
+heart rate detection	40	28	62.5\\
+language detection	35	15	60\\
+voice recognition	25	15	40\\
+speech to text	25	15	36.25\\
+lawnmowers	24	15	40\\
+facial recognition	22	13	40\\
+guns	20	10	30\\
+motrocycles	20	12	40\\
+voice based emotion detection	20	10	30\\
+facial detection	20	10	32\\
+discrete camera	20	15	30\\
+smartwatches	20	10	32.5\\
+google glass	20	12	40\\
+fitness trackers	19	10	30\\
+cubetastic	18	10	30\\
+discrete microphone	15	10	20\\
+age detection	12	10	21\\
+gender detection	10	10	15
+
+RISK:
+
+technology 	median	25\%		75\%\\
+guns	60	40	80\\
+motrocycles	45	27	70\\
+electricity	25	15	40\\
+lawnmowers	20	12	30\\
+facial recognition	17	12.5	30\\
+internet	15	10	30\\
+discrete camera	12	10	30\\
+location tracking	10	10	20\\
+age detection	10	10	15\\
+gender detection	10	10	12\\
+language detection	10	10	10\\
+voice based emotion detection	10	10	15\\
+facial detection	10	10	25\\
+voice recognition	10	10	15\\
+heart rate detection	10	10	10\\
+email	10	10	16\\
+speech to text	10	10	10\\
+discrete microphone	10	10	20\\
+smartphones	10	10	19\\
+laptops	10	10	15\\
+fitness trackers	10	10	10\\
+smartwatches	10	10	10\\
+google glass	10	10	20\\
+cubetastic	10	10	30
 
@@
 
-text text
+Privacy: ``privacy,'' revealing personal information, spying. \\
+Security:  ``security,'' compromise, malware, hacking. \\
+GPS tracking: ``location,'' ``GPS,'' being monitored.
+
+Unaware use: using data without permission or in a different way than understood by user. \\
+Unaware collection: collecting data without permission. \\
+Unaware access: disclosure of data without permission. \\
+False information: inaccurate or maliciously false data.
+
+Health Risk: radiation, cancer, or long-term effects.\\
+Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
+Discomfort: eye strain, headache, obscured vision, irritation. \\
+Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
+Theft: the device getting stolen.
+
+Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
+Social Stigma: judgment, hate, or bystander discomfort.\\ 
+Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky.
+
+Miscellaneous: odd comments, uncommon concerns. \\
+None: ``None,'' no threat, perceiving no big concerns \\
+Don't know: ``do not know,'' hinting at confusion \\
+Don't care: `` do not care,'' nonchalant answers
+
 %\section{Detailed Tech Rankings}
@@
 \end{document}
+\\

### 2014-12-26 wearables_survey.tex
Intro less rough done!

@@
 \section{Introduction}
-(REDO) Basically a longer version of the abstract, plus some additional motivational things thrown in here.
-I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong.
-Hmm.
-Think about what to put here.
+Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing to healthier living through fitness tracking.
+Wearable devices, or wearables, are the new front of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user.
+Wearbles are gaining lots of attention: Forbes has named 2014 the ``Year of Wearable Technology, \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.
 
-A huge paragraph or two on why wearables are important and how much they are in use.
-Basically, prove that the study is worth doing in the first place.
-Some sources to use: 2014 is year of wearables \cite{Forbes}.
-A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables \cite{Neilsen} says that most popular devices (61\%), followed by smart watches (45\%) and mHealth (mobile health) devices (17\%).
-It is estimated that ~15\% use it in daily life \cite{Nilsen}\cite{WearableStatNews}.
+More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}.
+It is estimated that 20\% the general population owns at least one wearable and 10\% uses at least one wearable in their daily lives \cite{WearableStatNews}.
+The demographics of wearables consumers are young and rich--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year.
+However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.
 
-People are getting upset and scared about the things that can happen with wearble devices.
-There was a scandal with fitbit where the 1) profiles were default public and 2) sex counted as an exercise (cite that), how google had to disable facial recognition for glass (cite) along with using voice commands rather than other commands for bystanders to be informed of what is going on (cite).
-We suspect that there will only be more and more situations like this to come, as wearables get increasingly powerful (cite) and are getting adopted by more people (cite), and across other demographics (cite).
+ %Most AR systems use voice as input \cite{roesner2014security},  along with using voice commands rather than other commands for bystanders to be informed of what is going on \cite{StarnerSpeech} but this might change since the interface needs to change.
 
-End this section with an explicit list of contributions made by this paper. \\[-.8cm]
+Even in early adoption, security and privacy concerns regarding wearable devices are becoming heightened as companies make headlines for incidents resulting in users' sexual activities exposed to the public.
+This occured when Fitbit's fitness profiles were public by default and allowed users to track sex as an exercise\cite{Fitbit}.
+In other instances, public discomfort prevented certain capabilities from being enabled.
+Google's Glass had to disable facial recognition for Glass \cite{GlassDetection} upon release.
+To avoid both scandalous breaches of privacy and public opposition for new capabilities, it is critical that we understand the threat landscape for wearable devices and which issues users most care about--before wearbles get increasingly more ubiquitous and powerful \cite{Implants}.
+In this work, we contribute the following: \\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item we got people's perception on various new threats for wearable devices, a wide range of threats.
-\item we found out what matters in their perception of these things--data type, data recipient, and device type and how much each of those matter. We have a cool regression model for that. 
-\item we found out how people's perception of threats change when it is with respect to other people consuming the data, or just the device (data type analysis ranking with appserver only verse everyone else).
-\item we got people's risk and benefit assessment of new technologies and capabilities. Most new capabilities are seen as low risk low benefit, but we suspect it's because people aren't familiar. 
-\item we found out what people were, nebulously, most concerned with. Privacy, then security, health, finances, social norms. 
-\item we calibrate our work so it's relevant and understandable with smartphone research and risk perception research. We can even say that we extended those areas too, if I want to be bold. 
+\item We show users' perceptions of a wide range of wearables threats.
+We contribute a topmost and bottommost concerns , along with an evaluation of which factors contribute to the severity of a threat.
+We find that data type, data recipient, and device type matter A\%, B\%, C\%, respectively.
+See section <todo> for details.
+\item We investigate how people's privacy preferences differ when data is perceived to be shared with people or a server.
+\item We show risk and benefit assessments of new technologies and capabilities; most are seen as low risk low benefit, but we hypothesize this is  the result of limited exposure. 
+\item We report people's self-reported top concerns for wearable devices.
+Privacy, by far, is the top concern.
+Other notable risks include information security, long-term health risks from use, finances, and change in social norms.
 \end{itemize}
@@
 
-BENEFIT:
+BENEFIT prompt:
 
-``We would like to ask you to rate the benefits associated with each of the following technologies.
+``We would like to ask you to rate the benefits associated with each of the following technologies.  \\[-.6cm]
 
@@
 for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.
+\\[-.6cm]
 
@@
 Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.
+\\[-.6cm]
 
@@
 
-RISK:
+RISK prompt:
 
-``We would like to ask you to rate the risks associated with each of the following technologies.
+``We would like to ask you to rate the risks associated with each of the following technologies. \\[-.6cm]
 
@@
 for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.
+\\[-.6cm]
 
@@
 But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.
+Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.\\[-.6cm]
 

### 2014-12-26 wearables_survey.tex
un-roughed Questions section a bit

@@
 
-More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}.
+More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}.
 It is estimated that 20\% the general population owns at least one wearable and 10\% uses at least one wearable in their daily lives \cite{WearableStatNews}.
@@
 
-\subsection{Threat Landscape Investigation} 
-(REDO) To generate the list of possible scenarios which can happen with a wearable device, we did three things.
-Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities.
-Secondly, we looked at past research in mobile devices and current wearable device considerations.
-Thirdly, we finished off brainstorming possible things yet to come by looking at vision videos for wearables, and the news for possible concerns.
+\subsection{Asking the Right Questions} 
+ We asked participants how they would feel if a device shared a particular piece of data with a target recipient.
+We purposefully asked specific questions limited to the participant, as these situations are easier to judge.
+The purpose of the bank of ~300 questions was not necessarily to get an absolute ranking of what upsets people and what does not, since the list isn't comprehensive of all possible threats (although top 10 and bottom 10 concerns can be seen in section <linkhere>).The real purpose behind asking an array of questions was to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event, while also exploring the new threat landscape for wearable devices.
 
-We already motivated why ubiquitous computing is relevant and we need to do it, so no need to do it here.
-In the end, we ended up focusing questions on new capabilities that wearables have that smartphones and other devices do not, existing sensors, any concerns which might infringe on security and privacy, along with a couple investigative ones (like if someone recorded all your conversations but never shared it, are you going to be upset?
-that might be taken out of this paper, but still).
+To synthesize the questions, we surveyed popular wearable devices' sensors, studied existing smartphone and wearables literature, and looked at vision videos for wearable devices.
+In the end, we especially chose  to investigate questions which focused on continuous audio recording, discrete image capture, continuous video capture, and biometrics, due to the prevalence of devices which take voice inputs as commands \cite{StarnerSpeech}, concern for image capture \cite{GlassDetection}, and popularity of fitness tracking \cite{Nilsen}.
+Exploratory questions, including but not limited to threats regarding information security, pattern recognition, and emotion detection are also studied.
 
-\subsection{Calibrating with Existing Works}
-(REDO) Mobile devices threats are well studied and the closest well-researched thing to wearable device threats.
-We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices.
-We purposed used the same scale and question format as she did in her study, but it's a pretty defensible scale to use anyway and the wording was about consistent with how we were going to do it anyway.
-Defend the likert scale use and the wording of the question a bit here.
-Because it is similar, and we also had calibrating questions, we can compare the threats with respect to existing threats studied.
-We're so relevant, yay.
+Questions which addressed situations applicable for both smart phone and wearables were deemphasized because these situations had been investigated.
+However, we did include these questions, primarily to calibrate our results for the other scenarios.
+We used a seven-point likert scale and used similar wording as Felt in her smartphone study \cite{Felt} so that we could determine both how changing the device in question caused a change in threat perception and how threatening new wearables threats were with respect to existing threats.
 
-We used a prompt similar to Fischoff's study so that we could compare our results to the ones that he got in his study, and to put more of the new technologies onto the risk/benefit map.
-This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies.
-This also makes the results that we have more accurate and tangible, since people have anchors to base their assessments off of, rather than comparing a bunch of things that seem nebulous to them.
+\subsection{Looking at the Bigger Picture}
+
+To complement our bank of targeted questions, we also asked participants to assess the comprehensive risks and benefits of a particular technology, over a long period of time, for all parties affected by the technology.
+The purpose of these questions were not necessarily to get an absolute ranking of technologies by risk or benefit, as perceptions may change (although you can see the rankings in appendix <linkhere>).
+However, the purpose of these questions was to gain insight into how participants perceived new technologies.
+
+We used a prompt similar to a seminal study in risk perception \cite{Fischhoff} and also asked our participants to rate some of the technologies in the study.
+We used technologies such as lawnmowers (considered to be low risk and low benefit) and electricity (considered to be low risk and high benefit) as comparison points for other technologies we ask our participants to assess.
+As a result, we have a mapping of risks and benefits of new technologies with respect to the well-studied technologies.
 
 \subsection{Validation}
-(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback.
-We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear.
-Logistically, we also used this time to time the survey, made sure the survey worked, and other things.
-Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.
-.
+We conducted a focus group to validate our survey scope.
+Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
+Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
+This time was used to discuss benefits and risks associated with wearables, talk through common concerns, and brainstorm additional scenarios for the survey.
+The focus group was also used to gauge survey comprehension, user fatigue, and other logistics.
 
@@
 We restricted participants to those over 18 years old.
-No other restrictions on participation were applier.
+No other restrictions on participation were applied.
 We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.

### 2014-12-29 wearables_survey.tex
Redo paper structure w/ Serge's feedback

@@
 
+%%%%% FEEDBACK TO INCORPORATE, from Serge
+
+%-"security and privacy concerns regarding wearable devices are becoming heightened as companies make headlines for incidents resulting in users’ sexual activities exposed to the public..." I would rewrite this.
+You don't really mean to say that tracking sexual activity is the *only* privacy and security concern.
+It's one of many.
+I would say at the beginning that there are myriad privacy/security concerns, and then go into specific examples (e.g., sex, facial recognition, etc.).
+%-I think you might want to motivate this better: why do we need to better understand the threat landscape?
+(Answer: to focus on the most concerning things and then warn users when they're about to occur or prevent them from happening altogether.)
+%-Start a new paragraph before the contribution bullets to say what we actually did. For example, "we surveyed 2,250 Internet users to determine..."
+%-For the bullets, these can be made much more concise.
+I would also frame them in terms of what we found, not what we did.
+For example, "we found that X% of participants found that Y threats were most concerning..."
+%-I would limit these bullets to the top 3-4 most interesting findings that we found.
+
 \section{Introduction}
@@
 However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.
-
- %Most AR systems use voice as input \cite{roesner2014security},  along with using voice commands rather than other commands for bystanders to be informed of what is going on \cite{StarnerSpeech} but this might change since the interface needs to change.
 
@@
 
-\section{Survey}
-The survey design process consisted of synthesizing a relevant and comprehensive set of questions, validating the relevance, clarity, and completeness of the questions, and concluded with finalizing distribution logistics.
-Details on the synthesis, validation, methodology, and data are below.
-
-\subsection{Asking the Right Questions} 
- We asked participants how they would feel if a device shared a particular piece of data with a target recipient.
-We purposefully asked specific questions limited to the participant, as these situations are easier to judge.
-The purpose of the bank of ~300 questions was not necessarily to get an absolute ranking of what upsets people and what does not, since the list isn't comprehensive of all possible threats (although top 10 and bottom 10 concerns can be seen in section <linkhere>).The real purpose behind asking an array of questions was to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event, while also exploring the new threat landscape for wearable devices.
-
-To synthesize the questions, we surveyed popular wearable devices' sensors, studied existing smartphone and wearables literature, and looked at vision videos for wearable devices.
-In the end, we especially chose  to investigate questions which focused on continuous audio recording, discrete image capture, continuous video capture, and biometrics, due to the prevalence of devices which take voice inputs as commands \cite{StarnerSpeech}, concern for image capture \cite{GlassDetection}, and popularity of fitness tracking \cite{Nilsen}.
-Exploratory questions, including but not limited to threats regarding information security, pattern recognition, and emotion detection are also studied.
-
-Questions which addressed situations applicable for both smart phone and wearables were deemphasized because these situations had been investigated.
-However, we did include these questions, primarily to calibrate our results for the other scenarios.
-We used a seven-point likert scale and used similar wording as Felt in her smartphone study \cite{Felt} so that we could determine both how changing the device in question caused a change in threat perception and how threatening new wearables threats were with respect to existing threats.
-
-\subsection{Looking at the Bigger Picture}
-
-To complement our bank of targeted questions, we also asked participants to assess the comprehensive risks and benefits of a particular technology, over a long period of time, for all parties affected by the technology.
-The purpose of these questions were not necessarily to get an absolute ranking of technologies by risk or benefit, as perceptions may change (although you can see the rankings in appendix <linkhere>).
-However, the purpose of these questions was to gain insight into how participants perceived new technologies.
-
-We used a prompt similar to a seminal study in risk perception \cite{Fischhoff} and also asked our participants to rate some of the technologies in the study.
-We used technologies such as lawnmowers (considered to be low risk and low benefit) and electricity (considered to be low risk and high benefit) as comparison points for other technologies we ask our participants to assess.
-As a result, we have a mapping of risks and benefits of new technologies with respect to the well-studied technologies.
-
-\subsection{Validation}
-We conducted a focus group to validate our survey scope.
-Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-This time was used to discuss benefits and risks associated with wearables, talk through common concerns, and brainstorm additional scenarios for the survey.
-The focus group was also used to gauge survey comprehension, user fatigue, and other logistics.
-
-\subsection{Methodology}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18 years old.
-No other restrictions on participation were applied.
-We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.
-
- %%%%%%%%%%%%%%%%%%%
-
-\section{Questions}
+\section{Methodology}
 The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (this was done to prevent any biases in answers from participants with respect to specific companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions.
@@
 
-\subsection{Format}
 (REDO) In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
@@
 
-\subsubsection{Threat Perceptions}
-(REDO) Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000.
-people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants).
-These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc.
+\subsection{Comprehension Questions}
+Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000.
+people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants)
 
@@
 \textit{What can the Cubetastic3000 do?}
+
+\subsection{Scenarios}
 
@@
 
-Concluding blurb here about how we were actually able to tease those dimensions out and have a regression model in section <later section which doesn't exist yet>.
+\subsection{Smartphone}
+Calibration ones
 
-\subsubsection{Technology Perceptions}
-(REDO) The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
+\subsection{Risk and Benefit}
+The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
 We wanted to study personal but also broad perceptions of wearble risks.
@@
 
-Note that some of these technologies were general technologies (internet), other were devices (smartphones), but most of them were new capabilities (facial detection).
-We were more interested in the capabilities, but found those other points to be useful for understanding where the risk/benefit of those capabilities stand respectively.
-
-\subsubsection{User Concerns}
-(REDO) Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.
+\subsection{Additional Questions}
+(REDO) During the exit portion of the survey, we asked for demographics (gender, age, education), if the person owns a wearable or not, and the IUIPC index.
+Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).
 
@@
 
-Take this with a grain of salt since users are not the most accurate at determining which is the most likely, but we can really see what users care about.
-The participants had as much space as they wanted to write their reply.
-People were primed for this question because we asked it after the other two sets of questions, but this just means that people have been thinking about it for a while.
-We were not looking for hard results, but more of inspiration to direct future work and to just check if we were also asking the right questions which captured the people's concerns throughout the survey.
+\subsection{Focus Group}
+We conducted a focus group to validate our survey scope.
+Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
+Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
+This time was used to discuss benefits and risks associated with wearables, talk through common concerns, and brainstorm additional scenarios for the survey.
+The focus group was also used to gauge survey comprehension, user fatigue, and other logistics.
 
-\subsubsection{Additional Questions}
-(REDO) During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not.
-We thought that would be important to know.
-Also, we imagined that privacy would be correlated to these results, which is why we made everyone take the IUIPC to see how much they cared about privacy.
-Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).
+\subsection{Recruitment}
+We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
+We restricted participants to those over 18 years old.
+No other restrictions on participation were applied.
+We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.
 
@@
 
-\subsubsection{Data Type}
+\subsection{Data Type}
 (REDO) Okay, I list all of the top 10/bottom 10 lists I generated: the one for all recipients, one only with respect to friends, work, and public, and another for the app only.
@@
 
-For all recipients \\[-.8cm]
+%For all recipients \\[-.8cm]
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  %\setcounter{enumi}{0}
-  \item a video of you unclothed
-  \item bank account information
-  \item social security number
-  \item video of you entering in your PIN
-  \item a photo of you unclothed
-  \item a photo of you that is incriminating or embarrassing
-  \item username and password for websites
-  \item credit card information
-  \item a video of you that is incriminating or embarassing
-  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
-\end{enumerate}
-
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  \setcounter{enumi}{63}
-  \item eye movement patterns (for eye tracking)
-  \item when and how much you exercise
-  \item when you are happy or having fun
-  \item which television shows you watch
-  \item when you are busy or interruptible
-  \item music from your device
-  \item your heart rate
-  \item your age 
-  \item the language you speak
-  \item your gender \\[-.8cm]
-\end{enumerate}
+%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+%  %\setcounter{enumi}{0}
+%  \item a video of you unclothed
+%  \item bank account information
+%  \item social security number
+%  \item video of you entering in your PIN
+%  \item a photo of you unclothed
+%  \item a photo of you that is incriminating or embarrassing
+%  \item username and password for websites
+%  \item credit card information
+%  \item a video of you that is incriminating or embarassing
+%  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
+%\end{enumerate}
+%
+%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+%  \setcounter{enumi}{63}
+%  \item eye movement patterns (for eye tracking)
+%  \item when and how much you exercise
+%  \item when you are happy or having fun
+%  \item which television shows you watch
+%  \item when you are busy or interruptible
+%  \item music from your device
+%  \item your heart rate
+%  \item your age 
+%  \item the language you speak
+%  \item your gender \\[-.8cm]
+%\end{enumerate}
 
@@
   \item when and how much you have sex (73.08\%)
-  \item a video of you that is incriminating/embarassing (71.88\%)
+  \item a video of you that is incriminating/embarrassing (71.88\%)
   \item a photo of you at home taken randomly by an inward-facing camera (66.67\%)  \\[-.8cm]
@@
 
-Results were that in the top 10, both app only and shared had: bank info, SSN, PIN, embarassing photo, naked photo, naked video.
+Results were that in the top 10, both app only and shared had: bank info, SSN, PIN, embarrassing photo, naked photo, naked video.
 Write a sentence on why I think that is here.
-The differences were that the app had: door pw, sex freq, embarssing videos, and photos at home, while the shared had the differing top 5 to be work conversations, credit card, username and password,  and phone conversations.
+The differences were that the app had: door pw, sex freq, embarrassing videos, and photos at home, while the shared had the differing top 5 to be work conversations, credit card, username and password,  and phone conversations.
 It's cool to see that it's like one is talking to a machine or a company and the other to a person, right?
@@
 
-\subsubsection{Data Recipient}
+\subsection{Data Recipient}
 (REDO) Data recipient matters in how upset people get, or well, how much their privacy is invaded and even how secure their information is.
@@
 
-\subsubsection{Device Type}
+\subsection{Device Type}
 (REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not.
@@
 
-\subsubsection{What Matters in Upsetting People}
-(REDO) Talk about the regression model here.
-Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.
-
-Also go into any correlations that I found with respect to demographics and the IUIPC index (I should do all of these things ASAP as soon as this paper is in good shape).
+\subsection{Correlation with Demographics}
+Talk about if any of the results correlated with demographics here.
+go into any correlations that I found with respect to demographics and the IUIPC index (I should do all of these things ASAP as soon as this paper is in good shape).
 There should be some interesting stuff there, whether there are specific correlations, or whether there is not.
@@
 
-\subsection{A Bigger Picture}
+\subsection{Risk and Benefit Ranks}
 
@@
 
-\subsubsection{Risk and Benefit Ranks} 
 (REDO) Talk through the graph shown above.
@@
 Refer to appendix \ref{sec:techrank} for the details (if I have space to include such a thing as the absolute benefit and risk ranking and quartiles in this paper..).
-
-\subsubsection{Lawnmower Ratios} 
-(REDO) The basic idea for this is that I am going to compare all of the newly assessed technologies with respect to the well-studied technology generally considered to be low-risk and low-benefit, since all new technologies fit this mold.
-This can give a more accurate idea into how each person thought something was risky or not (twice as risky as the closest tech they know, or about equal, etc.).
-Do some fancy graphing stuff here.
-Maybe another scatter plot, or an overlay of various distributions of ratio of perceived lawnmower risk to technology risk.
-Hmm.
 
@@
 We take this section to discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
+
+\subsection{What Matters in Upsetting People}
+(REDO) Talk about the REGRESSION MODEL here.
+Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.
 

### 2014-12-29 wearables_survey.tex
methodology un-roughed (except riskandben section)

@@
 \section{Methodology}
-The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (this was done to prevent any biases in answers from participants with respect to specific companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions.
+The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (done to prevent biases in answers from participants with respect to specific artifacts or companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions.
 Details on the question ordering, question formatting, and sample questions are below.
@@
 
-(REDO) In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
-Out of the 27 seen by the participant, 10 of the questions are randomly selected from a particular set of questions (see below).
-\\[-.8cm]
+In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
+Out of the 27 seen by each participant, 17 of the questions were constant, whereas 10 of the questions were selected at random from larger sets of questions.
+During the course of the survey, each participant answered:   \\[-.8cm]
 
@@
 \item 2 comprehension questions 
-\item 6/305 questions about various scenarios 
+\item 6/304 questions about various wearables scenarios 
 \item 2/5 questions about smartphone scenarios 
@@
 
-To mitigate any biases, we randomized the order in which users saw groups of questions.
-That is; the participant has an equal chance of seeing questions related to threat perceptions or questions related to risk and benefit assessment of technologies.
-Additionally, each question in the sections about various scenarios, questions about smartphone scenarios, and IUIPC questions were randomly selected.
-A participant was also equally likely to see the risk or benefit questions first when they got to the section pertaining to risk and benefit assessment of technologies.
+To mitigate any biases, the order in which question groups appeared to the user was randomized.
+Specifically, a participant had an equal chance of seeing questions related to the Cubetastic3000 or questions related to risk and benefit assessment.
+When a participant saw the risk and benefit assessment questions, risk or benefit questions were equally likely to be shown first.
+Whenever applicable, questions were randomly selected.
+For risk and benefit assessment, a technology was randomly selected for each participant, then risk and benefit questions for the same technology were selected for the participant.
 
 \subsection{Comprehension Questions}
-Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000.
-people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants)
+Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions.
+These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly.
+Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 464).
 
-\textit{Where and when would you wear the Cubetastic3000?}\\[-.5cm]
+\subsection{Wearables Scenarios}
+%okay, this section is kind of confusing, I must admit..
 
-\textit{What can the Cubetastic3000 do?}
+After participants had answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000 fictitious wearable device.
+Out of these 304 questions, 292 (73 data * 4 recipients) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+Additionally, there were 13 questions which did not follow the above format, lacking data to be shared and/or a recipient of any data.
+Of these questions, 5 questions were to calibrate with Felt's study on smartphones and the other 7  were exploratory questions.
+An example of a regular question, a calibration question, and exploratory question, respectively, are below:
 
-\subsection{Scenarios}
+\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?}\\[-.5cm]
 
-The purpose of the 6/305 questions were to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not.
-These are word for word modeled after the mobile user study.
-You can see that in the first example question, these three controls are highlighted.
-Other questions were used for calibration with the smartphone study, where we literally ask the same questions as the study, but toggling the device type, to see if this plays a role in risk perception.
+\textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]
 
-\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first}\\[-.5cm]
+\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}\\[-.5cm]
 
-\textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
+The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared and which recipient of the shared data would most upset users.
+The calibration questions were modeled after Felt's mobile user study, where we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.
+The remaining exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.
 
-\subsection{Smartphone}
-Calibration ones
+\subsection{Smartphone Scenarios}
+Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone.
+These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt's mobile user study for eliciting varying reactions from users.
+These questions were the basis for the five calibration wearables scenarios from the above section.
+Because we asked users questions differing only by the device in question, we are able to see how the change in device changes users' risk perception.
+Additionally, we compare our participants' perceptions of wearable device scenarios with existing perceptions of mobile device scenarios.
 
-\subsection{Risk and Benefit}
+\subsection{Risk and Benefit Assessment}
 The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
@@
 \subsection{Additional Questions}
-(REDO) During the exit portion of the survey, we asked for demographics (gender, age, education), if the person owns a wearable or not, and the IUIPC index.
-Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).
-
-\textit{What do you think are the most likely risks associated with wearable devices?}
+The exit portion of the survey consisted of demographics questions to better understand the answers.
+We included standard demographics questions such as age, gender, and education status, but also asked participants if they owned a wearable device to survey the population's exposure to these devices, prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences.
+We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}, rather than the Westin Index, which was found to be very coarse \cite{woodruff2014would}.
 
 \subsection{Focus Group}
-We conducted a focus group to validate our survey scope.
+We conducted a one-hour focus group to validate our design, gauge survey comprehension, and measure user fatigue.
+The focus group began with participants taking the survey.
+Afterward, the participants were asked to give feedback on the format and the content of the survey, noting any instructions or questions which were unclear and stating any suggestions for the content of the survey.
+The focus group concluded with a discussion of possible benefits and risks of wearable devices, to brainstorm any additional scenarios which may occur.
+Afterward, participants were debriefed and given \$30 in cash.
 Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
 Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-This time was used to discuss benefits and risks associated with wearables, talk through common concerns, and brainstorm additional scenarios for the survey.
-The focus group was also used to gauge survey comprehension, user fatigue, and other logistics.
 
@@
 On the other hand, the device type does not significantly impact how users perceive a situation.
+
+Specifically, people are most upset about x, y, z, when shared with public, work, or friends.
+
+People have different expectations of privacy when they perceive that data is being shared with an app rather than a human audience.
 

### 2014-12-29 wearables_survey.tex
done with methodology section

@@
 \subsection{Risk and Benefit Assessment}
-The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk.
-We wanted to study personal but also broad perceptions of wearble risks.
-the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings.
-We did this so that we can calibrate the new technologies that we ask about with the existing seminal study.
-Prompt can be seen at appendix \ref{sec:prompt}.
+In addition to investigating personal reactions to particular scenarios, we also wanted to study broad perceptions of various new technologies.
+Each participant saw 1 risk assessment question and 1 benefit assessment question regarding the same four previously studied technologies from the the seminal risk perception study by Fischhoff (handguns, motorcycles, lawnmowers, electricity), and 1 of the 20 new technologies.
+Participants were asked to rate the same randomized new technology for both risk and benefit assessment.
+The format of the questions were as follows:
 
-After that prompt, users were given this question and asked to fill in the numbers according to the previous prompt’s instructions.
-Each person got the same four calibration questions (handguns, motorcycles, lawnmowers, electricity), and 1/20 randomized new technology.
-People rated the same randomized new technology for both benefit and risk.
-
-\textit{Fill in your benefit numbers for the following technologies:}\\
-\textit{Fill in your risk numbers for the following technologies:}
+\textit{Fill in your risk (benefit) numbers for the following technologies:}\\[-.5cm]
 
@@
 \textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<New Tech Here>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\
+\textit{<Randomized>}: \_\_\_\_\_\_\_\\
+\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
 
-The list of technologies included: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
+To parallel the risk perception study, we gave our participants a similar prompt which instructed the participants to numerically express the conceived gross risk (gross benefit) for a long period of time for all parties involved.
+The prompt can be seen at appendix \ref{sec:prompt}.
+Specifically, we asked participants to evaluate the of following 20 new technologies: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
 

### 2014-12-29 wearables_survey.tex
part of results un-roughed. Still 4 sections to go.

@@
 These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly.
-Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 464).
+Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 465).
 
@@
 \section{Results}
-After removing X incomplete responses, our sample consisted of Y participants.
+After removing 465 incomplete responses, our sample consisted of 1,785 participants.
 Of these X, A\% were male, with a median age of B.
@@
 
-\subsection{Factors in Upsetting Users}
-We found that the data type and data recipient, respectively, are the most significant predictors of how upsetting or threatening a situation is perceived by a user.
-On the other hand, the device type does not significantly impact how users perceive a situation.
+Generally, any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deductible traits, such as the language being spoken, gender, and age, is considered the least sensitive.
+Additionally, data shared in any way, whether the recipient be friends, work contacts, or the public, is much more upsetting than the data is only shared with an app's server; there is no statistically significant difference between how upset a person would be if data was shared between the various recipients.
+Interestingly, people had another set of prioritized concerns when data was perceived to be shared with an app rather than a human recipient (for instance, people were okay with people knowing if they were busy or not, but not their device).
+Although whether the device in the scenario being a wearable or smart phone did elicit unique reactions of the situation from participants, no statistically significant conclusion can be made about whether one device was seen as more threatening than another device.
 
-Specifically, people are most upset about x, y, z, when shared with public, work, or friends.
+People consider most things to be non-risky.
 
-People have different expectations of privacy when they perceive that data is being shared with an app rather than a human audience.
+Self-reportedly, people are concerned about privacy.
 
@@
 \subsection{Correlation with Demographics}
-Talk about if any of the results correlated with demographics here.
-go into any correlations that I found with respect to demographics and the IUIPC index (I should do all of these things ASAP as soon as this paper is in good shape).
-There should be some interesting stuff there, whether there are specific correlations, or whether there is not.
-Both are good things to report and should be put here.
+%I didn't do the correlation yet
+We found that the very upset rate for participants was not correlated with (pick correct ones from IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), positively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), and negatively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients).
+
+%sentence for each factor and why it is/isn't correlated with the very upset rate; I just put in examples sentences here to fill it in; I will change them later. 
+Because wearable devices have been adopted by a younger, rich, technology-savvy demographic  \cite{cmo}, it is natural to see that younger or more educated participants have had a more favorable view of wearable devices.
+This may be due to cultural exposure through marketing or friends, or an attitude of openness to new technologies.
+Participants who had a higher IUIPC score, which infers a higher sensitivity to privacy, were more likely to be upset at the various scenarios which may occur when wearing a wearable device.
+Additionally, these people were more likely to be adverse to these technologies for the sake of preserving privacy, whether they had explicit concerns or a vague feeling of uneasiness.
+There was no correlation between a person's gender and their views of wearable devices, reaffirming that wearable devices are equally exposed to both genders.
 
@@
 \subsection{Perceived Concerns for Wearable Devices}
-(REDO) Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices.
-Without any doubt, the most common concern for owning and interacting with wearable devices for the every day user is the \textit{loss of privacy}.
-
-(I should probably make a table of the following. Ugh, but for now:)
+Near the end of the survey, we asked the participants an open-ended question, asking for the most likely risks associated with owning and interacting with wearable devices.
+Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:
 
@@
 Don't know		 30 (1.68\%)\\
-Don't care 			6 (0.34\%)\\
+Don't care 			6 (0.34\%)\\ [-.5cm]
 
-Talk about the coding labels and what they mean, in a very vague and compact way. Refer people to the appendix \ref{sec:coding} for what the coding means in detail.
-
-Takeaway is that people care about privacy, then security, health, social impact.
-Other interesting things to note are aesthetics, social stigma, and false information, which could be cool things to look into.
+Other significant secondary concerns included information compromise (Security), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact).
+Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.
 
@@
 
-\subsection{What Matters in Upsetting People}
+\subsection{A Regression Model}
 (REDO) Talk about the REGRESSION MODEL here.

### 2014-12-29 wearables_survey.tex
un-roughed almost all the results

@@
 
-People consider most things to be non-risky.
-
-Self-reportedly, people are concerned about privacy.
+Participants assessed many of the new technologies similarly as low risk and low benefit, which we suspect is due to the fact that most are not consciously aware of the way these technologies are being used.
+Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.
 
 \subsection{Data Type}
-(REDO) Okay, I list all of the top 10/bottom 10 lists I generated: the one for all recipients, one only with respect to friends, work, and public, and another for the app only.
-I think the interesting thing to do is to show the shared vs app only lists, and to highight what is different.
-If I could show the whole list of 70+ for both, that would be most insightful, but I don't have the place for it in this paper, so this will have to do.
-Maybe I can do a top/bottom 15 at the least, maybe that will be better?
+To determine the most concerning and least concerning data types, we consider the very upset rate (VUR) of various scenarios.
+To calculate these rates, we take the rate of responses where participants had indicated that they would be ``very upset'' (the maximum rating) with respect to the total number of responses for the question.
+Since people considered different things more or less sensitive with respect to the data recipient, we present the most and least concerning shared data along with the most and least concerning ``not shared'' data:
 
@@
 
-For shared only \\[-.8cm]
+For shared data (friends, work, public) \\[-.8cm]
 
@@
 
-For appserver only  \\[-.8cm]
+For not shared data (appserver only)  \\[-.8cm]
 
@@
 
-Results were that in the top 10, both app only and shared had: bank info, SSN, PIN, embarrassing photo, naked photo, naked video.
-Write a sentence on why I think that is here.
-The differences were that the app had: door pw, sex freq, embarrassing videos, and photos at home, while the shared had the differing top 5 to be work conversations, credit card, username and password,  and phone conversations.
-It's cool to see that it's like one is talking to a machine or a company and the other to a person, right?
+Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
+When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
+When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
+When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
 
-In the low 10, the common 6 were exercise details, age, tv shows, gender, heart rate, and language.
-For the 4 different low 10, the app only had: phone use, how much you like people, when and what you ate, and eye patterns for tracking.
-For shared, these 4 were name, having fun or happy, music, and if a person was busy or interruptible.
-Also, this is interesting.
-People don't want to share phone use, opinions on people, food habits, or eye patterns, but would find it useful to have for apps, and well, people don't care about observable things or happy/music with people.
-But maybe not apps since it seems creepy or will give them ads.
+On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
+When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
+When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
+When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
+However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
 
 \subsection{Data Recipient}
-(REDO) Data recipient matters in how upset people get, or well, how much their privacy is invaded and even how secure their information is.
-What really matters is if it is shared to people or not.
-There isn't much difference between the friends, work, and public--they are all quite upsetting.
-Friends is a little lower, but not too significantly (do stats-y thing here).
-The difference between public being lower than work is probably due to the fact that people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
-Basically, what matters is that there are guarantees that the information is bounded and used in a way that people would assume it would be used.
+People are upset when their data is shared without their permission, regardless of who the recipient is.
+Generally, there isn't a statistically significant difference between how upset people would be if data were to be shared with friends, work, and public, although when considering each scenario, there are certain scenarios which are considered to be more sensitive with one recipient than another.
+
+Out of all the recipients, friends are considered to be the least upsetting audience, but not too significantly (do stats-y thing here).
+There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
 
@@
 \subsection{Device Type}
+%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
+Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
+The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
+(A chi-square test can also accommodate more than 2 outcomes, whereas Fisher's exact test only works for 2 x 2; 2 outcomes and 2 conditions).
+http://en.wikipedia.org/wiki/Fisher%27s_exact_test
+%
+%For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test: http://en.wikipedia.org/wiki/McNemar%27s_test
+%
+%This site is good for quickly doing these tests on summary data: http://graphpad.com/quickcalcs/
+
 (REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not.
@@
 
-with upset rates (cubetastic upset rate | smartphone upset rate)\\
+  (cubetastic upset rate | smartphone upset rate)\\
 Q1: (14.81\% | 6.13\%)\\
@@
 \subsection{Risk and Benefit Ranks} 
+When assessing new technologies, participants generally had rated the technologies similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).
+We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
+A list of the ranking of most risky and most beneficial technologies can be see in appendix \ref{sec:techrank}; the most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
 
-We asked users to rate how beneficial or risky a technology was, for all parties affected by the technology (including manufacturers, consumers, and bystanders), over a long period of time, with respect to other, well studied technologies.
-This gives us an interesting insight into how people perceive these new technologies.
-For instance, the capacity for facial detection on a wearable device is perceived to be as risky as interacting with a physical lawnmower.
+%should I just put the list in here, in the main part of the paper?
 
@@
 	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
+	\label{fig:techplot}
 \end{figure}
 
-(REDO) Talk through the graph shown above.
-The basic takeaway is that all of the new technologies and capabilities are perceived to be low risk low benefit.
-We can see that for technologies that people are more familiar with, people rate it more beneficial and more risky (or is it because they are more relevant that they are more familiar to them?
-Can I make such a claim?).
-Interesting to note facial recognition versus detection, location tracking, and discrete camera.
-Refer to appendix \ref{sec:techrank} for the details (if I have space to include such a thing as the absolute benefit and risk ranking and quartiles in this paper..).
+Notably, technologies perceived to be beneficial include location tracking and heart rate detection.
+Again, this is probably do to the exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
+Technologies considered to be risky, such as a discrete camera and facial detection, seemed to be based on media exposure or general aversion to privacy invasion.
+However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
+As a takeaway, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
 
 \subsection{Perceived Concerns for Wearable Devices}
-Near the end of the survey, we asked the participants an open-ended question, asking for the most likely risks associated with owning and interacting with wearable devices.
+Near the end of the survey, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices.
 Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:
@@
 
-Other significant secondary concerns included information compromise (Security), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact).
+Other significant secondary concerns included information compromise (Security), financial cost of buying, replacing, or caring for the device (Financial), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact).
 Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

### 2014-12-30 wearables_survey.tex
inserted some comments

@@
 
+SAY THIS: full on stats test on all 74 data types seems unreasonable. Look at the regression model below.
+
 \subsection{Data Recipient}
@@
 \end{figure}
+
+SAY THIS: we performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size.
+To examine whether the violation of this assumption impacted our results, we further created a mixed effects model, in order to isolate the subjects variable (i.e., to examine the extent to which random effects stemming from individual differences may be responsible for the effects that we observed) !!!report effect sizes
 

### 2015-01-02 wearables_survey.tex
revisions with scanned comments

@@
 Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing to healthier living through fitness tracking.
-Wearable devices, or wearables, are the new front of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user.
-Wearbles are gaining lots of attention: Forbes has named 2014 the ``Year of Wearable Technology, \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.
+Wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user.
+Wearbles are gaining lots of attention.
+Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.
 
-More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}.
-It is estimated that 20\% the general population owns at least one wearable and 10\% uses at least one wearable in their daily lives \cite{WearableStatNews}.
-The demographics of wearables consumers are young and rich--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year.
+A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables found that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}.
+It is estimated that 20\% of the general population own at least one wearable and 10\% use at least one wearable in their daily lives \cite{WearableStatNews}.
+The demographics of wearables consumers are young and affluent--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year.
 However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.
 
-Even in early adoption, security and privacy concerns regarding wearable devices are becoming heightened as companies make headlines for incidents resulting in users' sexual activities exposed to the public.
-This occured when Fitbit's fitness profiles were public by default and allowed users to track sex as an exercise\cite{Fitbit}.
+Even in early adoption, security and privacy concerns regarding wearable devices are becoming heightened.
+Many of these concerns relate to users' activities being exposed to the public without awareness or consent.
+For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise\cite{Fitbit}, resulting in disclosing sensitive information about the user.
 In other instances, public discomfort prevented certain capabilities from being enabled.
-Google's Glass had to disable facial recognition for Glass \cite{GlassDetection} upon release.
-To avoid both scandalous breaches of privacy and public opposition for new capabilities, it is critical that we understand the threat landscape for wearable devices and which issues users most care about--before wearbles get increasingly more ubiquitous and powerful \cite{Implants}.
+Google's Glass had to disable facial recognition for Glass upon release \cite{GlassDetection}.
+
+To avoid both scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand the threat landscape for wearable devices and which issues users most care about--before wearbles become increasingly more ubiquitous and powerful \cite{Implants}.
+A better understanding of the threat landscape will enable researchers and companies alike to focus on the most concerning factors for the user--allowing research for effective warnings of relevant events and an informed focus of protecting the data of high priority.
+
+We surveyed 2,250 internet users to determine what data is sensitive, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
 In this work, we contribute the following: \\[-0.8cm]
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We show users' perceptions of a wide range of wearables threats.
-We contribute a topmost and bottommost concerns , along with an evaluation of which factors contribute to the severity of a threat.
-We find that data type, data recipient, and device type matter A\%, B\%, C\%, respectively.
-See section <todo> for details.
+\item We show users' perceptions of a wide range of wearables threats, along with an evaluation of which factors contribute to the severity of a threat.
+We find that data type and data recipient matter, but the device type does not.
 \item We investigate how people's privacy preferences differ when data is perceived to be shared with people or a server.
-\item We show risk and benefit assessments of new technologies and capabilities; most are seen as low risk low benefit, but we hypothesize this is  the result of limited exposure. 
+\item We show risk and benefit assessments of new technologies and capabilities relative to better understood technologies.
+Most are perceived as low-risk/low-benefit, but we hypothesize this is  the result of limited exposure.
 \item We report people's self-reported top concerns for wearable devices.
 Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, finances, and change in social norms.
+Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
 \end{itemize}
@@
 \section{Related Work}
-In this paper, we explore user perceptions of security threats for wearable devices.
-In this section, we discuss related works which explore threats for smartphones and wearable devices, discuss emerging challenges related to ubiquitous computing, and study user perceptions of threats and technologies.
+In this section, we discuss related work which explores threats for smartphones and wearable devices, discusses emerging challenges related to ubiquitous computing, and studies user perceptions of threats and technologies.
 
@@
 \section{Methodology}
-The survey consisted of questions regarding concerns with respect to a factious wearable device called the Cubetastic3000 (done to prevent biases in answers from participants with respect to specific artifacts or companies), smartphone concerns, risk and benefit assessment of technologies, and exit questions.
-Details on the question ordering, question formatting, and sample questions are below.
-The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
+Our survey was conducted in multiple parts.
+The first section of the survey consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the Cubetastic3000 (done to prevent biases in answers from participants with respect to specific artifacts or companies).
+The next section of questions consisted of questions regarding individual and situational smartphone concerns, which were questions more familiar to our participant base and are used for calibrating results.
+The following section of the survey consisted of risk and benefit assessment of technologies, where participants were asked to consider general, multi-situational concerns regarding specific technologies.
+The final section of the survey consisted of demographics questions on basic information, privacy concerns, and wearable device ownership.
+Details on the question ordering, question formatting, and sample questions are discussed in the remainder of this section.
 
-In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
+%%% commented out for anonymity; can comment back in later.
+%The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
+
+%In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
 Out of the 27 seen by each participant, 17 of the questions were constant, whereas 10 of the questions were selected at random from larger sets of questions.
-During the course of the survey, each participant answered:   \\[-.8cm]
+
+During the course of the survey, each participant answered 27 questions:   \\[-.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions 
-\item 6/304 questions about various wearables scenarios 
-\item 2/5 questions about smartphone scenarios 
-\item 1/20 benefit questions 
-\item 1/20 risk questions (same technology) 
-\item 4 demographics
-\item 1 open-ended question 
-\item 10 questions of IUIPC \\[-.8cm]
+\item 2 comprehension questions (attention checks)
+\item 6 questions about various wearables scenarios 
+\item 2 questions about smartphone scenarios 
+\item 2 risk/benefit questions 
+\item 15 demographics questions \\[-.8cm]
 \end{itemize}
 
-To mitigate any biases, the order in which question groups appeared to the user was randomized.
-Specifically, a participant had an equal chance of seeing questions related to the Cubetastic3000 or questions related to risk and benefit assessment.
-When a participant saw the risk and benefit assessment questions, risk or benefit questions were equally likely to be shown first.
-Whenever applicable, questions were randomly selected.
-For risk and benefit assessment, a technology was randomly selected for each participant, then risk and benefit questions for the same technology were selected for the participant.
+To mitigate any biases, the order in which question groups appeared to the user, the ordering within each group, and, when applicable, the order of the answers for questions, were randomized for each user.
+Details with respect to the relevant section of the survey are discussed in the respective subsections below.
 
@@
 
-After participants had answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000 fictitious wearable device.
-Out of these 304 questions, 292 (73 data * 4 recipients) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-Additionally, there were 13 questions which did not follow the above format, lacking data to be shared and/or a recipient of any data.
-Of these questions, 5 questions were to calibrate with Felt's study on smartphones and the other 7  were exploratory questions.
+After participants answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000.
+Out of these 304 questions, 292 (73 <data> * 4 <recipient>) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+
+The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared.
+Additionally, there were 13 questions which did not follow the above format, lacking <data> to be shared and/or a <recipient>.
+Of these questions, 5 questions were to calibrate with existing privacy work for smartphones and the other 7  were exploratory questions.
+The calibration questions were modeled after a mobile user study conducted by Felt et.
+al \cite{Felt}, where we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.
+The remaining exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.
 An example of a regular question, a calibration question, and exploratory question, respectively, are below:
 
-\textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?}\\[-.5cm]
+standard: \textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?}\\[-.5cm]
 
-\textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]
+calibration: \textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]
 
-\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}\\[-.5cm]
-
-The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared and which recipient of the shared data would most upset users.
-The calibration questions were modeled after Felt's mobile user study, where we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.
-The remaining exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.
+exploratory: \textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}\\[-.5cm]
 
@@
 Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone.
-These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt's mobile user study for eliciting varying reactions from users.
+These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et.
+al's mobile user study \cite{Felt} for eliciting varying reactions from users.
 These questions were the basis for the five calibration wearables scenarios from the above section.
@@
 
+MENTION VUR AND WHY WE USED IT.
+
 \subsection{Risk and Benefit Assessment}
-In addition to investigating personal reactions to particular scenarios, we also wanted to study broad perceptions of various new technologies.
-Each participant saw 1 risk assessment question and 1 benefit assessment question regarding the same four previously studied technologies from the the seminal risk perception study by Fischhoff (handguns, motorcycles, lawnmowers, electricity), and 1 of the 20 new technologies.
+
+In addition to investigating personal reactions to particular scenarios, we also wanted to study broad perceptions of various new technologies.We asked participants to evaluate the of following 20 new technologies: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
+
+For risk and benefit assessment, a technology was randomly selected for each participant, then risk and benefit questions for the same technology were selected for the participant.
+Each participant saw 1 risk assessment question and 1 benefit assessment question, in a randomized order.
+These questions ask about four previously studied technologies from the the seminal risk perception study by Fischhoff \cite{Fischhoff} (handguns, motorcycles, lawnmowers, and electricity), and 1 of the 20 new technologies.
 Participants were asked to rate the same randomized new technology for both risk and benefit assessment.
@@
 
-\textit{Fill in your risk (benefit) numbers for the following technologies:}\\[-.5cm]
+\textit{Fill in your risk/benefit numbers for the following technologies:}\\[-.5cm]
 
@@
 \textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Randomized>}: \_\_\_\_\_\_\_\\
+\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
 \textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
 
-To parallel the risk perception study, we gave our participants a similar prompt which instructed the participants to numerically express the conceived gross risk (gross benefit) for a long period of time for all parties involved.
-The prompt can be seen at appendix \ref{sec:prompt}.
-Specifically, we asked participants to evaluate the of following 20 new technologies: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
+To parallel the risk perception study, we gave our participants a similar prompt which instructed them to numerically express the conceived gross risk/gross benefit for a long period of time for all parties involved.
+The prompt can be seen in appendix \ref{sec:prompt}.
 
@@
 The exit portion of the survey consisted of demographics questions to better understand the answers.
-We included standard demographics questions such as age, gender, and education status, but also asked participants if they owned a wearable device to survey the population's exposure to these devices, prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences.
-We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}, rather than the Westin Index, which was found to be very coarse \cite{woodruff2014would}.
+We included standard demographics questions such as age, gender, and education, but also asked participants if they owned a wearable device to survey the population's exposure to these devices.
+We also prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences.
+We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}.
 
@@
 Afterward, participants were debriefed and given \$30 in cash.
+All of our participants were recruited locally through Craigslist.
 Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
@@
 We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18 years old.
+We restricted participants to those over 18 years old and living in the United States.
 No other restrictions on participation were applied.
-We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.
 
@@
 
-Generally, any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deductible traits, such as the language being spoken, gender, and age, is considered the least sensitive.
-Additionally, data shared in any way, whether the recipient be friends, work contacts, or the public, is much more upsetting than the data is only shared with an app's server; there is no statistically significant difference between how upset a person would be if data was shared between the various recipients.
-Interestingly, people had another set of prioritized concerns when data was perceived to be shared with an app rather than a human recipient (for instance, people were okay with people knowing if they were busy or not, but not their device).
-Although whether the device in the scenario being a wearable or smart phone did elicit unique reactions of the situation from participants, no statistically significant conclusion can be made about whether one device was seen as more threatening than another device.
+Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.
+Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public.
+Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat.
+When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit.
+Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.
 
-Participants assessed many of the new technologies similarly as low risk and low benefit, which we suspect is due to the fact that most are not consciously aware of the way these technologies are being used.
-Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.
+ROADMAP
 
@@
 
-%For all recipients \\[-.8cm]
+For all recipients \\[-.8cm]
 
-%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-%  %\setcounter{enumi}{0}
-%  \item a video of you unclothed
-%  \item bank account information
-%  \item social security number
-%  \item video of you entering in your PIN
-%  \item a photo of you unclothed
-%  \item a photo of you that is incriminating or embarrassing
-%  \item username and password for websites
-%  \item credit card information
-%  \item a video of you that is incriminating or embarassing
-%  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
-%\end{enumerate}
-%
-%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-%  \setcounter{enumi}{63}
-%  \item eye movement patterns (for eye tracking)
-%  \item when and how much you exercise
-%  \item when you are happy or having fun
-%  \item which television shows you watch
-%  \item when you are busy or interruptible
-%  \item music from your device
-%  \item your heart rate
-%  \item your age 
-%  \item the language you speak
-%  \item your gender \\[-.8cm]
-%\end{enumerate}
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  %\setcounter{enumi}{0}
+  \item a video of you unclothed (95.97\%)
+  \item bank account information (95.91\%)
+  \item social security number (94.84\%)
+  \item video of you entering in your PIN (92.67\%)
+  \item a photo of you unclothed (92.59\%)
+  \item a photo of you that is incriminating or embarrassing (91.39\%)
+  \item username and password for websites (89.55\%)
+  \item credit card information (88.98\%)
+  \item a video of you that is incriminating or embarrassing (88.41\%)
+  \item a photo you at home taken randomly by an inward-facing camera (87.50\%) \\[-.8cm]
+\end{enumerate}
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+  \setcounter{enumi}{63}
+  \item eye movement patterns (for eye tracking) (40.51\%) 
+  \item when and how much you exercise (38.66\%)
+  \item when you are happy or having fun (34.51\%)
+  \item which television shows you watch (30.20\%)
+  \item when you are busy or interruptible (29.50\%)
+  \item music from your device (28.06\%)
+  \item your heart rate (27.50\%)
+  \item your age (24.29\%)
+  \item the language you speak (15.86\%)
+  \item your gender (14.91\%) \\[-.8cm]
+\end{enumerate}
+
+TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why. SAY THIS: full on stats test on all 74 data types seems unreasonable. Look at the regression model below.
+
+\subsection{Data Recipient}
+People are upset when their data is shared without their permission, regardless of who the recipient is.
+Generally, there isn't a statistically significant difference between how upset people would be if data were to be shared with friends, work, and public, although when considering each scenario, there are certain scenarios which are considered to be more sensitive with one recipient than another.
+
+Out of all the recipients, friends are considered to be the least upsetting audience, but not too significantly (do stats-y thing here).
+There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{recipient.png}
+	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
+\end{figure}
+
+			Chi\^2	2-tail p	Sig?		n		effect size \\
+Friends-Work	20.365	<0.0001	Yes		5039		0.004\\
+Friends-Public	5.349	0.0207	No		5146		0.001\\
+Friends-App	380.000	<0.0001	Yes		5098		0.075\\
+Work-Public	5.054	0.0246	No		5133		0.001\\
+Work-App		564.318	<0.0001	Yes		5085		0.111\\
+Public-App		479.980	<0.0001	Yes		5192		0.092\\
+
+Friends-Work	0.867	0.3517	No		604		0.001\\
+Friends-Public	1.460	0.2229	No		639		0.002\\
+Friends-App	32.066	<0.0001	Yes		609		0.053\\
+Work-Public	0.670	0.7956	No		631		0.001\\
+Work-App		42.492	<0.0001	Yes		601		0.071\\
+Public-App		48.520	<0.0001	Yes		636		0.076\\
+
+SAY THIS: we performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size.
+To examine whether the violation of this assumption impacted our results, we further created a mixed effects model, in order to isolate the subjects variable (i.e., to examine the extent to which random effects stemming from individual differences may be responsible for the effects that we observed).
+When we preserve the independence (by randomly sampling, the results still hold.
 
@@
 
-SAY THIS: full on stats test on all 74 data types seems unreasonable. Look at the regression model below.
-
-\subsection{Data Recipient}
-People are upset when their data is shared without their permission, regardless of who the recipient is.
-Generally, there isn't a statistically significant difference between how upset people would be if data were to be shared with friends, work, and public, although when considering each scenario, there are certain scenarios which are considered to be more sensitive with one recipient than another.
-
-Out of all the recipients, friends are considered to be the least upsetting audience, but not too significantly (do stats-y thing here).
-There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{recipient.png}
-	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
-\end{figure}
-
-SAY THIS: we performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size.
-To examine whether the violation of this assumption impacted our results, we further created a mixed effects model, in order to isolate the subjects variable (i.e., to examine the extent to which random effects stemming from individual differences may be responsible for the effects that we observed) !!!report effect sizes
-
 \subsection{Device Type}
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-(A chi-square test can also accommodate more than 2 outcomes, whereas Fisher's exact test only works for 2 x 2; 2 outcomes and 2 conditions).
-http://en.wikipedia.org/wiki/Fisher%27s_exact_test
-%
-%For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test: http://en.wikipedia.org/wiki/McNemar%27s_test
-%
-%This site is good for quickly doing these tests on summary data: http://graphpad.com/quickcalcs/
 
@@
 Q4: (52.77\% | 55.79\%)\\
-Q5: (86.49\% | 91.82\%)
+Q5: (86.49\% | 91.82\%)\\
+
+			Chi\^2	2-tail p	Sig?		n		effect size\\
+Between-All	2.814	0.1395	No		3589		0.001\\
+Between-Q1	2.500	0.1139	No		714		0.004\\
+Between-Q2	17.333	<0.0001	Yes		708		0.024\\
+Between-Q3	0.020	0.8886	No		699		0.000\\
+Between-Q4	1.426	0.2324	No		731		0.002\\
+Between-Q5	1.611		0.2043	No		710		0.002\\
+
+			Chi\^2	2-tail p	Sig?	Odds ratio	Confidence	Odds range\\
+Within-All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
+Within-Q1		0		1		No	n/a	         n/a	                  n/a\\
+Within-Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
+Within-Q3		0		1		No	n/a	         n/a	                  n/a\\
+Within-Q4		0		1		No	0.5		95\%			0.008 to9.605\\
+Within-Q5		0		1		No	n/a	         n/a	                  n/a\\
+
+For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
+Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
+The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
+For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
 

### 2015-01-02 wearables_survey.tex
done editing methodology

@@
 
+%%% I actually think it flows better without having a subsection here..
+
+%\subsection{Question Format} 
+%
+%\subsubsection{Comprehension Questions} 
+%Talk about format here. 
+%
+%\subsubsection{Wearables Scenarios} 
+%Talk about format here. 
+%
+%\subsubsection{Smartphone Scenarios} 
+%Talk about format here. 
+%
+%\subsubsection{Risk and Benefit Assessment} 
+%Talk about format here.
+
 \subsection{Comprehension Questions}
@@
 These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly.
-Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants, which were 79\% of all incomplete or bad responses (n = 465).
+Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants.
 
@@
 Additionally, there were 13 questions which did not follow the above format, lacking <data> to be shared and/or a <recipient>.
-Of these questions, 5 questions were to calibrate with existing privacy work for smartphones and the other 7  were exploratory questions.
-The calibration questions were modeled after a mobile user study conducted by Felt et.
-al \cite{Felt}, where we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.
-The remaining exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.
+The 13 exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.
 An example of a regular question, a calibration question, and exploratory question, respectively, are below:
@@
 standard: \textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?}\\[-.5cm]
-
-calibration: \textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]
 
@@
 Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone.
+Unlike the wearables scenario questions, these questions only ask about various situations which may occur using a smartphone, without a <data> or <recipient>.
 These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et.
 al's mobile user study \cite{Felt} for eliciting varying reactions from users.
+
+calibration: \textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]
+
 These questions were the basis for the five calibration wearables scenarios from the above section.
@@
 Additionally, we compare our participants' perceptions of wearable device scenarios with existing perceptions of mobile device scenarios.
-
-MENTION VUR AND WHY WE USED IT.
+Of the 13 exploratory questions in the wearables section, 5 of those questions were to calibrate with existing privacy work for smartphones and the other 7  were exploratory questions.
+These wearables questions, like the smart phone questions, were modeled after the mobile user study conducted by Felt et.
+al \cite{Felt}, but we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.
 
@@
 Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+
+MENTION VUR AND WHY WE USED IT.
 
@@
 
-\subsection{A Regression Model}
-(REDO) Talk about the REGRESSION MODEL here.
-Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.
-
 \subsection{Future Research Directions}

### 2015-01-02 wearables_survey.tex
tweaks to results (more to go).

@@
 
-Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.
+%confusing runthrough of the results.. is this too packed? 
+%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.
 Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public.
@@
 
-ROADMAP
+Write about what is commented out above, but as a ROADMAP.
 
@@
 
-TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why. SAY THIS: full on stats test on all 74 data types seems unreasonable. Look at the regression model below.
+TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why.
+A statistical analysis with respect to all 74 <data> is not feasible to explore within this paper.
+However, we consider these data types in our regression model.
 
@@
 
-SAY THIS: we performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size.
+We performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.
+However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size.
 To examine whether the violation of this assumption impacted our results, we further created a mixed effects model, in order to isolate the subjects variable (i.e., to examine the extent to which random effects stemming from individual differences may be responsible for the effects that we observed).
-When we preserve the independence (by randomly sampling, the results still hold.
+When we perform the same tests on many subsets of questions, with one answer randomly sampled from each participant (preserving assumption about the independence of observations), the results are still equivalent.
 
@@
 
-\subsection{Correlation with Demographics}
+\subsection{Regression Model} 
+Introduce the model and what was considered in the model.
+Serge can probably do this better.
+Talk about which factors mattered, and how much, and also interesting statistics we found, if any.
+Also, correlations with demographics here as well!
+
 %I didn't do the correlation yet
-We found that the very upset rate for participants was not correlated with (pick correct ones from IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), positively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), and negatively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients).
+(EXAMPLE) We found that the very upset rate for participants was not correlated with (pick correct ones from IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), positively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), and negatively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients).
 
-%sentence for each factor and why it is/isn't correlated with the very upset rate; I just put in examples sentences here to fill it in; I will change them later. 
 Because wearable devices have been adopted by a younger, rich, technology-savvy demographic  \cite{cmo}, it is natural to see that younger or more educated participants have had a more favorable view of wearable devices.

### 2015-01-02 wearables_survey.tex
Finally got methodology section and results intro looking right.

@@
 
+\subsection{Analysis}
+After removing 465 incomplete responses, our sample consisted of 1,785 participants.
+Of these X, A\% were male, with a median age of B.
+For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale.
+The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced.
+Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission.
+Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were.
+Although participants gave a wide range of numbers (i.e.
+a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis.
+Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers.
+Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+
 %%%%%%%%%%%%%%%%%%%
@@
 \section{Results}
-After removing 465 incomplete responses, our sample consisted of 1,785 participants.
-Of these X, A\% were male, with a median age of B.
-Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
-
-MENTION VUR AND WHY WE USED IT.
-
 %confusing runthrough of the results.. is this too packed? 
@@
 
-Write about what is commented out above, but as a ROADMAP.
+In this section, we present the results of our multiple-part survey.
+We first discuss which <data>, <recipient>, and <device> types contributed to how threatening a situation was perceived by a participant.
+We follow this discussion with a regression model which discusses all of the factors which may have contributed to a participant being very upset at a given situation, including <data>, <recipient>, and <device> types, but also with respect to demographics questions.
+Next, we discuss the participants' risk/benefit assessment of various new technologies with respect to well-known, existing technologies.
+We conclude the section with participants self-reported concerns about the biggest risks in owning a wearable device.
 

### 2015-01-02 wearables_survey.tex
Yay fixed methodology formatting.

@@
 
-%%% I actually think it flows better without having a subsection here..
+\subsection{Question Format} 
+We talk about the format and justification of the questions from our survey below.
 
-%\subsection{Question Format} 
-%
-%\subsubsection{Comprehension Questions} 
-%Talk about format here. 
-%
-%\subsubsection{Wearables Scenarios} 
-%Talk about format here. 
-%
-%\subsubsection{Smartphone Scenarios} 
-%Talk about format here. 
-%
-%\subsubsection{Risk and Benefit Assessment} 
-%Talk about format here.
-
-\subsection{Comprehension Questions}
+\subsubsection{Comprehension Questions}
 Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions.
@@
 
-\subsection{Wearables Scenarios}
+\subsubsection{Wearables Scenarios}
 %okay, this section is kind of confusing, I must admit..
@@
 
-\subsection{Smartphone Scenarios}
+\subsubsection{Smartphone Scenarios}
 Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone.
@@
 
-\subsection{Risk and Benefit Assessment}
+\subsubsection{Risk and Benefit Assessment}
 
@@
 
-\subsection{Additional Questions}
+\subsubsection{Additional Questions}
 The exit portion of the survey consisted of demographics questions to better understand the answers.
@@
 \section{Results}
-%confusing runthrough of the results.. is this too packed? 
+%%%confusing runthrough of the results.. is this too packed. I wrote a roadmap paragraph instead based on this, which is below. Much better.
+
 %Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.

### 2015-01-02 wearables_survey.tex
finished the perceptions section of results (all other subsections remain).

@@
 \subsection{Perceived Concerns for Wearable Devices}
-Near the end of the survey, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices.
-Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:
+So far, participants had responded to questions regarding specific scenarios or assessed technologies presented to them.
+For completeness of the survey, we also wanted to capture the participants' general reactions to wearable devices as a whole.
+To do this, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices.
 
-Privacy 				464 (25.99\%) \\
-Security 				94 (5.27\%)\\
-Hacking 				38 (2.13\%)\\
-Spying 				50 (2.80\%)\\ [-.5cm]
+\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
 
-Unaware Use 			167 (9.36\%)\\
-Accidental Sharing 		66 (3.70\%)\\
-Unaware Collection		64 (3.59\%)\\
-Unaware Access	 	44 (2.46\%)\\
-False Information 		33 (1.85\%)\\[-.5cm]
+This question was asked along with the demographics questions, near the end of the survey, but before any IUIPC questions regarding privacy, to avoid biasing.
+The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
 
-Health Risk 			252 (14.12\%)\\
-Safety 				147 (8.24\%)\\
-Financial Cost	 		201 (11.26\%)\\[-.5cm]
+Without any doubt, the open-ended responses state that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}.
+This top concern surpassed all other concerns by about an order of magnitude or more:
 
-Social Impact 			135 (7.56\%)\\
-Social Stigma 			39 (2.18\%)\\
-Aesthetics 			19 (1.06\%)\\[-.5cm]
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{lll}
 
-Miscellaneous 		76 (4.26\%)\\
-None				51 (2.86\%)\\
-Don't know		 30 (1.68\%)\\
-Don't care 			6 (0.34\%)\\ [-.5cm]
+Concern &  Responses &  Frequency &   \\
+Privacy & 452 & (25.32\%) \\
+Being Unaware & 275 & (15.40\%) \\
+%Unaware Use & 167 & (9.36\%)\\
+%Unaware Collection & 64 & (3.59\%)\\
+%Unaware Access & 44 & (2.46\%)\\
+Health Risk & 191 & (10.70\%)\\
+Safety & 186 & (10.42\%)\\
+Financial Cost & 151 & (8.46\%)\\
+Security &	144 & (8.07\%)\\
+Social Impact &	157 & (8.80\%)\\
+Accidental Sharing &	69 & (3.87\%)\\
+Miscellaneous &	57 & (3.19\%)\\
+None	& 51 & (2.86\%)\\
+Social Stigma &	39 & (2.18\%)\\
+False Information & 33 & (1.85\%)\\
+Don't know & 31 & (1.74\%)\\
+Aesthetics 	& 19 & (1.06\%)\\
+Don't care 	& 11 & (0.62\%)\\
 
-Other significant secondary concerns included information compromise (Security), financial cost of buying, replacing, or caring for the device (Financial), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact).
+\end{tabular}
+\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
+\label{open-responses}
+\end{center}
+\end{table}
+
+Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as battery burns or distractions causing car accidents (Safety), the high financial cost of buying, replacing, or caring for the device (Financial),  information compromise (Security), and resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact).
 Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

### 2015-01-02 wearables_survey.tex
formatted some data in results (todo: just data, recipient, device section of results)

@@
 
-For all recipients \\[-.8cm]
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  %\setcounter{enumi}{0}
-  \item a video of you unclothed (95.97\%)
-  \item bank account information (95.91\%)
-  \item social security number (94.84\%)
-  \item video of you entering in your PIN (92.67\%)
-  \item a photo of you unclothed (92.59\%)
-  \item a photo of you that is incriminating or embarrassing (91.39\%)
-  \item username and password for websites (89.55\%)
-  \item credit card information (88.98\%)
-  \item a video of you that is incriminating or embarrassing (88.41\%)
-  \item a photo you at home taken randomly by an inward-facing camera (87.50\%) \\[-.8cm]
-\end{enumerate}
+<data> &  VUR  \\
+a video of you unclothed & 95.97\% \\
+bank account information & 95.91\% \\
+social security number & 94.84\% \\
+video of you entering in your PIN & 92.67\% \\
+a photo of you unclothed & 92.59\% \\
+an incriminating/embarrassing photo of you & 91.39\% \\
+username and password for websites & 89.55\% \\
+credit card information & 88.98\% \\
+an incriminating/embarrassing video of you & 88.41\% \\
+a random (inward-facing) photo you at home & 87.50\% \\
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  \setcounter{enumi}{63}
-  \item eye movement patterns (for eye tracking) (40.51\%) 
-  \item when and how much you exercise (38.66\%)
-  \item when you are happy or having fun (34.51\%)
-  \item which television shows you watch (30.20\%)
-  \item when you are busy or interruptible (29.50\%)
-  \item music from your device (28.06\%)
-  \item your heart rate (27.50\%)
-  \item your age (24.29\%)
-  \item the language you speak (15.86\%)
-  \item your gender (14.91\%) \\[-.8cm]
-\end{enumerate}
+\end{tabular}
+\caption{A table of the top 10 upsetting <data> types, irregardless of recipient or data type.}
+\label{top10}
+\end{center}
+\end{table}
+
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
+%starting from #63
+<data> &  VUR  \\
+eye movement patterns (for eye tracking) & 40.51\% \\
+when and how much you exercise  & 38.66\% \\
+when you are happy or having fun  & 34.51\% \\
+which television shows you watch & 30.20\% \\
+when you are busy or interruptible  & 29.50\% \\
+music from your device  & 28.06\% \\
+your heart rate & 27.50\% \\
+your age & 24.29\% \\
+the language you speak & 15.86\% \\
+your gender & 14.91\% \\
+
+\end{tabular}
+\caption{A table of the bottom 10 upsetting <data> types, irregardless of recipient or data type.}
+\label{bottom10}
+\end{center}
+\end{table}
 
@@
 Notably, technologies perceived to be beneficial include location tracking and heart rate detection.
-Again, this is probably do to the exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
+Again, we believe this is the result of exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
 Technologies considered to be risky, such as a discrete camera and facial detection, seemed to be based on media exposure or general aversion to privacy invasion.
 However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
-As a takeaway, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
+It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
 
@@
 Concern &  Responses &  Frequency &   \\
-Privacy & 452 & (25.32\%) \\
-Being Unaware & 275 & (15.40\%) \\
+Privacy & 452 & 25.32\% \\
+Being Unaware & 275 & 15.40\ \\
 %Unaware Use & 167 & (9.36\%)\\
@@
 %Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & (10.70\%)\\
-Safety & 186 & (10.42\%)\\
-Financial Cost & 151 & (8.46\%)\\
-Security &	144 & (8.07\%)\\
-Social Impact &	157 & (8.80\%)\\
-Accidental Sharing &	69 & (3.87\%)\\
-Miscellaneous &	57 & (3.19\%)\\
-None	& 51 & (2.86\%)\\
-Social Stigma &	39 & (2.18\%)\\
-False Information & 33 & (1.85\%)\\
-Don't know & 31 & (1.74\%)\\
-Aesthetics 	& 19 & (1.06\%)\\
-Don't care 	& 11 & (0.62\%)\\
+Health Risk & 191 & 10.70\%\\
+Safety & 186 & 10.42\%\\
+Financial Cost & 151 & 8.46\%\\
+Security &	144 & 8.07\%\\
+Social Impact &	157 & 8.80\%\\
+Accidental Sharing &	69 & 3.87\%\\
+Miscellaneous &	57 & 3.19\%\\
+None	& 51 & 2.86\%\\
+Social Stigma &	39 & 2.18\%\\
+False Information & 33 & 1.85\%\\
+Don't know & 31 & 1.74\%\\
+Aesthetics 	& 19 & 1.06\%\\
+Don't care 	& 11 & 0.62\%\\
 

### 2015-01-02 wearables_survey.tex
more formatting statistical results

@@
 
-			Chi\^2	2-tail p	Sig?		n		effect size \\
-Friends-Work	20.365	<0.0001	Yes		5039		0.004\\
-Friends-Public	5.349	0.0207	No		5146		0.001\\
-Friends-App	380.000	<0.0001	Yes		5098		0.075\\
-Work-Public	5.054	0.0246	No		5133		0.001\\
-Work-App		564.318	<0.0001	Yes		5085		0.111\\
-Public-App		479.980	<0.0001	Yes		5192		0.092\\
+%\begin{table}%[h]
+%\begin{center}
+%\begin{tabular}{llllll}
+%Recipients	& Chi^2 &	2-tail P & 	Sig?	& n & Effect Size \\
+%Work-App	& 564.318 & <0.0001 & Yes	& 5085 & 0.111\\
+%Public-App	& 479.980 & <0.0001 & Yes	& 5192 & 0.092\\
+%Friends-App & 380.000 & <0.0001 & Yes & 5098 & 0.075\\
+%Friends-Work & 20.365 & <0.0001 & Yes & 5039 & 0.004\\
+%Friends-Public & 5.349 & 0.0207 & No	& 5146 & 0.001\\
+%Work-Public&  5.054 & 0.0246 & No & 5133	& 0.001\\
+%\end{tabular}
+%\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
+%\label{recipient}
+%\end{center}
+%\end{table}
 
-Friends-Work	0.867	0.3517	No		604		0.001\\
-Friends-Public	1.460	0.2229	No		639		0.002\\
-Friends-App	32.066	<0.0001	Yes		609		0.053\\
-Work-Public	0.670	0.7956	No		631		0.001\\
-Work-App		42.492	<0.0001	Yes		601		0.071\\
-Public-App		48.520	<0.0001	Yes		636		0.076\\
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{llll}
+Recipients	& Chi^2 &	2-tail P &  Effect Size \\
+Work-App	& 564.318 & <0.0001 & 0.111\\
+Public-App	& 479.980 & <0.0001 &  0.092\\
+Friends-App & 380.000 & <0.0001 & 0.075\\
+Friends-Work & 20.365 & <0.0001 &  0.004\\
+Friends-Public & 5.349 & 0.0207 &  0.001\\
+Work-Public&  5.054 & 0.0246 &  0.001\\
+\end{tabular}
+\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
+\label{recipient}
+\end{center}
+\end{table}
+
+%Friends-Work	0.867	0.3517	No		604		0.001\\
+%Friends-Public	1.460	0.2229	No		639		0.002\\
+%Friends-App	32.066	<0.0001	Yes		609		0.053\\
+%Work-Public	0.670	0.7956	No		631		0.001\\
+%Work-App	42.492	<0.0001	Yes		601		0.071\\
+%Public-App	48.520	<0.0001	Yes		636		0.076\\
 
@@
 
-For shared data (friends, work, public) \\[-.8cm]
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
+<data> & VUR  \\
+social security number & 98.04\% \\
+a video of you unclothed & 97.44\% \\
+bank account information & 97.10\% \\
+recordings of your work conversations & 96.97\% \\
+an incriminating/embarrassing photo of you & 96.36\% \\
+a photo of you unclothed & 96.30\% \\
+credit card information & 95.92\% \\
+username and password for websites & 95.41\% \\
+a video of you entering in your PIN & 93.91\% \\
+recordings of your phone conversations & 93.88\% \\
+\end{tabular}
+\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
+\label{sharedtop10}
+\end{center}
+\end{table}
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  %\setcounter{enumi}{0}
-  \item social security number (98.04\%)
-  \item a video of you unclothed (97.44\%)
-  \item bank account information (97.10\%)
-  \item recordings of your work conversations (96.97\%)
-  \item a photo of you that is incriminating/embarrassing (96.36\%)
-  \item a photo of you unclothed (96.30\%)
-  \item credit card information (95.92\%)
-  \item username and password for websites (95.41\%)
-  \item a video of you entering in your PIN (93.91\%)
-  \item recordings of your phone conversations (93.88\%) \\[-.8cm]
-\end{enumerate}
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
+%starting from #63
+<data> &  VUR  \\
+bank account information & 90.91\% \\
+a video of you unclothed & 90.62\% \\
+social security number  & 88.68\% \\
+video of you entering your PIN & 88.57\% \\
+an incriminating/embarrassing photo of you & 78.05\% \\
+a photo of you unclothed & 77.78\% \\
+a video of you entering a passcode to a door & 75.00\% \\
+when and how much you have sex & 73.08\% \\
+an incriminating/embarrassing video of you & 71.88\% \\
+a random (inward-facing) photo of you at home & 66.67\% \\
+\end{tabular}
+\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
+\label{notsharedtop10}
+\end{center}
+\end{table}
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  \setcounter{enumi}{63}
-  \item your name (47.25\%)
-  \item when and how much you exercise (46.07\%)
-  \item when you were happy or having fun (38.10\%)
-  \item what television shows you watch (35.96\%)
-  \item when you are busy or interruptible (34.34\%)
-  \item your heart rate (32.28\%)
-  \item music from your device (31.87\%)
-  \item your age (29.67\%)
-  \item the language you speak (20.95\%)
-  \item your gender (16.81\%) \\[-.8cm]
-\end{enumerate}
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
+%starting from #63
+<data> &  VUR  \\
+your name & 47.25\% \\
+when and how much you exercise & 46.07\% \\
+when you were happy or having fun & 38.10\% \\
+what television shows you watch & 35.96\% \\
+when you are busy or interruptible & 34.34\% \\
+your heart rate & 32.28\% \\
+music from your device & 31.87\% \\
+your age & 29.67\% \\
+the language you speak & 20.95\% \\
+your gender & 16.81\% \\
+\end{tabular}
+\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
+\label{sharedbottom10}
+\end{center}
+\end{table}
 
-For not shared data (appserver only)  \\[-.8cm]
-
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  %\setcounter{enumi}{0}
-  \item bank account information (90.91\%)
-  \item a video of you unclothed (90.62\%)
-  \item social security number (88.68\%)
-  \item video of you entering your PIN (88.57\%)
-  \item a photo of you that is incriminating/embarrassing (78.05\%)
-  \item a photo of you unclothed (77.78\%)
-  \item a video of you entering a passcode to a door (75.00\%)
-  \item when and how much you have sex (73.08\%)
-  \item a video of you that is incriminating/embarrassing (71.88\%)
-  \item a photo of you at home taken randomly by an inward-facing camera (66.67\%)  \\[-.8cm]
-\end{enumerate}
-
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-  \setcounter{enumi}{63}
-  \item when and how much you exercise (16.67\%)
-  \item how much you use your phone (15.79\%)
-  \item your age (14.29\%)
-  \item how much you like the people you interact with (13.79\%)
-  \item when, what, and how much you ate (12.50\%)
-  \item which television shows you watch (11.43\%)
-  \item your gender (9.52\%)
-  \item your heart rate (9.09\%)
-  \item eye movement patterns (for eye tracking) (6.98\%)
-  \item the language you speak (2.50\%)\\[-.8cm]
-\end{enumerate}
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
+%starting from #63
+<data> &  VUR  \\
+when and how much you exercise & 16.67\% \\
+how much you use your phone & 15.79\% \\
+your age & 14.29\% \\
+how much you like the people you interact with & 13.79\% \\
+when, what, and how much you ate & 12.50\% \\
+which television shows you watch & 11.43\% \\
+your gender & 9.52\% \\
+your heart rate & 9.09\% \\
+eye movement patterns (for eye tracking) & 6.98\% \\
+the language you speak & 2.50\% \\
+\end{tabular}
+\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
+\label{notsharedbottom10}
+\end{center}
+\end{table}
 

### 2015-01-02 wearables_survey.tex
commiting changes only to the .text file.. oops sorry serge

@@
 \end{tabular}
-\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
+\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
 \label{recipient}
@@
 
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{ll}
   (cubetastic upset rate | smartphone upset rate)\\
@@
 Q5: (86.49\% | 91.82\%)\\ 
+\end{tabular}
+\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
+\label{deviceVUR}
+\end{center}
+\end{table}
 
-			Chi\^2	2-tail p	Sig?		n		effect size\\
-Between-All	2.814	0.1395	No		3589		0.001\\
-Between-Q1	2.500	0.1139	No		714		0.004\\
-Between-Q2	17.333	<0.0001	Yes		708		0.024\\
-Between-Q3	0.020	0.8886	No		699		0.000\\
-Between-Q4	1.426	0.2324	No		731		0.002\\
-Between-Q5	1.611		0.2043	No		710		0.002\\
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{llll}
+%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
+%All	2.814	0.1395	No		3589		0.001\\
+%Q1	2.500	0.1139	No		714		0.004\\
+%Q2	17.333	<0.0001	Yes		708		0.024\\
+%Q3	0.020	0.8886	No		699		0.000\\
+%Q4	1.426	0.2324	No		731		0.002\\
+%Q5	1.611		0.2043	No		710		0.002\\
+Question & Chi^2 &	2-tail P & Effect Size\\
+All & 2.814 & 0.1395 & 0.001\\
+Q1 & 2.500 & 0.1139 & 0.004\\
+Q2 & 17.333 & <0.0001 & 0.024\\
+Q3 & 0.020 & 0.8886 & 0.000\\
+Q4 & 1.426 & 0.2324 & 0.002\\
+Q5 & 1.611	 & 0.2043 & 0.002\\
+\end{tabular}
+\caption{Results of the effects of <device> type contributing to VUR.
+Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
+\label{betweendevice}
+\end{center}
+\end{table}
 
-			Chi\^2	2-tail p	Sig?	Odds ratio	Confidence	Odds range\\
-Within-All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
-Within-Q1		0		1		No	n/a	         n/a	                  n/a\\
-Within-Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
-Within-Q3		0		1		No	n/a	         n/a	                  n/a\\
-Within-Q4		0		1		No	0.5		95\%			0.008 to9.605\\
-Within-Q5		0		1		No	n/a	         n/a	                  n/a\\
+\begin{table}%[h]
+\begin{center}
+\begin{tabular}{llll}
+%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
+%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
+%Q1		0		1		No	n/a	         n/a	                  n/a\\
+%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
+%Q3		0		1		No	n/a	         n/a	                  n/a\\
+%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
+%Q5		0		1		No	n/a	         n/a	                  n/a\\
+Question & Chi^2 &	2-tail P & Effect Size \\
+All & 0.444  & 0.505 & 0.006\\
+Q1 & 0 & 1 & 0 \\
+Q2 & 0 & 1 & 0\\
+Q3 & 0 & 1 & 0\\
+Q4 & 0 & 1 & 0\\
+Q5 & 0 & 1 & 0\\
+\end{tabular}
+\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
+\label{withindevice}
+\end{center}
+\end{table}
 

### 2015-01-02 wearables_survey.tex

@@
 \subsection{Data Type}
-To determine the most concerning and least concerning data types, we consider the very upset rate (VUR) of various scenarios.
-To calculate these rates, we take the rate of responses where participants had indicated that they would be ``very upset'' (the maximum rating) with respect to the total number of responses for the question.
-Since people considered different things more or less sensitive with respect to the data recipient, we present the most and least concerning shared data along with the most and least concerning ``not shared'' data:
+INTRO HERE.
 
@@
 \begin{center}
-\begin{tabular}{ll}
+\begin{tabular}{| l | c |}
 
@@
 \begin{center}
-\begin{tabular}{ll}
+\begin{tabular}{| l | c |}
 %starting from #63
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{| c | c | c | c |}
 Recipients	& Chi^2 &	2-tail P &  Effect Size \\
@@
 \begin{center}
-\begin{tabular}{ll}
+\begin{tabular}{| l | c |}
 <data> & VUR  \\
@@
 \begin{center}
-\begin{tabular}{ll}
-  (cubetastic upset rate | smartphone upset rate)\\
-Q1: (14.81\% | 6.13\%)\\
-Q2: (44.11\% | 19.85\%)\\
-Q3: (87.09\% | 58.44\%)\\
-Q4: (52.77\% | 55.79\%)\\
-Q5: (86.49\% | 91.82\%)\\ 
+\begin{tabular}{| c | c | c |}
+ Question &  Wearable VUR & Smartphone VUR \\
+Q1 & 14.81\%  &  6.13\%\\
+Q2 & 44.11\%  &  19.85\%\\
+Q3 & 87.09\%  &  58.44\%\\
+Q4 & 52.77\%  & 55.79\%\\
+Q5 & 86.49\%  &  91.82\%\\ 
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{| c | c | c | c |}
 %Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{| c | c | c | c |}
 %Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\

### 2015-01-02 wearables_survey.tex

@@
 \documentclass{acm_proc_article-sp}
+
+\usepackage{url}
 
@@
 
-\begin{table}%[h]
+\begin{table}[t]
 \begin{center}
 \begin{tabular}{| c | c | c | c |}
-Recipients	& Chi^2 &	2-tail P &  Effect Size \\
+Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
 Work-App	& 564.318 & <0.0001 & 0.111\\
@@
 %Q5	1.611		0.2043	No		710		0.002\\
-Question & Chi^2 &	2-tail P & Effect Size\\
+Question & $\chi^2$ &	2-tail P & Effect Size\\
 All & 2.814 & 0.1395 & 0.001\\
@@
 %Q5		0		1		No	n/a	         n/a	                  n/a\\
-Question & Chi^2 &	2-tail P & Effect Size \\
+Question & $\chi^2$ &	2-tail P & Effect Size \\
 All & 0.444  & 0.505 & 0.006\\
@@
 
-Concern &  Responses &  Frequency &   \\
+Concern &  Responses &  Frequency   \\
 Privacy & 452 & 25.32\% \\

### 2015-01-02 wearables_survey.tex
took out within-subjects part of device analysis for results.

@@
 \usepackage{url}
+
+%%% still need to break urls
+
+%\usepackage{breakurl}
+%\usepackage[breaklinks]{hyperref}
 
@@
 
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{| c | c | c | c |}
-%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
-%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
-%Q1		0		1		No	n/a	         n/a	                  n/a\\
-%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
-%Q3		0		1		No	n/a	         n/a	                  n/a\\
-%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
-%Q5		0		1		No	n/a	         n/a	                  n/a\\
-Question & $\chi^2$ &	2-tail P & Effect Size \\
-All & 0.444  & 0.505 & 0.006\\
-Q1 & 0 & 1 & 0 \\
-Q2 & 0 & 1 & 0\\
-Q3 & 0 & 1 & 0\\
-Q4 & 0 & 1 & 0\\
-Q5 & 0 & 1 & 0\\
-\end{tabular}
-\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-\label{withindevice}
-\end{center}
-\end{table}
+Talk about results of between-subjects analysis here.
 
-For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
+%\begin{table}%[h]
+%\begin{center}
+%\begin{tabular}{| c | c | c | c |}
+%Question & $\chi^2$ &	2-tail P & Effect Size \\
+%All & 0.444  & 0.505 & 0.006\\
+%Q1 & 0 & 1 & 0 \\
+%Q2 & 0 & 1 & 0\\
+%Q3 & 0 & 1 & 0\\
+%Q4 & 0 & 1 & 0\\
+%Q5 & 0 & 1 & 0\\
+%\end{tabular}
+%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
+%\label{withindevice}
+%\end{center}
+%\end{table}
+
+there are too few instances where a participant got both, and therefore not enough data to really do analysis: Results of the effects of <device> type contributing to VUR.
+Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.
+
+%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
 Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
@@
 For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-Exact question details here, and statistical stuff. Conclude with whatever conclusion I happen to come to after performing the statistical analysis.
 

### 2015-01-02 wearables_survey.tex
Started rewroding Methodology

--- 2015-01-02 wearables_survey.tex
@@
 \section{Methodology}
-Our survey was conducted in multiple parts.
-The first section of the survey consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the Cubetastic3000 (done to prevent biases in answers from participants with respect to specific artifacts or companies).
-The next section of questions consisted of questions regarding individual and situational smartphone concerns, which were questions more familiar to our participant base and are used for calibrating results.
-The following section of the survey consisted of risk and benefit assessment of technologies, where participants were asked to consider general, multi-situational concerns regarding specific technologies.
-The final section of the survey consisted of demographics questions on basic information, privacy concerns, and wearable device ownership.
+Our survey consisted of multiple parts.
+The first section consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the ``Cubetastic3000.'' We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media).
+The next set of questions focused on individual and situational smartphone concerns.
+These questions focused on the same scenarios, but we substituted smartphones for wearable technologies in order to see whether participants familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
+The next section of the survey involved performing overall risk/benefit rankings of various wearable technologies relative to better understood technologies.
+Finally, we collected demographic information, which included general privacy attitudes and whether participants owned any wearable devices.
 Details on the question ordering, question formatting, and sample questions are discussed in the remainder of this section.
@@
 
-\begin{table}%[h]
+\begin{table}[t]
 \begin{center}

### 2015-01-03 wearables_survey.tex
Added keywords, wrote 1/3 related work sections.

@@
 % A category with the (minimum) three required fields
-\category{look it up}{keyword1}{keyword2}{keyword3}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
 
-\terms{term1} {term2} {term3}
+\terms{Human Factors}{Measurement}{Security}
 
@@
 \section{Related Work}
-In this section, we discuss related work which explores threats for smartphones and wearable devices, discusses emerging challenges related to ubiquitous computing, and studies user perceptions of threats and technologies.
+In this section, we discuss related work which discusses emerging challenges related to ubiquitous computing, explores threats for smartphones, and studies user perceptions of threats and technologies.
+
+\subsection{Ubiquitous Sensing}
+Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}.
+More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}.
+The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}.
+Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.
 
@@
 
-\subsection{Ubiquitous Computing}
-(REDO) As technology becomes more and more ubiquitous, more sensors will record more things about more people more of the time.
-There are an endless amount of unique situations which can negatively impact a person's privacy or security.
-There is a clear need to better communicate these risks to people (cite webcam paper and other papers here?), but there are too many things to warn people about.
-Therefore, we need to know what are the most threatening and also most relevant situations to inform the users about, since we can't bug them all the time about everything.
-
-We need to investigate the threat landscape and people's privacy concerns now, before wearables are widely adopted, or designed without these considerations in mind.
-So although our research is at at time when things are rapidly changing and most people don't have wearables, it is crucial to do the research now so we can prevent badness later.
+We are the first study of this kind! Wheee, say it explicitly.
 

### 2015-01-03 wearables_survey.tex
polished off the discussion section!

@@
 
-\subsection{Concerns for Smartphones and Wearables}
+\subsection{Smartphones and Wearables Concerns}
 (REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort.
@@
 
-\subsection{User Perception}
+\subsection{Risk Perception}
 (REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people.
@@
 \subsection{Future Research Directions}
-(REDO, ask David's/Serge's input for this section) Additional future work is encouraged in the area of studying privacy with respect to ubiquitous computing, since we proved it was the number one concern of the users of wearable devices.
-Clearly, this is a hard question which has been worked on for a long time but not yet fully addressed.
-Even this survey just barely touched on the various factors which can influence privacy perceptions and how upset people would be.
 
- Also, maybe some work with respect to security threats, and how feasible they might be, and some defenses against stopping wearables devices from getting sensitive information (like blocking text, detecting sensitive situations like the bathroom, etc.).
-Research which defends against false information, false positive commands, and just more safeguards against the new system for wearables, whatever that is, is also something to really look into.
-
- Work making sure that people are aware of what is going on, using indicators, not-too-transparent interfaces, and maybe being polite (recording rules follow social rules--think polite glass talk from Jaeyeon at MSR) are going to be valuable as wearables get more sophisticated but also more adopted by people.
-Think about it--put people in control of the technology, not technology shifting the social norms (our survey says that one of the top concerns of people were about how wearables will change social norms).
+Our survey shows that photos, videos, and textual information is generally considered to be very sensitive.
+Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
+We also show that users are significantly more willing to offer certain data if it will only be shared with the application; and additionally, that users consider privacy as their number-one concern.
+Research in effective sandboxing and other software protections, effective notifications, and usable indicators are encouraged at this time.
+Lastly, exploratory research investigating user-reported concerns, are relevant--especially the social impact of wearable devices, measurement of inaccuracy of sensor readings presented by wearables, and rate of accidental information sharing.
 
 \subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearable devices and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen}\cite{WearableStatNews}, so our study is reflective of the status quo.
+One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities.
+83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, so our study is reflective of the status quo.
 We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables.
@@
 
-The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
+%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
 For this reason, people were heavily primed for the open-ended question.
@@
 
-(REDO, Should I even say this?) I messed up that motorcycle question.
+%(REDO, Should I even say this?) I messed up that motorcycle question.
 I wish I actually had a calibration point for high risk high benefit for the Fischoff technology assessment questions.
@@
 
-BENEFIT prompt:
+Benefit prompt:
 

### 2015-01-03 wearables_survey.tex
finished the related work section!

@@
 \subsection{Smartphones and Wearables Concerns}
-(REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort.
-I will talk about how I model Adrienne's work in the next section, Survey, just give a nod to it here and go into it later.
-Since my results were that people care about privacy, security, health, and social change/social stigma, any phone studies which hint at any of those things will be good to put here.
-Be sure to go cite a fair number of them.
-Related work section is the part where it looks like I know stuff.
 
-Mention any studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod.
-Especially mention ones on privacy and perceptions, since I know those exist.
-I doubt there will be ones for social norm shifts/social stigma, or health concerns, but maybe I can at least include some security ones here too.
-Throughout mentioning all of these works, highlight how my study is different from previous studies.
-
-We are the first study of this kind! Wheee, say it explicitly.
+There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro} .
+However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user.
+Felt et.
+al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint.
+The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
+Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges.
+To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.
 
 \subsection{Risk Perception}
-(REDO) In this paper, we investigate one of the two important questions--what are the most relevant situations to people.
-We do this firstly because people are really bad at knowing the likelihood of something, especially a threat with respect to security or privacy, is going to happen (sources here).
-And while the most damaging situations should also be addressed, this is not yet possible since these technologies haven't been adopted and the damage hasn't happened, so we don't know yet.
-Additionally, since the number one concern that people had with these devices was privacy (can I say result here?
-I guess I already did in abstract), we need to know what people consider private, which is more nuanced and requires a user study like this survey.
 
-We also study risk.
-Mention Fischoff here.
-This is a very seminal paper in risk perception and it also studies how safe enough something has to be before people can accept something.
-I will talk about how I model my work in the next section, Survey, just give it a nod here and go into it later.
-Also mention at least a couple more works related to risk perception here to round it off.
+While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology.
+A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies.
+In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
 

### 2015-01-03 wearables_survey.tex
wrote abstract, conclusion, ethics, and acknowledgements sections.

@@
 \begin{abstract}
-(Okay, kind of intimidated with writing the abstract.
-My plan is to write intro/conclusion first and then condense it into here, while nodding off to the contributions that we made.) At the very least, I can say that we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices.
-Data type, data recipient, and device type all matter different amounts.
-All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies.
-Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma.
-Fantastic ending sentence here.
+There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint.
+These works generally focus on X and Y.
+However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user.
+We surveyed 2,250 users about 74 data types, 4 recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of a threat.
+We also asked participants to rate 20 new technologies, as well as asked for what they think is the most likely risk associated with wearables.
+Our ranking for concerns can be used to guide future research in wearables security, especially research regarding protecting sensitive data and effective notifications and indicators.
 \end{abstract}
@@
 
-There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro} .
+There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}.
 However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user.
@@
 \section{Conclusion}
-(REDO) END STRONG!
-Should I put this before the Discussion?
-Echo the introduction a little, remind the people of the takeaways in a way that highlights the contribution of this paper.
-Intro: ``we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices.
-Data type, data recipient, and device type all matter different amounts.
-All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies.
-Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma.
-Fantastic ending sentence here.''
 
-I can talk about the results a little bit more in depth because people have already supposedly read my whole paper now.
-Pull out the subtleties I couldn't have done in the introduction, and go into specific details, shooting out numbers and statistics.
-Then conclude the whole thing with an inspirational pitch on how there is much future work to be done in this area, how this area is exciting, and how I basically helped people see both of these things.
+We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
+Participants rated how upset they would be if 305 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
+We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
+An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
+We also state what users perceived as the most significant concerns with respect to wearable devices.
+We conclude by discussing future research directions in the wearables and user study space.
 
@@
 %ACKNOWLEDGMENTS are optional
+\section{Research Ethics} 
+We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
+Survey data was collected in an anonymous manner.
+Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
+
 \section{Acknowledgments}
-NSF funding, SCRUB, BLUES. Also any people who helped.
+The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
+Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
+Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
 

### 2015-01-03 wearables_survey.tex
Fixed URL wrapping in bibliography, edited Abstract.

@@
 
-\usepackage{url}
+\usepackage{color}
 
@@
 
-%\usepackage{breakurl}
-%\usepackage[breaklinks]{hyperref}
+\usepackage[hyphens]{url}
 
@@
 \begin{abstract}
-There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint.
-These works generally focus on X and Y.
-However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user.
-We surveyed 2,250 users about 74 data types, 4 recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of a threat.
-We also asked participants to rate 20 new technologies, as well as asked for what they think is the most likely risk associated with wearables.
-Our ranking for concerns can be used to guide future research in wearables security, especially research regarding protecting sensitive data and effective notifications and indicators.
+We performed an online survey to examine computer users' risk perceptions surrounding current and future wearable computing devices.
+We controlled for the different data types that might be captured, who might have access to that data, as well as whether it was captured on a wearable device or a smartphone (i.e., an existing device with which participants were already familiar).
+In the end, we surveyed 2,250 users about 74 data types, 4 data recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these threats.
+Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
+The results of this study can be used to guide future research in wearable device security, especially research that helps to protect sensitive data and guides the design of effective privacy notifications and indicators.
 \end{abstract}
@@
 \section{Introduction}
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing to healthier living through fitness tracking.
+Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
 Wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user.

### 2015-01-03 wearables_survey.tex
Edited Intro

@@
 
-\title{Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices}
+\title{A Survey Wearable Device Risk Perceptions}
 %\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
@@
 
-\numberofauthors{3}
-
+\numberofauthors{1}
 \author{
-% 1st. author
-\alignauthor
-Linda N. Lee\\
-       \affaddr{UC Berkeley}\\
-       \email{lnl@cs.berkeley.edu}
-% 2nd. author
-\alignauthor
-Serge Egelman\\
-       \affaddr{UC Berkeley}\\
-       \affaddr{ICSI}\\
-       \email{serge@cs.berkeley.edu}
-% 3rd. author
-\alignauthor David Wagner\\
-       \affaddr{UC Berkeley}\\
-       \email{daw@cs.berkeley.edu}
+ \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
+   \vspace{0.5em}
+   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}\\
+   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
 }
@@
 \begin{abstract}
-We performed an online survey to examine computer users' risk perceptions surrounding current and future wearable computing devices.
-We controlled for the different data types that might be captured, who might have access to that data, as well as whether it was captured on a wearable device or a smartphone (i.e., an existing device with which participants were already familiar).
-In the end, we surveyed 2,250 users about 74 data types, 4 data recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these threats.
+We performed an online survey to examine risk perceptions surrounding wearable computing devices.
+We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology).
+We surveyed 1,785 participants about 74 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
 Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
@@
 
-\terms{Human Factors}{Measurement}{Security}
+%\terms{Human Factors}{Measurement}{Security}
 
@@
 Wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user.
-Wearbles are gaining lots of attention.
-Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.
+Wearbles are gaining a lot of attention.
+Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one~\cite{NPD}.
 
-A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables found that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}.
-It is estimated that 20\% of the general population own at least one wearable and 10\% use at least one wearable in their daily lives \cite{WearableStatNews}.
+A survey of 3,956 respondents who are either current users or non-users with high interest in wearables found that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
+It is estimated that 20\% of the general population own at least one wearable and 10\% use at least one wearable in their daily lives~\cite{WearableStatNews}.
 The demographics of wearables consumers are young and affluent--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year.
-However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.
+However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop~\cite{cmo}.
 
-Even in early adoption, security and privacy concerns regarding wearable devices are becoming heightened.
-Many of these concerns relate to users' activities being exposed to the public without awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise\cite{Fitbit}, resulting in disclosing sensitive information about the user.
-In other instances, public discomfort prevented certain capabilities from being enabled.
-Google's Glass had to disable facial recognition for Glass upon release \cite{GlassDetection}.
+Despite early adoption, wearable device security and privacy concerns are prevalent.
+Many of these concerns relate to users' activities being exposed to the public without their awareness or consent.
+For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the disclosure of sensitive user information.
+In other instances, public discomfort prevented companies from enabling certain capabilities; Google's Glass had facial recognition disabled upon release~\cite{GlassDetection}.
 
-To avoid both scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand the threat landscape for wearable devices and which issues users most care about--before wearbles become increasingly more ubiquitous and powerful \cite{Implants}.
-A better understanding of the threat landscape will enable researchers and companies alike to focus on the most concerning factors for the user--allowing research for effective warnings of relevant events and an informed focus of protecting the data of high priority.
+To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand user concerns surrounding wearable devices---before wearables become increasingly ubiquitous and powerful~\cite{Implants}.
+A better understanding of users' risk perceptions will enable researchers and companies alike to focus on the most concerning factors for the user---allowing research for effective warnings of relevant events and an informed focus of protecting the most sensitive data.
 
-We surveyed 2,250 internet users to determine what data is sensitive, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-In this work, we contribute the following: \\[-0.8cm]
+To this end, we surveyed 1,785 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We show users' perceptions of a wide range of wearables threats, along with an evaluation of which factors contribute to the severity of a threat.
-We find that data type and data recipient matter, but the device type does not.
-\item We investigate how people's privacy preferences differ when data is perceived to be shared with people or a server.
-\item We show risk and benefit assessments of new technologies and capabilities relative to better understood technologies.
-Most are perceived as low-risk/low-benefit, but we hypothesize this is  the result of limited exposure.
-\item We report people's self-reported top concerns for wearable devices.
+\item We compare users' perceptions of a wide range of privacy and security risks surrounding wearable devices. In general, users care much more about the recipient of the data, than the type of data.
+\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
+\item While our participants viewed the data-collection capabilities of wearable devices as benign relative to more accepted technologies, we hypothesize that this is due to their lack of exposure to these newer technologies.
+%\item We report people's self-reported top concerns for wearable devices.
 Privacy, by far, is the top concern.

### 2015-01-03 wearables_survey.tex
Commented on Related Work

@@
 \section{Related Work}
-In this section, we discuss related work which discusses emerging challenges related to ubiquitous computing, explores threats for smartphones, and studies user perceptions of threats and technologies.
+In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
 
 \subsection{Ubiquitous Sensing}
-Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}.
+{\color{red} This is plagiarized from our CHI paper!
+REWRITE!!!
+} Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}.
 More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}.
@@
 \subsection{Smartphones and Wearables Concerns}
-
+{\color{red} Add way more details about Felt's study, so that it's clear how we borrowed the methodology, without the reader having to read that paper.}
 There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}.
@@
 
-\subsection{Risk Perception}
-
+\subsection{Technology Risk Perceptions}
+{\color{red} Again, you need to add lots more about this paper, so that it's clear from your description what they did, and how we build upon it.}
 While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology.

### 2015-01-03 wearables_survey.tex
Edited up to 3.1

@@
 
+{\color{red} You really need to cite ~\cite{Denning2014} in this section.}
+
+{\color{red} To make it flow, add 1-3 sentences here about the gaps in the related work, which then motivates our study (e.g., while people have looked at X, we are aware of no work that has looked at Y.
+Thus, we performed a survey to examine Y).}
+
 %%%%%%%%%%%%%%%%%%%
@@
 \section{Methodology}
-Our survey consisted of multiple parts.
-The first section consisted of questions regarding individual and situational concerns with respect to a fictitious wearable device called the ``Cubetastic3000.'' We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media).
-The next set of questions focused on individual and situational smartphone concerns.
-These questions focused on the same scenarios, but we substituted smartphones for wearable technologies in order to see whether participants familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
-The next section of the survey involved performing overall risk/benefit rankings of various wearable technologies relative to better understood technologies.
+Our survey consisted of multiple sections.
+In one section, we presented participants with scenarios surrounding a fictitious wearable device called the ``Cubetastic3000,'' and asked them to rate their level of concern for each scenario.
+We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media).
+In another section of the survey, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
+In another section of the survey, we asked participants to compute overall risk/benefit rankings of various wearable technologies relative to better understood technologies.
 Finally, we collected demographic information, which included general privacy attitudes and whether participants owned any wearable devices.
-Details on the question ordering, question formatting, and sample questions are discussed in the remainder of this section.
 
@@
 \item 2 risk/benefit questions 
-\item 15 demographics questions \\[-.8cm]
+\item 15 demographic questions \\[-.8cm]
 \end{itemize}
 
-To mitigate any biases, the order in which question groups appeared to the user, the ordering within each group, and, when applicable, the order of the answers for questions, were randomized for each user.
-Details with respect to the relevant section of the survey are discussed in the respective subsections below.
+We randomized the order in which participants completed each section of the survey, as well as the order of the questions within each sections.
 
 \subsection{Question Format} 
-We talk about the format and justification of the questions from our survey below.
+In this section, we present the details of each survey section.
 

### 2015-01-05 wearables_survey.tex
304 > 305; added in coding agreement statistics.

@@
 
-After participants answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000.
-Out of these 304 questions, 292 (73 <data> * 4 <recipient>) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+After participants answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 305 questions on various scenarios which can occur when wearing the Cubetastic3000.
+Out of these 305 questions, 292 (73 <data> * 4 <recipient>) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
 
@@
 Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers.
-Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+Two researchers independently coded 1,785 open-ended responses and had an initial agreement rate of 89.78\%.
+The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
 

### 2015-01-05 wearables_survey.tex
entered in demographics statistics in methodology: analysis section.
Edited up to Data Recipient

--- 2015-01-03 wearables_survey.tex
@@
 \usepackage[hyphens]{url}
+
+\def\etal{{\it et al.~}}
+
+\newenvironment{packed_enum}{
+\begin{enumerate}
+  \setlength{\itemsep}{1pt}
+  \setlength{\parskip}{0pt}
+  \setlength{\parsep}{0pt}
+}{\end{enumerate}}
+
+\newenvironment{packed_item}{
+\begin{itemize}
+  \setlength{\itemsep}{1pt}
+  \setlength{\parskip}{0pt}
+  \setlength{\parsep}{0pt}
+}{\end{itemize}}
 
@@
 Our survey consisted of multiple sections.
-In one section, we presented participants with scenarios surrounding a fictitious wearable device called the ``Cubetastic3000,'' and asked them to rate their level of concern for each scenario.
-We used this fictitious device as an example in order to minimize any biases that participants might have to specific devices or companies (e.g., visceral reactions to Google Glass based on stories they may have heard in the popular media).
+In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen.
 In another section of the survey, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
-In another section of the survey, we asked participants to compute overall risk/benefit rankings of various wearable technologies relative to better understood technologies.
-Finally, we collected demographic information, which included general privacy attitudes and whether participants owned any wearable devices.
+In another section of the survey, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies.
+Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
 
@@
 
-During the course of the survey, each participant answered 27 questions:   \\[-.8cm]
+\subsection{Question Format}
+In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions (attention checks)
-\item 6 questions about various wearables scenarios 
+\item 2 comprehension questions
+\item 6 questions about wearable computing scenarios 
 \item 2 questions about smartphone scenarios 
@@
 
-We randomized the order in which participants completed each section of the survey, as well as the order of the questions within each sections.
-
-\subsection{Question Format} 
-In this section, we present the details of each survey section.
+We randomized the order in which participants completed each section of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of the questions within each section.
 
 \subsubsection{Comprehension Questions}
-Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions.
-These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly.
-Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants.
+Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device.
+Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which would be the basis for all questions on wearable computing risks.
+We highlighted the capabilities of this device and described several use cases.
+To ensure that participants had read and understood this device's capabilities, we presented them with two comprehension questions.
 
@@
 
-After participants answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000.
-Out of these 304 questions, 292 (73 <data> * 4 <recipient>) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first.
+All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
+Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+We created an initial pool of 292 questions by combining 73 data types (<data>) with 4 data recipients (<recipient>).
+The 4 possible data recipients were:
 
-The main purposes of these questions were to, firstly, determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event or not and, secondly, to investigate what information would most upset users when shared.
-Additionally, there were 13 questions which did not follow the above format, lacking <data> to be shared and/or a <recipient>.
-The 13 exploratory questions were additional scenarios which did not fit the standard question format but were relevant to ask our participants.
-An example of a regular question, a calibration question, and exploratory question, respectively, are below:
+\begin{packed_item}
+\item Your work contacts
+\item Your friends
+\item The public
+\item The app's server (but didn't share it with anyone else)
+\end{packed_item}
 
-standard: \textit{How would you feel if an app on your Cubetastic3000 learned how you were feeling based on your heart rate and shared that with the public, without asking you first?}\\[-.5cm]
-
-exploratory: \textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}\\[-.5cm]
+The main purpose of these questions was to determine the extent to which the data type and data recipient played a role in upsetting participants when data is inappropriately shared.
+Additionally, we added 12 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we thought were relevant nonetheless.
+An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' Thus, there were a total of 304 questions in this set, from which we randomly presented each participant with 6 questions.
 
 \subsubsection{Smartphone Scenarios}
-Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone.
-Unlike the wearables scenario questions, these questions only ask about various situations which may occur using a smartphone, without a <data> or <recipient>.
-These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et.
-al's mobile user study \cite{Felt} for eliciting varying reactions from users.
+We presented participants with a second set of scenarios in order to control for the type of device being used.
+These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+We randomly presented participants with 2 of the following 5 questions:
 
-calibration: \textit{How would you feel if an app on your Cubetastic3000 connected to a Bluetooth device (like a headset) without asking you first?} \\[-.5cm]
-
-These questions were the basis for the five calibration wearables scenarios from the above section.
-Because we asked users questions differing only by the device in question, we are able to see how the change in device changes users' risk perception.
-Additionally, we compare our participants' perceptions of wearable device scenarios with existing perceptions of mobile device scenarios.
-Of the 13 exploratory questions in the wearables section, 5 of those questions were to calibrate with existing privacy work for smartphones and the other 7  were exploratory questions.
-These wearables questions, like the smart phone questions, were modeled after the mobile user study conducted by Felt et.
-al \cite{Felt}, but we ask the same questions but with respect to wearables rather than smart phones, to see if a change in device changes users' risk perception.
+\begin{packed_item}
+\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
+\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
+\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
+\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
+\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?}
+\end{packed_item}
 
@@
 
-In addition to investigating personal reactions to particular scenarios, we also wanted to study broad perceptions of various new technologies.We asked participants to evaluate the of following 20 new technologies: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice based emotion detection, location tracking, speech to text, language detection, heart rate detection, age detection, and gender detection.
+In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies, and how those perceptions compared to other well-established technologies.
+To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to relatively rank several technologies by both their risk and benefit to society.
+We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
+We chose these technologies because they represented varying levels of risks and benefits.
 
-For risk and benefit assessment, a technology was randomly selected for each participant, then risk and benefit questions for the same technology were selected for the participant.
-Each participant saw 1 risk assessment question and 1 benefit assessment question, in a randomized order.
-These questions ask about four previously studied technologies from the the seminal risk perception study by Fischhoff \cite{Fischhoff} (handguns, motorcycles, lawnmowers, and electricity), and 1 of the 20 new technologies.
-Participants were asked to rate the same randomized new technology for both risk and benefit assessment.
-The format of the questions were as follows:
+Alongside the 4 well-established technologies, we asked participants to evaluate one of 20 possible technologies relevant to wearable computing: the Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
+Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
 
-\textit{Fill in your risk/benefit numbers for the following technologies:}\\[-.5cm]
+To parallel Fischhoff \etal's risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
+We randomized whether they performed the ranking for risks or benefits first.
+The prompt is listed in Appendix \ref{sec:prompt}.
+The question format was as follows:
+
+\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
 
@@
 
-To parallel the risk perception study, we gave our participants a similar prompt which instructed them to numerically express the conceived gross risk/gross benefit for a long period of time for all parties involved.
-The prompt can be seen in appendix \ref{sec:prompt}.
-
 \subsubsection{Additional Questions}
-The exit portion of the survey consisted of demographics questions to better understand the answers.
-We included standard demographics questions such as age, gender, and education, but also asked participants if they owned a wearable device to survey the population's exposure to these devices.
-We also prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences.
-We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}.
+The exit portion of the survey consisted of standard demographics questions such as age, gender, and education.
+We also asked participants if they owned a wearable device so that we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
+Finally, we included the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so that we could control for participants' general privacy attitudes.
 
 \subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge survey comprehension, and measure user fatigue.
+We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
 The focus group began with participants taking the survey.
-Afterward, the participants were asked to give feedback on the format and the content of the survey, noting any instructions or questions which were unclear and stating any suggestions for the content of the survey.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, to brainstorm any additional scenarios which may occur.
-Afterward, participants were debriefed and given \$30 in cash.
-All of our participants were recruited locally through Craigslist.
-Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
+Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
+The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
+Finally, we compensated participants with \$30 in cash.
+We recruited all of our focus group participants from Craigslist.
+Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
 Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
 
-\subsection{Recruitment}
+\subsection{Recruitment and Analysis Method}
 We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18 years old and living in the United States.
-No other restrictions on participation were applied.
+We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above.
+Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
+We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,785.
 
-\subsection{Analysis}
-After removing 465 incomplete responses, our sample consisted of 1,785 participants.
-Of these X, A\% were male, with a median age of B.
-For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale.
-The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced.
-Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission.
-Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were.
-Although participants gave a wide range of numbers (i.e.
-a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis.
-Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers.
-Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than than the average of all Likert scores.
+We did this for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
+Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
+Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is if they were maximally upset or not, rather than how upset they were.
+In the risk/benefit section, followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+Rather, we report medians and quartiles, which are not heavily impacted by outliers.
+Finally, for the open-ended question at the end, two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
 
@@
 In this section, we present the results of our multiple-part survey.
-We first discuss which <data>, <recipient>, and <device> types contributed to how threatening a situation was perceived by a participant.
-We follow this discussion with a regression model which discusses all of the factors which may have contributed to a participant being very upset at a given situation, including <data>, <recipient>, and <device> types, but also with respect to demographics questions.
-Next, we discuss the participants' risk/benefit assessment of various new technologies with respect to well-known, existing technologies.
-We conclude the section with participants self-reported concerns about the biggest risks in owning a wearable device.
+We first discuss participants responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived by participants.
+Next, we discuss participants' risk/benefit assessment of various new technologies with respect to well-established technologies.
+We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
 
-\subsection{Data Type}
-INTRO HERE.
+\subsection{Concern Factors}
 
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
+In this section, we discuss the factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable device or a smartphone.
+We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of these factors, including demographic traits.
 
-<data> &  VUR  \\
-a video of you unclothed & 95.97\% \\
-bank account information & 95.91\% \\
-social security number & 94.84\% \\
-video of you entering in your PIN & 92.67\% \\
-a photo of you unclothed & 92.59\% \\
-an incriminating/embarrassing photo of you & 91.39\% \\
-username and password for websites & 89.55\% \\
-credit card information & 88.98\% \\
-an incriminating/embarrassing video of you & 88.41\% \\
-a random (inward-facing) photo you at home & 87.50\% \\
+\subsubsection{Data Recipient}
+Based on our data, we observed that the largest effect seemed to stem from who the recipient of the data was: across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.4\%), work contacts (75.1\%), and the public (72.4\%) were much higher.
+A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
+However, these effect sizes were relatively small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
 
-\end{tabular}
-\caption{A table of the top 10 upsetting <data> types, irregardless of recipient or data type.}
-\label{top10}
-\end{center}
-\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
-%starting from #63
-<data> &  VUR  \\
-eye movement patterns (for eye tracking) & 40.51\% \\
-when and how much you exercise  & 38.66\% \\
-when you are happy or having fun  & 34.51\% \\
-which television shows you watch & 30.20\% \\
-when you are busy or interruptible  & 29.50\% \\
-music from your device  & 28.06\% \\
-your heart rate & 27.50\% \\
-your age & 24.29\% \\
-the language you speak & 15.86\% \\
-your gender & 14.91\% \\
-
-\end{tabular}
-\caption{A table of the bottom 10 upsetting <data> types, irregardless of recipient or data type.}
-\label{bottom10}
-\end{center}
-\end{table}
-
-TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why.
-A statistical analysis with respect to all 74 <data> is not feasible to explore within this paper.
-However, we consider these data types in our regression model.
-
-\subsection{Data Recipient}
-People are upset when their data is shared without their permission, regardless of who the recipient is.
-Generally, there isn't a statistically significant difference between how upset people would be if data were to be shared with friends, work, and public, although when considering each scenario, there are certain scenarios which are considered to be more sensitive with one recipient than another.
+%SE: Edited up to here.
+%Comment on independence of observations, differences between public/work, and end the subsection
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{recipient.png}
-	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
-\end{figure}
+%SE: This doesn't add much, the numbers can be put in the text to save space.
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{recipient.png}
+%	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
+%\end{figure}
 
-%\begin{table}%[h]
+\begin{table}[t]
+\begin{center}
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
+\hline
+Work-App	& 564.32 & <0.0001 & 5,085 & 0.111\\
+Public-App	& 479.98 & <0.0001 & 5,192 & 0.092\\
+Friends-App & 380.00 & <0.0001 & 5,098 & 0.075\\
+Friends-Work & 20.37 & <0.0001 & 5,039 & 0.004\\
+Friends-Public & 5.35 & <0.0207 & 5,146 & 0.001\\
+Work-Public&  5.05 & <0.0246 & 5,133	& 0.001\\
+\hline
+\end{tabular}
+\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
+\label{recipient}
+\end{center}
+\end{table}
+
+%\begin{table}[t]
 %\begin{center}
-%\begin{tabular}{llllll}
-%Recipients	& Chi^2 &	2-tail P & 	Sig?	& n & Effect Size \\
-%Work-App	& 564.318 & <0.0001 & Yes	& 5085 & 0.111\\
-%Public-App	& 479.980 & <0.0001 & Yes	& 5192 & 0.092\\
-%Friends-App & 380.000 & <0.0001 & Yes & 5098 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 & Yes & 5039 & 0.004\\
-%Friends-Public & 5.349 & 0.0207 & No	& 5146 & 0.001\\
-%Work-Public&  5.054 & 0.0246 & No & 5133	& 0.001\\
+%\begin{tabular}{|l|r|r|r|r|}
+%\hline
+%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
+%\hline
+%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
+%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
+%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
+%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
+%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
+%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
+%\hline
 %\end{tabular}
-%\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
+%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
 %\label{recipient}
@@
 
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | c | c | c |}
-Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-Work-App	& 564.318 & <0.0001 & 0.111\\
-Public-App	& 479.980 & <0.0001 &  0.092\\
-Friends-App & 380.000 & <0.0001 & 0.075\\
-Friends-Work & 20.365 & <0.0001 &  0.004\\
-Friends-Public & 5.349 & 0.0207 &  0.001\\
-Work-Public&  5.054 & 0.0246 &  0.001\\
-\end{tabular}
-\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%Friends-Work	0.867	0.3517	No		604		0.001\\
-%Friends-Public	1.460	0.2229	No		639		0.002\\
-%Friends-App	32.066	<0.0001	Yes		609		0.053\\
-%Work-Public	0.670	0.7956	No		631		0.001\\
-%Work-App	42.492	<0.0001	Yes		601		0.071\\
-%Public-App	48.520	<0.0001	Yes		636		0.076\\
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{| c | c | c | c |}
+%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
+%Work-App	& 564.318 & <0.0001 & 0.111\\
+%Public-App	& 479.980 & <0.0001 &  0.092\\
+%Friends-App & 380.000 & <0.0001 & 0.075\\
+%Friends-Work & 20.365 & <0.0001 &  0.004\\
+%Friends-Public & 5.349 & 0.0207 &  0.001\\
+%Work-Public&  5.054 & 0.0246 &  0.001\\
+%\end{tabular}
+%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
+%\label{recipient}
+%\end{center}
+%\end{table}
 
@@
 
-\subsection{Device Type}
+\subsubsection{Data Type}
+INTRO HERE.
+
+\begin{table}[t]
+\begin{center}
+\begin{tabular}{| l | c |}
+
+<data> &  VUR  \\
+a video of you unclothed & 95.97\% \\
+bank account information & 95.91\% \\
+social security number & 94.84\% \\
+video of you entering in your PIN & 92.67\% \\
+a photo of you unclothed & 92.59\% \\
+an incriminating/embarrassing photo of you & 91.39\% \\
+username and password for websites & 89.55\% \\
+credit card information & 88.98\% \\
+an incriminating/embarrassing video of you & 88.41\% \\
+a random (inward-facing) photo you at home & 87.50\% \\
+
+\end{tabular}
+\caption{A table of the top 10 upsetting <data> types, irregardless of recipient or data type.}
+\label{top10}
+\end{center}
+\end{table}
+
+\begin{table}[t]
+\begin{center}
+\begin{tabular}{| l | c |}
+%starting from #63
+<data> &  VUR  \\
+eye movement patterns (for eye tracking) & 40.51\% \\
+when and how much you exercise  & 38.66\% \\
+when you are happy or having fun  & 34.51\% \\
+which television shows you watch & 30.20\% \\
+when you are busy or interruptible  & 29.50\% \\
+music from your device  & 28.06\% \\
+your heart rate & 27.50\% \\
+your age & 24.29\% \\
+the language you speak & 15.86\% \\
+your gender & 14.91\% \\
+
+\end{tabular}
+\caption{A table of the bottom 10 upsetting <data> types, irregardless of recipient or data type.}
+\label{bottom10}
+\end{center}
+\end{table}
+
+TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why.
+A statistical analysis with respect to all 74 <data> is not feasible to explore within this paper.
+However, we consider these data types in our regression model.
+
+\subsubsection{Device Type}
 
@@
 
-\subsection{Regression Model} 
+\subsubsection{Regression Model} 
 Introduce the model and what was considered in the model.
@@
 
-\subsection{Risk and Benefit Ranks} 
+\subsection{Risk and Benefit Rankings} 
 When assessing new technologies, participants generally had rated the technologies similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).
@@
 %Appendix A
-\section{Fischoff Prompts}
+\section{Fischhoff Prompts}
 \label{sec:prompt}
 
-Benefit prompt:
+\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
 
-``We would like to ask you to rate the benefits associated with each of the following technologies.  \\[-.6cm]
+{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
+(e.g.
+for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
 
-Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.
-\\[-.6cm]
-
-Do not consider the costs or risks associated with these items.
+\textit{Do not consider the costs or risks associated with these items.
 It is true, for example, that sometimes swimmers can drown.
 But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.
-\\[-.6cm]
+Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
 
-Please rate the following technologies below with a number.
+\textit{Please rate the following technologies below with a number.
+We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
+Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
+(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
+
+{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
+(e.g.
+for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
+
+\textit{Do not consider the costs or benefits associated with these items.
+It is true, for example, that electricity also creates a market for home appliances.
+But evaluating such benefits is not your present job.
+Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
+
+\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
 Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17)''
+(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
 
-RISK prompt:
+%\section{Risk and Benefit Rankings}
+%\label{sec:techrank}
+%
+%BENEFIT: 
+%
+%technology 	median	25\%		75\% \\
+%electricity	87	50	100\\
+%internet	65	45	100\\
+%laptops	60	40	80\\
+%email	50	30	75\\
+%smartphones	50	32.5	75\\
+%location tracking	40	20	67.5\\
+%heart rate detection	40	28	62.5\\
+%language detection	35	15	60\\
+%voice recognition	25	15	40\\
+%speech to text	25	15	36.25\\
+%lawnmowers	24	15	40\\
+%facial recognition	22	13	40\\
+%guns	20	10	30\\
+%motrocycles	20	12	40\\
+%voice based emotion detection	20	10	30\\
+%facial detection	20	10	32\\
+%discrete camera	20	15	30\\
+%smartwatches	20	10	32.5\\
+%google glass	20	12	40\\
+%fitness trackers	19	10	30\\
+%cubetastic	18	10	30\\
+%discrete microphone	15	10	20\\
+%age detection	12	10	21\\
+%gender detection	10	10	15
+%
+%RISK: 
+%
+%technology 	median	25\%		75\%\\
+%guns	60	40	80\\
+%motrocycles	45	27	70\\
+%electricity	25	15	40\\
+%lawnmowers	20	12	30\\
+%facial recognition	17	12.5	30\\
+%internet	15	10	30\\
+%discrete camera	12	10	30\\
+%location tracking	10	10	20\\
+%age detection	10	10	15\\
+%gender detection	10	10	12\\
+%language detection	10	10	10\\
+%voice based emotion detection	10	10	15\\
+%facial detection	10	10	25\\
+%voice recognition	10	10	15\\
+%heart rate detection	10	10	10\\
+%email	10	10	16\\
+%speech to text	10	10	10\\
+%discrete microphone	10	10	20\\
+%smartphones	10	10	19\\
+%laptops	10	10	15\\
+%fitness trackers	10	10	10\\
+%smartwatches	10	10	10\\
+%google glass	10	10	20\\
+%cubetastic	10	10	30
 
-``We would like to ask you to rate the risks associated with each of the following technologies. \\[-.6cm]
-
-Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.
-\\[-.6cm]
-
-Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.\\[-.6cm]
-
-Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)''
-
-\section{Risk and Benefit Rankings}
-\label{sec:techrank}
-
-BENEFIT:
-
-technology 	median	25\%		75\% \\
-electricity	87	50	100\\
-internet	65	45	100\\
-laptops	60	40	80\\
-email	50	30	75\\
-smartphones	50	32.5	75\\
-location tracking	40	20	67.5\\
-heart rate detection	40	28	62.5\\
-language detection	35	15	60\\
-voice recognition	25	15	40\\
-speech to text	25	15	36.25\\
-lawnmowers	24	15	40\\
-facial recognition	22	13	40\\
-guns	20	10	30\\
-motrocycles	20	12	40\\
-voice based emotion detection	20	10	30\\
-facial detection	20	10	32\\
-discrete camera	20	15	30\\
-smartwatches	20	10	32.5\\
-google glass	20	12	40\\
-fitness trackers	19	10	30\\
-cubetastic	18	10	30\\
-discrete microphone	15	10	20\\
-age detection	12	10	21\\
-gender detection	10	10	15
-
-RISK:
-
-technology 	median	25\%		75\%\\
-guns	60	40	80\\
-motrocycles	45	27	70\\
-electricity	25	15	40\\
-lawnmowers	20	12	30\\
-facial recognition	17	12.5	30\\
-internet	15	10	30\\
-discrete camera	12	10	30\\
-location tracking	10	10	20\\
-age detection	10	10	15\\
-gender detection	10	10	12\\
-language detection	10	10	10\\
-voice based emotion detection	10	10	15\\
-facial detection	10	10	25\\
-voice recognition	10	10	15\\
-heart rate detection	10	10	10\\
-email	10	10	16\\
-speech to text	10	10	10\\
-discrete microphone	10	10	20\\
-smartphones	10	10	19\\
-laptops	10	10	15\\
-fitness trackers	10	10	10\\
-smartwatches	10	10	10\\
-google glass	10	10	20\\
-cubetastic	10	10	30
-
-\section{Coding Label Definitions}
-\label{sec:coding}
-
-Privacy: ``privacy,'' revealing personal information, spying. \\
-Security:  ``security,'' compromise, malware, hacking. \\
-GPS tracking: ``location,'' ``GPS,'' being monitored.
-
-Unaware use: using data without permission or in a different way than understood by user. \\
-Unaware collection: collecting data without permission. \\
-Unaware access: disclosure of data without permission. \\
-False information: inaccurate or maliciously false data.
-
-Health Risk: radiation, cancer, or long-term effects.\\
-Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-Discomfort: eye strain, headache, obscured vision, irritation. \\
-Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-Theft: the device getting stolen.
-
-Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-Social Stigma: judgment, hate, or bystander discomfort.\\ 
-Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky.
-
-Miscellaneous: odd comments, uncommon concerns. \\
-None: ``None,'' no threat, perceiving no big concerns \\
-Don't know: ``do not know,'' hinting at confusion \\
-Don't care: `` do not care,'' nonchalant answers
+%\section{Coding Label Definitions}
+%\label{sec:coding}
+%
+%Privacy: ``privacy,'' revealing personal information, spying. \\
+%Security:  ``security,'' compromise, malware, hacking. \\
+%GPS tracking: ``location,'' ``GPS,'' being monitored. 
+%
+%Unaware use: using data without permission or in a different way than understood by user. \\
+%Unaware collection: collecting data without permission. \\
+%Unaware access: disclosure of data without permission. \\
+%False information: inaccurate or maliciously false data.
+%
+%Health Risk: radiation, cancer, or long-term effects.\\
+%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
+%Discomfort: eye strain, headache, obscured vision, irritation. \\
+%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
+%Theft: the device getting stolen. 
+%
+%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
+%Social Stigma: judgment, hate, or bystander discomfort.\\ 
+%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
+%
+%Miscellaneous: odd comments, uncommon concerns. \\
+%None: ``None,'' no threat, perceiving no big concerns \\
+%Don't know: ``do not know,'' hinting at confusion \\
+%Don't care: `` do not care,'' nonchalant answers
 

### 2015-01-05 wearables_survey.tex

@@
 The main purpose of these questions was to determine the extent to which the data type and data recipient played a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 12 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we thought were relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' Thus, there were a total of 304 questions in this set, from which we randomly presented each participant with 6 questions.
+Additionally, we added 13 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we thought were relevant nonetheless.
+An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' Thus, there were a total of 305 questions in this set, from which we randomly presented each participant with 6 questions.
 
@@
 We presented participants with a second set of scenarios in order to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 305 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
 We randomly presented participants with 2 of the following 5 questions:
@@
 We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,785.
+Of these, 57.87\% were male, with a median age of 29 ($\sigma$ = 10.37).
 
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than than the average of all Likert scores.
+In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than the average of all Likert scores.
 We did this for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
@@
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end, two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+Finally, for the open-ended question at the end, two researchers independently coded 1,785 responses and had an initial agreement rate of 89.78\%.
+The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
 

### 2015-01-05 wearables_survey.tex
Redid Related Work: smartphones, risk perceptions.

--- 2015-01-05 wearables_survey.tex
@@
 \subsection{Smartphones and Wearables Concerns}
-{\color{red} Add way more details about Felt's study, so that it's clear how we borrowed the methodology, without the reader having to read that paper.}
 There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}.
-However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user.
+However, works like these are not grounded in user research and do not make claims about what the the most relevant concerns for the average user are.
 Felt et.
-al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint.
+al's study of smartphone user concerns \cite{Felt} was the first to investigate the smartphone security and privacy landscape from a user study standpoint.
 The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
+Participants were asked how upset they would be if a certain action had occurred without their permission.
+Participants rated each situation on a likert scale ranging from indifferent (1) to very upset (5).
 Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges.
-To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.
+We use a similar scale to ask our users how upset they would be if a certain action was taken without their permission, but ask questions about new capabilities on wearable devices.
+To our knowledge, our work is the first of its kind to investigate such user concerns.
 
 \subsection{Technology Risk Perceptions}
-{\color{red} Again, you need to add lots more about this paper, so that it's clear from your description what they did, and how we build upon it.}
 While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology.
 A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies.
-In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
-
-{\color{red} You really need to cite ~\cite{Denning2014} in this section.}
-
-{\color{red} To make it flow, add 1-3 sentences here about the gaps in the related work, which then motivates our study (e.g., while people have looked at X, we are aware of no work that has looked at Y.
-Thus, we performed a survey to examine Y).}
+In the study, participants were prompted to rate the risks and benefits of 30 activities and technologies for all people affected by the technology, for a long period of time.
+The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e.
+a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
+In our survey, we use a similar prompt to ask participants to rate the risks and benefits of 20 new technologies.
+Denning et.
+al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
+Bystanders expressed concerns due to the subtle, easy-to-use, and prevalent nature of wearables.
+While people have conducted studies on privacy concerns with respect to wearables, we are aware of no work which as looked at privacy perspectives of the owner of the device.
+In our survey, we show how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
 
@@
 After removing 465 incomplete responses, our sample consisted of 1,785 participants.
-Of these X, A\% were male, with a median age of B.
+Of these X, 57.87\% were male, with a median age of 29 (sigma = 10.37).
 For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale.

### 2015-01-05 wearables_survey.tex
redid all of related work now. looks much better. `

@@
 \subsection{Ubiquitous Sensing}
-{\color{red} This is plagiarized from our CHI paper!
-REWRITE!!!
-} Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}.
-More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}.
-The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}.
-Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.
+At an unprecedented rate, we are moving towards automated capture and ubiquitous access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables.
+Wearbles have new capabilities which allow capture of unique data about the user and his/her surroundings.
+As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security concerns ~\cite{palen2003unpacking}.
+Privacy in ubiquitous systems can be achieved my adhering to principles such as notice, choice, and consent ~\cite{langheinrich2001privacy}.
 

### 2015-01-05 wearables_survey.tex
wrote data type section.

@@
 
-\subsection{Question Format}
+\subsection{Survey Questions}
 In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
@@
 
+Friends 69.43\%, Work 74.12\%, Public 72.36\%, AppOnly 42.3\%
+
 %SE: This doesn't add much, the numbers can be put in the text to save space.
+%LL: Agreed.
+
 %\begin{figure}
@@
 \subsubsection{Data Type}
-INTRO HERE.
+Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}.
+Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information.
+Information which can be used to impersonate the user (i.e.
+username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data.
 
@@
 
-TALK ABOUT WHAT WAS SENSITIVE AND WHAT WAS NOT, and generally why.
-A statistical analysis with respect to all 74 <data> is not feasible to explore within this paper.
-However, we consider these data types in our regression model.
+A statistical analysis regarding the significance and confidence of <data> types with respect to all 74 was not performed due to the space constraints of the paper.
+We do consider all <data> in our regression model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
 

### 2015-01-05 wearables_survey.tex
wrote the device type section.

@@
 \subsubsection{Data Type}
-Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}.
 Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information.
@@
 username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data.
+Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}.
+{\color{red} should I say anything about the full list of 74 data types?}
 
@@
 \subsubsection{Device Type}
-
-(REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not.
-In either case, this matters the least, and device type and data recipient are more influencing factors.
-This is just the result of biases in people we can't quite quantify.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{device-type.png}
-	\caption{(This is a placeholder! TODO: generate a better version of this)}
-\end{figure}
+Participants had unique VUR rates for situations only differing in the device.
+Our participants had a 70.23\% VUR when asked about wearables devices and 40.62\% VUR when asked about smartphones.The VUR rates for both devices for all 5 quesions are in table ~\ref{deviceVUR}.
+However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
+Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
+The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
+There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.
 
@@
  Question &  Wearable VUR & Smartphone VUR \\
+ All & 70.23\% & 40.62\%\\
 Q1 & 14.81\%  &  6.13\%\\
@@
 
-Talk about results of between-subjects analysis here.
-
 %\begin{table}%[h]
@@
 
-there are too few instances where a participant got both, and therefore not enough data to really do analysis: Results of the effects of <device> type contributing to VUR.
-Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.
-
 %For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
@@
 
-%I didn't do the correlation yet
-(EXAMPLE) We found that the very upset rate for participants was not correlated with (pick correct ones from IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), positively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), and negatively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients).
-
-Because wearable devices have been adopted by a younger, rich, technology-savvy demographic  \cite{cmo}, it is natural to see that younger or more educated participants have had a more favorable view of wearable devices.
-This may be due to cultural exposure through marketing or friends, or an attitude of openness to new technologies.
-Participants who had a higher IUIPC score, which infers a higher sensitivity to privacy, were more likely to be upset at the various scenarios which may occur when wearing a wearable device.
-Additionally, these people were more likely to be adverse to these technologies for the sake of preserving privacy, whether they had explicit concerns or a vague feeling of uneasiness.
-There was no correlation between a person's gender and their views of wearable devices, reaffirming that wearable devices are equally exposed to both genders.
-
 \subsection{Risk and Benefit Rankings} 
@@
 
-%should I just put the list in here, in the main part of the paper?
+{\color{red} can you redo the graph for figure ~\ref{fig:techplot}? I trust your judgement on how it should look and what to emphasize.}
 

### 2015-01-05 wearables_survey.tex
Minor edits in beginning of analysis

--- 2015-01-05 wearables_survey.tex
@@
 \subsection{Ubiquitous Sensing}
-At an unprecedented rate, we are moving towards automated capture and ubiquitous access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables.
-Wearbles have new capabilities which allow capture of unique data about the user and his/her surroundings.
-As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security concerns ~\cite{palen2003unpacking}.
-Privacy in ubiquitous systems can be achieved my adhering to principles such as notice, choice, and consent ~\cite{langheinrich2001privacy}.
+{\color{red} This is plagiarized from our CHI paper!
+REWRITE!!!
+} Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}.
+More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}.
+The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}.
+Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.
 
 \subsection{Smartphones and Wearables Concerns}
+{\color{red} Add way more details about Felt's study, so that it's clear how we borrowed the methodology, without the reader having to read that paper.}
 There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}.
-However, works like these are not grounded in user research and do not make claims about what the the most relevant concerns for the average user are.
+However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user.
 Felt et.
-al's study of smartphone user concerns \cite{Felt} was the first to investigate the smartphone security and privacy landscape from a user study standpoint.
+al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint.
 The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
-Participants were asked how upset they would be if a certain action had occurred without their permission.
-Participants rated each situation on a likert scale ranging from indifferent (1) to very upset (5).
 Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges.
-We use a similar scale to ask our users how upset they would be if a certain action was taken without their permission, but ask questions about new capabilities on wearable devices.
-To our knowledge, our work is the first of its kind to investigate such user concerns.
+To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.
 
 \subsection{Technology Risk Perceptions}
+{\color{red} Again, you need to add lots more about this paper, so that it's clear from your description what they did, and how we build upon it.}
 While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology.
 A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies.
-In the study, participants were prompted to rate the risks and benefits of 30 activities and technologies for all people affected by the technology, for a long period of time.
-The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e.
-a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
-In our survey, we use a similar prompt to ask participants to rate the risks and benefits of 20 new technologies.
-Denning et.
-al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
-Bystanders expressed concerns due to the subtle, easy-to-use, and prevalent nature of wearables.
-While people have conducted studies on privacy concerns with respect to wearables, we are aware of no work which as looked at privacy perspectives of the owner of the device.
-In our survey, we show how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
+In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
+
+{\color{red} You really need to cite ~\cite{Denning2014} in this section.}
+
+{\color{red} To make it flow, add 1-3 sentences here about the gaps in the related work, which then motivates our study (e.g., while people have looked at X, we are aware of no work that has looked at Y.
+Thus, we performed a survey to examine Y).}
 
@@
 
+%SE: Are the above numbers correct? Also, can you add a range of ages?
+
 In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than the average of all Likert scores.
@@
 Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is if they were maximally upset or not, rather than how upset they were.
-In the risk/benefit section, followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end, two researchers independently coded 1,785 responses and had an initial agreement rate of 89.78\%.
+Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.8\%.
 The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
@@
 
-In this section, we present the results of our multiple-part survey.
-We first discuss participants responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived by participants.
-Next, we discuss participants' risk/benefit assessment of various new technologies with respect to well-established technologies.
+In this section, we present our survey results.
+We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
+Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
 We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.

### 2015-01-05 wearables_survey.tex
finished results.

--- 2015-01-05 wearables_survey.tex
@@
 
-Out of all the recipients, friends are considered to be the least upsetting audience, but not too significantly (do stats-y thing here).
-There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+{\color{red} can you comment on the independence, since you have the csv?
+it would be a pain for me to do find out how many people got the same situational questions which only differ by recipient.
+:(} There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
 
-Friends 69.43\%, Work 74.12\%, Public 72.36\%, AppOnly 42.3\%
+Participants had different sensitivities depending on if they perceived that their data would be shared with an application or a person.
+We found the top and bottom ten concerns with respect to a non-human audience (app's servers) versus a human audience (friends, work contacts, and public).
+Participants were more uncomfortable about privacy and theft (i.e.
+frequency of sex, photos at home, and passcodes to doors).
+when sharing data with an application.
+They were also more uncomfortable sharing phone or text conversations and credentials (i.e.
+username and password for websites, credit card information) to a human audience than to a server.
+Additionally, they concerned more concerned On the other hand, participants were comfortable sharing behavioral patterns and personal opinions (i.e.
+phone use, opinions of people, eye patterns, and food eaten) with an app's server rather than a human audience.
+For a human audience, participants were most comfortable sharing data which would come up in conversation (i.e music on their device, if one was having fun, and if one if busy or interruptible), but found these topics more disturbing to share with an app's server.
+{\color{red} should we creatively include stats for these in the appendix, in a space-conscious way?}.
 
@@
 %\end{figure}
+
+% LL: I thought this would be better, but then it looked stupid, so I commented it out.
+
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{|l|c|}
+%\hline
+%Recipients	& VUR \\
+%\hline
+%App	& 42.3\% \\
+%Friends & 69.4\% \\
+%Work & 75.1\% \\
+%Public & 72.4\% \\
+%\hline
+%\end{tabular}
+%\caption{VUR rates by recipient.}
+%\label{whomVUR}
+%\end{center}
+%\end{table}
 
@@
 
-We performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.
-However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size.
-To examine whether the violation of this assumption impacted our results, we further created a mixed effects model, in order to isolate the subjects variable (i.e., to examine the extent to which random effects stemming from individual differences may be responsible for the effects that we observed).
-When we perform the same tests on many subsets of questions, with one answer randomly sampled from each participant (preserving assumption about the independence of observations), the results are still equivalent.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
-<data> & VUR  \\
-social security number & 98.04\% \\
-a video of you unclothed & 97.44\% \\
-bank account information & 97.10\% \\
-recordings of your work conversations & 96.97\% \\
-an incriminating/embarrassing photo of you & 96.36\% \\
-a photo of you unclothed & 96.30\% \\
-credit card information & 95.92\% \\
-username and password for websites & 95.41\% \\
-a video of you entering in your PIN & 93.91\% \\
-recordings of your phone conversations & 93.88\% \\
-\end{tabular}
-\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-\label{sharedtop10}
-\end{center}
-\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
-%starting from #63
-<data> &  VUR  \\
-bank account information & 90.91\% \\
-a video of you unclothed & 90.62\% \\
-social security number  & 88.68\% \\
-video of you entering your PIN & 88.57\% \\
-an incriminating/embarrassing photo of you & 78.05\% \\
-a photo of you unclothed & 77.78\% \\
-a video of you entering a passcode to a door & 75.00\% \\
-when and how much you have sex & 73.08\% \\
-an incriminating/embarrassing video of you & 71.88\% \\
-a random (inward-facing) photo of you at home & 66.67\% \\
-\end{tabular}
-\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-\label{notsharedtop10}
-\end{center}
-\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
-%starting from #63
-<data> &  VUR  \\
-your name & 47.25\% \\
-when and how much you exercise & 46.07\% \\
-when you were happy or having fun & 38.10\% \\
-what television shows you watch & 35.96\% \\
-when you are busy or interruptible & 34.34\% \\
-your heart rate & 32.28\% \\
-music from your device & 31.87\% \\
-your age & 29.67\% \\
-the language you speak & 20.95\% \\
-your gender & 16.81\% \\
-\end{tabular}
-\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-\label{sharedbottom10}
-\end{center}
-\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
-%starting from #63
-<data> &  VUR  \\
-when and how much you exercise & 16.67\% \\
-how much you use your phone & 15.79\% \\
-your age & 14.29\% \\
-how much you like the people you interact with & 13.79\% \\
-when, what, and how much you ate & 12.50\% \\
-which television shows you watch & 11.43\% \\
-your gender & 9.52\% \\
-your heart rate & 9.09\% \\
-eye movement patterns (for eye tracking) & 6.98\% \\
-the language you speak & 2.50\% \\
-\end{tabular}
-\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-\label{notsharedbottom10}
-\end{center}
-\end{table}
-
-Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{| l | c |}
+%<data> & VUR  \\
+%social security number & 98.04\% \\
+%a video of you unclothed & 97.44\% \\
+%bank account information & 97.10\% \\
+%recordings of your work conversations & 96.97\% \\
+%an incriminating/embarrassing photo of you & 96.36\% \\
+%a photo of you unclothed & 96.30\% \\
+%credit card information & 95.92\% \\
+%username and password for websites & 95.41\% \\
+%a video of you entering in your PIN & 93.91\% \\
+%recordings of your phone conversations & 93.88\% \\
+%\end{tabular}
+%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
+%\label{sharedtop10}
+%\end{center}
+%\end{table}
+%
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{| l | c |}
+%%starting from #63
+%<data> &  VUR  \\
+%bank account information & 90.91\% \\
+%a video of you unclothed & 90.62\% \\
+%social security number  & 88.68\% \\
+%video of you entering your PIN & 88.57\% \\
+%an incriminating/embarrassing photo of you & 78.05\% \\
+%a photo of you unclothed & 77.78\% \\
+%a video of you entering a passcode to a door & 75.00\% \\
+%when and how much you have sex & 73.08\% \\
+%an incriminating/embarrassing video of you & 71.88\% \\
+%a random (inward-facing) photo of you at home & 66.67\% \\
+%\end{tabular}
+%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
+%\label{notsharedtop10}
+%\end{center}
+%\end{table}
+%
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{| l | c |}
+%%starting from #63
+%<data> &  VUR  \\
+%your name & 47.25\% \\
+%when and how much you exercise & 46.07\% \\
+%when you were happy or having fun & 38.10\% \\
+%what television shows you watch & 35.96\% \\
+%when you are busy or interruptible & 34.34\% \\
+%your heart rate & 32.28\% \\
+%music from your device & 31.87\% \\
+%your age & 29.67\% \\
+%the language you speak & 20.95\% \\
+%your gender & 16.81\% \\
+%\end{tabular}
+%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
+%\label{sharedbottom10}
+%\end{center}
+%\end{table}
+%
+%
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{| l | c |}
+%%starting from #63
+%<data> &  VUR  \\
+%when and how much you exercise & 16.67\% \\
+%how much you use your phone & 15.79\% \\
+%your age & 14.29\% \\
+%how much you like the people you interact with & 13.79\% \\
+%when, what, and how much you ate & 12.50\% \\
+%which television shows you watch & 11.43\% \\
+%your gender & 9.52\% \\
+%your heart rate & 9.09\% \\
+%eye movement patterns (for eye tracking) & 6.98\% \\
+%the language you speak & 2.50\% \\
+%\end{tabular}
+%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
+%\label{notsharedbottom10}
+%\end{center}
+%\end{table}
+%
+%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
 When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
@@
 When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-
-On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
+%
+%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
 When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.

### 2015-01-05 wearables_survey.tex
beefed up related work, tweaked results.

@@
 
+\subsection{Crowdsourced User Studies}
+Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}.
+While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S.
+population \cite{ross2010crowdworkers}\cite{kelley2010conducting}.
+Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S.
+public \cite{kang2014privacy}.
+
 %%%%%%%%%%%%%%%%%%%
@@
 
-{\color{red} can you comment on the independence, since you have the csv?
-it would be a pain for me to do find out how many people got the same situational questions which only differ by recipient.
-:(} There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+{\color{red} Serge, this paragraph can be re-worded as you see fit.
+I just plopped in some stuff.} this test violates that assumption of CHI square, however, based on the condition randomization and very large sample size, we do not believe this to be an issue.
+Nonetheless, we checked this by also performing the analysis by using only one data point per recipient (to preserve that assumption), and yielded the same results.
+There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
 
@@
 
-Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}.
-While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S.
-population \cite{ross2010crowdworkers}\cite{kelley2010conducting}.
-Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S.
-public \cite{kang2014privacy}.
-
 %The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.

### 2015-01-05 wearables_survey.tex
more little tweaks

--- 2015-01-05 wearables_survey.tex
@@
 \subsubsection{Wearables Scenarios}
-%okay, this section is kind of confusing, I must admit..
-
 We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first.
@@
 Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}.
-{\color{red} should I say anything about the full list of 74 data types?}
+Generally, the most concerning and least concerning data types did not change by recipient.
+{\color{red} can be said for ~top/bottom5 looking at the recipient lists I commented out; but this isn't too official since we do no stat tests.}
 

### 2015-01-05 wearables_survey.tex
Updated numbers

@@
 We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology).
-We surveyed 1,785 participants about 74 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
+We surveyed 1,785 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
 Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
@@
 
-A survey of 3,956 respondents who are either current users or non-users with high interest in wearables found that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
+A survey of 3,956 respondents with high interest in wearables found that the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
 It is estimated that 20\% of the general population own at least one wearable and 10\% use at least one wearable in their daily lives~\cite{WearableStatNews}.
@@
 
-Despite early adoption, wearable device security and privacy concerns are prevalent.
+Despite high early adoption rates, wearable device security and privacy concerns are rampant.
 Many of these concerns relate to users' activities being exposed to the public without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the disclosure of sensitive user information.
-In other instances, public discomfort prevented companies from enabling certain capabilities; Google's Glass had facial recognition disabled upon release~\cite{GlassDetection}.
+For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive user information.
+In other instances, public discomfort prevented companies from enabling certain capabilities; Google's Glass had facial recognition disabled upon release to mitigate potential privacy concerns~\cite{GlassDetection}.
 
@@
 Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-We created an initial pool of 292 questions by combining 73 data types (<data>) with 4 data recipients (<recipient>).
+We created an initial pool of 292 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
 The 4 possible data recipients were:
@@
 The main purpose of these questions was to determine the extent to which the data type and data recipient played a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 13 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we thought were relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' Thus, there were a total of 305 questions in this set, from which we randomly presented each participant with 6 questions.
+Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we thought were relevant nonetheless.
+An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' Thus, there were a total of 304 questions in this set, from which we randomly presented each participant with 6 questions.
 
@@
 We presented participants with a second set of scenarios in order to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 305 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
 We randomly presented participants with 2 of the following 5 questions:
@@
 
-A statistical analysis regarding the significance and confidence of <data> types with respect to all 74 was not performed due to the space constraints of the paper.
-We do consider all <data> in our regression model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
+A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
+We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
 
@@
 We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 305 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
+Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
 We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.

### 2015-01-05 wearables_survey.tex
Edited Related Work

@@
 \subsection{Ubiquitous Sensing}
-At an unprecedented rate, we are moving towards automated capture and ubiquitous access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables.
-Wearbles have new capabilities which allow capture of unique data about the user and his/her surroundings.
-As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security concerns ~\cite{palen2003unpacking}.
-Privacy in ubiquitous systems can be achieved my adhering to principles such as notice, choice, and consent ~\cite{langheinrich2001privacy}.
+Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables.
+Wearables have new capabilities that allow capture of unique data about the user and his/her surroundings.
+As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}.
+Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}.
 
 \subsection{Smartphones and Wearables Concerns}
-There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}.
-However, works like these are not grounded in user research and do not make claims about what the the most relevant concerns for the average user are.
-Felt et.
-al's study of smartphone user concerns \cite{Felt} was the first to investigate the smartphone security and privacy landscape from a user study standpoint.
-The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
+%I really don't know what this first sentence means...
+
+Much of the previous work addresses the anticipated privacy and security challenges related to mobile and wearable devices from a systems standpoint (e.g.,~\cite{DiPietro}).
+However, system designs to improve end-user security need to be grounded in user research to better understand end-user concerns.
+Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}.
+Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
 Participants were asked how upset they would be if a certain action had occurred without their permission.
-Participants rated each situation on a likert scale ranging from indifferent (1) to very upset (5).
-Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges.
-We use a similar scale to ask our users how upset they would be if a certain action was taken without their permission, but ask questions about new capabilities on wearable devices.
-To our knowledge, our work is the first of its kind to investigate such user concerns.
+Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.
+
+Denning et.
+al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
+Bystanders expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables.
+While this research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.
 
 \subsection{Technology Risk Perceptions}
-While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology.
-A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies.
-In the study, participants were prompted to rate the risks and benefits of 30 activities and technologies for all people affected by the technology, for a long period of time.
+Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}.
+In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies.
+They were primed to think about all people affected by the technology, and to think about long-term vs.
+short-term risks and benefits..
 The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e.
 a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
-In our survey, we use a similar prompt to ask participants to rate the risks and benefits of 20 new technologies.
-Denning et.
-al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
-Bystanders expressed concerns due to the subtle, easy-to-use, and prevalent nature of wearables.
-While people have conducted studies on privacy concerns with respect to wearables, we are aware of no work which as looked at privacy perspectives of the owner of the device.
-In our survey, we show how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
+Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
 
-\subsection{Crowdsourced User Studies}
-Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}.
+%I'm not sure that having a background on crowdsourcing is relevant, especially given the space limitations.
+Instead, you need WAY more related work on ubiquitous privacy concerns, as well as smartphone privacy concerns.
+There's also probably more general work on risk perceptions that should probably be cited.
+
+%\subsection{Crowdsourced User Studies}
+%Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}.
 While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S.

### 2015-01-05 wearables_survey.tex
started fixing 17's numbers: demographics in results section, open-ended answers.

--- 2015-01-05 wearables_survey.tex
@@
 We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,785.
-Of these, 57.87\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-%SE: Are the above numbers correct? Also, can you add a range of ages?
+Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
 
@@
 Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is if they were maximally upset or not, rather than how upset they were.
-In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+In the risk/benefit section, followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.8\%.
+Finally, for the open-ended question at the end, two researchers independently coded 1,785 responses and had an initial agreement rate of 89.73\%.
 The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
@@
 
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
+In this section, we present the results of our multiple-part survey.
+We first discuss participants responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived by participants.
+Next, we discuss participants' risk/benefit assessment of various new technologies with respect to well-established technologies.
 We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
@@
 Health Risk & 191 & 10.70\%\\
-Safety & 186 & 10.42\%\\
+Safety & 185 & 10.42\%\\
 Financial Cost & 151 & 8.46\%\\

### 2015-01-05 wearables_survey.tex
Edited up to 4.1.1

--- 2015-01-05 wearables_survey.tex
@@
 We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology).
-We surveyed 1,785 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
+We surveyed 1,784 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
 Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
@@
 
-To this end, we surveyed 1,785 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]
+To this end, we surveyed 1,784 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]
 
@@
 We highlighted the capabilities of this device and described several use cases.
-To ensure that participants had read and understood this device's capabilities, we presented them with two comprehension questions.
+To ensure that participants had read and understood this device's capabilities, we presented them with two multiple-choice comprehension questions.
 
@@
 Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-We created an initial pool of 292 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
+We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
 The 4 possible data recipients were:
@@
 
-To parallel Fischhoff \etal's risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
+To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
 We randomized whether they performed the ranking for risks or benefits first.
@@
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,785.
+We filtered out an additional 100 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,784.
 Of these, 57.87\% were male, with a median age of 29 ($\sigma$ = 10.37).
@@
 
-%SE: Edited up to here.
 %Comment on independence of observations, differences between public/work, and end the subsection
 
-{\color{red} Serge, this paragraph can be re-worded as you see fit.
-I just plopped in some stuff.} this test violates that assumption of CHI square, however, based on the condition randomization and very large sample size, we do not believe this to be an issue.
-Nonetheless, we checked this by also performing the analysis by using only one data point per recipient (to preserve that assumption), and yielded the same results.
-There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+We note that this chi-square test violates the assumption of independence of observations, since each participant responded to multiple scenarios.
+However, based on the randomization of treatments and very large sample size, we do not believe that this impacted our results.
+Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and observed that our previous results held: participants were significantly more concerned about having their data seen by actual humans (as opposed to app servers), though the specific human had no observable effect (i.e., between the public, friends, and work contacts).
 
-Participants had different sensitivities depending on if they perceived that their data would be shared with an application or a person.
-We found the top and bottom ten concerns with respect to a non-human audience (app's servers) versus a human audience (friends, work contacts, and public).
-Participants were more uncomfortable about privacy and theft (i.e.
-frequency of sex, photos at home, and passcodes to doors).
-when sharing data with an application.
+%SE: this needs to be rewritten below.
+
+We compared the top and bottom ten concerns between a non-human audience (app's servers) and a human audience (friends, work contacts, and the public).
+While many of the most and least concerning scenarios were the same between these two groups, participants were more uncomfortable about privacy and theft (i.e.
+frequency of sex, photos at home, and passcodes to doors) when sharing data with an application.
 They were also more uncomfortable sharing phone or text conversations and credentials (i.e.
@@
 For a human audience, participants were most comfortable sharing data which would come up in conversation (i.e music on their device, if one was having fun, and if one if busy or interruptible), but found these topics more disturbing to share with an app's server.
-{\color{red} should we creatively include stats for these in the appendix, in a space-conscious way?}.
+
+There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
 

### 2015-01-05 wearables_survey.tex

@@
 \subsection{Recruitment and Analysis Method}
+
 We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
@@
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 100 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,784.
-Of these, 57.87\% were male, with a median age of 29 ($\sigma$ = 10.37).
+We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
+Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
 
@@
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.8\%.
+Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.7\%.
 The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

### 2015-01-05 wearables_survey.tex
minor numbers

@@
 We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology).
-We surveyed 1,784 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
+We surveyed 1,785 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
 Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
@@
 
-To this end, we surveyed 1,784 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]
+To this end, we surveyed 1,785 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]
 
@@
 We highlighted the capabilities of this device and described several use cases.
-To ensure that participants had read and understood this device's capabilities, we presented them with two multiple-choice comprehension questions.
+To ensure that participants had read and understood this device's capabilities, we presented them with two comprehension questions.
 
@@
 Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
+We created an initial pool of 292 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
 The 4 possible data recipients were:
@@
 
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
+To parallel Fischhoff \etal's risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
 We randomized whether they performed the ranking for risks or benefits first.
@@
 
+%% I EDITED THESE NUMBERS for 17 year old
+
 We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
@@
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-%SE: Are the above numbers correct? Also, can you add a range of ages?
+We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses {\color{red} filtered one for being 17}, leaving us with a total sample size of 1,784.
+Of these, 55.10\% were male, with ages ranging from 18 to 73 ($\mu$ = 29, $\sigma$ = 10.37).
 
@@
 Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is if they were maximally upset or not, rather than how upset they were.
-In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+In the risk/benefit section, followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.7\%.
+Finally, for the open-ended question at the end, two researchers independently coded 1,784 responses and had an initial agreement rate of 89.73\%.
 The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
@@
 
+%SE: Edited up to here.
 %Comment on independence of observations, differences between public/work, and end the subsection
 
-We note that this chi-square test violates the assumption of independence of observations, since each participant responded to multiple scenarios.
-However, based on the randomization of treatments and very large sample size, we do not believe that this impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and observed that our previous results held: participants were significantly more concerned about having their data seen by actual humans (as opposed to app servers), though the specific human had no observable effect (i.e., between the public, friends, and work contacts).
+{\color{red} Serge, this paragraph can be re-worded as you see fit.
+I just plopped in some stuff.} this test violates that assumption of CHI square, however, based on the condition randomization and very large sample size, we do not believe this to be an issue.
+Nonetheless, we checked this by also performing the analysis by using only one data point per recipient (to preserve that assumption), and yielded the same results.
+There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
 
-%SE: this needs to be rewritten below.
-
-We compared the top and bottom ten concerns between a non-human audience (app's servers) and a human audience (friends, work contacts, and the public).
-While many of the most and least concerning scenarios were the same between these two groups, participants were more uncomfortable about privacy and theft (i.e.
-frequency of sex, photos at home, and passcodes to doors) when sharing data with an application.
+Participants had different sensitivities depending on if they perceived that their data would be shared with an application or a person.
+We found the top and bottom ten concerns with respect to a non-human audience (app's servers) versus a human audience (friends, work contacts, and public).
+Participants were more uncomfortable about privacy and theft (i.e.
+frequency of sex, photos at home, and passcodes to doors).
+when sharing data with an application.
 They were also more uncomfortable sharing phone or text conversations and credentials (i.e.
@@
 For a human audience, participants were most comfortable sharing data which would come up in conversation (i.e music on their device, if one was having fun, and if one if busy or interruptible), but found these topics more disturbing to share with an app's server.
-
-There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+{\color{red} should we creatively include stats for these in the appendix, in a space-conscious way?}.
 
@@
 
+%% I EDITED THESE NUMBERS for 17 year old
+
 \begin{table}[h]

### 2015-01-05 wearables_survey.tex

--- 2015-01-05 wearables_survey.tex
@@
 
-%SE: Are the above numbers correct? Also, can you add a range of ages?
-
 In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than the average of all Likert scores.
@@
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.7\%.
+Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses and had an initial agreement rate of 89.7\%.
 The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

### 2015-01-05 wearables_survey.tex
Fixed ALL of analysis, taking out 17-year old boy.

@@
 
-\title{A Survey Wearable Device Risk Perceptions}
+\title{A Survey of Wearable Device Risk Perceptions}
 %\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
@@
 \section{Results}
-%%%confusing runthrough of the results.. is this too packed. I wrote a roadmap paragraph instead based on this, which is below. Much better.
-
-%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.
-Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public.
-Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat.
-When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit.
-Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.
-
 In this section, we present our survey results.
@@
 \subsubsection{Data Recipient}
-Based on our data, we observed that the largest effect seemed to stem from who the recipient of the data was: across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.4\%), work contacts (75.1\%), and the public (72.4\%) were much higher.
+Based on our data, we observed that the largest effect seemed to stem from who the recipient of the data was: across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
 A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
 However, these effect sizes were relatively small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-%Comment on independence of observations, differences between public/work, and end the subsection
 
@@
 
+%Comment on differences between public/work, and end the subsection
 %SE: this needs to be rewritten below.
@@
 
-% LL: I thought this would be better, but then it looked stupid, so I commented it out.
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|c|}
-%\hline
-%Recipients	& VUR \\
-%\hline
-%App	& 42.3\% \\
-%Friends & 69.4\% \\
-%Work & 75.1\% \\
-%Public & 72.4\% \\
-%\hline
-%\end{tabular}
-%\caption{VUR rates by recipient.}
-%\label{whomVUR}
-%\end{center}
-%\end{table}
-
 \begin{table}[t]
@@
 \hline
-Work-App	& 564.32 & <0.0001 & 5,085 & 0.111\\
-Public-App	& 479.98 & <0.0001 & 5,192 & 0.092\\
-Friends-App & 380.00 & <0.0001 & 5,098 & 0.075\\
-Friends-Work & 20.37 & <0.0001 & 5,039 & 0.004\\
-Friends-Public & 5.35 & <0.0207 & 5,146 & 0.001\\
-Work-Public&  5.05 & <0.0246 & 5,133	& 0.001\\
+Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
+Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
+Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
+Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
+Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
+Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
 \hline
@@
 \begin{tabular}{| l | c |}
-
+\hline
 <data> &  VUR  \\
+\hline
 a video of you unclothed & 95.97\% \\
@@
 social security number & 94.84\% \\
-video of you entering in your PIN & 92.67\% \\
+video of you entering in your PIN & 92.59\% \\
 a photo of you unclothed & 92.59\% \\
@@
 a random (inward-facing) photo you at home & 87.50\% \\
-
+\hline
 \end{tabular}
@@
 %starting from #63
+\hline
 <data> &  VUR  \\
+\hline
 eye movement patterns (for eye tracking) & 40.51\% \\
 when and how much you exercise  & 38.66\% \\
-when you are happy or having fun  & 34.51\% \\
+when you are happy or having fun  & 34.75\% \\
 which television shows you watch & 30.20\% \\
@@
 the language you speak & 15.86\% \\
-your gender & 14.91\% \\
-
+your gender & 15.00\% \\ 
+\hline
 \end{tabular}
@@
 Participants had unique VUR rates for situations only differing in the device.
-Our participants had a 70.23\% VUR when asked about wearables devices and 40.62\% VUR when asked about smartphones.The VUR rates for both devices for all 5 quesions are in table ~\ref{deviceVUR}.
+Our participants had a 58.79\% VUR when asked about wearables devices and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
 However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
@@
 \begin{center}
-\begin{tabular}{| c | c | c |}
+\begin{tabular}{| c | r | r |}
+\hline
  Question &  Wearable VUR & Smartphone VUR \\
- All & 70.23\% & 40.62\%\\
+ \hline
+ All & 58.79\% & 46.64\%\\
 Q1 & 14.81\%  &  6.13\%\\
@@
 Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.79\%\\
+Q4 & 52.77\%  & 55.74\%\\
 Q5 & 86.49\%  &  91.82\%\\ 
+\hline
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{| c | c | c | c |}
+\begin{tabular}{|l|r|r|r|r|}
 %Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
@@
 %Q5	1.611		0.2043	No		710		0.002\\
-Question & $\chi^2$ &	2-tail P & Effect Size\\
-All & 2.814 & 0.1395 & 0.001\\
-Q1 & 2.500 & 0.1139 & 0.004\\
-Q2 & 17.333 & <0.0001 & 0.024\\
-Q3 & 0.020 & 0.8886 & 0.000\\
-Q4 & 1.426 & 0.2324 & 0.002\\
-Q5 & 1.611 & 0.2043 & 0.002\\
+\hline
+Question & $\chi^2$ & 2-tail P & n  & Effect Size\\
+\hline
+All & 2.202 & 0.1378 & 3588 & 0.001\\
+Q1 & 2.500 & 0.1139 & 714 & 0.004\\
+Q2 & 17.333 & <0.0001 & 708 &  0.024\\
+Q3 & 0.020 & 0.8886 & 699 &  0.000\\
+Q4 & 1.413 & 0.2345 & 730& 0.002\\
+Q5 & 1.604 & 0.2054 & 709 & 0.002\\
+\hline
 \end{tabular}
@@
 
-%% I EDITED THESE NUMBERS for 17 year old
-
 \begin{table}[h]
 \begin{center}
-\begin{tabular}{lll}
-
+\begin{tabular}{|l|r|r|}
+\hline
 Concern &  Responses &  Frequency   \\
+\hline
 Privacy & 452 & 25.32\% \\
@@
 Don't care 	& 11 & 0.62\%\\
-
+\hline
 \end{tabular}

### 2015-01-05 wearables_survey.tex
Added JoongHwa as an author.

@@
 \author{
- \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
+ \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
    \vspace{0.5em}
    \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}\\
-   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+   \affaddr{\textsuperscript{2}University of California, Berkeley, \{dlwndghk94\}@berkeley.edu}\\
+   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
 }

### 2015-01-05 wearables_survey.tex
spacing fixes
put in placeholder appendix for data types.
Edited up to devices

--- 2015-01-05 wearables_survey.tex
@@
 \subsubsection{Smartphone Scenarios}
+\label{sec:smartphones}
+
 We presented participants with a second set of scenarios in order to control for the type of device being used.
@@
 
-\begin{packed_item}
+\begin{packed_enum}
 \item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
@@
 \item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?}
-\end{packed_item}
+\end{packed_enum}
 
@@
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses and had an initial agreement rate of 89.7\%.
+Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,785 responses and had an initial agreement rate of 89.7\%.
 The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
@@
 However, based on the randomization of treatments and very large sample size, we do not believe that this impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and observed that our previous results held: participants were significantly more concerned about having their data seen by actual humans (as opposed to app servers), though the specific human had no observable effect (i.e., between the public, friends, and work contacts).
+Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and found that the test was robust to this violation: participants were significantly more concerned about having their data seen by actual humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups were not significant (i.e., between the public, friends, and work contacts).
 
@@
 
-We compared the top and bottom ten concerns between a non-human audience (app's servers) and a human audience (friends, work contacts, and the public).
-While many of the most and least concerning scenarios were the same between these two groups, participants were more uncomfortable about privacy and theft (i.e.
-frequency of sex, photos at home, and passcodes to doors) when sharing data with an application.
-They were also more uncomfortable sharing phone or text conversations and credentials (i.e.
-username and password for websites, credit card information) to a human audience than to a server.
-Additionally, they concerned more concerned On the other hand, participants were comfortable sharing behavioral patterns and personal opinions (i.e.
-phone use, opinions of people, eye patterns, and food eaten) with an app's server rather than a human audience.
-For a human audience, participants were most comfortable sharing data which would come up in conversation (i.e music on their device, if one was having fun, and if one if busy or interruptible), but found these topics more disturbing to share with an app's server.
+We compared the 10 most concerning scenarios when sharing with an app's servers versus with a human audience (friends, work contacts, and the public).
+We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same:
 
-There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
+\begin{packed_enum}
+\item Bank account information
+\item A video of you unclothed
+\item Social security number
+\item Video of you entering your PIN
+\item An incriminating/embarrassing photo of you
+\item A photo of you unclothed
+\end{packed_enum}
+
+What is interesting about this finding is that while the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
+For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
+This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.
 
@@
 %<data> & VUR  \\
-%social security number & 98.04\% \\
-%a video of you unclothed & 97.44\% \\
-%bank account information & 97.10\% \\
+%social security number & 98.04\% \\ CC
+%a video of you unclothed & 97.44\% \\ CC
+%bank account information & 97.10\% \\ CC
 %recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\
-%a photo of you unclothed & 96.30\% \\
+%an incriminating/embarrassing photo of you & 96.36\% \\ CC
+%a photo of you unclothed & 96.30\% \\ CC
 %credit card information & 95.92\% \\ 
 %username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\
+%a video of you entering in your PIN & 93.91\% \\ CC
 %recordings of your phone conversations & 93.88\% \\ 
@@
 %<data> &  VUR  \\
-%bank account information & 90.91\% \\
-%a video of you unclothed & 90.62\% \\
-%social security number  & 88.68\% \\
-%video of you entering your PIN & 88.57\% \\
-%an incriminating/embarrassing photo of you & 78.05\% \\
-%a photo of you unclothed & 77.78\% \\
+%bank account information & 90.91\% \\ CC
+%a video of you unclothed & 90.62\% \\ CC
+%social security number  & 88.68\% \\ CC
+%video of you entering your PIN & 88.57\% \\ CC
+%an incriminating/embarrassing photo of you & 78.05\% \\ CC
+%a photo of you unclothed & 77.78\% \\ CC
 %a video of you entering a passcode to a door & 75.00\% \\ 
@@
 \subsubsection{Data Type}
-Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information.
-Information which can be used to impersonate the user (i.e.
-username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data.
-Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}.
-Generally, the most concerning and least concerning data types did not change by recipient.
-{\color{red} can be said for ~top/bottom5 looking at the recipient lists I commented out; but this isn't too official since we do no stat tests.}
+Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
+The 10 most and least concerning data types can be seen in Table \ref{top10}.
+
+The least concerning data types were all related in that they all consisted of information that could be observed through observations of public behavior.
+For instance, demographic information (e.g., age, gender, language spoken).
+It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
 
@@
 \begin{center}
-\begin{tabular}{| l | c |}
-
-<data> &  VUR  \\
-a video of you unclothed & 95.97\% \\
-bank account information & 95.91\% \\
-social security number & 94.84\% \\
-video of you entering in your PIN & 92.67\% \\
-a photo of you unclothed & 92.59\% \\
-an incriminating/embarrassing photo of you & 91.39\% \\
-username and password for websites & 89.55\% \\
-credit card information & 88.98\% \\
-an incriminating/embarrassing video of you & 88.41\% \\
-a random (inward-facing) photo you at home & 87.50\% \\
-
+\small
+\begin{tabular}{| r | l | r |}
+Rank & Data &  VUR  \\
+\hline
+1 & a video of you unclothed & 95.97\% \\
+2 & bank account information & 95.91\% \\
+3 & social security number & 94.84\% \\
+4 & video of you entering in your PIN & 92.67\% \\
+5 & a photo of you unclothed & 92.59\% \\
+6 & an incriminating/embarrassing photo of you & 91.39\% \\
+7 & username and password for websites & 89.55\% \\
+8 & credit card information & 88.98\% \\
+9 & an incriminating/embarrassing video of you & 88.41\% \\
+10 & a random (inward-facing) photo you at home & 87.50\% \\
+ & \vdots & \\
+64 & eye movement patterns (for eye tracking) & 40.51\% \\
+65 & when and how much you exercise  & 38.66\% \\
+66 & when you are happy or having fun  & 34.51\% \\
+67 & which television shows you watch & 30.20\% \\
+68 & when you are busy or interruptible  & 29.50\% \\
+69 & music from your device  & 28.06\% \\
+70 & your heart rate & 27.50\% \\
+71 & your age & 24.29\% \\
+72 & the language you speak & 15.86\% \\
+73 & your gender & 14.91\% \\ 
+\hline
 \end{tabular}
-\caption{A table of the top 10 upsetting <data> types, irregardless of recipient or data type.}
+\caption{The 10 most and least upsetting data types, across all recipients.}
 \label{top10}
@@
 
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| l | c |}
-%starting from #63
-<data> &  VUR  \\
-eye movement patterns (for eye tracking) & 40.51\% \\
-when and how much you exercise  & 38.66\% \\
-when you are happy or having fun  & 34.51\% \\
-which television shows you watch & 30.20\% \\
-when you are busy or interruptible  & 29.50\% \\
-music from your device  & 28.06\% \\
-your heart rate & 27.50\% \\
-your age & 24.29\% \\
-the language you speak & 15.86\% \\
-your gender & 14.91\% \\
-
-\end{tabular}
-\caption{A table of the bottom 10 upsetting <data> types, irregardless of recipient or data type.}
-\label{bottom10}
-\end{center}
-\end{table}
-
-A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
+%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
 We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
@@
 
-\begin{table}%[h]
+\begin{table}[t]
 \begin{center}
-\begin{tabular}{| c | c | c |}
+\begin{tabular}{| c | r | r |}
  Question &  Wearable VUR & Smartphone VUR \\
+ \hline
  All & 70.23\% & 40.62\%\\
@@
 Q5 & 86.49\%  &  91.82\%\\ 
+\hline
 \end{tabular}
-\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
+\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
 \label{deviceVUR}
@@
 %Q5	1.611		0.2043	No		710		0.002\\
-Question & $\chi^2$ &	2-tail P & Effect Size\\
+
+%SE: Can you add sample sizes to this table?
+Question & $\chi^2$ & p-value & $\phi$ \\
+\hline
 All & 2.814 & 0.1395 & 0.001\\
@@
 Q5 & 1.611 & 0.2043 & 0.002\\
+\hline
 \end{tabular}
-\caption{Results of the effects of <device> type contributing to VUR.
-Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
+\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
 \label{betweendevice}
@@
 This top concern surpassed all other concerns by about an order of magnitude or more:
-
-%% I EDITED THESE NUMBERS for 17 year old
 

### 2015-01-05 wearables_survey.tex

@@
 We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
-The 4 possible data recipients were:
+The 4 possible data recipients were:  \\[-.8cm]
 
@@
 \subsubsection{Smartphone Scenarios}
+
 \label{sec:smartphones}
@@
 These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented participants with 2 of the following 5 questions:
+We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]
 
@@
 65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.51\% \\
+66 & when you are happy or having fun  & 34.75\% \\
 67 & which television shows you watch & 30.20\% \\
@@
 72 & the language you speak & 15.86\% \\
-73 & your gender & 14.91\% \\ 
+73 & your gender & 15.00\% \\ 
 \hline
@@
 \begin{tabular}{| c | r | r |}
+\hline
  Question &  Wearable VUR & Smartphone VUR \\
  \hline
- All & 70.23\% & 40.62\%\\
+ All & 58.79\% & 46.64\%\\
 Q1 & 14.81\%  &  6.13\%\\
@@
 Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.79\%\\
+Q4 & 52.77\%  & 55.74\%\\
 Q5 & 86.49\%  &  91.82\%\\ 
@@
 %SE: Can you add sample sizes to this table?
-Question & $\chi^2$ & p-value & $\phi$ \\
+Question & $\chi^2$ & p-value & n & $\phi$ \\
 \hline
-All & 2.814 & 0.1395 & 0.001\\
-Q1 & 2.500 & 0.1139 & 0.004\\
-Q2 & 17.333 & <0.0001 & 0.024\\
-Q3 & 0.020 & 0.8886 & 0.000\\
-Q4 & 1.426 & 0.2324 & 0.002\\
-Q5 & 1.611 & 0.2043 & 0.002\\
+All & 2.202 & <0.1378 & 3,588 & 0.001\\
+Q1 & 2.500 & <0.1139 & 714 & 0.004\\
+Q2 & 17.333 & <0.0001 & 708 &  0.024\\
+Q3 & 0.020 & <0.8886 & 699 &  0.000\\
+Q4 & 1.413 & <0.2345 & 730& 0.002\\
+Q5 & 1.604 & <0.2054 & 709 & 0.002\\
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
-
+\begin{tabular}{|l|r|r|}
+\hline
 Concern &  Responses &  Frequency   \\
+\hline
 Privacy & 452 & 25.32\% \\
@@
 
+\section{List of all <data>}
+{\color{red} Placeholder for space measuring.} \\[-.8cm]
+
+\begin{enumerate}\itemsep0pt \parskip0pt \parsep0pt
+  \item foo
+  \item bar
+   \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+\end{enumerate}
+
 %\section{Risk and Benefit Rankings}

### 2015-01-05 wearables_survey.tex
working on related work with new references (still rough).

--- 2015-01-05 wearables_survey.tex
@@
 
-%%%%% FEEDBACK TO INCORPORATE, from Serge
-
-%-"security and privacy concerns regarding wearable devices are becoming heightened as companies make headlines for incidents resulting in users’ sexual activities exposed to the public..." I would rewrite this.
-You don't really mean to say that tracking sexual activity is the *only* privacy and security concern.
-It's one of many.
-I would say at the beginning that there are myriad privacy/security concerns, and then go into specific examples (e.g., sex, facial recognition, etc.).
-%-I think you might want to motivate this better: why do we need to better understand the threat landscape?
-(Answer: to focus on the most concerning things and then warn users when they're about to occur or prevent them from happening altogether.)
-%-Start a new paragraph before the contribution bullets to say what we actually did. For example, "we surveyed 2,250 Internet users to determine..."
-%-For the bullets, these can be made much more concise.
-I would also frame them in terms of what we found, not what we did.
-For example, "we found that X% of participants found that Y threats were most concerning..."
-%-I would limit these bullets to the top 3-4 most interesting findings that we found.
-
 \section{Introduction}
@@
 
+~\cite{Egelman2015} {\color{red} Serge: talk about this; you wrote it and it's not out yet.}
+~\cite{bellotti1993design}: framework for designing for privacy in ubicomp.
+~\cite{hong2004privacy}: privacy risk model for ubicomp. 
+~\cite{jiang2002approximate}: social privacy model for ubicomp.
+
 \subsection{Smartphones and Wearables Concerns}
@@
 
-Much of the previous work addresses the anticipated privacy and security challenges related to mobile and wearable devices from a systems standpoint (e.g.,~\cite{DiPietro}).
-However, system designs to improve end-user security need to be grounded in user research to better understand end-user concerns.
+Designs to improve end-user security need to be grounded in user research to better understand end-user concerns.
 Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}.
@@
 
-\subsection{Technology Risk Perceptions}
+~\cite{chin2012measuring}: understanding user attitudes toward security and privacy for smartphones. 
+~\cite{felt2012android}: if attention to, understand, and act on permission information during installation.
+~\cite{laurier2001people}: Why people say where they are during mobile phone calls
+~\cite{palen2000going}: behavior and practice of new mobile phone users
+
+\subsection{User Perceptions and Behaviors}
+
 Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}.
@@
 Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+
+~\cite{acquisti2005privacy} Privacy and decision making: ppl lack enough info to make privacy-sensitive decisions; even if, likely to trade off long-term privacy for short-term benefits.
+~\cite{jensen2005privacy}: Self-reports versus observed behavior
+~\cite{spiekermann2001privacy}: Privacy Preferences Versus Actual Behavior
 
@@
 
+\section{List of all <data>}
+{\color{red} Placeholder for space measuring.} \\[-.8cm]
+
+\begin{small}
+\begin{enumerate}\itemsep0pt \parskip0pt \parsep0pt
+  \item foo
+  \item bar
+   \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+  \item foo
+  \item bar
+\end{enumerate}
+\end{small}
+
 %\section{Risk and Benefit Rankings}

### 2015-01-05 wearables_survey.tex

--- 2015-01-05 wearables_survey.tex
@@
 
+\begin{small}
 \begin{enumerate}\itemsep0pt \parskip0pt \parsep0pt
@@
 \end{enumerate}
+\end{small}
 

### 2015-01-05 wearables_survey.tex
addressing Serge's comments, added missing hlines for tables, minor formatting.

@@
 \subsection{Smartphones and Wearables Concerns}
-%I really don't know what this first sentence means...
-
 Designs to improve end-user security need to be grounded in user research to better understand end-user concerns.
@@
 
-%In total, the survey consisted of 367 unique questions, with each participant answering 27 questions.
-Out of the 27 seen by each participant, 17 of the questions were constant, whereas 10 of the questions were selected at random from larger sets of questions.
-
 \subsection{Survey Questions}
@@
 \subsubsection{Smartphone Scenarios}
-
 \label{sec:smartphones}
-
 We presented participants with a second set of scenarios in order to control for the type of device being used.
@@
 \subsubsection{Risk and Benefit Assessment}
-
 In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies, and how those perceptions compared to other well-established technologies.
@@
 \subsection{Recruitment and Analysis Method}
-
 We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
@@
 \subsection{Concern Factors}
-
 In this section, we discuss the factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable device or a smartphone.
@@
 This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.
-
-%SE: This doesn't add much, the numbers can be put in the text to save space.
-%LL: Agreed.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{recipient.png}
-%	\caption{(This is a placeholder! TODO: generate a better plot for data recipient)}
-%\end{figure}
 
@@
 \begin{tabular}{| r | l | r |}
+\hline
 Rank & Data &  VUR  \\
@@
 %Q5	1.611		0.2043	No		710		0.002\\
-
-%SE: Can you add sample sizes to this table?
+\hline
 Question & $\chi^2$ & p-value & n & $\phi$ \\

### 2015-01-05 wearables_survey.tex
finished the related work section.

@@
 \subsection{Ubiquitous Sensing}
-Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables.
-Wearables have new capabilities that allow capture of unique data about the user and his/her surroundings.
+Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
+Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors.
+Examples of such efforts include frameworks to design for privacy environments ~\cite{bellotti1993design} and evaluating ubiquitous computing applications ~\cite{scholtz2004toward}.
+There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model ~\cite{hong2004privacy} and a social-based model ~\cite{jiang2002approximate}.
+
+Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings.
 As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}.
 Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}.
-
-~\cite{Egelman2015} {\color{red} Serge: talk about this; you wrote it and it's not out yet.}
-~\cite{bellotti1993design}: framework for designing for privacy in ubicomp.
-~\cite{hong2004privacy}: privacy risk model for ubicomp. 
-~\cite{jiang2002approximate}: social privacy model for ubicomp.
+An example of research which helps such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
 
 \subsection{Smartphones and Wearables Concerns}
-Designs to improve end-user security need to be grounded in user research to better understand end-user concerns.
-Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}.
+Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones ~\cite{chin2012measuring}, observe behaviors of new smartphone users ~\cite{palen2000going}, investigate user understanding of permissions ~\cite{felt2012android}.
+
+Among such studies, Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}.
 Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
@@
 
-~\cite{chin2012measuring}: understanding user attitudes toward security and privacy for smartphones. 
-~\cite{felt2012android}: if attention to, understand, and act on permission information during installation.
-~\cite{laurier2001people}: Why people say where they are during mobile phone calls
-~\cite{palen2000going}: behavior and practice of new mobile phone users
+%~\cite{laurier2001people}: Why people say where they are during mobile phone calls
 
@@
 They were primed to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits..
+short-term risks and benefits.
 The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e.
@@
 
-~\cite{acquisti2005privacy} Privacy and decision making: ppl lack enough info to make privacy-sensitive decisions; even if, likely to trade off long-term privacy for short-term benefits.
-~\cite{jensen2005privacy}: Self-reports versus observed behavior
-~\cite{spiekermann2001privacy}: Privacy Preferences Versus Actual Behavior
+While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.
+Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.
 
@@
 
-%(REDO, Should I even say this?) I messed up that motorcycle question.
-I wish I actually had a calibration point for high risk high benefit for the Fischoff technology assessment questions.
-But well, none of the new technologies fit that description so we didn't really need it critically.
-
 %%%%%%%%%%%%%%%%%%%
@@
 
-%\end{document}  % This is where a 'short' article might terminate
+%COMMENTED OUT FOR ANONYMITY!!
 
-%ACKNOWLEDGMENTS are optional
-\section{Research Ethics} 
-We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
+%\section{Research Ethics} 
+%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
 Survey data was collected in an anonymous manner.
@@
 
-\section{Acknowledgments}
-The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
+%\section{Acknowledgments}
+%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
 Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
@@
 %%%%%%%%%%%%%%%%%%%
-
-% The following two commands are all you need in the initial runs of your .tex file to produce the bib
-%  and remember to run: latex bibtex latex latex to resolve all references
 

### 2015-01-05 wearables_survey.tex
minor wording changes

@@
 Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}.
-An example of research which helps such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
+An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
 

### 2015-01-05 wearables_survey.tex
little tweaks in related work

@@
 Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors.
-Examples of such efforts include frameworks to design for privacy environments ~\cite{bellotti1993design} and evaluating ubiquitous computing applications ~\cite{scholtz2004toward}.
-There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model ~\cite{hong2004privacy} and a social-based model ~\cite{jiang2002approximate}.
+Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}.
+There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.
 
@@
 \subsection{Smartphones and Wearables Concerns}
-Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones ~\cite{chin2012measuring}, observe behaviors of new smartphone users ~\cite{palen2000going}, investigate user understanding of permissions ~\cite{felt2012android}.
+Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.
 

### 2015-01-05 wearables_survey.tex
minor changes in risk/ben section.

@@
 \subsubsection{Regression Model} 
-Introduce the model and what was considered in the model.
-Serge can probably do this better.
-Talk about which factors mattered, and how much, and also interesting statistics we found, if any.
-Also, correlations with demographics here as well!
+{\color{red} SERGE TODO: fill in this section.}
 
 \subsection{Risk and Benefit Rankings} 
-When assessing new technologies, participants generally had rated the technologies similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).
+When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).
 We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
@@
 
-{\color{red} can you redo the graph for figure ~\ref{fig:techplot}? I trust your judgement on how it should look and what to emphasize.}
+{\color{red} SERGE TODO: redo the graph for figure ~\ref{fig:techplot}.}
 

### 2015-01-06 wearables_survey.tex
Added the two Camp references into the related work section.

@@
 As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}.
-Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}.
+This is because the internet is ubiquitous but, have characteristics of a private space~\cite{camp2000internet}.
+Privacy in ubiquitous systems can be achieved by  identifying subtle trust assumptions of systems for design~\cite{camp2003designing} and adhering to privacy principles~\cite{langheinrich2001privacy}.
 An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.

### 2015-01-06 wearables_survey.tex
changed transitions in methodology intro

@@
 In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen.
-In another section of the survey, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
-In another section of the survey, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies.
+Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
+Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies.
 Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.

### 2015-01-06 wearables_survey.tex
missing %
fixed wrong order in open-response table

@@
 
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{|l|r|}
+%\hline
+%Recipients & VUR \\
+%\hline
+%App &  42.3\% \\
+%Friends & 69.5\% \\
+%Work & 75.2\% \\
+%Public & 72.4\% \\ 
+%\hline
+%\end{tabular}
+%\caption{generated for my presentation.}
+%\label{nouse}
+%\end{center}
+%\end{table}
+
 \begin{table}[t]
@@
 Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\ \\
+Being Unaware & 275 & 15.40\% \\
 %Unaware Use & 167 & (9.36\%)\\
@@
 Safety & 185 & 10.42\%\\
+Social Impact &	157 & 8.80\%\\
 Financial Cost & 151 & 8.46\%\\
 Security &	144 & 8.07\%\\
-Social Impact &	157 & 8.80\%\\
 Accidental Sharing &	69 & 3.87\%\\
@@
 
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as battery burns or distractions causing car accidents (Safety), the high financial cost of buying, replacing, or caring for the device (Financial),  information compromise (Security), and resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact).
+Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as battery burns or distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
 Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

### 2015-01-06 wearables_survey.tex
David's feedback for abstract and intro

@@
 
-\title{A Survey of Wearable Device Risk Perceptions}
+\title{Risk Perceptions for Wearable Devices}
 %\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
@@
    \vspace{0.5em}
-   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}\\
-   \affaddr{\textsuperscript{2}University of California, Berkeley, \{dlwndghk94\}@berkeley.edu}\\
+   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
    \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
@@
 We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology).
-We surveyed 1,784 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks.
+We examine different data types that might be captured,  and the effect of who the data is shared with.
+We surveyed 1,784 participants about 72 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
 Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
@@
 \section{Introduction}
+With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
 Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user.
-Wearbles are gaining a lot of attention.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one~\cite{NPD}.
+Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and one of the top 25 market research companies estimates that 52\% of technology consumers are aware of wearables and among those, 33\% said they were likely to buy one~\cite{NPD}.
 
-A survey of 3,956 respondents with high interest in wearables found that the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
+The market for wearable devices is currently in its infancy, so it is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
+A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
 It is estimated that 20\% of the general population own at least one wearable and 10\% use at least one wearable in their daily lives~\cite{WearableStatNews}.
-The demographics of wearables consumers are young and affluent--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year.
-However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop~\cite{cmo}.
+The demographics of wearables consumers are young: 48\% of owners are between 18 and 34 years old.
+However, it is expected that this \$700 million industry will reach other demographics~\cite{cmo}.
 
-Despite high early adoption rates, wearable device security and privacy concerns are rampant.
+Wearable devices bring with them some new potential security and privacy concerns.
 Many of these concerns relate to users' activities being exposed to the public without their awareness or consent.
 For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive user information.
-In other instances, public discomfort prevented companies from enabling certain capabilities; Google's Glass had facial recognition disabled upon release to mitigate potential privacy concerns~\cite{GlassDetection}.
+In other instances, public discomfort prevented companies from enabling certain capabilities; Google Glass apos are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
 
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand user concerns surrounding wearable devices---before wearables become increasingly ubiquitous and powerful~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies alike to focus on the most concerning factors for the user---allowing research for effective warnings of relevant events and an informed focus of protecting the most sensitive data.
+To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand user concerns surrounding wearable devices before wearables become increasingly ubiquitous and powerful~\cite{Implants}.
+A better understanding of users' risk perceptions will enable researchers and companies to focus on users' greatest concerns.
+The goal of this paper is to gain a better sense of what those concerns might be.
 
-To this end, we surveyed 1,784 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]
+To this end, we surveyed 1,784 Internet users to determine their risk perceptions regarding wearable devices. In this work, we contribute the following: \\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a wide range of privacy and security risks surrounding wearable devices. In general, users care much more about the recipient of the data, than the type of data.
+\item We compare users' perceptions of a wide range of privacy and security risks with wearable devices. Users care much more about the recipient of the data, than the type of data.
 \item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item While our participants viewed the data-collection capabilities of wearable devices as benign relative to more accepted technologies, we hypothesize that this is due to their lack of exposure to these newer technologies.
+\item Our participants viewed the data-collection capabilities of wearable devices as benign compared to more accepted technologies.
+However, we suspect that this may be due to their lack of exposure to these newer technologies.
 %\item We report people's self-reported top concerns for wearable devices.

### 2015-01-06 wearables_survey.tex
Started adding regression model

--- 2015-01-06 wearables_survey.tex
@@
 \subsubsection{Regression Model} 
-{\color{red} SERGE TODO: fill in this section.}
+In order to examine the relative effect of each factor on participants' VURs, we constructed a statistical model to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
+We performed a binary logistic regression using generalized estimating equations, which accounts for our repeated measures experimental design (i.e., each participant contributed multiple data points).
 

### 2015-01-07 wearables_survey.tex
Added demographics

@@
 
+\subsubsection{Demographic Factors}
+
+We observed that participants' responses to our scenarios were correlated with several demographic factors.
+First, we observed that by far the biggest factor in participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the fraction of scenarios that each participant reported as being very upsetting ($\rho=0.446$, $p<0.0005$).
+Similarly, we observed that age was also a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
+We suspect that the age effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$), as others have also observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
+
+While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
+60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
+Finally, we observed no correlation between education level and VUR.
+
 \subsubsection{Regression Model} 

### 2015-01-07 wearables_survey.tex

@@
 \subsection{Ubiquitous Sensing}
-Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
+Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
 Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors.

### 2015-01-07 wearables_survey.tex
Started working on regression models

--- 2015-01-07 wearables_survey.tex
@@
 \subsubsection{Regression Model} 
-In order to examine the relative effect of each factor on participants' VURs, we constructed a statistical model to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed a binary logistic regression using generalized estimating equations, which accounts for our repeated measures experimental design (i.e., each participant contributed multiple data points).
+In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
+We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
+Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
+
+\begin{table}
+\centering
+\begin{tabular}{|l| r|}
+\hline
+Variables Included & QIC\\
+\hline
+\hline
+(Intercept) & 18,539.3\\
+\hline
+Device Type & 18,122.9\\
+\hline
+Data Recipient & 17,383.6\\
+\hline
+IUIPC (covariate) & 17,725.6\\
+\hline
+Data Type & 14,794.5\\
+\hline
+Device Type & \\
+Data Recipient & \\
+Data Type & 13,942.9\\
+\hline
+Data Recipient & \\
+Data Type & 13,951.2\\
+\hline
+\end{tabular}
+\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.}
+\label{regression}
+\end{table}
 

### 2015-01-07 wearables_survey.tex
Wrote regression section

@@
 We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
 
@@
 \centering
-\begin{tabular}{|l| r|}
+\begin{tabular}{|l| r| r| r|}
 \hline
-Variables Included & QIC\\
+Parameters & $\chi^2$ & $df$ & QIC\\
 \hline
 \hline
-(Intercept) & 18,539.3\\
+(Intercept) & 255.0 & 1 & 18,477.5\\
 \hline
-Device Type & 18,122.9\\
+(Intercept) & 78.4 & 1 & 18,122.9\\
+Device Type & 400.3 & 1 & \\
 \hline
-Data Recipient & 17,383.6\\
+(Intercept) & 289.1 & 1 & 17,667.5\\
+IUIPC (covariate) & 368.5 & 1 & \\
 \hline
-IUIPC (covariate) & 17,725.6\\
+(Intercept) & 297.8 & 1 &17,383.6\\
+Data Recipient & 913.4 & 4 & \\
 \hline
-Data Type & 14,794.5\\
+(Intercept) & 374.6 & 1 & 14,794.5\\
+Data Type & 1,866.5 & 77 & \\
 \hline
-Device Type & \\
-Data Recipient & \\
-Data Type & 13,942.9\\
+(Intercept) & 303. & 1 & 13,942.9\\
+Device Type & 11.1 & 1 &  \\
+Data Recipient & 624.6 & 3 & \\
+Data Type & 1,961.2 & 76 &  \\
 \hline
-Data Recipient & \\
-Data Type & 13,951.2\\
+(Intercept) & 28.4 & 1 & 12,752.8 \\
+Device Type & 8.8 & 1 &  \\
+Data Recipient & 577.8 & 3 & \\
+Data Type & 1,752.1 & 76 & \\
+IUIPC (covariate) & 378.7 & 1 & \\
 \hline
 \end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.}
+\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
+The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
 \label{regression}
 \end{table}
+
+We created several models using our three dependent variables as factors: device type (smartphone vs.
+wearable), data recipient, and data type.
+We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
+For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
+Thus, we opted to remove the other covariates from our analysis.
+
+Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
+As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
+Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
 
@@
 
-\section{List of all <data>}
-{\color{red} Placeholder for space measuring.} \\[-.8cm]
-
-\begin{small}
-\begin{enumerate}\itemsep0pt \parskip0pt \parsep0pt
-  \item foo
-  \item bar
-   \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-  \item foo
-  \item bar
-\end{enumerate}
-\end{small}
-
 %\section{Risk and Benefit Rankings}

### 2015-01-07 wearables_survey.tex
Anonymized and removed last appendix

@@
 
+%\numberofauthors{1}
+%\author{
+% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
+%   \vspace{0.5em}
+%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
+%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+%}
+
 \numberofauthors{1}
 \author{
- \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
+ \alignauthor Anonymous\\
    \vspace{0.5em}
-   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+   \affaddr{Some Place}
 }
@@
 We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
-A list of the ranking of most risky and most beneficial technologies can be see in appendix \ref{sec:techrank}; the most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
-
-{\color{red} SERGE TODO: redo the graph for figure ~\ref{fig:techplot}.}
+The most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
 

### 2015-01-07 wearables_survey.tex
Spliced related work: Felt and Fischhoff in Methodology: Motivation (rough) and the rest of related work is after the Discussion section (also still rough).

@@
 
-\section{Related Work}
-In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
+\section{Methodology}
+%David TODO: add sentence about the methodology motivation in the overview paragraph. 
+Our survey consisted of multiple sections.
+In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen.
+Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
+Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies.
+Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
 
-\subsection{Ubiquitous Sensing}
-Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
-Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors.
-Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}.
-There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.
+%LL: this commented out for anonymity; can comment back in later.
+%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
 
-Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings.
-As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}.
-This is because the internet is ubiquitous but, have characteristics of a private space~\cite{camp2000internet}.
-Privacy in ubiquitous systems can be achieved by  identifying subtle trust assumptions of systems for design~\cite{camp2003designing} and adhering to privacy principles~\cite{langheinrich2001privacy}.
-An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
+%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
+The rest were put at the end of the paper, as you requested.
 
-\subsection{Smartphones and Wearables Concerns}
-Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.
+\subsection{ROUGH: Methodology Motivation} %LL: this text was previously inside related work
+{\color{red} Note: this section is a placeholder.
+Maybe we should put as a subsection inside the methodology section.
+TODO: reword so that these works seem not like related work, but as motivation for our methodology; i.e.
+``here are two methodologies from relevant work swe chose to use for reasons.'' We can also say that we extend their works.}
 
+\subsubsection{Smartphone User Concerns} %LL: this text was previously inside related work
 Among such studies, Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}.
@@
 
-Denning et.
-al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
-Bystanders expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables.
-While this research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.
-
-%~\cite{laurier2001people}: Why people say where they are during mobile phone calls
-
-\subsection{User Perceptions and Behaviors}
-
+\subsubsection{Technology Risk Perception} %LL: this text was previously inside related work
 Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}.
@@
 Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.
-Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.
-
-%I'm not sure that having a background on crowdsourcing is relevant, especially given the space limitations.
-Instead, you need WAY more related work on ubiquitous privacy concerns, as well as smartphone privacy concerns.
-There's also probably more general work on risk perceptions that should probably be cited.
-
-%\subsection{Crowdsourced User Studies}
-%Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}.
-While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S.
-population \cite{ross2010crowdworkers}\cite{kelley2010conducting}.
-Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S.
-public \cite{kang2014privacy}.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-Our survey consisted of multiple sections.
-In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen.
-Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
-Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies.
-Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
-
-%%% commented out for anonymity; can comment back in later.
-%The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
 
@@
 
+% LL: David, thanks for polishing up the related work!
+%LL: Related work put at the end upon David's Suggestion. Paper flow is much better. 
+\section{Related Work}
+In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
+
+\subsection{Ubiquitous Sensing}
+Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
+Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors.
+Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}.
+There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.
+
+Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings.
+As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}.
+This is because the internet is ubiquitous but, have characteristics of a private space~\cite{camp2000internet}.
+Privacy in ubiquitous systems can be achieved by  identifying subtle trust assumptions of systems for design~\cite{camp2003designing} and adhering to privacy principles~\cite{langheinrich2001privacy}.
+An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
+
+\subsection{Smartphones and Wearables Concerns}
+Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.
+
+Denning et.
+al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
+Bystanders expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables.
+While this research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.
+
+\subsection{User Perceptions and Behaviors}
+While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.
+Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.
+
 %The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
@@
 
-%COMMENTED OUT FOR ANONYMITY!!
+%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
 

### 2015-01-07 wearables_survey.tex
added more commented comments and inline comments

@@
 \section{Related Work}
-In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
+{\color{red} this section is still rough!
+David will redo.} In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
 

### 2015-01-07 wearables_survey.tex
Small tweak to wording.

@@
 Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which would be the basis for all questions on wearable computing risks.
+Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearable computing risks.
 We highlighted the capabilities of this device and described several use cases.

### 2015-01-07 wearables_survey.tex
Minor spelling fix

@@
 For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive user information.
-In other instances, public discomfort prevented companies from enabling certain capabilities; Google Glass apos are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
+In other instances, public discomfort prevented companies from enabling certain capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
 
@@
 TODO: reword so that these works seem not like related work, but as motivation for our methodology; i.e.
-``here are two methodologies from relevant work swe chose to use for reasons.'' We can also say that we extend their works.}
+``here are two methodologies from relevant work we chose to use for reasons.'' We can also say that we extend their works.}
 
@@
 a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
-Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+Using this methodology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
 
@@
 We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
-The most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
+The most risky and most beneficial technologies reveal the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
 
@@
 Notably, technologies perceived to be beneficial include location tracking and heart rate detection.
-Again, we believe this is the result of exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
+Again, we believe this is the result of exposure people have to these technologies--GPS or other location-based applications on smart phones and fitness trackers are the most popular type of wearable device.
 Technologies considered to be risky, such as a discrete camera and facial detection, seemed to be based on media exposure or general aversion to privacy invasion.

### 2015-01-07 wearables_survey.tex
added J's feedback: Risk and benefit assessment; clarification on teh 20 technologies and commenting out citation (we didn't pick the 20 techs because of Egelman's work, so it is distracting to put it in here, especially with related work athe end now)
oops; facial detection -> facial recognition in section Results: Risk and Benefit Rankings

--- 2015-01-07 wearables_survey.tex
@@
 Alongside the 4 well-established technologies, we asked participants to evaluate one of 20 possible technologies relevant to wearable computing: the Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
+Note that we ask about familiar new technologies such as the internet, general classes and specific artifacts of wearable devices, and a range of new capabilities.
+
+%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
+%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
 
@@
 Again, we believe this is the result of exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
-Technologies considered to be risky, such as a discrete camera and facial detection, seemed to be based on media exposure or general aversion to privacy invasion.
+Technologies considered to be risky, such as a discrete camera and facial recognition, seemed to be based on media exposure or general aversion to privacy invasion.
 However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.

### 2015-01-07 wearables_survey.tex
keywords: wearables -> wearable devices
Overhaul of Discussion: Future Research Directions.

@@
 
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearables} % NOT required for Proceedings
+\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
 
@@
 \subsection{Future Research Directions}
+Wearables are still in their infancy.
+Perceptions of situations and new capabilities will change rapidly with new capabilities and increased exposure, respectively.
+However, videos, and textual information is considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
+Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
 
-Our survey shows that photos, videos, and textual information is generally considered to be very sensitive.
-Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-We also show that users are significantly more willing to offer certain data if it will only be shared with the application; and additionally, that users consider privacy as their number-one concern.
-Research in effective sandboxing and other software protections, effective notifications, and usable indicators are encouraged at this time.
-Lastly, exploratory research investigating user-reported concerns, are relevant--especially the social impact of wearable devices, measurement of inaccuracy of sensor readings presented by wearables, and rate of accidental information sharing.
+While privacy and security concerns were expected, consider these unexpected user concerns as starting points for future research: the high financial costs of wearables, health concerns of constant device use, safety issues related to device operation, the social impact of wearable devices, and improving aesthetics of wearables.
 

### 2015-01-07 wearables_survey.tex
Reworded Discussion: Limitations

@@
 One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, so our study is reflective of the status quo.
+83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
 We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables.

### 2015-01-07 wearables_survey.tex
Starting a pass over Methodology.

--- 2015-01-07 wearables_survey.tex
@@
 \section{Methodology}
-%David TODO: add sentence about the methodology motivation in the overview paragraph. 
-Our survey consisted of multiple sections.
-In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen.
-Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones).
-Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies.
-Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
+
+Our survey contained two main sections.
+In one section, we presented participants with scenarios---something undesirable a wearable device might do---and asked them to rate their level of concern if each scenario were to happen.
+This was intended to elicit their perception of the severity of the impact of the risk.
+In the other section, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
+Our survey design is based on two prior risk perception studies, as we describe next.
+
+%Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
 

### 2015-01-07 wearables_survey.tex
Adding a bit on reference to prior studies.

@@
 
-\subsection{ROUGH: Methodology Motivation} %LL: this text was previously inside related work
-{\color{red} Note: this section is a placeholder.
-Maybe we should put as a subsection inside the methodology section.
-TODO: reword so that these works seem not like related work, but as motivation for our methodology; i.e.
-``here are two methodologies from relevant work swe chose to use for reasons.'' We can also say that we extend their works.}
+\subsection{ROUGH: Methodology Motivation}
 
-\subsubsection{Smartphone User Concerns} %LL: this text was previously inside related work
-Among such studies, Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}.
+\subsubsection{Smartphone User Concerns}
+Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
 Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
 Participants were asked how upset they would be if a certain action had occurred without their permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.
+Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
+Our methodology follows that study closely, but with a different set of scenarios that are appropriate to wearable devices.
 

### 2015-01-07 wearables_survey.tex
Reword description of Fischoff

@@
 
-\subsection{ROUGH: Methodology Motivation}
+\subsection{Methodology Motivation}
 
@@
 
-\subsubsection{Technology Risk Perception} %LL: this text was previously inside related work
-Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}.
-In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies.
-They were primed to think about all people affected by the technology, and to think about long-term vs.
+\subsubsection{Technology Risk Perception}
+Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
+In their study, participants were asked to separately rate the risks and benefits of these technologies.
+They were told to think about all people affected by the technology, and to think about long-term vs.
 short-term risks and benefits.
-The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e.
-a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
-Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
+We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
+
+%Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
 

### 2015-01-07 wearables_survey.tex
re-worded tech perceptiosn section

--- 2015-01-07 wearables_survey.tex
@@
 We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
-The most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
 
@@
 
-Notably, technologies perceived to be beneficial include location tracking and heart rate detection.
-Again, we believe this is the result of exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
-Technologies considered to be risky, such as a discrete camera and facial recognition, seemed to be based on media exposure or general aversion to privacy invasion.
-However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
+Participants rated the the most familiar technologies as the most beneficial (top 5: internet, laptops, email, smartphones, and location tracking).
+Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications.
+The most risky technologies were ones perceived to be privacy-invasive (bottom 5: facial recognition, internet, discreet video camera, location tracking, and facial detection).
+People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
 It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.

### 2015-01-07 wearables_survey.tex
more rewording for risk and benefit rankings

@@
 
-Participants rated the the most familiar technologies as the most beneficial (top 5: internet, laptops, email, smartphones, and location tracking).
+Participants rated the the most familiar technologies as the most beneficial; 5 most beneficial technologies were internet, laptops, email, smartphones, and location tracking.
 Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications.
-The most risky technologies were ones perceived to be privacy-invasive (bottom 5: facial recognition, internet, discreet video camera, location tracking, and facial detection).
+The most risky technologies were ones perceived to be privacy-invasive; 5 most risky technologies were facial recognition, internet, discreet video camera, location tracking, and facial detection.
 People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.

### 2015-01-07 wearables_survey.tex
Small tweaks to methodology

--- 2015-01-07 wearables_survey.tex
@@
 
-\subsubsection{Smartphone User Concerns}
+\subsubsection{Smartphone Risk Scenarios}
 Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
+Their survey asked 3,115 smartphone users about 99 risk scenarios.
 Participants were asked how upset they would be if a certain action had occurred without their permission.
 Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology follows that study closely, but with a different set of scenarios that are appropriate to wearable devices.
+Our methodology follows that study closely, but with a different set of scenarios chosen to shed light on security and privacy risks of wearable devices.
 
@@
 We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
+The most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).
 
@@
 
-Participants rated the the most familiar technologies as the most beneficial (top 5: internet, laptops, email, smartphones, and location tracking).
-Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications.
-The most risky technologies were ones perceived to be privacy-invasive (bottom 5: facial recognition, internet, discreet video camera, location tracking, and facial detection).
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
+Notably, technologies perceived to be beneficial include location tracking and heart rate detection.
+Again, we believe this is the result of exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device.
+Technologies considered to be risky, such as a discrete camera and facial recognition, seemed to be based on media exposure or general aversion to privacy invasion.
+However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
 It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.

### 2015-01-07 wearables_survey.tex
fixed couple technical errors, added comments inline in related work section

--- 2015-01-07 wearables_survey.tex
@@
 We compared the 10 most concerning scenarios when sharing with an app's servers versus with a human audience (friends, work contacts, and the public).
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same:
+We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
 
@@
 \item An incriminating/embarrassing photo of you
-\item A photo of you unclothed
+\item A photo of you unclothed \\[-.8cm]
 \end{packed_enum}
@@
 One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
+83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
 We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables.
@@
 \section{Related Work}
-{\color{red} this section is still rough!
-David will redo.} In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
+{\color{red} this section is still rough! David will redo.} 
+In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
 
 \subsection{Ubiquitous Sensing}
+{\color{red} this section is still rough! David will redo.} 
 Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
@@
 \subsection{Smartphones and Wearables Concerns}
+{\color{red} this section is still rough! David will redo.} 
 Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.
@@
 \subsection{User Perceptions and Behaviors}
+{\color{red} this section is still rough! David will redo.} 
 While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.

### 2015-01-07 wearables_survey.tex

--- 2015-01-07 wearables_survey.tex
@@
 
-%Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
 
@@
 \subsection{Risk and Benefit Rankings}
+
 When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).

### 2015-01-07 wearables_survey.tex
Added new figure

@@
 
-When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).
+When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (Figure \ref{fig:techplot}).
 We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{techplot.png}
-	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
+	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
+	\caption{Participants' risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearables (Google Glass and the Cubetastic3000).}
 	\label{fig:techplot}

### 2015-01-07 wearables_survey.tex
Added verbiage for risks/benefits

--- 2015-01-07 wearables_survey.tex
@@
 
-When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}).
-We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
-
-\begin{figure}
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=0.5\textwidth]{techplot.png}
-	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
+	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
+	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
 	\label{fig:techplot}
@@
 
-Participants rated the the most familiar technologies as the most beneficial; 5 most beneficial technologies were internet, laptops, email, smartphones, and location tracking.
-Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications.
-The most risky technologies were ones perceived to be privacy-invasive; 5 most risky technologies were facial recognition, internet, discreet video camera, location tracking, and facial detection.
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
-It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
+We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
+We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
+They did this alongside well-establish technologies studied by Fischhoff\etal\cite{Fischhoff}, which we used to calibrate our results.
+When assessing new technologies, participants generally rated all familiar technologies and those related to wearables as being low-risk.
+Figure \ref{fig:techplot} depicts participants' median ratings.
+We found that the calibration technologies were all rated as the most risky.
+At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
+
+As a group, participants rated the familiar technologies as the most beneficial.
+We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
+Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
+People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+
+At the same time, these perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits, but they do reflect the general public's present exposure to these technologies and also show that people do perceive specific risks and benefits.
+We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
+We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
 

### 2015-01-07 wearables_survey.tex
Small revisions to Methodology

@@
 Our survey contained two main sections.
-In one section, we presented participants with scenarios---something undesirable a wearable device might do---and asked them to rate their level of concern if each scenario were to happen.
+In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
 This was intended to elicit their perception of the severity of the impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
+In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
 Our survey design is based on two prior risk perception studies, as we describe next.
 
-%Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
+%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
 
@@
 We presented participants with a second set of scenarios in order to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]
+These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+We randomly presented each participant with 2 of the following 5 questions: \\[-.8cm]
 
@@
 \subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies, and how those perceptions compared to other well-established technologies.
-To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to relatively rank several technologies by both their risk and benefit to society.
+In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies and how those perceptions compared to other well-established technologies.
+To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society.
 We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.

### 2015-01-07 wearables_survey.tex
Editing on analysis method.

@@
 
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than the average of all Likert scores.
-We did this for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
+In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
+The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
+We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
 Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is if they were maximally upset or not, rather than how upset they were.
+Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
+
 In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
 Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses and had an initial agreement rate of 89.7\%.
-The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
+Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
+The researchers discussed any disagreements and resolved them so that the final codings reflect unanimous agreement.
 

### 2015-01-07 wearables_survey.tex
put data type subsection before recipent subsection

--- 2015-01-07 wearables_survey.tex
@@
 
-\subsubsection{Smartphone Risk Scenarios}
+\subsubsection{Smartphone User Concerns}
 Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
+Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges.
 Participants were asked how upset they would be if a certain action had occurred without their permission.
 Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology follows that study closely, but with a different set of scenarios chosen to shed light on security and privacy risks of wearable devices.
+Our methodology follows that study closely, but with a different set of scenarios that are appropriate to wearable devices.
 
@@
 We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of these factors, including demographic traits.
+
+\subsubsection{Data Type}
+Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
+The 10 most and least concerning data types can be seen in Table \ref{top10}.
+
+The least concerning data types were all related in that they all consisted of information that could be observed through observations of public behavior.
+For instance, demographic information (e.g., age, gender, language spoken).
+It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| r | l | r |}
+\hline
+Rank & Data &  VUR  \\
+\hline
+1 & a video of you unclothed & 95.97\% \\
+2 & bank account information & 95.91\% \\
+3 & social security number & 94.84\% \\
+4 & video of you entering in your PIN & 92.67\% \\
+5 & a photo of you unclothed & 92.59\% \\
+6 & an incriminating/embarrassing photo of you & 91.39\% \\
+7 & username and password for websites & 89.55\% \\
+8 & credit card information & 88.98\% \\
+9 & an incriminating/embarrassing video of you & 88.41\% \\
+10 & a random (inward-facing) photo you at home & 87.50\% \\
+ & \vdots & \\
+64 & eye movement patterns (for eye tracking) & 40.51\% \\
+65 & when and how much you exercise  & 38.66\% \\
+66 & when you are happy or having fun  & 34.75\% \\
+67 & which television shows you watch & 30.20\% \\
+68 & when you are busy or interruptible  & 29.50\% \\
+69 & music from your device  & 28.06\% \\
+70 & your heart rate & 27.50\% \\
+71 & your age & 24.29\% \\
+72 & the language you speak & 15.86\% \\
+73 & your gender & 15.00\% \\ 
+\hline
+\end{tabular}
+\caption{The 10 most and least upsetting data types, across all recipients.}
+\label{top10}
+\end{center}
+\end{table}
+
+%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
+We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
 
@@
 
-\subsubsection{Data Type}
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-The 10 most and least concerning data types can be seen in Table \ref{top10}.
-
-The least concerning data types were all related in that they all consisted of information that could be observed through observations of public behavior.
-For instance, demographic information (e.g., age, gender, language spoken).
-It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
 \subsubsection{Device Type}
@@
 
-\begin{figure}[t]
+When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (Figure \ref{fig:techplot}).
+We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.
+
+\begin{figure}
 	\centering
 	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
+	\caption{Participants' risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearables (Google Glass and the Cubetastic3000).}
 	\label{fig:techplot}
@@
 
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-They did this alongside well-establish technologies studied by Fischhoff\etal\cite{Fischhoff}, which we used to calibrate our results.
-When assessing new technologies, participants generally rated all familiar technologies and those related to wearables as being low-risk.
-Figure \ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-At the same time, these perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits, but they do reflect the general public's present exposure to these technologies and also show that people do perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
+Participants rated the the most familiar technologies as the most beneficial; 5 most beneficial technologies were internet, laptops, email, smartphones, and location tracking.
+Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications.
+The most risky technologies were ones perceived to be privacy-invasive; 5 most risky technologies were facial recognition, internet, discreet video camera, location tracking, and facial detection.
+People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower.
+It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
 

### 2015-01-07 wearables_survey.tex
rough todo to emphasize data type more in the paper.

--- 2015-01-07 wearables_survey.tex
@@
 
+\subsubsection{Data Type}
+blah emph: this matters most  blaaah. The 10 most and least concerning data types can be seen in Table \ref{top10}.
+
+%%add in stats on top 10, 20, bottom 10, 20.
+Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
+
+The least concerning data types were all related in that they all consisted of information that could be observed through observations of public behavior.
+For instance, demographic information (e.g., age, gender, language spoken).
+It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
+
+I need Michael's auto screen lock technology.
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| r | l | r |}
+\hline
+Rank & Data &  VUR  \\
+\hline
+1 & a video of you unclothed & 95.97\% \\
+2 & bank account information & 95.91\% \\
+3 & social security number & 94.84\% \\
+4 & video of you entering in your PIN & 92.67\% \\
+5 & a photo of you unclothed & 92.59\% \\
+6 & an incriminating/embarrassing photo of you & 91.39\% \\
+7 & username and password for websites & 89.55\% \\
+8 & credit card information & 88.98\% \\
+9 & an incriminating/embarrassing video of you & 88.41\% \\
+10 & a random (inward-facing) photo you at home & 87.50\% \\
+ & \vdots & \\
+64 & eye movement patterns (for eye tracking) & 40.51\% \\
+65 & when and how much you exercise  & 38.66\% \\
+66 & when you are happy or having fun  & 34.75\% \\
+67 & which television shows you watch & 30.20\% \\
+68 & when you are busy or interruptible  & 29.50\% \\
+69 & music from your device  & 28.06\% \\
+70 & your heart rate & 27.50\% \\
+71 & your age & 24.29\% \\
+72 & the language you speak & 15.86\% \\
+73 & your gender & 15.00\% \\ 
+\hline
+\end{tabular}
+\caption{The 10 most and least upsetting data types, across all recipients.}
+\label{top10}
+\end{center}
+\end{table}
+
+%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
+We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
+
 \subsubsection{Data Recipient}
-Based on our data, we observed that the largest effect seemed to stem from who the recipient of the data was: across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
+Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
 A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
@@
 
-What is interesting about this finding is that while the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
+While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
 For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
@@
 However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Data Type}
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-The 10 most and least concerning data types can be seen in Table \ref{top10}.
-
-The least concerning data types were all related in that they all consisted of information that could be observed through observations of public behavior.
-For instance, demographic information (e.g., age, gender, language spoken).
-It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
 
@@
 %\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
+%\appendix
+%%Appendix A
+%\section{Fischhoff Prompts}
+%\label{sec:prompt} 
+%
+%\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
+%
+%{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
 (e.g.
 for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
+%
+%\textit{Do not consider the costs or risks associated with these items.
 It is true, for example, that sometimes swimmers can drown.
@@
 Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
+%
+%\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
@@
 (For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
+%
+%{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
 (e.g.
 for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
+%
+%\textit{Do not consider the costs or benefits associated with these items.
 It is true, for example, that electricity also creates a market for home appliances.
@@
 Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
+%
+%\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.

### 2015-01-07 wearables_survey.tex
got rid of "I need Michael's screen lock technology."
ha, ha, I left my computer open. I have mischevious friends.
redid the data type section to reflect that it is most important

@@
 \subsubsection{Data Type}
-blah emph: this matters most  blaaah. The 10 most and least concerning data types can be seen in Table \ref{top10}.
+Based on our data, we observed that the largest effect stemmed from the type of data being shared in a given scenario.
+We present various statistical models in section \ref{sec:regression} to support this conclusion.
+Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
+The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
 
-%%add in stats on top 10, 20, bottom 10, 20.
 Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
 Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
 
-The least concerning data types were all related in that they all consisted of information that could be observed through observations of public behavior.
+Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior.
 For instance, demographic information (e.g., age, gender, language spoken).
 It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-I need Michael's auto screen lock technology.
 
@@
 
-\subsubsection{Regression Model} 
+\subsubsection{Regression Models} 
+\label{sec:regression}
 In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
@@
 \subsection{Risk and Benefit Rankings} 
-
 \begin{figure}[t]

### 2015-01-07 wearables_survey.tex
Some edits to related work.

@@
 
-% LL: David, thanks for polishing up the related work!
-%LL: Related work put at the end upon David's Suggestion. Paper flow is much better. 
 \section{Related Work}
-{\color{red} this section is still rough! David will redo.} 
-In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.
+In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
 
 \subsection{Ubiquitous Sensing}
-{\color{red} this section is still rough! David will redo.} 
-Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices.
-Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors.
-Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}.
-There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.
-
-Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings.
-As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}.
-This is because the internet is ubiquitous but, have characteristics of a private space~\cite{camp2000internet}.
-Privacy in ubiquitous systems can be achieved by  identifying subtle trust assumptions of systems for design~\cite{camp2003designing} and adhering to privacy principles~\cite{langheinrich2001privacy}.
-An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
+Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Many researchers have worked to study how privacy can be preserved in such a future.
+Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
+Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
+However, none of these works attempted to quantify or rank user concern over different privacy risks.
 
 \subsection{Smartphones and Wearables Concerns}
-{\color{red} this section is still rough! David will redo.} 
-Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.
+Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
 
-Denning et.
-al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}.
-Bystanders expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables.
-While this research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.
+Recently Denning et.
+al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
+Participants in their study expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables.
+While their research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.
 

### 2015-01-08 wearables_survey.tex
deleting spaces in the .tex file, no changes to content.
maybe we have space for the fischoff prompt in the appendix

@@
 \maketitle
-
 \begin{abstract}
@@
 \subsection{Methodology Motivation}
-
 \subsubsection{Smartphone Risk Scenarios}
@@
 %\balancecolumns
-%\appendix
-%%Appendix A
-%\section{Fischhoff Prompts}
-%\label{sec:prompt} 
-%
-%\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-%
-%{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
+\appendix
+%Appendix A
+\section{Fischhoff Prompts}
+\label{sec:prompt}
+
+\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
+
+{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
 (e.g.
 for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-%
-%\textit{Do not consider the costs or risks associated with these items.
+
+\textit{Do not consider the costs or risks associated with these items.
 It is true, for example, that sometimes swimmers can drown.
@@
 Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-%
-%\textit{Please rate the following technologies below with a number.
+
+\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
@@
 (For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-%
-%{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
+
+{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
 (e.g.
 for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-%
-%\textit{Do not consider the costs or benefits associated with these items.
+
+\textit{Do not consider the costs or benefits associated with these items.
 It is true, for example, that electricity also creates a market for home appliances.
@@
 Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-%
-%\textit{Please rate the following technologies below with a number.
+
+\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.

### 2015-01-08 wearables_survey.tex
wordsmithing on page1,2

@@
 We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 72 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps to protect sensitive data and guides the design of effective privacy notifications and indicators.
+We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
+Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
+The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
 \end{abstract}
@@
 
-Wearable devices bring with them some new potential security and privacy concerns.
+Wearable devices bring with them new potential security and privacy concerns.
 Many of these concerns relate to users' activities being exposed to the public without their awareness or consent.
@@
 
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand user concerns surrounding wearable devices before wearables become increasingly ubiquitous and powerful~\cite{Implants}.
+To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
 A better understanding of users' risk perceptions will enable researchers and companies to focus on users' greatest concerns.
@@
 In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity of the impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
+This was intended to elicit their perception of the severity and impact of the risk.
+In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
 Our survey design is based on two prior risk perception studies, as we describe next.
@@
 \item The public
-\item The app's server (but didn't share it with anyone else)
+\item The app's server (but didn't share it with anyone else)\\[-.8cm]
 \end{packed_item}

### 2015-01-08 wearables_survey.tex
added figure for cubetastic qiestion

@@
 \subsubsection{Wearables Scenarios}
-We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first.
+We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first (see Figure \ref{fig:prompt}).
 All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
@@
 The 4 possible data recipients were: \\[-.8cm]
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.47\textwidth]{prompt.pdf}
+	\caption{An example of a wearable scenario question participants saw while taking the survey.}
+	\label{fig:prompt}
+\end{figure}
 

### 2015-01-08 wearables_survey.tex
formatting and wordsmithing commences: Wearables Scenarios section

@@
 \subsubsection{Wearables Scenarios}
-We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first (see Figure \ref{fig:prompt}).
-All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>).
-The 4 possible data recipients were: \\[-.8cm]
+We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
+Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
+Our questions were of the format:
+
+\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+
+We created an initial pool of 304 questions by combining 88 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
 

### 2015-01-08 wearables_survey.tex
lots of wordsmithing

@@
 Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and one of the top 25 market research companies estimates that 52\% of technology consumers are aware of wearables and among those, 33\% said they were likely to buy one~\cite{NPD}.
+Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
 
@@
 To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' greatest concerns.
-The goal of this paper is to gain a better sense of what those concerns might be.
+A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
+The goal of this paper is to gain a better sense of what those concerns are.
 
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a wide range of privacy and security risks with wearable devices. Users care much more about the recipient of the data, than the type of data.
+\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
 \item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed the data-collection capabilities of wearable devices as benign compared to more accepted technologies.
-However, we suspect that this may be due to their lack of exposure to these newer technologies.
+\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
+However, we suspect that this may be due to a lack of exposure to these newer technologies.
 %\item We report people's self-reported top concerns for wearable devices.
@@
 Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without their permission.
+Participants were asked how upset they would be if a certain action had occurred without permission.
 Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology follows that study closely, but with a different set of scenarios chosen to shed light on security and privacy risks of wearable devices.
+Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
 
@@
 Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits of these technologies.
+In their study, participants were asked to separately rate the risks and benefits for those technologies.
 They were told to think about all people affected by the technology, and to think about long-term vs.
 short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
+Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
 We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
@@
 
-We randomized the order in which participants completed each section of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of the questions within each section.
+We randomized the order participants completed sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
 
@@
 
-We created an initial pool of 304 questions by combining 88 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
+We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
 
@@
 \label{sec:smartphones}
-We presented participants with a second set of scenarios in order to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of the following 5 questions: \\[-.8cm]
+We presented participants with a second set of scenarios to control for the type of device being used.
+These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
 
@@
 \subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we also examined broad perceptions of various new technologies and how those perceptions compared to other well-established technologies.
-To this end, we modeled this section of the survey after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society.
+In addition to investigating reactions to particular scenarios, we also examined broad perceptions of new technologies and how those perceptions compared to other understood technologies.
+To this end, we modeled this section after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society.
 We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
@@
 \subsubsection{Additional Questions}
-The exit portion of the survey consisted of standard demographics questions such as age, gender, and education.
-We also asked participants if they owned a wearable device so that we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-Finally, we included the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so that we could control for participants' general privacy attitudes.
+The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
+Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
+We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
 
@@
 We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above.
+We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
@@
 \subsection{Concern Factors}
-In this section, we discuss the factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable device or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of these factors, including demographic traits.
+In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
+We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
 
 \subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the type of data being shared in a given scenario.
+Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
 We present various statistical models in section \ref{sec:regression} to support this conclusion.
@@
 
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior.
-For instance, demographic information (e.g., age, gender, language spoken).
-It is possible that people rated some of these as unconcerning because they believed that many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
+Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
+It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
 
@@
 A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were relatively small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
+However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
 
-We note that this chi-square test violates the assumption of independence of observations, since each participant responded to multiple scenarios.
-However, based on the randomization of treatments and very large sample size, we do not believe that this impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and found that the test was robust to this violation: participants were significantly more concerned about having their data seen by actual humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups were not significant (i.e., between the public, friends, and work contacts).
+We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
+But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
+Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
+Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
 
@@
 
-We compared the 10 most concerning scenarios when sharing with an app's servers versus with a human audience (friends, work contacts, and the public).
+We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
 We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
@@
 \subsubsection{Device Type}
-Participants had unique VUR rates for situations only differing in the device.
-Our participants had a 58.79\% VUR when asked about wearables devices and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
+Participants had unique VUR rates for scenarios only differing in device.
+Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
 However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
@@
 The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.
+Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
 
@@
 
-We observed that participants' responses to our scenarios were correlated with several demographic factors.
-First, we observed that by far the biggest factor in participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the fraction of scenarios that each participant reported as being very upsetting ($\rho=0.446$, $p<0.0005$).
+Participants' responses to scenarios were correlated with several demographic factors.
+First, we observed the biggest predictor, by far, of participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
 Similarly, we observed that age was also a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the age effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$), as others have also observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
+We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
 
@@
 
-At the same time, these perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits, but they do reflect the general public's present exposure to these technologies and also show that people do perceive specific risks and benefits.
+These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
+However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
 We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
@@
 \subsection{Perceived Concerns for Wearable Devices}
-So far, participants had responded to questions regarding specific scenarios or assessed technologies presented to them.
-For completeness of the survey, we also wanted to capture the participants' general reactions to wearable devices as a whole.
-To do this, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices.
+We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
 
@@
 
-This question was asked along with the demographics questions, near the end of the survey, but before any IUIPC questions regarding privacy, to avoid biasing.
+This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
 The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
 
-Without any doubt, the open-ended responses state that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more:
+Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
+This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
+Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
 
-\begin{table}[h]
+\begin{table}[t]
 \begin{center}
@@
 \caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{open-responses}
+\label{openresponses}
 \end{center}
 \end{table}
-
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as battery burns or distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.
 
@@
 \section{Discussion}
-We take this section to discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
+Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
 
 \subsection{Future Research Directions}
-Wearables are still in their infancy.
-Perceptions of situations and new capabilities will change rapidly with new capabilities and increased exposure, respectively.
-However, videos, and textual information is considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which can detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
+Wearables are still in infancy.
+Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
+However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
+Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
 
-While privacy and security concerns were expected, consider these unexpected user concerns as starting points for future research: the high financial costs of wearables, health concerns of constant device use, safety issues related to device operation, the social impact of wearable devices, and improving aesthetics of wearables.
+While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
 
 \subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities.
+One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
 83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables.
-However, that will also have its own bias and limitations as well, since they would not reflect the general population.
+We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
+However, that will also have its own biases and limitations, since this does not reflect the general population.
 We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
@@
 al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables.
-While their research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.
+Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
+While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
 

### 2015-01-08 wearables_survey.tex
wordsmithing

@@
 
-The market for wearable devices is currently in its infancy, so it is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
+The market for wearable devices is currently in infancy.
+It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
 A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population own at least one wearable and 10\% use at least one wearable in their daily lives~\cite{WearableStatNews}.
-The demographics of wearables consumers are young: 48\% of owners are between 18 and 34 years old.
-However, it is expected that this \$700 million industry will reach other demographics~\cite{cmo}.
+It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
+Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
 
 Wearable devices bring with them new potential security and privacy concerns.
-Many of these concerns relate to users' activities being exposed to the public without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive user information.
-In other instances, public discomfort prevented companies from enabling certain capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
+Many concerns exposure of users' activities without their awareness or consent.
+For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
+Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
 
@@
 
-To this end, we surveyed 1,784 Internet users to determine their risk perceptions regarding wearable devices. In this work, we contribute the following: \\[-0.8cm]
+We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
 
@@
 In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior risk perception studies, as we describe next.
+Our survey design is based on two prior perception studies, as we describe next.
 
@@
 
-We randomized the order participants completed sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
+We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
 
 \subsubsection{Comprehension Questions}
-Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearable computing risks.
-We highlighted the capabilities of this device and described several use cases.
-To ensure that participants had read and understood this device's capabilities, we presented them with two multiple-choice comprehension questions.
+Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
+Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
+We highlighted the capabilities of this device and described use cases.
+To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
 
@@
 
-The main purpose of these questions was to determine the extent to which the data type and data recipient played a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we thought were relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' Thus, there were a total of 304 questions in this set, from which we randomly presented each participant with 6 questions.
+The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
+Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
+An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
 
@@
 \subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we also examined broad perceptions of new technologies and how those perceptions compared to other understood technologies.
-To this end, we modeled this section after the seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which they asked participants to rank several technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
-We chose these technologies because they represented varying levels of risks and benefits.
+In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
+We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
+We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
 
-Alongside the 4 well-established technologies, we asked participants to evaluate one of 20 possible technologies relevant to wearable computing: the Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-Note that we ask about familiar new technologies such as the internet, general classes and specific artifacts of wearable devices, and a range of new capabilities.
+Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
+We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
 

### 2015-01-08 wearables_survey.tex
Small tweak to related work

@@
 {\color{red} this section is still rough! David will redo.} 
-While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.
+One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.
 Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.

### 2015-01-08 wearables_survey.tex
Finish my pass through the related work section.

@@
 \subsection{User Perceptions and Behaviors}
-{\color{red} this section is still rough! David will redo.} 
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}.
-Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.
+In this paper we focus on measuring people's perceptions of security and privacy risks.
+One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
 

### 2015-01-08 wearables_survey.tex
Small changes to Section 3.2

@@
 We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-They did this alongside well-establish technologies studied by Fischhoff\etal\cite{Fischhoff}, which we used to calibrate our results.
-When assessing new technologies, participants generally rated all familiar technologies and those related to wearables as being low-risk.
-Figure \ref{fig:techplot} depicts participants' median ratings.
+To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
+We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
+Figure~\ref{fig:techplot} depicts participants' median ratings.
 We found that the calibration technologies were all rated as the most risky.

### 2015-01-08 wearables_survey.tex
wordsmithing for linebreaks

--- 2015-01-08 wearables_survey.tex
@@
 
-In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not heavily impacted by outliers.
-Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed any disagreements and resolved them so that the final codings reflect unanimous agreement.
+In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+Rather, we report medians and quartiles, which are not impacted by outliers.
+For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
+The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
 
@@
 For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.
+This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
 
@@
 
-Participants' responses to scenarios were correlated with several demographic factors.
-First, we observed the biggest predictor, by far, of participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was also a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
+Participants' responses were correlated with demographic factors.
+We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
+Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
 We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.

### 2015-01-08 wearables_survey.tex
finished final linebreak edits
Primal's feedbackgit add wearables_survey.tex! added in distribution of 1,2,3,4,5; VUR rate -> VUR; Device type -> data. No room for extra source he suggested.

@@
 The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
+We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
+Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654).
+Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
 
@@
 In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
+We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
 Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
@@
 
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
+\subsubsection{Device}
+Participants had unique VURs for scenarios only differing in device.
+Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
 However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
@@
 \begin{center}
-\begin{tabular}{|l|r|r|r|r|}
+\begin{tabular}{|c|r|r|r|r|}
 %Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
@@
 (Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
+Device & 400.3 & 1 & \\
 \hline
@@
 (Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
+Device & 11.1 & 1 &  \\
 Data Recipient & 624.6 & 3 & \\
@@
 (Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
+Device  & 8.8 & 1 &  \\
 Data Recipient & 577.8 & 3 & \\
@@
 
-We created several models using our three dependent variables as factors: device type (smartphone vs.
+We created several models using our three dependent variables as factors: device (smartphone vs.
 wearable), data recipient, and data type.
@@
 As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
+Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
 
@@
 
-\subsection{Perceived Concerns for Wearable Devices}
+\subsection{Self-Reported Concerns for Wearables}
 We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
@@
 The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
+\\
 
@@
 We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
+Participants how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
 We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.

### 2015-02-20 appendixes.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
 \appendix
-%Appendix A
 \section{Fischhoff Prompts}
@@
 
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
+\section{Coding Label Definitions}
+\label{sec:coding}
 
-%\section{Detailed Tech Rankings}
+Privacy: ``privacy,'' revealing personal information, spying. \\
+Security:  ``security,'' compromise, malware, hacking. \\
+GPS tracking: ``location,'' ``GPS,'' being monitored.
 
-\balancecolumns
+Unaware use: using data without permission or in a different way than understood by user. \\
+Unaware collection: collecting data without permission. \\
+Unaware access: disclosure of data without permission. \\
+False information: inaccurate or maliciously false data.
 
-% That's all folks!
-\end{document}
-\\
+Health Risk: radiation, cancer, or long-term effects.\\
+Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
+Discomfort: eye strain, headache, obscured vision, irritation. \\
+Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
+Theft: the device getting stolen.
+
+Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
+Social Stigma: judgment, hate, or bystander discomfort.\\ 
+Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky.
+
+Miscellaneous: odd comments, uncommon concerns. \\
+None: ``None,'' no threat, perceiving no big concerns \\
+Don't know: ``do not know,'' hinting at confusion \\
+Don't care: `` do not care,'' nonchalant answers

### 2015-02-20 conclusion.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654).
-Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusion}
@@
 
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
+%commented out for anonymity
 
@@
 Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-02-20 intro.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
@@
 \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-02-20 methodology.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
 \section{Methodology}
@@
 Our survey design is based on two prior perception studies, as we describe next.
-
 %Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
 
@@
 We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
 %Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
@@
 	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
+	\includegraphics[width=0.47\textwidth]{images/prompt.pdf}
 	\caption{An example of a wearable scenario question participants saw while taking the survey.}
@@
 The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-02-20 paper.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
-
 \usepackage{color}
-
-%%% still need to break urls
-
 \usepackage[hyphens]{url}
@@
 \def\etal{{\it et al.~}}
-
 \newenvironment{packed_enum}{
@@
 }{\end{enumerate}}
-
 \newenvironment{packed_item}{
@@
 
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
+\input{title.tex}
+\input{abstract.tex}
+\input{intro.tex}
+\input{methodology.tex}
+\input{results.tex}
+\input{discussion.tex} 
+\input{related_work.tex} 
+\input{conclusion.tex} 
+\bibliographystyle{abbrv}
+\bibliography{bibliography.bib} 
+\input{appendixes.tex}
 
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
 \end{document}
-\\

### 2015-02-20 related_work.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
 \section{Related Work}
@@
 Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-02-20 results.tex
cleanup

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654).
-Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
 \section{Results}
@@
 	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
+	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
 	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
@@
 \end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-02-24 untitled folder 2/app.tex
histograms
histograms

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
\hline
 Rank & Q &  VUR & Distribution  \\ 
\hline
1 & Learnedthelanguageyouwerespeaking & 2.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedthelanguageyouwerespeakingAPPSERVER} \\ \hline 
2 & Learnedwhenhowmuchandwhatyouareeating & 12.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenhowmuchandwhatyouareeatingAPPSERVER} \\ \hline 
3 & Learnedyourheartrate & 9.09\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourheartrateAPPSERVER} \\ \hline 
4 & Learnedyourage & 14.29\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourageAPPSERVER} \\ \hline 
5 & Learnedwhenyouarebusyorinterruptible & 17.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouarebusyorinterruptibleAPPSERVER} \\ \hline 
6 & Learnedhowmuchyouuseyourphone & 15.79\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchyouuseyourphoneAPPSERVER} \\ \hline 
7 & Learnedyourfingerprintsomehow & 55.32\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourfingerprintsomehowAPPSERVER} \\ \hline 
8 & Learnedwhereyouarecurrentlygoing & 35.29\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyouarecurrentlygoingAPPSERVER} \\ \hline 
9 & Recordedyourworkconversations & 53.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourworkconversationsAPPSERVER} \\ \hline 
10 & Learnedwhoyouwerespendingtimewith & 31.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhoyouwerespendingtimewithAPPSERVER} \\ \hline 
11 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosyoudownloadedontheinternetsavedonyourdeviceAPPSERVER} \\ \hline 
12 & Learnedwhenyouwerehappyorhavingfun & 24.32\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouwerehappyorhavingfunAPPSERVER} \\ \hline 
13 & Tookavideoofyouunclothed & 90.63\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouunclothedAPPSERVER} \\ \hline 
14 & Trackedwhereyouare(Likeagps) & 25.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../trackedwhereyouare(likeaGPS)APPSERVER} \\ \hline 
15 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 38.3\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofpeople(withanoutward-facingcamera)atrandomAPPSERVER} \\ \hline 
16 & Learnedyourcreditcardinformation & 65.52\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourcreditcardinformationAPPSERVER} \\ \hline 
17 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 30.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../trackedwhereyouareveryaccurately(whereyouareinaroom)APPSERVER} \\ \hline 
18 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 13.79\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowcloseyouaretootherpeopleyouinteractwithAPPSERVER} \\ \hline 
19 & Learnedwhenyouwerelyingnervousorstressed & 41.46\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouwerelyingnervousorstressedAPPSERVER} \\ \hline 
20 & Copiedanduploadedmusicfromyourdevice & 20.83\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedmusicfromyourdeviceAPPSERVER} \\ \hline 
21 & Sharedvideosotherssentyousavedonyourdevice & 30.56\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosotherssentyousavedonyourdeviceAPPSERVER} \\ \hline 
22 & Learnedyoursocialsecuritynumber & 88.68\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyoursocialsecuritynumberAPPSERVER} \\ \hline 
23 & Learnedwhereyouworksomehow & 46.34\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyouworksomehowAPPSERVER} \\ \hline 
24 & Learnedwhatmedicalconditionsyouhave & 40.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatmedicalconditionsyouhaveAPPSERVER} \\ \hline 
25 & Recordedyourpassingconversations & 55.88\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourpassingconversationsAPPSERVER} \\ \hline 
26 & Tookapictureofyoursignature & 59.26\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookapictureofyoursignatureAPPSERVER} \\ \hline 
27 & Learnedhowmuchyouuseyourcomputer & 28.57\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchyouuseyourcomputerAPPSERVER} \\ \hline 
28 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 71.88\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookanincriminatingvideoofyoudoingsomethingembarrassingAPPSERVER} \\ \hline 
29 & Tookavideoofyouoff-Guard & 53.85\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouoff-guardAPPSERVER} \\ \hline 
30 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedaudiorecordingsyoumadeonyourdeviceAPPSERVER} \\ \hline 
31 & Learnedyourusernameforwebsites & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourusernameforwebsitesAPPSERVER} \\ \hline 
32 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 38.1\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyoutalkingtoyourself(makingvoicenotes)APPSERVER} \\ \hline 
33 & Learnedhowmuchmoneyyouhave & 63.41\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchmoneyyouhaveAPPSERVER} \\ \hline 
34 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 18.92\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureAPPSERVER} \\ \hline 
35 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 22.58\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)APPSERVER} \\ \hline 
36 & Recordedyourphoneconversations & 56.67\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourphoneconversationsAPPSERVER} \\ \hline 
37 & Learnedhowmuchdebtyouhave & 59.46\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchdebtyouhaveAPPSERVER} \\ \hline 
38 & Learnedyourusernameandpasswordforwebsites & 64.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourusernameandpasswordforwebsitesAPPSERVER} \\ \hline 
39 & Learnedyourgender & 9.52\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourgenderAPPSERVER} \\ \hline 
40 & Sharedphotosyoutookwhicharealreadyonyourdevice & 27.27\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosyoutookwhicharealreadyonyourdeviceAPPSERVER} \\ \hline 
41 & Tookphotosatwork(Withanoutward-Facingcamera) & 62.16\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosatwork(withanoutward-facingcamera)APPSERVER} \\ \hline 
42 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 78.05\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookanincriminatingphotoofyoudoingsomethingembarrassingAPPSERVER} \\ \hline 
43 & Learnedyouraddress & 51.16\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyouraddressAPPSERVER} \\ \hline 
44 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouenteringinadigitalpasscodetoalockeddoorAPPSERVER} \\ \hline 
45 & Recordedthesoundaroundyou & 35.9\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedthesoundaroundyouAPPSERVER} \\ \hline 
46 & Tookavideoofyouenteringinyourpinatanatm & 88.57\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouenteringinyourPINatanATMAPPSERVER} \\ \hline 
47 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 28.13\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofpeople(withanoutward-facingcamera)atrandomAPPSERVER} \\ \hline 
48 & Learnedwhereyoulivesomehow & 40.63\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyoulivesomehowAPPSERVER} \\ \hline 
49 & Learnedwhattelevisionshowsyouwatch & 11.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhattelevisionshowsyouwatchAPPSERVER} \\ \hline 
50 & Tookaphotoofyouintoxicated & 53.13\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouintoxicatedAPPSERVER} \\ \hline 
51 & Tookvideosatwork(Withanoutward-Facingcamera) & 51.85\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosatwork(withanoutward-facingcamera)APPSERVER} \\ \hline 
52 & Learnedwhenandhowmuchyouspendtimealone & 35.48\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowmuchyouspendtimealoneAPPSERVER} \\ \hline 
53 & Learnedwhenyouaresickorhealthy & 26.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouaresickorhealthyAPPSERVER} \\ \hline 
54 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 6.98\% & \includegraphics[width = 2cm, height = 0.5cm]{../scannedyoureyetolearnyoureyepatterns(foreyetracking)APPSERVER} \\ \hline 
55 & Learnedwhatmedicationyoutake & 37.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatmedicationyoutakeAPPSERVER} \\ \hline 
56 & Learnedwhatwebsitesyougoto & 37.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatwebsitesyougotoAPPSERVER} \\ \hline 
57 & Learnedwhenandhowmuchyouhavesex & 73.08\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowmuchyouhavesexAPPSERVER} \\ \hline 
58 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 66.67\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)atrandomAPPSERVER} \\ \hline 
59 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 71.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)athomeAPPSERVER} \\ \hline 
60 & Tookaphotoofyouoff-Guard & 45.95\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouoff-guardAPPSERVER} \\ \hline 
61 & Learnedyourname & 32.56\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyournameAPPSERVER} \\ \hline 
62 & Learnedwhenandhowwellyouaresleeping & 21.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowwellyouaresleepingAPPSERVER} \\ \hline 
63 & Tookaphotoofyouunclothed & 77.78\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouunclothedAPPSERVER} \\ \hline 
64 & Tookavideoofyouintoxicated & 68.75\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouintoxicatedAPPSERVER} \\ \hline 
65 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 60.53\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)athomeAPPSERVER} \\ \hline 
66 & Learnedyourbankaccountinformation & 90.91\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourbankaccountinformationAPPSERVER} \\ \hline 
67 & Sharedphotosotherssenttoyousavedonyourdevice & 41.18\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosotherssenttoyousavedonyourdeviceAPPSERVER} \\ \hline 
68 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 32.14\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceAPPSERVER} \\ \hline 
69 & Learnedwhenhowandhowmuchyouexercise & 16.67\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenhowandhowmuchyouexerciseAPPSERVER} \\ \hline 
70 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 48.39\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)atrandomAPPSERVER} \\ \hline 
71 & Learnedwhatproductsyoubuy & 26.32\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatproductsyoubuyAPPSERVER} \\ \hline 
72 & Sharedvideosyoutookwhicharealreadyonyourdevice & 51.61\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosyoutookwhicharealreadyonyourdeviceAPPSERVER} \\ \hline 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-02-24 untitled folder 2/test.tex
histograms
histograms

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
+\documentclass[a4paper,12pt]{article}
+\usepackage[cm]{fullpage}
 \begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
 
@@
 \small
-\begin{tabular}{| r | l | r |}
+\begin{tabular}{| l | r | r | r | c |}
 \hline
-Rank & Data &  VUR  \\
+Technology & 1st Quartile &  Median & 3rd Quartile & Distribution  \\
 \hline
@@
 \end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
 \end{document}
-\\

### 2015-02-24 untitled folder 2/wearables-survey-paper-master/conclusion.tex
histograms
histograms

--- 2015-02-20 conclusion.tex
@@
 We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
+We examine how upset participants would in  304 scenarios, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
 We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.

### 2015-02-24 untitled folder 2/wearables-survey-paper-master/discussion.tex
histograms
histograms

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
-\begin{abstract}
-We performed an online survey to examine risk perceptions surrounding wearable computing devices.
-We examine different data types that might be captured,  and the effect of who the data is shared with.
-We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks.
-Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies.
-The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
 \section{Discussion}
@@
 We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-02-24 tables/benefit.tex
linda's push

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Language Detection  & 15.0 & 35.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionben} \\ 
Email  & 29.0 & 50.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailben} \\ 
Heart Rate Detection  & 26.0 & 40.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionben} \\ 
Cubetastic  & 10.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticben} \\ 
Speech To Text  & 15.0 & 25.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextben} \\ 
Location Tracking  & 20.0 & 40.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingben} \\ 
Facial Detection  & 10.0 & 20.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionben} \\ 
Age Detection  & 10.0 & 12.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionben} \\ 
Discreet Video Camera  & 15.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocameraben} \\ 
Facial Recognition  & 12.5 & 22.0 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\ 
Internet  & 45.0 & 65.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetben} \\ 
Voice Recognition  & 15.0 & 25.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionben} \\ 
Discreet Microphone  & 10.0 & 15.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophoneben} \\ 
Motorcycle & 12.0 & 20.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
Gender Detection  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionben} \\ 
Voice Based Emotion Detection  & 10.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionben} \\ 
Smartwatches  & 10.0 & 20.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesben} \\ 
Electricity & 50.0 & 88.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\ 
Google Glass  & 12.0 & 20.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassben} \\ 
Laptops  & 40.0 & 60.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsben} \\ 
Lawnmower & 15.0 & 24.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
Handgun & 10.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\ 
Smartphones  & 30.0 & 50.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesben} \\ 
Fitness Trackers  & 10.0 & 18.5 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersben} \\ 
\hline
\end{tabular}
\caption{Benefit Table}
\label{top10}
\end{center}
\end{table}

### 2015-02-24 tables/collapsed.tex
linda's push

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
\hline
 Rank & Q &  VUR & Distribution  \\ 
\hline
1 & Learnedyourheartrate & 27.5 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourheartratecombined} \\ 
2 & Learnedwhenyouarebusyorinterruptible & 29.5 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenyouarebusyorinterruptiblecombined} \\ 
3 & Tookavideoofyouunclothed & 95.97 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookavideoofyouunclothedcombined} \\ 
4 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
5 & Learnedwhenhowandhowmuchyouexercise & 38.66 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenhowandhowmuchyouexercisecombined} \\ 
6 & Learnedwhenyouwerehappyorhavingfun & 34.75 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenyouwerehappyorhavingfuncombined} \\ 
7 & Learnedyoursocialsecuritynumber & 94.84 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyoursocialsecuritynumbercombined} \\ 
8 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
9 & Learnedwhatwebsitesyougoto & 66.44 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhatwebsitesyougotocombined} \\ 
10 & Recordedyourphoneconversations & 85.16 & \includegraphics[width = 0.5cm, height = 0.5cm]{../recordedyourphoneconversationscombined} \\ 
11 & Learnedyourgender & 15.0 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourgendercombined} \\ 
12 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
13 & Learnedyourfingerprintsomehowwith & 77.78 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourfingerprintsomehowwithcombined} \\ 
14 & Recordedyourpassingconversations & 78.13 & \includegraphics[width = 0.5cm, height = 0.5cm]{../recordedyourpassingconversationscombined} \\ 
15 & Learnedhowmuchmoneyyouhave & 84.44 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedhowmuchmoneyyouhavecombined} \\ 
16 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51 & \includegraphics[width = 0.5cm, height = 0.5cm]{../trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
17 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21 & \includegraphics[width = 0.5cm, height = 0.5cm]{../sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
18 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookavideoofyouenteringinyourPINatanATMcombined} \\ 
19 & Recordedyourworkconversations & 86.82 & \includegraphics[width = 0.5cm, height = 0.5cm]{../recordedyourworkconversationscombined} \\ 
20 & Tookaphotoofyouintoxicated & 78.95 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookaphotoofyouintoxicatedcombined} \\ 
21 & Learnedwhereyouarecurrentlygoing & 60.87 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhereyouarecurrentlygoingcombined} \\ 
22 & Learnedwhenyouwerelyingnervousorstressed & 69.74 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenyouwerelyingnervousorstressedcombined} \\ 
23 & Learnedwhereyouworksomehow & 58.09 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhereyouworksomehowcombined} \\ 
24 & Learnedyourusernameforwebsites & 73.44 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourusernameforwebsitescombined} \\ 
25 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
26 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81 & \includegraphics[width = 0.5cm, height = 0.5cm]{../sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
27 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49 & \includegraphics[width = 0.5cm, height = 0.5cm]{../sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
28 & Tookavideoofyouintoxicated & 83.21 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookavideoofyouintoxicatedcombined} \\ 
29 & Learnedthelanguageyouwerespeaking & 15.86 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedthelanguageyouwerespeakingcombined} \\ 
30 & Tookavideoofyouoff-Guard & 76.0 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookavideoofyouoff-guardcombined} \\ 
31 & Learnedwhatproductsyoubuy & 50.0 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhatproductsyoubuycombined} \\ 
32 & Learnedwhatmedicalconditionsyouhave & 77.7 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhatmedicalconditionsyouhavecombined} \\ 
33 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63 & \includegraphics[width = 0.5cm, height = 0.5cm]{../sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
34 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & \includegraphics[width = 0.5cm, height = 0.5cm]{../scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
35 & Learnedwhoyouwerespendingtimewith & 60.0 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhoyouwerespendingtimewithcombined} \\ 
36 & Learnedwhenyouaresickorhealthy & 48.17 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenyouaresickorhealthycombined} \\ 
37 & Learnedyouraddress & 72.61 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyouraddresscombined} \\ 
38 & Learnedwhereyoulivesomehow & 65.0 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhereyoulivesomehowcombined} \\ 
39 & Learnedyourage & 24.29 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyouragecombined} \\ 
40 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookphotosatwork(withanoutward-facingcamera)combined} \\ 
41 & Learnedyourfingerprintsomehow & 67.23 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourfingerprintsomehowcombined} \\ 
42 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4 & \includegraphics[width = 0.5cm, height = 0.5cm]{../copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
43 & Learnedyourusernameandpasswordforwebsites & 89.55 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourusernameandpasswordforwebsitescombined} \\ 
44 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 0.5cm, height = 0.5cm]{../copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
45 & Tookaphotoofyouoff-Guard & 72.55 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookaphotoofyouoff-guardcombined} \\ 
46 & Tookaphotoofyouunclothed & 92.59 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookaphotoofyouunclothedcombined} \\ 
47 & Learnedwhenandhowwellyouaresleeping & 40.56 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenandhowwellyouaresleepingcombined} \\ 
48 & Learnedyourcreditcardinformation & 88.98 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourcreditcardinformationcombined} \\ 
49 & Copiedanduploadedmusicfromyourdevice & 28.06 & \includegraphics[width = 0.5cm, height = 0.5cm]{../copiedanduploadedmusicfromyourdevicecombined} \\ 
50 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
51 & Learnedyourname & 42.54 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyournamecombined} \\ 
52 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
53 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
54 & Sharedvideosotherssentyousavedonyourdevice & 70.59 & \includegraphics[width = 0.5cm, height = 0.5cm]{../sharedvideosotherssentyousavedonyourdevicecombined} \\ 
55 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
56 & Trackedwhereyouare(Likeagps) & 61.24 & \includegraphics[width = 0.5cm, height = 0.5cm]{../trackedwhereyouare(likeaGPS)combined} \\ 
57 & Learnedhowmuchyouuseyourphone & 51.95 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedhowmuchyouuseyourphonecombined} \\ 
58 & Recordedthesoundaroundyou & 60.45 & \includegraphics[width = 0.5cm, height = 0.5cm]{../recordedthesoundaroundyoucombined} \\ 
59 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
60 & Learnedwhenandhowmuchyouhavesex & 81.95 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenandhowmuchyouhavesexcombined} \\ 
61 & Learnedwhenhowmuchandwhatyouareeating & 42.86 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
62 & Learnedwhatmedicationyoutake & 69.49 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhatmedicationyoutakecombined} \\ 
63 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59 & \includegraphics[width = 0.5cm, height = 0.5cm]{../recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
64 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookvideosatwork(withanoutward-facingcamera)combined} \\ 
65 & Learnedwhattelevisionshowsyouwatch & 30.2 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhattelevisionshowsyouwatchcombined} \\ 
66 & Learnedyourbankaccountinformation & 95.91 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedyourbankaccountinformationcombined} \\ 
67 & Learnedhowmuchyouuseyourcomputer & 44.93 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedhowmuchyouuseyourcomputercombined} \\ 
68 & Learnedwhenandhowmuchyouspendtimealone & 61.27 & \includegraphics[width = 0.5cm, height = 0.5cm]{../learnedwhenandhowmuchyouspendtimealonecombined} \\ 
69 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
70 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89 & \includegraphics[width = 0.5cm, height = 0.5cm]{../sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
71 & Tookapictureofyoursignature & 68.07 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookapictureofyoursignaturecombined} \\ 
72 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & \includegraphics[width = 0.5cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-02-24 tables/risk.tex
linda's push

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Voice Based Emotion Detection  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionrisk} \\ 
Facial Detection  & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionrisk} \\ 
Facial Recognition  & 10.0 & 17.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} \\ 
Language Detection  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionrisk} \\ 
Gender Detection  & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionrisk} \\ 
Heart Rate Detection  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionrisk} \\ 
Age Detection  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionrisk} \\ 
Smartwatches  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesrisk} \\ 
Discreet Microphone  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophonerisk} \\ 
Location Tracking  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingrisk} \\ 
Electricity & 15.0 & 25.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} \\ 
Speech To Text  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextrisk} \\ 
Google Glass  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassrisk} \\ 
Laptops  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsrisk} \\ 
Email  & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailrisk} \\ 
Internet  & 10.0 & 15.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetrisk} \\ 
Smartphones  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesrisk} \\ 
Discreet Video Camera  & 10.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocamerarisk} \\ 
Cubetastic  & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticrisk} \\ 
Voice Recognition  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionrisk} \\ 
Handgun & 40.0 & 60.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} \\ 
Lawnmower & 12.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} \\ 
Motorcycle & 27.0 & 45.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} \\ 
Fitness Trackers  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersrisk} \\ 
\hline
\end{tabular}
\caption{Risk Table}
\label{top10}
\end{center}
\end{table}

### 2015-02-24 tables/work.tex
linda's push

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{3}{|r|}{{Continued on next page}} \\ \hline \hline
\endfoot
\hline 
\endlastfoot

\hline
1 & Learnedwhenyouwerehappyorhavingfun & 43.75\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunWORKCONTACTS} \\ \hline 
2 & Recordedyourpassingconversations & 87.5\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyourpassingconversationsWORKCONTACTS} \\ \hline 
3 & Tookavideoofyouenteringinyourpinatanatm & 87.5\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMWORKCONTACTS} \\ \hline 
4 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 61.11\% & \includegraphics[width = 0.5cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)WORKCONTACTS} \\ \hline 
5 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 93.55\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\ \hline 
6 & Learnedyourgender & 15.79\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourgenderWORKCONTACTS} \\ \hline 
7 & Learnedhowmuchyouuseyourphone & 68.75\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchyouuseyourphoneWORKCONTACTS} \\ \hline 
8 & Learnedwhenyouwerelyingnervousorstressed & 91.89\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedWORKCONTACTS} \\ \hline 
9 & Learnedwhenyouaresickorhealthy & 62.22\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouaresickorhealthyWORKCONTACTS} \\ \hline 
10 & Tookapictureofyoursignature & 85.71\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookapictureofyoursignatureWORKCONTACTS} \\ \hline 
11 & Learnedyourname & 26.47\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyournameWORKCONTACTS} \\ \hline 
12 & Trackedwhereyouare(Likeagps) & 63.64\% & \includegraphics[width = 0.5cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)WORKCONTACTS} \\ \hline 
13 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 88.24\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
14 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 89.19\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\ \hline 
15 & Learnedwhereyouarecurrentlygoing & 65.85\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingWORKCONTACTS} \\ \hline 
16 & Tookaphotoofyouintoxicated & 87.1\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookaphotoofyouintoxicatedWORKCONTACTS} \\ \hline 
17 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 78.13\% & \includegraphics[width = 0.5cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)WORKCONTACTS} \\ \hline 
18 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 86.27\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceWORKCONTACTS} \\ \hline 
19 & Learnedwhenhowandhowmuchyouexercise & 66.67\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexerciseWORKCONTACTS} \\ \hline 
20 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 66.67\% & \includegraphics[width = 0.5cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)WORKCONTACTS} \\ \hline 
21 & Recordedyourphoneconversations & 90.32\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyourphoneconversationsWORKCONTACTS} \\ \hline 
22 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 94.29\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingWORKCONTACTS} \\ \hline 
23 & Learnedyourusernameandpasswordforwebsites & 94.29\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesWORKCONTACTS} \\ \hline 
24 & Learnedyourheartrate & 44.12\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourheartrateWORKCONTACTS} \\ \hline 
25 & Learnedwhatmedicationyoutake & 81.25\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatmedicationyoutakeWORKCONTACTS} \\ \hline 
26 & Learnedwhereyoulivesomehow & 69.44\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhereyoulivesomehowWORKCONTACTS} \\ \hline 
27 & Copiedanduploadedmusicfromyourdevice & 42.11\% & \includegraphics[width = 0.5cm, height = 0.5cm]{copiedanduploadedmusicfromyourdeviceWORKCONTACTS} \\ \hline 
28 & Sharedvideosyoutookwhicharealreadyonyourdevice & 79.31\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\ \hline 
29 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 71.88\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
30 & Learnedhowmuchmoneyyouhave & 93.1\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchmoneyyouhaveWORKCONTACTS} \\ \hline 
31 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 51.35\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithWORKCONTACTS} \\ \hline 
32 & Tookavideoofyouoff-Guard & 91.43\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouoff-guardWORKCONTACTS} \\ \hline 
33 & Learnedyourfingerprintsomehow & 70.27\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourfingerprintsomehowWORKCONTACTS} \\ \hline 
34 & Learnedyouraddress & 81.58\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyouraddressWORKCONTACTS} \\ \hline 
35 & Learnedwhenandhowwellyouaresleeping & 62.07\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingWORKCONTACTS} \\ \hline 
36 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 82.86\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdeviceWORKCONTACTS} \\ \hline 
37 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)WORKCONTACTS} \\ \hline 
38 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 81.48\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
39 & Tookphotosatwork(Withanoutward-Facingcamera) & 81.48\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)WORKCONTACTS} \\ \hline 
40 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 63.16\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureWORKCONTACTS} \\ \hline 
41 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 82.05\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
42 & Learnedwhenhowmuchandwhatyouareeating & 75.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingWORKCONTACTS} \\ \hline 
43 & Sharedphotosyoutookwhicharealreadyonyourdevice & 79.55\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\ \hline 
44 & Learnedwhatwebsitesyougoto & 86.84\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatwebsitesyougotoWORKCONTACTS} \\ \hline 
45 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 88.57\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)WORKCONTACTS} \\ \hline 
46 & Learnedthelanguageyouwerespeaking & 28.13\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedthelanguageyouwerespeakingWORKCONTACTS} \\ \hline 
47 & Tookaphotoofyouoff-Guard & 80.49\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookaphotoofyouoff-guardWORKCONTACTS} \\ \hline 
48 & Sharedvideosotherssentyousavedonyourdevice & 80.49\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdeviceWORKCONTACTS} \\ \hline 
49 & Learnedwhoyouwerespendingtimewith & 76.19\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithWORKCONTACTS} \\ \hline 
50 & Learnedwhenandhowmuchyouhavesex & 90.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexWORKCONTACTS} \\ \hline 
51 & Recordedthesoundaroundyou & 75.76\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedthesoundaroundyouWORKCONTACTS} \\ \hline 
52 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 94.59\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingWORKCONTACTS} \\ \hline 
53 & Learnedwhatproductsyoubuy & 62.5\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatproductsyoubuyWORKCONTACTS} \\ \hline 
54 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 81.08\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorWORKCONTACTS} \\ \hline 
55 & Recordedyourworkconversations & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyourworkconversationsWORKCONTACTS} \\ \hline 
56 & Tookaphotoofyouunclothed & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookaphotoofyouunclothedWORKCONTACTS} \\ \hline 
57 & Tookavideoofyouunclothed & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouunclothedWORKCONTACTS} \\ \hline 
58 & Learnedyourbankaccountinformation & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourbankaccountinformationWORKCONTACTS} \\ \hline 
59 & Learnedhowmuchdebtyouhave & 87.18\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchdebtyouhaveWORKCONTACTS} \\ \hline 
60 & Learnedhowmuchyouuseyourcomputer & 45.45\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerWORKCONTACTS} \\ \hline 
61 & Learnedyourusernameforwebsites & 84.62\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourusernameforwebsitesWORKCONTACTS} \\ \hline 
62 & Learnedwhenandhowmuchyouspendtimealone & 80.95\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealoneWORKCONTACTS} \\ \hline 
63 & Learnedyourcreditcardinformation & 95.12\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourcreditcardinformationWORKCONTACTS} \\ \hline 
64 & Learnedwhenyouarebusyorinterruptible & 36.36\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptibleWORKCONTACTS} \\ \hline 
65 & Learnedwhattelevisionshowsyouwatch & 36.36\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchWORKCONTACTS} \\ \hline 
66 & Learnedyoursocialsecuritynumber & 93.75\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyoursocialsecuritynumberWORKCONTACTS} \\ \hline 
67 & Learnedyourage & 36.67\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourageWORKCONTACTS} \\ \hline 
68 & Learnedwhatmedicalconditionsyouhave & 85.29\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhaveWORKCONTACTS} \\ \hline 
69 & Sharedphotosotherssenttoyousavedonyourdevice & 75.61\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdeviceWORKCONTACTS} \\ \hline 
70 & Learnedwhereyouworksomehow & 57.14\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhereyouworksomehowWORKCONTACTS} \\ \hline 
71 & Tookavideoofyouintoxicated & 88.89\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouintoxicatedWORKCONTACTS} \\ \hline 
72 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.22\% & \includegraphics[width = 0.5cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdeviceWORKCONTACTS} \\ \hline 
\hline

\end{longtable}
\end{document}

### 2015-02-24 untitled folder 2/untitled folder/histograms/learnedhowyouwerefeelingbasedonheartratebreathingand:ortemperature FRIENDSdsfasdfas.py

@@ -1,63 +1,0 @@
-
-import numpy as np
-import matplotlib.pyplot as plt
-from pylab import *
-
-def parse(text):
-	f = open(text,'r')
-	line = f.readline()
-	prev = None
-	combined = []
-
-	while line:
-		x = line.split()
-		if prev != None and prev != x[0]:
-			plt.hist(edgecolor = "none",x = combined,color = 'green',bins = range(0,7),alpha = 0.5, align = 'mid', rwidth = 1)
-		# plt.tick_params(\
-  #   axis='x',          # changes apply to the x-axis
-  #   which='both',      # both major and minor ticks are affected
-  #   bottom='off',      # ticks along the bottom edge are off
-  #   top='off',         # ticks along the top edge are off
-  #   labelbottom='off') # labels along the bottom edge are off
-		#plt.xticks(np.arange(1,6))
-			plt.xticks([])
-			plt.yticks([])
-			plt.axis('off')
-
-
-			savefig(str(prev) + " combined", dpi=None, facecolor='w', edgecolor='w',
-			orientation='portrait', papertype=None, format=None,
-			transparent=False, bbox_inches='tight', pad_inches=0,
-			frameon=None)
-			combined = []
-			plt.clf()
-		prev = x[0]
-
-		numbers = list(x[2])
-
-		title = str(x[0])+ " " + str(x[1])
-		for i in range(len(numbers)):
-			numbers[i] = int(numbers[i])
-			combined.append(numbers[i])
-		plt.hist(edgecolor = "none",x = numbers,color = 'green',bins = range(0,7),alpha = 0.5, align = 'mid', rwidth = 1)
-		# plt.tick_params(\
-  #   axis='x',          # changes apply to the x-axis
-  #   which='both',      # both major and minor ticks are affected
-  #   bottom='off',      # ticks along the bottom edge are off
-  #   top='off',         # ticks along the top edge are off
-  #   labelbottom='off') # labels along the bottom edge are off
-		#plt.xticks(np.arange(1,6))
-		plt.xticks([])
-		plt.yticks([])
-		plt.axis('off')
-
-		savefig(title, dpi=None, facecolor='w', edgecolor='w',
-		orientation='portrait', papertype=None, format=None,
-		transparent=False, bbox_inches='tight', pad_inches=0,
-		frameon=None)
-		line = f.readline()
-		plt.clf()
-
-
-	
-parse("file.txt")

### 2015-02-24 tables/work.tex
tables without lines
title

@@
 \endlastfoot
-
+1 & Learnedyourgender & 15.79\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourgenderWORKCONTACTS} \\  
+2 & Learnedyourname & 26.47\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyournameWORKCONTACTS} \\  
+3 & Learnedthelanguageyouwerespeaking & 28.13\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedthelanguageyouwerespeakingWORKCONTACTS} \\  
+4 & Learnedwhenyouarebusyorinterruptible & 36.36\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptibleWORKCONTACTS} \\  
+5 & Learnedwhattelevisionshowsyouwatch & 36.36\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchWORKCONTACTS} \\  
+6 & Learnedyourage & 36.67\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourageWORKCONTACTS} \\  
+7 & Copiedanduploadedmusicfromyourdevice & 42.11\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedmusicfromyourdeviceWORKCONTACTS} \\  
+8 & Learnedwhenyouwerehappyorhavingfun & 43.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunWORKCONTACTS} \\  
+9 & Learnedyourheartrate & 44.12\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourheartrateWORKCONTACTS} \\  
+10 & Learnedhowmuchyouuseyourcomputer & 45.45\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerWORKCONTACTS} \\  
+11 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 51.35\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithWORKCONTACTS} \\  
+12 & Learnedwhereyouworksomehow & 57.14\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouworksomehowWORKCONTACTS} \\  
+13 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 61.11\% & \includegraphics[width = 2cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)WORKCONTACTS} \\  
+14 & Learnedwhenandhowwellyouaresleeping & 62.07\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingWORKCONTACTS} \\  
+15 & Learnedwhenyouaresickorhealthy & 62.22\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouaresickorhealthyWORKCONTACTS} \\  
+16 & Learnedwhatproductsyoubuy & 62.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatproductsyoubuyWORKCONTACTS} \\  
+17 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 63.16\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureWORKCONTACTS} \\
+18 & Trackedwhereyouare(Likeagps) & 63.64\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)WORKCONTACTS} \\  
+19 & Learnedwhereyouarecurrentlygoing & 65.85\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingWORKCONTACTS} \\  
+20 & Learnedwhenhowandhowmuchyouexercise & 66.67\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexerciseWORKCONTACTS} \\  
+21 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 66.67\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)WORKCONTACTS} \\
+22 & Learnedhowmuchyouuseyourphone & 68.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourphoneWORKCONTACTS} \\  
+23 & Learnedwhereyoulivesomehow & 69.44\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyoulivesomehowWORKCONTACTS} \\  
+24 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)WORKCONTACTS} \\  
+25 & Learnedyourfingerprintsomehow & 70.27\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourfingerprintsomehowWORKCONTACTS} \\  
+26 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 71.88\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\  
+27 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.22\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdeviceWORKCONTACTS} \\  
+28 & Learnedwhenhowmuchandwhatyouareeating & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingWORKCONTACTS} \\  
+29 & Sharedphotosotherssenttoyousavedonyourdevice & 75.61\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdeviceWORKCONTACTS} \\  
+30 & Recordedthesoundaroundyou & 75.76\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedthesoundaroundyouWORKCONTACTS} \\  
+31 & Learnedwhoyouwerespendingtimewith & 76.19\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithWORKCONTACTS} \\  
+32 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 78.13\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)WORKCONTACTS} \\  
+33 & Sharedvideosyoutookwhicharealreadyonyourdevice & 79.31\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\  
+34 & Sharedphotosyoutookwhicharealreadyonyourdevice & 79.55\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\  
+35 & Tookaphotoofyouoff-Guard & 80.49\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouoff-guardWORKCONTACTS} \\  
+36 & Sharedvideosotherssentyousavedonyourdevice & 80.49\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdeviceWORKCONTACTS} \\  
+37 & Learnedwhenandhowmuchyouspendtimealone & 80.95\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealoneWORKCONTACTS} \\  
+38 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 81.08\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorWORKCONTACTS} \\  
+39 & Learnedwhatmedicationyoutake & 81.25\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicationyoutakeWORKCONTACTS} \\  
+40 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 81.48\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\  
+41 & Tookphotosatwork(Withanoutward-Facingcamera) & 81.48\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)WORKCONTACTS} \\  
+42 & Learnedyouraddress & 81.58\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouraddressWORKCONTACTS} \\  
+43 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 82.05\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\  
+44 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 82.86\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdeviceWORKCONTACTS} \\  
+45 & Learnedyourusernameforwebsites & 84.62\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameforwebsitesWORKCONTACTS} \\  
+46 & Learnedwhatmedicalconditionsyouhave & 85.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhaveWORKCONTACTS} \\  
+47 & Tookapictureofyoursignature & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{tookapictureofyoursignatureWORKCONTACTS} \\  
+48 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 86.27\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceWORKCONTACTS} \\  
+49 & Learnedwhatwebsitesyougoto & 86.84\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatwebsitesyougotoWORKCONTACTS} \\  
+50 & Tookaphotoofyouintoxicated & 87.1\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouintoxicatedWORKCONTACTS} \\  
+51 & Learnedhowmuchdebtyouhave & 87.18\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchdebtyouhaveWORKCONTACTS} \\  
+52 & Recordedyourpassingconversations & 87.5\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourpassingconversationsWORKCONTACTS} \\  
+53 & Tookavideoofyouenteringinyourpinatanatm & 87.5\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMWORKCONTACTS} \\  
+54 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 88.24\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\  
+55 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 88.57\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)WORKCONTACTS} \\  
+56 & Tookavideoofyouintoxicated & 88.89\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouintoxicatedWORKCONTACTS} \\  
+57 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 89.19\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\  
+58 & Learnedwhenandhowmuchyouhavesex & 90.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexWORKCONTACTS} \\  
+59 & Recordedyourphoneconversations & 90.32\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourphoneconversationsWORKCONTACTS} \\  
+60 & Tookavideoofyouoff-Guard & 91.43\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouoff-guardWORKCONTACTS} \\  
+61 & Learnedwhenyouwerelyingnervousorstressed & 91.89\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedWORKCONTACTS} \\  
+62 & Learnedhowmuchmoneyyouhave & 93.1\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchmoneyyouhaveWORKCONTACTS} \\  
+63 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 93.55\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\  
+64 & Learnedyoursocialsecuritynumber & 93.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyoursocialsecuritynumberWORKCONTACTS} \\  
+65 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 94.29\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingWORKCONTACTS} \\  
+66 & Learnedyourusernameandpasswordforwebsites & 94.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesWORKCONTACTS} \\  
+67 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 94.59\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingWORKCONTACTS} \\  
+68 & Learnedyourcreditcardinformation & 95.12\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourcreditcardinformationWORKCONTACTS} \\  
+69 & Recordedyourworkconversations & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourworkconversationsWORKCONTACTS} \\  
+70 & Tookaphotoofyouunclothed & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouunclothedWORKCONTACTS} \\  
+71 & Tookavideoofyouunclothed & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouunclothedWORKCONTACTS} \\  
+72 & Learnedyourbankaccountinformation & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourbankaccountinformationWORKCONTACTS} \\  
 \hline
-1 & Learnedwhenyouwerehappyorhavingfun & 43.75\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunWORKCONTACTS} \\ \hline 
-2 & Recordedyourpassingconversations & 87.5\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyourpassingconversationsWORKCONTACTS} \\ \hline 
-3 & Tookavideoofyouenteringinyourpinatanatm & 87.5\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMWORKCONTACTS} \\ \hline 
-4 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 61.11\% & \includegraphics[width = 0.5cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)WORKCONTACTS} \\ \hline 
-5 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 93.55\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\ \hline 
-6 & Learnedyourgender & 15.79\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourgenderWORKCONTACTS} \\ \hline 
-7 & Learnedhowmuchyouuseyourphone & 68.75\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchyouuseyourphoneWORKCONTACTS} \\ \hline 
-8 & Learnedwhenyouwerelyingnervousorstressed & 91.89\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedWORKCONTACTS} \\ \hline 
-9 & Learnedwhenyouaresickorhealthy & 62.22\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouaresickorhealthyWORKCONTACTS} \\ \hline 
-10 & Tookapictureofyoursignature & 85.71\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookapictureofyoursignatureWORKCONTACTS} \\ \hline 
-11 & Learnedyourname & 26.47\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyournameWORKCONTACTS} \\ \hline 
-12 & Trackedwhereyouare(Likeagps) & 63.64\% & \includegraphics[width = 0.5cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)WORKCONTACTS} \\ \hline 
-13 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 88.24\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
-14 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 89.19\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\ \hline 
-15 & Learnedwhereyouarecurrentlygoing & 65.85\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingWORKCONTACTS} \\ \hline 
-16 & Tookaphotoofyouintoxicated & 87.1\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookaphotoofyouintoxicatedWORKCONTACTS} \\ \hline 
-17 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 78.13\% & \includegraphics[width = 0.5cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)WORKCONTACTS} \\ \hline 
-18 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 86.27\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceWORKCONTACTS} \\ \hline
-19 & Learnedwhenhowandhowmuchyouexercise & 66.67\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexerciseWORKCONTACTS} \\ \hline 
-20 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 66.67\% & \includegraphics[width = 0.5cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)WORKCONTACTS} \\ \hline
-21 & Recordedyourphoneconversations & 90.32\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyourphoneconversationsWORKCONTACTS} \\ \hline 
-22 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 94.29\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingWORKCONTACTS} \\ \hline 
-23 & Learnedyourusernameandpasswordforwebsites & 94.29\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesWORKCONTACTS} \\ \hline 
-24 & Learnedyourheartrate & 44.12\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourheartrateWORKCONTACTS} \\ \hline 
-25 & Learnedwhatmedicationyoutake & 81.25\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatmedicationyoutakeWORKCONTACTS} \\ \hline 
-26 & Learnedwhereyoulivesomehow & 69.44\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhereyoulivesomehowWORKCONTACTS} \\ \hline 
-27 & Copiedanduploadedmusicfromyourdevice & 42.11\% & \includegraphics[width = 0.5cm, height = 0.5cm]{copiedanduploadedmusicfromyourdeviceWORKCONTACTS} \\ \hline 
-28 & Sharedvideosyoutookwhicharealreadyonyourdevice & 79.31\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\ \hline 
-29 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 71.88\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
-30 & Learnedhowmuchmoneyyouhave & 93.1\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchmoneyyouhaveWORKCONTACTS} \\ \hline 
-31 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 51.35\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithWORKCONTACTS} \\ \hline 
-32 & Tookavideoofyouoff-Guard & 91.43\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouoff-guardWORKCONTACTS} \\ \hline 
-33 & Learnedyourfingerprintsomehow & 70.27\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourfingerprintsomehowWORKCONTACTS} \\ \hline 
-34 & Learnedyouraddress & 81.58\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyouraddressWORKCONTACTS} \\ \hline 
-35 & Learnedwhenandhowwellyouaresleeping & 62.07\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingWORKCONTACTS} \\ \hline 
-36 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 82.86\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdeviceWORKCONTACTS} \\ \hline 
-37 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)WORKCONTACTS} \\ \hline 
-38 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 81.48\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
-39 & Tookphotosatwork(Withanoutward-Facingcamera) & 81.48\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)WORKCONTACTS} \\ \hline 
-40 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 63.16\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureWORKCONTACTS} \\ \hline
-41 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 82.05\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\ \hline 
-42 & Learnedwhenhowmuchandwhatyouareeating & 75.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingWORKCONTACTS} \\ \hline 
-43 & Sharedphotosyoutookwhicharealreadyonyourdevice & 79.55\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\ \hline 
-44 & Learnedwhatwebsitesyougoto & 86.84\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatwebsitesyougotoWORKCONTACTS} \\ \hline 
-45 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 88.57\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)WORKCONTACTS} \\ \hline 
-46 & Learnedthelanguageyouwerespeaking & 28.13\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedthelanguageyouwerespeakingWORKCONTACTS} \\ \hline 
-47 & Tookaphotoofyouoff-Guard & 80.49\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookaphotoofyouoff-guardWORKCONTACTS} \\ \hline 
-48 & Sharedvideosotherssentyousavedonyourdevice & 80.49\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdeviceWORKCONTACTS} \\ \hline 
-49 & Learnedwhoyouwerespendingtimewith & 76.19\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithWORKCONTACTS} \\ \hline 
-50 & Learnedwhenandhowmuchyouhavesex & 90.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexWORKCONTACTS} \\ \hline 
-51 & Recordedthesoundaroundyou & 75.76\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedthesoundaroundyouWORKCONTACTS} \\ \hline 
-52 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 94.59\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingWORKCONTACTS} \\ \hline 
-53 & Learnedwhatproductsyoubuy & 62.5\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatproductsyoubuyWORKCONTACTS} \\ \hline 
-54 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 81.08\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorWORKCONTACTS} \\ \hline 
-55 & Recordedyourworkconversations & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{recordedyourworkconversationsWORKCONTACTS} \\ \hline 
-56 & Tookaphotoofyouunclothed & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookaphotoofyouunclothedWORKCONTACTS} \\ \hline 
-57 & Tookavideoofyouunclothed & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouunclothedWORKCONTACTS} \\ \hline 
-58 & Learnedyourbankaccountinformation & 100.0\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourbankaccountinformationWORKCONTACTS} \\ \hline 
-59 & Learnedhowmuchdebtyouhave & 87.18\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchdebtyouhaveWORKCONTACTS} \\ \hline 
-60 & Learnedhowmuchyouuseyourcomputer & 45.45\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerWORKCONTACTS} \\ \hline 
-61 & Learnedyourusernameforwebsites & 84.62\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourusernameforwebsitesWORKCONTACTS} \\ \hline 
-62 & Learnedwhenandhowmuchyouspendtimealone & 80.95\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealoneWORKCONTACTS} \\ \hline 
-63 & Learnedyourcreditcardinformation & 95.12\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourcreditcardinformationWORKCONTACTS} \\ \hline 
-64 & Learnedwhenyouarebusyorinterruptible & 36.36\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptibleWORKCONTACTS} \\ \hline 
-65 & Learnedwhattelevisionshowsyouwatch & 36.36\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchWORKCONTACTS} \\ \hline 
-66 & Learnedyoursocialsecuritynumber & 93.75\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyoursocialsecuritynumberWORKCONTACTS} \\ \hline 
-67 & Learnedyourage & 36.67\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedyourageWORKCONTACTS} \\ \hline 
-68 & Learnedwhatmedicalconditionsyouhave & 85.29\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhaveWORKCONTACTS} \\ \hline 
-69 & Sharedphotosotherssenttoyousavedonyourdevice & 75.61\% & \includegraphics[width = 0.5cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdeviceWORKCONTACTS} \\ \hline 
-70 & Learnedwhereyouworksomehow & 57.14\% & \includegraphics[width = 0.5cm, height = 0.5cm]{learnedwhereyouworksomehowWORKCONTACTS} \\ \hline 
-71 & Tookavideoofyouintoxicated & 88.89\% & \includegraphics[width = 0.5cm, height = 0.5cm]{tookavideoofyouintoxicatedWORKCONTACTS} \\ \hline 
-72 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.22\% & \includegraphics[width = 0.5cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdeviceWORKCONTACTS} \\ \hline 
-\hline
-
 \end{longtable}

### 2015-02-25 discussion.tex
restructuring latex and some discussion work

--- 2015-02-24 untitled folder 2/wearables-survey-paper-master/discussion.tex
@@
 
+\subsection{Underestimation of Risk} 
+{\color{red} where people are underestimating risk, why people rated risks the way that they did, and talk about common themes.
+Here, it's more to discuss any social factors which cannot be explicitly proven given the data we have, but we can always suggest explanations for why this has happened.
+
+Any economics or behavioral papers to support our claims would be great here.}
+
+\subsection{Interpreting the Survey Results}
+One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
+83\% of our participants reported that they do not own a wearable device.
+We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
+However, that will also have its own biases and limitations, since this does not reflect the general population.
+At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, so our study reflective of the status quo.
+We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
+
+{\color {red} privacy paradox (privacy concerns asked out of context vs how people react to in real life are not representative)}
+
 \subsection{Future Research Directions}
+{\color {red} including recipients like "advertisers" and "acquaintances" may lead to more contrasting results.}
+
 Wearables are still in infancy.
@@
 While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

### 2015-02-25 results-demographics.tex
restructuring latex and some discussion work

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
 \subsubsection{Demographic Factors}
@@
 Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-02-25 results-openended.tex
restructuring latex and some discussion work

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
 \subsection{Self-Reported Concerns for Wearables}
@@
 
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
+Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy} (see Table \ref{openresponses}).
+Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
 

### 2015-02-25 results-techrank.tex
restructuring latex and some discussion work

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
 \subsection{Risk and Benefit Rankings} 
@@
 
+{\color {red} people may have evaluated the risks only thinking of physical risk, not privacy risk.
+This might have happened because among the 5 presented options, the wearable-related one is the odd one out; all other options involve some physical risk scenario.
+These other options, by being the most prominent (4 versus 1), frame the risk perception in the user's mind as meaning "physical risk", and users may consequently ignore or downplay privacy risks.
+It would have been better to ask 4+4  questions (or 2+2 to keep the survey short) rather than the current 4+1.
+AND "with the exception of electricity, the calibration technologies were seen as lower benefit than the others".
+This is true for some, but not all of the others.
+Specifically, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
+AND The differences in risk that *are* found between the different wearable-related are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.}
+
 These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
@@
 We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-02-25 tex-inputs/results-devices.tex
cleanup

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
 \subsubsection{Device}
@@
 For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-02-25 tex-inputs/results-intro.tex
cleanup

--- 2015-02-20 results.tex
@@
 \section{Results}
-In this section, we present our survey results.
+We present our survey results and provide analyses of the data.
 We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
@@
 \subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
+Many factors impact participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
 We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-02-25 tex-inputs/results-recipient.tex
cleanup

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
 \subsubsection{Data Recipient}
@@
 
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
+{\color {red} we're not saying that there is no distinction, just that there is more distinction between people and the app server."users make little distinction between sharing data with friends, co-workers, or the general public”: at first sight, this result is in conflict with privacy studies specifically in the social arena (e.g., Facebook).
+The authors may want to comment on this fact if they have any explanation.}

### 2015-02-25 tex-inputs/results-regression.tex
cleanup

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
 \subsubsection{Regression Models} 
@@
 Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-02-25 tex-inputs/results-type.tex
cleanup

--- 2015-02-20 results.tex
@@
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
 \subsubsection{Data Type}
@@
 We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
 The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
@@
 We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-02-25 tex-inputs/intro.tex
added some todos inline to the paper

--- 2015-02-20 intro.tex
@@
 \section{Introduction}
+
+{\color {red} Let's redo this whole introduction section. Make it more focused toward economic concerns, and really motivate the purpose of this paper}
+
+{\color {red} "there has been extensive work on the need for showing users how certaind data is being captured so that they can have more control..
+now we have wearables, and collect more data types.
+We have an issue of showing everyone everything all the time, since attention is a finite resources.
+We need to identify situations that people want to warn them about, and transparently access things that they are benign."}
+
 With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
@@
 Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
+Many concerns expose users' activities without their awareness or consent.
 For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.

### 2015-02-25 tex-inputs/methodology.tex
cleanup
added some todos inline to the paper

--- 2015-02-20 methodology.tex
@@
 
-\subsection{Methodology Motivation}
+\subsection{Motivation}
 \subsubsection{Smartphone Risk Scenarios}
@@
 %Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+
+\subsection{Inspiration} 
+%LL: This needs to be a lot better, and sound not so hand-wavey.
+
+{\color {red} talk about the brainstorming here, and how the questions were formulated.
+Mention that I took the most popular wearable devices of the time into account, looked at their sensors, and came up with possible uses.
+I followed that up with some permissions from the mobile app world, watching vision videos, etc.}
 
@@
 
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
 Rather, we report medians and quartiles, which are not impacted by outliers.

### 2015-02-25 tex-inputs/discussion.tex
discussion section redo

\section{Discussion}
Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.

\subsection{Interpreting the Survey Results}
One of the main limitations of this work is that our participants might not have interest in or knowledge of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device. These participants may have underestimated or overestimated the risk perceived in various scenarios. People may be overreacting to recent events for scenarios \footnote{During our study, there were many stories covering injuries from exploding batteries (http://www.bloomberg.com/news/articles/2014-08-11/exploding-lithium-batteries-riskier-to-planes-research), which were explicitly and repeated mentioned when self-reporting concerns.}. People may be underestimating the risk of sharing certain data due to unawareness of what can be inferred from the data, or not have an idea of how to rate a new technology with respect to familiar ones. Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}. {\color {red} Any economics or behavioral papers to support our claims and elaborate on this would be great here. Maybe ones on perception, estimation, etc.}

We believed that getting a representative survey base was a useful endeavor. We could have easily recruited only wearables owners or people specifically interested in wearables. However, that will also have its own biases and limitations, since this does not reflect the general population. At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, so our study reflective of the status quo. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

Privacy concerns asked out of context differ from how users may react to these same concerns in real life. This is an unavoidable, yet important consideration of any study of this nature. This privacy paradox means that our findings may not be exactly representative of how upset users may be in real life, but do reflect their perceptions of wearable devices and various associated scenarios.

\subsection{Future Research Directions}
Further work can be done to expand various aspects of this study. Investigating more fine-grained data types (e.g. investigating if various types of location data, versus just location data in general) would be a useful endeavor to gain further insight into user perception. Adding more recipients, like ``advertisers'' or ``acquaintances'' may lead to more contrasting results.

While privacy and security concerns were expected, consider the following self-reported user concerns as inspiration for future research: addressing the high financial costs of wearables, communicating the reality of health concerns from constant use, creating distraction-free interfaces to prevent safety issues, minimizing negative social impacts of wearable device use, and improving device aesthetics.

Wearables are still in infancy. Perceptions of situations and capabilities will change rapidly with advancements and increased exposure. However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

### 2015-02-25 tex-inputs/background.tex
started background and scoping; finished up a couple sections

\section{Current Wearable Devices}  %aka background
%LL: This needs to be a lot better, and sound not so hand-wavey.
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors and capabilities of the most popular wearable devices on the market at the time of this study. The most common wearables of the time were in the form of fitness trackers and smart watches. However, there are also wearable glasses \footnote{ https://www.google.com/intl/en/glass/start/how-it-looks/, http://www.sony.net/SonyInfo/News/Press/201412/14-118E/index.html}, rings \footnote{https://ringly.com/}, bracelets \footnote{http://www.intel.com/content/www/us/en/wearables/fashion-technology.html} and more.

 At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \footnote{http://www.fitbit.com/, http://time.com/516/26-fitness-trackers-ranked-from-worst-to-first/}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \footnote{https://getpebble.com/, http://www.theverge.com/2014/1/7/5284144/the-best-wearables-of-ces-2014-stream, http://readwrite.com/2014/02/10/10-cool-things-a-pebble-smartwatch-can-do}, and google glass \footnote{http://en.wikipedia.org/wiki/Google\_Glass, http://www.engadget.com/2014/07/30/the-top-9-wearables-on-you-can-buy-right-now/}. These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.

 Google glass has since disappeared due to complaints from the public \footnote{http://www.google.com/glass/start/, http://uk.pcmag.com/wearable-tech/36416/opinion/rest-in-peace-google-glass-2012-2014}, and many instances of assault for wearing the product had contributed to this \footnote{http://www.businessinsider.com/i-was-assaulted-for-wearing-google-glass-2014-4, http://www.cnet.com/news/journalist-i-was-assaulted-on-street-for-wearing-google-glass/, http://mashable.com/2014/02/26/google-glass-assault/, http://www.cnn.com/2014/04/14/tech/mobile/google-glass-attack/}.

### 2015-02-25 tables/riskbenefit.tex
redoing the intro

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
&\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
\hline
Technology &  Median & Q1 & Q3 & Distribution &  Median& Q1 & Q3 & Distribution   \\ 
\hline
location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\

Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\

Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk}  & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\

\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-02-25 tex-inputs/intro.tex
redoing the intro

@@
 
-{\color {red} Let's redo this whole introduction section. Make it more focused toward economic concerns, and really motivate the purpose of this paper}
+Wearable technologies, or ``wearables,'' are intimately related with both fields of ubiquitous computing and wearable computers.
+This \$700 million industry \cite{cmo} of electronically enhanced clothing items and accessories aims to interweave technological interaction into everyday life.
+A top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
+With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are transforming ubiquitous computing into a part of every day life.
+Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''
 
-{\color {red} "there has been extensive work on the need for showing users how certaind data is being captured so that they can have more control..
-now we have wearables, and collect more data types.
-We have an issue of showing everyone everything all the time, since attention is a finite resources.
-We need to identify situations that people want to warn them about, and transparently access things that they are benign."}
+Because interactions with the wearables so frictionless, they are a popular choice for augmenting life with novel feedback and taking advantage of pre-existing applications more seamlessly.
+The constantly captured data from these devices has many benefits, ranging form a more natural, human-centered interface experience to healthier, fitness-data inspired lifestyle.
+It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits.
 
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
+Despite their popularity, the market is still in its infancy.
+It is hard to predict what device and applications will be most popular.
+Therefore, we use the current interest as a baseline.
+The most common wearables at the time of this study were in the form of fitness trackers and smart watches, with a survey of 3,956 wearables-enthusiastic respondents reporting the most popular devices as fitness bands (61\%), smart watches (45\%) and other health devices (17\%)~\cite{Nilsen}.
+However, there are also wearable glasses \cite{ 2_google_2014, 3_sony_global_2014}, rings \cite{4_ringly_2014}, bracelets \cite{5_intel_2014} and more.
+New wearables trends for 2015 include smart clothes made out fiber-optic fabrics which give information about workouts and UV technology hairslide which measures sun exposure \cite{1_digital_trends_2014, 2_arthur_2014}.
 
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
+%% LL: worked upto here. below is rough.
 
@@
 
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
+Although Google Glass was most iconic wearable of its time, it has since disappeared due to complaints from the public\cite{13_google_2015}.
+No formal statement from Google addresses the states that the reason for its disappearance is due to negative social pressures.
+However, most suspect that this is the reason for its disappearance, rather than a shift in interest.
+One popular tech magazine called glass the ``straw the broke the back of the privacy camel's back \cite{14_dvorak_2014}''.
+The wearable device was not acceptable to the public at large, making bystanders feel uncomfortable with the possibility of recording personal details, conversations, and photos.
+Many instances of assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} on wearers were also reported, resulting from a combination of privacy invasion and social tension\footnote{Google has come to represent gentrification in San Francisco ...
+[which] makes wearable device owners look and sound like one of the people whom residents of the city have come to feel oppressed by \cite{17_matyszczyk_2014}.
+The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers.} .
+The public was generally unsympathetic to the situation, tweets including, ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.
+Gentrification at this [point] feels like destruction of property,'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.
+
+{\color {red} This calls for privacy research in this area!
+It's more important than ever!
+Or something along those lines.}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
 A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
 The goal of this paper is to gain a better sense of what those concerns are.
+{\color {red} "there has been extensive work on the need for showing users how certaind data is being captured so that they can have more control..
+now we have wearables, and collect more data types.
+We have an issue of showing everyone everything all the time, since attention is a finite resources.
+We need to identify situations that people want to warn them about, and transparently access things that they are benign."}
 
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
+To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study.
+At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}.
+These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.
+
+{\color {red} better intro to here} We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
 

### 2015-02-25 tex-inputs/results-recipient.tex
sprinkled things to talk about inline

@@
+%!TEX root = paper.tex
+
 \subsubsection{Data Recipient}
@@
 But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
+Similarly, we are unaware of a more appropriate test, given our data format; Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
+Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation.
 Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
@@
 The authors may want to comment on this fact if they have any explanation.}
+
+{\color {red} add a discussion here about the variance between the recipients. Mention specific numbers. Was there a change in distribution just because we changed the recipient type?}

### 2015-02-25 tex-inputs/intro.tex
small clarifying comment
Fixed so it compiles again...
tweaked intro

@@
 
+{\color {red} WORKED UPTO HERE BELOW IS ROUGH}
+
 Wearable devices bring with them new potential security and privacy concerns.
@@
 For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
+Additionally, public discomfort prevented companies from enabling capabilities.
+Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
 

### 2015-02-25 tex-inputs/intro.tex
more hashing out of introduction and scoping

@@
+%!TEX root = ../paper.tex
+
 \section{Introduction}
@@
 
-%% LL: worked upto here. below is rough.
-
-{\color {red} WORKED UPTO HERE BELOW IS ROUGH}
-
 Wearable devices bring with them new potential security and privacy concerns.
@@
 The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers.} .
-The public was generally unsympathetic to the situation, tweets including, ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.
-Gentrification at this [point] feels like destruction of property,'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.
+The public was generally unsympathetic to the situation, tweeting or commenting, ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.
 
@@
 It's more important than ever!
-Or something along those lines.}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
+Or something along those lines.}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices to prevent negative social impact and breaches of privacy.
+There has been extensive work on the need for showing users and bystanders how certain data is being captured so that they can have more control.
+We have an issue of showing everyone everything all the time, since attention is a finite resources.
+We need to identify situations that people want to warn them about, and transparently access things that are benign.
 A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
 The goal of this paper is to gain a better sense of what those concerns are.
-{\color {red} "there has been extensive work on the need for showing users how certaind data is being captured so that they can have more control..
-now we have wearables, and collect more data types.
-We have an issue of showing everyone everything all the time, since attention is a finite resources.
-We need to identify situations that people want to warn them about, and transparently access things that they are benign."}
 

### 2015-02-25 tex-inputs/methodology.tex
started background and scoping; finished up a couple sections
Fixed so it compiles again...
Added more on demographics

--- 2015-02-20 methodology.tex
@@
+%!TEX root = ../paper.tex
+
 \section{Methodology}
@@
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
+We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and three participants who were under 18, leaving us with a total sample size of 1,782.
+Of these, 57.9\% were male (1,031), 41.0\% were female (731), and 20 participants declined to state their genders.
+Ages ranged from 18 to 73, with a mean of 32.1 ($\sigma$ = 10.37).
+Almost half of our participants had completed a college degree or more (49.2\% of 1,782), which includes the 219 (12.3\% of 1,782) who reported graduate degrees.
+While our sample was younger and more educated than the U.S.
+population as a whole, we believe it is still consistent with the U.S.
+Internet-using population.
 

### 2015-02-25 tex-inputs/intro.tex
minor rewording

@@
 For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities.
-Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
+Additionally, public discomfort prevented Google from enabling capabilities such as facial detection on Google Glass \cite{GlassDetection}.
 
@@
 However, most suspect that this is the reason for its disappearance, rather than a shift in interest.
-One popular tech magazine called glass the ``straw the broke the back of the privacy camel's back \cite{14_dvorak_2014}''.
-The wearable device was not acceptable to the public at large, making bystanders feel uncomfortable with the possibility of recording personal details, conversations, and photos.
-Many instances of assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} on wearers were also reported, resulting from a combination of privacy invasion and social tension\footnote{Google has come to represent gentrification in San Francisco ...
+One popular tech magazine called glass the ``straw the broke the back of the privacy camel's back \cite{14_dvorak_2014},'' and made bystanders feel uncomfortable with the possibility of recording personal details, conversations, and photos.
+Many instances of assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} on wearers were reported, resulting from a combination of privacy concerns and social tension\footnote{Google has come to represent gentrification in San Francisco ...
 [which] makes wearable device owners look and sound like one of the people whom residents of the city have come to feel oppressed by \cite{17_matyszczyk_2014}.
-The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers.} .
-The public was generally unsympathetic to the situation, tweeting or commenting, ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.
+The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers .
+The public was generally unsympathetic to the assults aggravated by social tension.
+Tweeting and comments included: ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.}.
 

### 2015-02-26 Tables(2)/app.tex
fixed tables in tables(2)
title

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Learnedyourbankaccountinformation & 90.91\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourbankaccountinformationAPPSERVER} \\ 
2 & Tookavideoofyouunclothed & 90.63\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouunclothedAPPSERVER} \\ 
3 & Learnedyoursocialsecuritynumber & 88.68\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyoursocialsecuritynumberAPPSERVER} \\ 
4 & Tookavideoofyouenteringinyourpinatanatm & 88.57\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMAPPSERVER} \\ 
5 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 78.05\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingAPPSERVER} \\ 
6 & Tookaphotoofyouunclothed & 77.78\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouunclothedAPPSERVER} \\ 
7 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorAPPSERVER} \\ 
8 & Learnedwhenandhowmuchyouhavesex & 73.08\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexAPPSERVER} \\ 
9 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 71.88\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingAPPSERVER} \\ 
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 71.43\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomeAPPSERVER} \\ 
11 & Tookavideoofyouintoxicated & 68.75\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouintoxicatedAPPSERVER} \\ 
12 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 66.67\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomAPPSERVER} \\ 
13 & Learnedyourcreditcardinformation & 65.52\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourcreditcardinformationAPPSERVER} \\ 
14 & Learnedyourusernameandpasswordforwebsites & 64.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesAPPSERVER} \\ 
15 & Learnedhowmuchmoneyyouhave & 63.41\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchmoneyyouhaveAPPSERVER} \\ 
16 & Tookphotosatwork(Withanoutward-Facingcamera) & 62.16\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)APPSERVER} \\ 
17 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 60.53\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomeAPPSERVER} \\ 
18 & Learnedhowmuchdebtyouhave & 59.46\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchdebtyouhaveAPPSERVER} \\ 
19 & Tookapictureofyoursignature & 59.26\% & \includegraphics[width = 2cm, height = 0.5cm]{tookapictureofyoursignatureAPPSERVER} \\ 
20 & Recordedyourphoneconversations & 56.67\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourphoneconversationsAPPSERVER} \\ 
21 & Recordedyourpassingconversations & 55.88\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourpassingconversationsAPPSERVER} \\ 
22 & Learnedyourfingerprintsomehow & 55.32\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourfingerprintsomehowAPPSERVER} \\ 
23 & Tookavideoofyouoff-Guard & 53.85\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouoff-guardAPPSERVER} \\ 
24 & Recordedyourworkconversations & 53.33\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourworkconversationsAPPSERVER} \\ 
25 & Tookaphotoofyouintoxicated & 53.13\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouintoxicatedAPPSERVER} \\ 
26 & Tookvideosatwork(Withanoutward-Facingcamera) & 51.85\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)APPSERVER} \\ 
27 & Sharedvideosyoutookwhicharealreadyonyourdevice & 51.61\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdeviceAPPSERVER} \\ 
28 & Learnedyouraddress & 51.16\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouraddressAPPSERVER} \\ 
29 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdeviceAPPSERVER} \\ 
30 & Learnedyourusernameforwebsites & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameforwebsitesAPPSERVER} \\ 
31 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 48.39\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomAPPSERVER} \\ 
32 & Learnedwhereyouworksomehow & 46.34\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouworksomehowAPPSERVER} \\ 
33 & Tookaphotoofyouoff-Guard & 45.95\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouoff-guardAPPSERVER} \\ 
34 & Learnedwhenyouwerelyingnervousorstressed & 41.46\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedAPPSERVER} \\ 
35 & Sharedphotosotherssenttoyousavedonyourdevice & 41.18\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdeviceAPPSERVER} \\ 
36 & Learnedwhereyoulivesomehow & 40.63\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyoulivesomehowAPPSERVER} \\ 
37 & Learnedwhatmedicalconditionsyouhave & 40.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhaveAPPSERVER} \\ 
38 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 38.3\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomAPPSERVER} \\ 
39 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 38.1\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)APPSERVER} \\ 
40 & Learnedwhatmedicationyoutake & 37.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicationyoutakeAPPSERVER} \\ 
41 & Learnedwhatwebsitesyougoto & 37.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatwebsitesyougotoAPPSERVER} \\ 
42 & Recordedthesoundaroundyou & 35.9\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedthesoundaroundyouAPPSERVER} \\ 
43 & Learnedwhenandhowmuchyouspendtimealone & 35.48\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealoneAPPSERVER} \\ 
44 & Learnedwhereyouarecurrentlygoing & 35.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingAPPSERVER} \\ 
45 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdeviceAPPSERVER} \\ 
46 & Learnedyourname & 32.56\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyournameAPPSERVER} \\ 
47 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 32.14\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceAPPSERVER} \\ 
48 & Learnedwhoyouwerespendingtimewith & 31.43\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithAPPSERVER} \\ 
49 & Sharedvideosotherssentyousavedonyourdevice & 30.56\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdeviceAPPSERVER} \\ 
50 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 30.0\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)APPSERVER} \\ 
51 & Learnedhowmuchyouuseyourcomputer & 28.57\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerAPPSERVER} \\ 
52 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 28.13\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomAPPSERVER} \\ 
53 & Sharedphotosyoutookwhicharealreadyonyourdevice & 27.27\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdeviceAPPSERVER} \\ 
54 & Learnedwhatproductsyoubuy & 26.32\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatproductsyoubuyAPPSERVER} \\ 
55 & Learnedwhenyouaresickorhealthy & 26.19\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouaresickorhealthyAPPSERVER} \\ 
56 & Trackedwhereyouare(Likeagps) & 25.0\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)APPSERVER} \\ 
57 & Learnedwhenyouwerehappyorhavingfun & 24.32\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunAPPSERVER} \\ 
58 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 22.58\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)APPSERVER} \\ 
59 & Learnedwhenandhowwellyouaresleeping & 21.43\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingAPPSERVER} \\ 
60 & Copiedanduploadedmusicfromyourdevice & 20.83\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedmusicfromyourdeviceAPPSERVER} \\ 
61 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 18.92\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureAPPSERVER} \\ 
62 & Learnedwhenyouarebusyorinterruptible & 17.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptibleAPPSERVER} \\ 
63 & Learnedwhenhowandhowmuchyouexercise & 16.67\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexerciseAPPSERVER} \\ 
64 & Learnedhowmuchyouuseyourphone & 15.79\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourphoneAPPSERVER} \\ 
65 & Learnedyourage & 14.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourageAPPSERVER} \\ 
66 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 13.79\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithAPPSERVER} \\ 
67 & Learnedwhenhowmuchandwhatyouareeating & 12.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingAPPSERVER} \\ 
68 & Learnedwhattelevisionshowsyouwatch & 11.43\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchAPPSERVER} \\ 
69 & Learnedyourgender & 9.52\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourgenderAPPSERVER} \\ 
70 & Learnedyourheartrate & 9.09\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourheartrateAPPSERVER} \\ 
71 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 6.98\% & \includegraphics[width = 2cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)APPSERVER} \\ 
72 & Learnedthelanguageyouwerespeaking & 2.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedthelanguageyouwerespeakingAPPSERVER} \\ 
\end{longtable}

\end{document}

### 2015-02-26 Tables(2)/collapsed.tex
fixed tables in tables(2)
title

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR(\%)}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR(\%)}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Tookavideoofyouunclothed & 95.97 & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouunclothedcombined} \\ 
2 & Learnedyourbankaccountinformation & 95.91 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourbankaccountinformationcombined} \\ 
3 & Learnedyoursocialsecuritynumber & 94.84 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyoursocialsecuritynumbercombined} \\ 
4 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMcombined} \\ 
5 & Tookaphotoofyouunclothed & 92.59 & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouunclothedcombined} \\ 
6 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
7 & Learnedyourusernameandpasswordforwebsites & 89.55 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitescombined} \\ 
8 & Learnedyourcreditcardinformation & 88.98 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourcreditcardinformationcombined} \\ 
9 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
 & \vdots & & \\
64 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & \includegraphics[width = 2cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
65 & Learnedwhenhowandhowmuchyouexercise & 38.66 & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexercisecombined} \\ 
66 & Learnedwhenyouwerehappyorhavingfun & 34.75 & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfuncombined} \\ 
67 & Learnedwhattelevisionshowsyouwatch & 30.2 & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchcombined} \\ 
68 & Learnedwhenyouarebusyorinterruptible & 29.5 & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptiblecombined} \\ 
69 & Copiedanduploadedmusicfromyourdevice & 28.06 & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedmusicfromyourdevicecombined} \\ 
70 & Learnedyourheartrate & 27.5 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourheartratecombined} \\ 
71 & Learnedyourage & 24.29 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouragecombined} \\ 
72 & Learnedthelanguageyouwerespeaking & 15.86 & \includegraphics[width = 2cm, height = 0.5cm]{learnedthelanguageyouwerespeakingcombined} \\ 
73 & Learnedyourgender & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourgendercombined} \\ 
\end{longtable}

\end{document}

### 2015-02-26 Tables(2)/friends.tex
fixed tables in tables(2)
title

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Tookavideoofyouenteringinyourpinatanatm & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMFRIENDS} \\  
2 & Learnedyoursocialsecuritynumber & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyoursocialsecuritynumberFRIENDS} \\  
3 & Learnedyourcreditcardinformation & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourcreditcardinformationFRIENDS} \\  
4 & Tookavideoofyouunclothed & 97.83\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouunclothedFRIENDS} \\  
5 & Learnedyourusernameandpasswordforwebsites & 96.77\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesFRIENDS} \\  
6 & Tookaphotoofyouunclothed & 96.15\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouunclothedFRIENDS} \\  
7 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 95.24\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorFRIENDS} \\  
8 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 94.87\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingFRIENDS} \\  
9 & Recordedyourworkconversations & 94.74\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourworkconversationsFRIENDS} \\  
10 & Learnedyourbankaccountinformation & 94.44\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourbankaccountinformationFRIENDS} \\  
11 & Recordedyourphoneconversations & 93.55\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourphoneconversationsFRIENDS} \\  
12 & Learnedwhatmedicalconditionsyouhave & 92.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhaveFRIENDS} \\  
13 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 91.89\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingFRIENDS} \\  
14 & Learnedhowmuchmoneyyouhave & 90.7\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchmoneyyouhaveFRIENDS} \\  
15 & Learnedyourusernameforwebsites & 90.32\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameforwebsitesFRIENDS} \\  
16 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 87.8\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomeFRIENDS} \\  
17 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 87.18\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdeviceFRIENDS} \\  
18 & Recordedyourpassingconversations & 86.11\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourpassingconversationsFRIENDS} \\  
19 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomeFRIENDS} \\  
20 & Learnedhowmuchdebtyouhave & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchdebtyouhaveFRIENDS} \\  
21 & Sharedphotosotherssenttoyousavedonyourdevice & 85.19\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdeviceFRIENDS} \\  
22 & Tookavideoofyouoff-Guard & 85.19\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouoff-guardFRIENDS} \\  
23 & Tookaphotoofyouoff-Guard & 83.33\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouoff-guardFRIENDS} \\  
24 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 82.86\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomFRIENDS} \\  
25 & Sharedvideosotherssentyousavedonyourdevice & 82.86\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdeviceFRIENDS} \\  
26 & Tookavideoofyouintoxicated & 81.48\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouintoxicatedFRIENDS} \\  
27 & Tookaphotoofyouintoxicated & 80.43\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouintoxicatedFRIENDS} \\  
28 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 80.0\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)FRIENDS} \\  
29 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 79.17\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceFRIENDS} \\  
30 & Learnedwhatmedicationyoutake & 79.17\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicationyoutakeFRIENDS} \\  
31 & Learnedwhenandhowmuchyouhavesex & 78.72\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexFRIENDS} \\  
32 & Learnedyourfingerprintsomehow & 77.78\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourfingerprintsomehowFRIENDS} \\  
33 & Tookphotosatwork(Withanoutward-Facingcamera) & 76.32\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)FRIENDS} \\  
34 & Sharedphotosyoutookwhicharealreadyonyourdevice & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdeviceFRIENDS} \\  
35 & Learnedwhenyouwerelyingnervousorstressed & 74.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedFRIENDS} \\  
36 & Tookvideosatwork(Withanoutward-Facingcamera) & 74.19\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)FRIENDS} \\  
37 & Learnedwhereyouarecurrentlygoing & 74.19\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingFRIENDS} \\  
38 & Learnedwhatwebsitesyougoto & 74.19\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatwebsitesyougotoFRIENDS} \\  
39 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 73.53\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)FRIENDS} \\  
40 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 73.17\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomFRIENDS} \\  
41 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 72.73\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomFRIENDS} \\  
42 & Learnedwhoyouwerespendingtimewith & 71.43\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithFRIENDS} \\  
43 & Recordedthesoundaroundyou & 71.43\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedthesoundaroundyouFRIENDS} \\  
44 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 70.0\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)FRIENDS} \\  
45 & Learnedwhereyouworksomehow & 69.57\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouworksomehowFRIENDS} \\  
46 & Learnedhowmuchyouuseyourphone & 67.44\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourphoneFRIENDS} \\  
47 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 63.89\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdeviceFRIENDS} \\  
48 & Tookapictureofyoursignature & 63.64\% & \includegraphics[width = 2cm, height = 0.5cm]{tookapictureofyoursignatureFRIENDS} \\  
49 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 63.27\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomFRIENDS} \\  
50 & Learnedyouraddress & 62.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouraddressFRIENDS} \\  
51 & Learnedwhereyoulivesomehow & 61.54\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyoulivesomehowFRIENDS} \\  
52 & Sharedvideosyoutookwhicharealreadyonyourdevice & 58.82\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdeviceFRIENDS} \\  
53 & Trackedwhereyouare(Likeagps) & 57.69\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)FRIENDS} \\  
54 & Learnedwhatproductsyoubuy & 57.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatproductsyoubuyFRIENDS} \\  
55 & Learnedwhenandhowmuchyouspendtimealone & 51.52\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealoneFRIENDS} \\  
56 & Learnedhowmuchyouuseyourcomputer & 51.22\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerFRIENDS} \\  
57 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureFRIENDS} \\  
58 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithFRIENDS} \\  
59 & Learnedyourname & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyournameFRIENDS} \\  
60 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 48.84\% & \includegraphics[width = 2cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)FRIENDS} \\  
61 & Learnedwhenandhowwellyouaresleeping & 43.9\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingFRIENDS} \\  
62 & Learnedwhenhowmuchandwhatyouareeating & 41.86\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingFRIENDS} \\  
63 & Learnedwhenyouarebusyorinterruptible & 40.63\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptibleFRIENDS} \\  
64 & Learnedwhenyouaresickorhealthy & 40.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouaresickorhealthyFRIENDS} \\  
65 & Learnedwhenyouwerehappyorhavingfun & 40.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunFRIENDS} \\  
66 & Learnedwhattelevisionshowsyouwatch & 38.46\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchFRIENDS} \\  
67 & Learnedwhenhowandhowmuchyouexercise & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexerciseFRIENDS} \\  
68 & Learnedyourheartrate & 21.82\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourheartrateFRIENDS} \\  
69 & Learnedyourage & 17.86\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourageFRIENDS} \\  
70 & Learnedthelanguageyouwerespeaking & 17.14\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedthelanguageyouwerespeakingFRIENDS} \\  
71 & Learnedyourgender & 15.91\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourgenderFRIENDS} \\  
72 & Copiedanduploadedmusicfromyourdevice & 4.76\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedmusicfromyourdeviceFRIENDS} \\  
\end{longtable}

\end{document}

### 2015-02-26 Tables(2)/recipient.tex
fixed tables in tables(2)
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | p{3cm} | p{1cm} | p{1cm} | p{2cm} |}
\hline
Rank & Recipient & VUR(\%) & Variance & Distribution\\
\hline
1& Work & 75.16 & 0.7742& \includegraphics[width = 2cm, height = 2cm]{../recipient_work}\\ 
2& Public & 72.41 & 0.9278& \includegraphics[width = 2cm, height = 2cm]{../recipient_pub}\\ 
3& Friends & 69.47 & 1.0764 & \includegraphics[width = 2cm, height = 2cm]{../recipient_friends}\\ 
4& All & 64.78 & 1.2334& \includegraphics[width = 2cm, height = 2cm]{../recipient_total}\\ 
5& Appserver & 42.28 & 1.7516& \includegraphics[width = 2cm, height = 2cm]{../recipient_app}\\ 
\hline
\end{tabular}
\end{center}
\end{table}

### 2015-02-26 Tables(2)/risk.tex
fixed tables in tables(2)
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocamerarisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassrisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityRisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionrisk} \\ 
 & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../risk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerRisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionrisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetrisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunRisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersrisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleRisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../emailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionrisk} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-02-26 Tables(2)/untitled folder 2/friends.tex
fixed tables in tables(2)
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
\hline
 Rank & Q &  VUR & Distribution  \\ 
\hline
1 & Learnedwhatmedicalconditionsyouhave & 92.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatmedicalconditionsyouhaveFRIENDS} \\ \hline 
2 & Learnedyouraddress & 62.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyouraddressFRIENDS} \\ \hline 
3 & Learnedwhenhowmuchandwhatyouareeating & 41.86\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenhowmuchandwhatyouareeatingFRIENDS} \\ \hline 
4 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 87.8\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)athomeFRIENDS} \\ \hline 
5 & Tookphotosatwork(Withanoutward-Facingcamera) & 76.32\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosatwork(withanoutward-facingcamera)FRIENDS} \\ \hline 
6 & Sharedvideosyoutookwhicharealreadyonyourdevice & 58.82\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosyoutookwhicharealreadyonyourdeviceFRIENDS} \\ \hline 
7 & Sharedphotosotherssenttoyousavedonyourdevice & 85.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosotherssenttoyousavedonyourdeviceFRIENDS} \\ \hline 
8 & Tookavideoofyouoff-Guard & 85.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouoff-guardFRIENDS} \\ \hline 
9 & Copiedanduploadedmusicfromyourdevice & 4.76\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedmusicfromyourdeviceFRIENDS} \\ \hline 
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)athomeFRIENDS} \\ \hline 
11 & Learnedhowmuchdebtyouhave & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchdebtyouhaveFRIENDS} \\ \hline 
12 & Learnedyourfingerprintsomehowwith & 77.78\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourfingerprintsomehowwithFRIENDS} \\ \hline 
13 & Tookvideosatwork(Withanoutward-Facingcamera) & 74.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosatwork(withanoutward-facingcamera)FRIENDS} \\ \hline 
14 & Learnedwhereyouarecurrentlygoing & 74.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyouarecurrentlygoingFRIENDS} \\ \hline 
15 & Learnedwhatwebsitesyougoto & 74.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatwebsitesyougotoFRIENDS} \\ \hline 
16 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 73.53\% & \includegraphics[width = 2cm, height = 0.5cm]{../trackedwhereyouareveryaccurately(whereyouareinaroom)FRIENDS} \\ \hline 
17 & Learnedwhattelevisionshowsyouwatch & 38.46\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhattelevisionshowsyouwatchFRIENDS} \\ \hline 
18 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 79.17\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceFRIENDS} \\ \hline 
19 & Learnedwhatmedicationyoutake & 79.17\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatmedicationyoutakeFRIENDS} \\ \hline 
20 & Learnedwhereyouworksomehow & 69.57\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyouworksomehowFRIENDS} \\ \hline 
21 & Learnedyourusernameandpasswordforwebsites & 96.77\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourusernameandpasswordforwebsitesFRIENDS} \\ \hline 
22 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 63.27\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofpeople(withanoutward-facingcamera)atrandomFRIENDS} \\ \hline 
23 & Recordedyourworkconversations & 94.74\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourworkconversationsFRIENDS} \\ \hline 
24 & Learnedhowmuchyouuseyourphone & 67.44\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchyouuseyourphoneFRIENDS} \\ \hline 
25 & Learnedthelanguageyouwerespeaking & 17.14\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedthelanguageyouwerespeakingFRIENDS} \\ \hline 
26 & Tookavideoofyouintoxicated & 81.48\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouintoxicatedFRIENDS} \\ \hline 
27 & Trackedwhereyouare(Likeagps) & 57.69\% & \includegraphics[width = 2cm, height = 0.5cm]{../trackedwhereyouare(likeaGPS)FRIENDS} \\ \hline 
28 & Learnedwhenandhowmuchyouspendtimealone & 51.52\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowmuchyouspendtimealoneFRIENDS} \\ \hline 
29 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureFRIENDS} \\ \hline 
30 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowcloseyouaretootherpeopleyouinteractwithFRIENDS} \\ \hline 
31 & Learnedyourname & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyournameFRIENDS} \\ \hline 
32 & Learnedhowmuchmoneyyouhave & 90.7\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchmoneyyouhaveFRIENDS} \\ \hline 
33 & Learnedwhoyouwerespendingtimewith & 71.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhoyouwerespendingtimewithFRIENDS} \\ \hline 
34 & Recordedthesoundaroundyou & 71.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedthesoundaroundyouFRIENDS} \\ \hline 
35 & Learnedyourusernameforwebsites & 90.32\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourusernameforwebsitesFRIENDS} \\ \hline 
36 & Tookavideoofyouunclothed & 97.83\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouunclothedFRIENDS} \\ \hline 
37 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 91.89\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookanincriminatingvideoofyoudoingsomethingembarrassingFRIENDS} \\ \hline 
38 & Learnedhowmuchyouuseyourcomputer & 51.22\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchyouuseyourcomputerFRIENDS} \\ \hline 
39 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 82.86\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)atrandomFRIENDS} \\ \hline 
40 & Sharedvideosotherssentyousavedonyourdevice & 82.86\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosotherssentyousavedonyourdeviceFRIENDS} \\ \hline 
41 & Learnedwhenhowandhowmuchyouexercise & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenhowandhowmuchyouexerciseFRIENDS} \\ \hline 
42 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 70.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)FRIENDS} \\ \hline 
43 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 72.73\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofpeople(withanoutward-facingcamera)atrandomFRIENDS} \\ \hline 
44 & Learnedwhenandhowwellyouaresleeping & 43.9\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowwellyouaresleepingFRIENDS} \\ \hline 
45 & Sharedphotosyoutookwhicharealreadyonyourdevice & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosyoutookwhicharealreadyonyourdeviceFRIENDS} \\ \hline 
46 & Recordedyourphoneconversations & 93.55\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourphoneconversationsFRIENDS} \\ \hline 
47 & Tookapictureofyoursignature & 63.64\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookapictureofyoursignatureFRIENDS} \\ \hline 
48 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 80.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyoutalkingtoyourself(makingvoicenotes)FRIENDS} \\ \hline 
49 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 94.87\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookanincriminatingphotoofyoudoingsomethingembarrassingFRIENDS} \\ \hline 
50 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 95.24\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouenteringinadigitalpasscodetoalockeddoorFRIENDS} \\ \hline 
51 & Learnedyourage & 17.86\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourageFRIENDS} \\ \hline 
52 & Learnedwhenyouarebusyorinterruptible & 40.63\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouarebusyorinterruptibleFRIENDS} \\ \hline 
53 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 48.84\% & \includegraphics[width = 2cm, height = 0.5cm]{../scannedyoureyetolearnyoureyepatterns(foreyetracking)FRIENDS} \\ \hline 
54 & Learnedyourgender & 15.91\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourgenderFRIENDS} \\ \hline 
55 & Learnedyourbankaccountinformation & 94.44\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourbankaccountinformationFRIENDS} \\ \hline 
56 & Tookaphotoofyouoff-Guard & 83.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouoff-guardFRIENDS} \\ \hline 
57 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 73.17\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)atrandomFRIENDS} \\ \hline 
58 & Tookavideoofyouenteringinyourpinatanatm & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouenteringinyourPINatanATMFRIENDS} \\ \hline 
59 & Learnedyoursocialsecuritynumber & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyoursocialsecuritynumberFRIENDS} \\ \hline 
60 & Learnedyourcreditcardinformation & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourcreditcardinformationFRIENDS} \\ \hline 
61 & Tookaphotoofyouintoxicated & 80.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouintoxicatedFRIENDS} \\ \hline 
62 & Tookaphotoofyouunclothed & 96.15\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouunclothedFRIENDS} \\ \hline 
63 & Learnedwhenandhowmuchyouhavesex & 78.72\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowmuchyouhavesexFRIENDS} \\ \hline 
64 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 63.89\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosyoudownloadedontheinternetsavedonyourdeviceFRIENDS} \\ \hline 
65 & Learnedwhenyouwerelyingnervousorstressed & 74.29\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouwerelyingnervousorstressedFRIENDS} \\ \hline 
66 & Learnedwhenyouaresickorhealthy & 40.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouaresickorhealthyFRIENDS} \\ \hline 
67 & Learnedwhenyouwerehappyorhavingfun & 40.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouwerehappyorhavingfunFRIENDS} \\ \hline 
68 & Recordedyourpassingconversations & 86.11\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourpassingconversationsFRIENDS} \\ \hline 
69 & Learnedyourheartrate & 21.82\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourheartrateFRIENDS} \\ \hline 
70 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 87.18\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedaudiorecordingsyoumadeonyourdeviceFRIENDS} \\ \hline 
71 & Learnedwhereyoulivesomehow & 61.54\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyoulivesomehowFRIENDS} \\ \hline 
72 & Learnedwhatproductsyoubuy & 57.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatproductsyoubuyFRIENDS} \\ \hline 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-02-26 Tables(2)/untitled folder 2/risk.tex
fixed tables in tables(2)
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Voice Based Emotion Detection  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionrisk} \\ 
Facial Detection  & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionrisk} \\ 
Facial Recognition  & 10.0 & 17.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionrisk} \\ 
Language Detection  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionrisk} \\ 
Gender Detection  & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionrisk} \\ 
Heart Rate Detection  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionrisk} \\ 
Age Detection  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionrisk} \\ 
Smartwatches  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesrisk} \\ 
Discreet Microphone  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophonerisk} \\ 
Location Tracking  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingrisk} \\ 
Electricity & 15.0 & 25.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityRisk} \\ 
Speech To Text  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextrisk} \\ 
Google Glass  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassrisk} \\ 
Laptops  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsrisk} \\ 
Email  & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../emailrisk} \\ 
Internet  & 10.0 & 15.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetrisk} \\ 
Smartphones  & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesrisk} \\ 
Discreet Video Camera  & 10.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocamerarisk} \\ 
Cubetastic  & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticrisk} \\ 
Voice Recognition  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionrisk} \\ 
Handgun & 40.0 & 60.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunRisk} \\ 
Lawnmower & 12.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerRisk} \\ 
Motorcycle & 27.0 & 45.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleRisk} \\ 
Fitness Trackers  & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersrisk} \\ 
\hline
\end{tabular}
\caption{Risk Table}
\label{top10}
\end{center}
\end{table}

### 2015-02-26 Tables(2)/work.tex
fixed tables in tables(2)
title

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Recordedyourworkconversations & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourworkconversationsWORKCONTACTS} \\  
2 & Tookaphotoofyouunclothed & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouunclothedWORKCONTACTS} \\  
3 & Tookavideoofyouunclothed & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouunclothedWORKCONTACTS} \\  
4 & Learnedyourbankaccountinformation & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourbankaccountinformationWORKCONTACTS} \\  
5 & Learnedyourcreditcardinformation & 95.12\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourcreditcardinformationWORKCONTACTS} \\  
6 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 94.59\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingWORKCONTACTS} \\  
7 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 94.29\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingWORKCONTACTS} \\  
8 & Learnedyourusernameandpasswordforwebsites & 94.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesWORKCONTACTS} \\  
9 & Learnedyoursocialsecuritynumber & 93.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyoursocialsecuritynumberWORKCONTACTS} \\  
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 93.55\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\  
11 & Learnedhowmuchmoneyyouhave & 93.1\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchmoneyyouhaveWORKCONTACTS} \\  
12 & Learnedwhenyouwerelyingnervousorstressed & 91.89\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedWORKCONTACTS} \\  
13 & Tookavideoofyouoff-Guard & 91.43\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouoff-guardWORKCONTACTS} \\  
14 & Recordedyourphoneconversations & 90.32\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourphoneconversationsWORKCONTACTS} \\  
15 & Learnedwhenandhowmuchyouhavesex & 90.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexWORKCONTACTS} \\  
16 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 89.19\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomeWORKCONTACTS} \\  
17 & Tookavideoofyouintoxicated & 88.89\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouintoxicatedWORKCONTACTS} \\  
18 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 88.57\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)WORKCONTACTS} \\  
19 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 88.24\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\  
20 & Recordedyourpassingconversations & 87.5\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourpassingconversationsWORKCONTACTS} \\  
21 & Tookavideoofyouenteringinyourpinatanatm & 87.5\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMWORKCONTACTS} \\  
22 & Learnedhowmuchdebtyouhave & 87.18\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchdebtyouhaveWORKCONTACTS} \\  
23 & Tookaphotoofyouintoxicated & 87.1\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouintoxicatedWORKCONTACTS} \\  
24 & Learnedwhatwebsitesyougoto & 86.84\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatwebsitesyougotoWORKCONTACTS} \\  
25 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 86.27\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdeviceWORKCONTACTS} \\  
26 & Tookapictureofyoursignature & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{tookapictureofyoursignatureWORKCONTACTS} \\  
27 & Learnedwhatmedicalconditionsyouhave & 85.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhaveWORKCONTACTS} \\  
28 & Learnedyourusernameforwebsites & 84.62\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameforwebsitesWORKCONTACTS} \\  
29 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 82.86\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdeviceWORKCONTACTS} \\  
30 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 82.05\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\  
31 & Learnedyouraddress & 81.58\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouraddressWORKCONTACTS} \\  
32 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 81.48\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomWORKCONTACTS} \\  
33 & Tookphotosatwork(Withanoutward-Facingcamera) & 81.48\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)WORKCONTACTS} \\  
34 & Learnedwhatmedicationyoutake & 81.25\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicationyoutakeWORKCONTACTS} \\  
35 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 81.08\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorWORKCONTACTS} \\  
36 & Learnedwhenandhowmuchyouspendtimealone & 80.95\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealoneWORKCONTACTS} \\  
37 & Tookaphotoofyouoff-Guard & 80.49\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouoff-guardWORKCONTACTS} \\  
38 & Sharedvideosotherssentyousavedonyourdevice & 80.49\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdeviceWORKCONTACTS} \\  
39 & Sharedphotosyoutookwhicharealreadyonyourdevice & 79.55\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\  
40 & Sharedvideosyoutookwhicharealreadyonyourdevice & 79.31\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdeviceWORKCONTACTS} \\  
41 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 78.13\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)WORKCONTACTS} \\  
42 & Learnedwhoyouwerespendingtimewith & 76.19\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithWORKCONTACTS} \\  
43 & Recordedthesoundaroundyou & 75.76\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedthesoundaroundyouWORKCONTACTS} \\  
44 & Sharedphotosotherssenttoyousavedonyourdevice & 75.61\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdeviceWORKCONTACTS} \\  
45 & Learnedwhenhowmuchandwhatyouareeating & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingWORKCONTACTS} \\  
46 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.22\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdeviceWORKCONTACTS} \\  
47 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 71.88\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomWORKCONTACTS} \\  
48 & Learnedyourfingerprintsomehow & 70.27\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourfingerprintsomehowWORKCONTACTS} \\  
49 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)WORKCONTACTS} \\  
50 & Learnedwhereyoulivesomehow & 69.44\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyoulivesomehowWORKCONTACTS} \\  
51 & Learnedhowmuchyouuseyourphone & 68.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourphoneWORKCONTACTS} \\  
52 & Learnedwhenhowandhowmuchyouexercise & 66.67\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexerciseWORKCONTACTS} \\  
53 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 66.67\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)WORKCONTACTS} \\  
54 & Learnedwhereyouarecurrentlygoing & 65.85\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingWORKCONTACTS} \\  
55 & Trackedwhereyouare(Likeagps) & 63.64\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)WORKCONTACTS} \\  
56 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 63.16\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperatureWORKCONTACTS} \\  
57 & Learnedwhatproductsyoubuy & 62.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatproductsyoubuyWORKCONTACTS} \\  
58 & Learnedwhenyouaresickorhealthy & 62.22\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouaresickorhealthyWORKCONTACTS} \\  
59 & Learnedwhenandhowwellyouaresleeping & 62.07\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingWORKCONTACTS} \\  
60 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 61.11\% & \includegraphics[width = 2cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)WORKCONTACTS} \\  
61 & Learnedwhereyouworksomehow & 57.14\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouworksomehowWORKCONTACTS} \\  
62 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 51.35\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithWORKCONTACTS} \\  
63 & Learnedhowmuchyouuseyourcomputer & 45.45\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerWORKCONTACTS} \\  
64 & Learnedyourheartrate & 44.12\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourheartrateWORKCONTACTS} \\  
65 & Learnedwhenyouwerehappyorhavingfun & 43.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunWORKCONTACTS} \\  
66 & Copiedanduploadedmusicfromyourdevice & 42.11\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedmusicfromyourdeviceWORKCONTACTS} \\  
67 & Learnedyourage & 36.67\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourageWORKCONTACTS} \\  
68 & Learnedwhenyouarebusyorinterruptible & 36.36\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptibleWORKCONTACTS} \\  
69 & Learnedwhattelevisionshowsyouwatch & 36.36\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchWORKCONTACTS} \\  
70 & Learnedthelanguageyouwerespeaking & 28.13\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedthelanguageyouwerespeakingWORKCONTACTS} \\  
71 & Learnedyourname & 26.47\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyournameWORKCONTACTS} \\  
72 & Learnedyourgender & 15.79\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourgenderWORKCONTACTS} \\  
\end{longtable}

\end{document}

### 2015-02-26 Tables(2)/excelp.py

@@ -1,0 +1,199 @@
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+from xlrd import open_workbook
+from numpy import median
+def parser(x):
+	x = open_workbook("data.xlsm")
+	sheet = x.sheet_by_index(3)
+	rtn = dict()
+	benefit_dic = dict()
+	risk_dic = dict()
+	final_dic = dict()
+	stat = dict()
+	temp = dict()
+	for j in range(312,323):
+		lst = []
+
+		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
+
+
+			for i in range(1,1785):
+				cat = sheet.cell_value(i,j)
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+				if arg > 100:
+					arg = 100
+				if sheet.cell_value(0,j) == "ben":
+					ben_arg = str(sheet.cell_value(i,3)).replace(" ", "")
+					if ben_arg+ "ben" in benefit_dic:
+						benefit_dic[ben_arg+ "ben"].append(arg)
+					else:
+						benefit_dic[ben_arg + "ben"] = [arg]
+
+
+				if str(sheet.cell_value(i,3)  +sheet.cell_value(0,j)) in rtn:
+					rtn[str(sheet.cell_value(i,3))  + sheet.cell_value(0,j)].append(arg)
+				else:
+					rtn[str(sheet.cell_value(i,3))  +sheet.cell_value(0,j)] = [arg]
+
+
+		else:
+			for i in range(1,1785):
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+					if arg > 100:
+						arg = 100
+					lst.append(int(arg))
+			if len(lst)!= 0:
+				check = sheet.cell_value(0,j)
+				if "Electricity" in check:
+					if "risk" in check:
+						check = "Electricity Risk"
+					else:
+						check = "Electricity Benefit"
+				elif "Motorcycle" in check:
+					if "risk" in check:
+						print("here it is")
+						check = "Motorcycle Risk"
+					else:
+						check = "Motorcycle Benefit"
+				elif "Handgun" in check:
+					if "risk" in check:
[…]

### 2015-02-26 Tables(2)/parser.py

@@ -1,0 +1,381 @@
+
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+
+def parse(text):
+
+	f = open(text,'r')
+	# friends = open("friends.tex",'w')
+	# work = open("work.tex",'w')
+	# pub = open("pub.tex",'w')
+	# app = open("app.tex",'w')
+	collapsed = open("collapsed.tex",'w')
+	VUR_combined = open("VURcombined.tex",'w')
+	recipient = open("recipient.tex",'w')
+	x = """\\documentclass[a4paper,12pt]{article}
+\\usepackage[cm]{fullpage}
+\\usepackage{longtable}
+\\usepackage{graphicx}
+\\begin{document}
+\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
+
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endfirsthead
+
+\\multicolumn{3}{c}%
+{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endhead
+
+\\hline \\multicolumn{4}{|r|}{{Continued on next page}} \\\\ \\hline
+\\endfoot
+\\hline 
+\\endlastfoot\n"""
+	recipient.write("""\\begin{table}[t]
+\\begin{center}
+\\small
+\\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
+\\hline
+Rank & Recipient & VUR & Variance & Distribution\\\\
+\\hline\n""")
+	# friends.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
[…]

### 2015-02-26 Tables(2)/untitled folder 2/untitled folder/histograms/learnedhowyouwerefeelingbasedonheartratebreathingand:ortemperature FRIENDSdsfasdfas.py

@@ -1,0 +1,63 @@
+
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+
+def parse(text):
+	f = open(text,'r')
+	line = f.readline()
+	prev = None
+	combined = []
+
+	while line:
+		x = line.split()
+		if prev != None and prev != x[0]:
+			plt.hist(edgecolor = "none",x = combined,color = 'green',bins = range(0,7),alpha = 0.5, align = 'mid', rwidth = 1)
+		# plt.tick_params(\
+  #   axis='x',          # changes apply to the x-axis
+  #   which='both',      # both major and minor ticks are affected
+  #   bottom='off',      # ticks along the bottom edge are off
+  #   top='off',         # ticks along the top edge are off
+  #   labelbottom='off') # labels along the bottom edge are off
+		#plt.xticks(np.arange(1,6))
+			plt.xticks([])
+			plt.yticks([])
+			plt.axis('off')
+
+
+			savefig(str(prev) + " combined", dpi=None, facecolor='w', edgecolor='w',
+			orientation='portrait', papertype=None, format=None,
+			transparent=False, bbox_inches='tight', pad_inches=0,
+			frameon=None)
+			combined = []
+			plt.clf()
+		prev = x[0]
+
+		numbers = list(x[2])
+
+		title = str(x[0])+ " " + str(x[1])
+		for i in range(len(numbers)):
+			numbers[i] = int(numbers[i])
+			combined.append(numbers[i])
+		plt.hist(edgecolor = "none",x = numbers,color = 'green',bins = range(0,7),alpha = 0.5, align = 'mid', rwidth = 1)
+		# plt.tick_params(\
+  #   axis='x',          # changes apply to the x-axis
+  #   which='both',      # both major and minor ticks are affected
+  #   bottom='off',      # ticks along the bottom edge are off
+  #   top='off',         # ticks along the top edge are off
+  #   labelbottom='off') # labels along the bottom edge are off
+		#plt.xticks(np.arange(1,6))
+		plt.xticks([])
+		plt.yticks([])
+		plt.axis('off')
+
+		savefig(title, dpi=None, facecolor='w', edgecolor='w',
+		orientation='portrait', papertype=None, format=None,
+		transparent=False, bbox_inches='tight', pad_inches=0,
+		frameon=None)
+		line = f.readline()
+		plt.clf()
+
+
+	
+parse("file.txt")

### 2015-03-03 tables-more/benefit.tex
started to look at results

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
Ben & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../ben} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 tables-more/pub.tex
started to look at results

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingphotoofyoudoingsomethingembarrassingPUBLIC} \\  
2 & Learnedyoursocialsecuritynumber & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyoursocialsecuritynumberPUBLIC} \\  
3 & Learnedhowmuchmoneyyouhave & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchmoneyyouhavePUBLIC} \\  
4 & Recordedyourphoneconversations & 97.22\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourphoneconversationsPUBLIC} \\  
5 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 96.97\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)athomePUBLIC} \\  
6 & Recordedyourworkconversations & 96.67\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourworkconversationsPUBLIC} \\  
7 & Sharedvideosotherssentyousavedonyourdevice & 95.83\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosotherssentyousavedonyourdevicePUBLIC} \\  
8 & Learnedyourbankaccountinformation & 95.83\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourbankaccountinformationPUBLIC} \\  
9 & Learnedyourusernameandpasswordforwebsites & 95.35\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameandpasswordforwebsitesPUBLIC} \\  
10 & Tookavideoofyouunclothed & 94.44\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouunclothedPUBLIC} \\  
11 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 94.12\% & \includegraphics[width = 2cm, height = 0.5cm]{tookanincriminatingvideoofyoudoingsomethingembarrassingPUBLIC} \\  
12 & Tookavideoofyouenteringinyourpinatanatm & 93.94\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinyourPINatanATMPUBLIC} \\  
13 & Learnedyourcreditcardinformation & 93.55\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourcreditcardinformationPUBLIC} \\  
14 & Learnedyouraddress & 93.18\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouraddressPUBLIC} \\  
15 & Trackedwhereyouare(Likeagps) & 92.11\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouare(likeaGPS)PUBLIC} \\  
16 & Tookaphotoofyouunclothed & 91.67\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouunclothedPUBLIC} \\  
17 & Tookavideoofyouintoxicated & 91.67\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouintoxicatedPUBLIC} \\  
18 & Tookaphotoofyouintoxicated & 90.7\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouintoxicatedPUBLIC} \\  
19 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 90.24\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)atrandomPUBLIC} \\  
20 & Learnedhowmuchdebtyouhave & 90.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchdebtyouhavePUBLIC} \\  
21 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 89.19\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouenteringinadigitalpasscodetoalockeddoorPUBLIC} \\  
22 & Learnedwhereyoulivesomehow & 87.88\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyoulivesomehowPUBLIC} \\  
23 & Learnedwhenandhowmuchyouhavesex & 87.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouhavesexPUBLIC} \\  
24 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 86.49\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofyou(withaninward-facingcamera)athomePUBLIC} \\  
25 & Learnedwhatmedicalconditionsyouhave & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicalconditionsyouhavePUBLIC} \\  
26 & Recordedyourpassingconversations & 85.29\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyourpassingconversationsPUBLIC} \\  
27 & Sharedphotosotherssenttoyousavedonyourdevice & 84.62\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosotherssenttoyousavedonyourdevicePUBLIC} \\  
28 & Tookvideosatwork(Withanoutward-Facingcamera) & 83.87\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosatwork(withanoutward-facingcamera)PUBLIC} \\  
29 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 83.33\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofyou(withaninward-facingcamera)atrandomPUBLIC} \\  
30 & Sharedvideosyoutookwhicharealreadyonyourdevice & 82.93\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoutookwhicharealreadyonyourdevicePUBLIC} \\  
31 & Tookphotosatwork(Withanoutward-Facingcamera) & 82.14\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosatwork(withanoutward-facingcamera)PUBLIC} \\  
32 & Learnedyourfingerprintsomehow & 80.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourfingerprintsomehowPUBLIC} \\  
33 & Tookaphotoofyouoff-Guard & 80.0\% & \includegraphics[width = 2cm, height = 0.5cm]{tookaphotoofyouoff-guardPUBLIC} \\  
34 & Tookavideoofyouoff-Guard & 79.17\% & \includegraphics[width = 2cm, height = 0.5cm]{tookavideoofyouoff-guardPUBLIC} \\  
35 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 78.05\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedyoutalkingtoyourself(makingvoicenotes)PUBLIC} \\  
36 & Sharedphotosyoutookwhicharealreadyonyourdevice & 77.78\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoutookwhicharealreadyonyourdevicePUBLIC} \\  
37 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 76.19\% & \includegraphics[width = 2cm, height = 0.5cm]{trackedwhereyouareveryaccurately(whereyouareinaroom)PUBLIC} \\  
38 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 76.09\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedphotosyoudownloadedfromtheinternetsavedonyourdevicePUBLIC} \\  
39 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 75.61\% & \includegraphics[width = 2cm, height = 0.5cm]{tookvideosofpeople(withanoutward-facingcamera)atrandomPUBLIC} \\  
40 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedaudiorecordingsyoumadeonyourdevicePUBLIC} \\  
41 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{sharedvideosyoudownloadedontheinternetsavedonyourdevicePUBLIC} \\  
42 & Learnedwhenyouwerelyingnervousorstressed & 74.36\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerelyingnervousorstressedPUBLIC} \\  
43 & Learnedyourusernameforwebsites & 74.29\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourusernameforwebsitesPUBLIC} \\  
44 & Learnedwhatmedicationyoutake & 73.68\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatmedicationyoutakePUBLIC} \\  
45 & Learnedwhatwebsitesyougoto & 70.27\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatwebsitesyougotoPUBLIC} \\  
46 & Learnedwhenandhowmuchyouspendtimealone & 69.44\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowmuchyouspendtimealonePUBLIC} \\  
47 & Learnedyourname & 68.97\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyournamePUBLIC} \\  
48 & Learnedwhereyouarecurrentlygoing & 68.75\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouarecurrentlygoingPUBLIC} \\  
49 & Learnedwhereyouworksomehow & 64.86\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhereyouworksomehowPUBLIC} \\  
50 & Recordedthesoundaroundyou & 64.71\% & \includegraphics[width = 2cm, height = 0.5cm]{recordedthesoundaroundyouPUBLIC} \\  
51 & Tookapictureofyoursignature & 64.52\% & \includegraphics[width = 2cm, height = 0.5cm]{tookapictureofyoursignaturePUBLIC} \\  
52 & Learnedwhenyouaresickorhealthy & 61.9\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouaresickorhealthyPUBLIC} \\  
53 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 61.22\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowcloseyouaretootherpeopleyouinteractwithPUBLIC} \\  
54 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.11\% & \includegraphics[width = 2cm, height = 0.5cm]{tookphotosofpeople(withanoutward-facingcamera)atrandomPUBLIC} \\  
55 & Learnedwhoyouwerespendingtimewith & 60.0\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhoyouwerespendingtimewithPUBLIC} \\  
56 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 59.46\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)PUBLIC} \\  
57 & Learnedhowmuchyouuseyourphone & 56.1\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourphonePUBLIC} \\  
58 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 55.56\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturePUBLIC} \\  
59 & Learnedwhatproductsyoubuy & 55.56\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhatproductsyoubuyPUBLIC} \\  
60 & Learnedhowmuchyouuseyourcomputer & 52.5\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedhowmuchyouuseyourcomputerPUBLIC} \\  
61 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{scannedyoureyetolearnyoureyepatterns(foreyetracking)PUBLIC} \\  
62 & Learnedwhenhowmuchandwhatyouareeating & 45.71\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowmuchandwhatyouareeatingPUBLIC} \\  
63 & Learnedwhenandhowwellyouaresleeping & 41.94\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenandhowwellyouaresleepingPUBLIC} \\  
64 & Copiedanduploadedmusicfromyourdevice & 37.5\% & \includegraphics[width = 2cm, height = 0.5cm]{copiedanduploadedmusicfromyourdevicePUBLIC} \\  
65 & Learnedyourheartrate & 36.84\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourheartratePUBLIC} \\  
66 & Learnedwhenhowandhowmuchyouexercise & 34.48\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenhowandhowmuchyouexercisePUBLIC} \\  
67 & Learnedyourage & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyouragePUBLIC} \\  
68 & Learnedwhattelevisionshowsyouwatch & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhattelevisionshowsyouwatchPUBLIC} \\  
69 & Learnedwhenyouwerehappyorhavingfun & 32.43\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouwerehappyorhavingfunPUBLIC} \\  
70 & Learnedwhenyouarebusyorinterruptible & 28.89\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedwhenyouarebusyorinterruptiblePUBLIC} \\  
71 & Learnedyourgender & 19.44\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedyourgenderPUBLIC} \\  
72 & Learnedthelanguageyouwerespeaking & 18.42\% & \includegraphics[width = 2cm, height = 0.5cm]{learnedthelanguageyouwerespeakingPUBLIC} \\  
\end{longtable}

\end{document}

### 2015-03-03 tables-more/riskbenefit.tex
started to look at results

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
&\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
\hline
Technology &  Median & Q1 & Q3 & Distribution &  Median& Q1 & Q3 & Distribution   \\ 
\hline
location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\

Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerRisk} & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\

Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleRisk}  & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunRisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\

\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 tables-more/untitled folder 2/benefit.tex
started to look at results

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Language Detection  & 15.0 & 35.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
Email  & 29.0 & 50.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
Heart Rate Detection  & 26.0 & 40.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
Cubetastic  & 10.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
Speech To Text  & 15.0 & 25.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
Location Tracking  & 20.0 & 40.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
Facial Detection  & 10.0 & 20.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
Age Detection  & 10.0 & 12.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
Discreet Video Camera  & 15.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
Facial Recognition  & 12.5 & 22.0 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
Internet  & 45.0 & 65.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
Voice Recognition  & 15.0 & 25.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
Discreet Microphone  & 10.0 & 15.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
Motorcycle & 12.0 & 20.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Gender Detection  & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
Voice Based Emotion Detection  & 10.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
Smartwatches  & 10.0 & 20.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
Electricity & 50.0 & 88.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
Google Glass  & 12.0 & 20.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
Laptops  & 40.0 & 60.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
Lawnmower & 15.0 & 24.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Handgun & 10.0 & 20.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
Smartphones  & 30.0 & 50.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
Fitness Trackers  & 10.0 & 18.5 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
\hline
\end{tabular}
\caption{Benefit Table}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 tables-more/untitled folder 2/pub.tex
started to look at results

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
\hline
 Rank & Q &  VUR & Distribution  \\ 
\hline
1 & Learnedwhenandhowmuchyouhavesex & 87.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowmuchyouhavesexPUBLIC} \\ \hline 
2 & Copiedanduploadedmusicfromyourdevice & 37.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedmusicfromyourdevicePUBLIC} \\ \hline 
3 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.11\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofpeople(withanoutward-facingcamera)atrandomPUBLIC} \\ \hline 
4 & Learnedyourcreditcardinformation & 93.55\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourcreditcardinformationPUBLIC} \\ \hline 
5 & Learnedwhenandhowmuchyouspendtimealone & 69.44\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowmuchyouspendtimealonePUBLIC} \\ \hline 
6 & Learnedwhereyouarecurrentlygoing & 68.75\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyouarecurrentlygoingPUBLIC} \\ \hline 
7 & Tookphotosatwork(Withanoutward-Facingcamera) & 82.14\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosatwork(withanoutward-facingcamera)PUBLIC} \\ \hline 
8 & Tookavideoofyouunclothed & 94.44\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouunclothedPUBLIC} \\ \hline 
9 & Learnedwhenhowandhowmuchyouexercise & 34.48\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenhowandhowmuchyouexercisePUBLIC} \\ \hline 
10 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 94.12\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookanincriminatingvideoofyoudoingsomethingembarrassingPUBLIC} \\ \hline 
11 & Sharedphotosyoutookwhicharealreadyonyourdevice & 77.78\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosyoutookwhicharealreadyonyourdevicePUBLIC} \\ \hline 
12 & Trackedwhereyouare(Likeagps) & 92.11\% & \includegraphics[width = 2cm, height = 0.5cm]{../trackedwhereyouare(likeaGPS)PUBLIC} \\ \hline 
13 & Tookavideoofyouenteringinyourpinatanatm & 93.94\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouenteringinyourPINatanATMPUBLIC} \\ \hline 
14 & Learnedyourusernameandpasswordforwebsites & 95.35\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourusernameandpasswordforwebsitesPUBLIC} \\ \hline 
15 & Learnedwhatwebsitesyougoto & 70.27\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatwebsitesyougotoPUBLIC} \\ \hline 
16 & Recordedthesoundaroundyou & 64.71\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedthesoundaroundyouPUBLIC} \\ \hline 
17 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 59.46\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)PUBLIC} \\ \hline 
18 & Learnedyourusernameforwebsites & 74.29\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourusernameforwebsitesPUBLIC} \\ \hline 
19 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 90.24\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)atrandomPUBLIC} \\ \hline 
20 & Learnedwhatmedicationyoutake & 73.68\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatmedicationyoutakePUBLIC} \\ \hline 
21 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 89.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouenteringinadigitalpasscodetoalockeddoorPUBLIC} \\ \hline 
22 & Learnedwhereyoulivesomehow & 87.88\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyoulivesomehowPUBLIC} \\ \hline 
23 & Learnedwhenyouarebusyorinterruptible & 28.89\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouarebusyorinterruptiblePUBLIC} \\ \hline 
24 & Learnedyouraddress & 93.18\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyouraddressPUBLIC} \\ \hline 
25 & Learnedwhenandhowwellyouaresleeping & 41.94\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenandhowwellyouaresleepingPUBLIC} \\ \hline 
26 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 50.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../scannedyoureyetolearnyoureyepatterns(foreyetracking)PUBLIC} \\ \hline 
27 & Tookaphotoofyouintoxicated & 90.7\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouintoxicatedPUBLIC} \\ \hline 
28 & Learnedwhenhowmuchandwhatyouareeating & 45.71\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenhowmuchandwhatyouareeatingPUBLIC} \\ \hline 
29 & Tookapictureofyoursignature & 64.52\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookapictureofyoursignaturePUBLIC} \\ \hline 
30 & Learnedyourname & 68.97\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyournamePUBLIC} \\ \hline 
31 & Learnedwhereyouworksomehow & 64.86\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhereyouworksomehowPUBLIC} \\ \hline 
32 & Learnedwhoyouwerespendingtimewith & 60.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhoyouwerespendingtimewithPUBLIC} \\ \hline 
33 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 76.09\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosyoudownloadedfromtheinternetsavedonyourdevicePUBLIC} \\ \hline 
34 & Learnedwhenyouwerehappyorhavingfun & 32.43\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouwerehappyorhavingfunPUBLIC} \\ \hline 
35 & Learnedyourage & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyouragePUBLIC} \\ \hline 
36 & Learnedwhattelevisionshowsyouwatch & 33.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhattelevisionshowsyouwatchPUBLIC} \\ \hline 
37 & Tookvideosatwork(Withanoutward-Facingcamera) & 83.87\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosatwork(withanoutward-facingcamera)PUBLIC} \\ \hline 
38 & Sharedvideosotherssentyousavedonyourdevice & 95.83\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosotherssentyousavedonyourdevicePUBLIC} \\ \hline 
39 & Learnedyourbankaccountinformation & 95.83\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourbankaccountinformationPUBLIC} \\ \hline 
40 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 78.05\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyoutalkingtoyourself(makingvoicenotes)PUBLIC} \\ \hline 
41 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../copiedanduploadedaudiorecordingsyoumadeonyourdevicePUBLIC} \\ \hline 
42 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 75.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosyoudownloadedontheinternetsavedonyourdevicePUBLIC} \\ \hline 
43 & Learnedwhenyouaresickorhealthy & 61.9\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouaresickorhealthyPUBLIC} \\ \hline 
44 & Learnedyourfingerprintsomehow & 80.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourfingerprintsomehowPUBLIC} \\ \hline 
45 & Tookaphotoofyouoff-Guard & 80.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouoff-guardPUBLIC} \\ \hline 
46 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 55.56\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturePUBLIC} \\ \hline 
47 & Learnedwhatproductsyoubuy & 55.56\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatproductsyoubuyPUBLIC} \\ \hline 
48 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 86.49\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofyou(withaninward-facingcamera)athomePUBLIC} \\ \hline 
49 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 61.22\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowcloseyouaretootherpeopleyouinteractwithPUBLIC} \\ \hline 
50 & Tookavideoofyouoff-Guard & 79.17\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouoff-guardPUBLIC} \\ \hline 
51 & Learnedhowmuchdebtyouhave & 90.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchdebtyouhavePUBLIC} \\ \hline 
52 & Learnedwhatmedicalconditionsyouhave & 85.71\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhatmedicalconditionsyouhavePUBLIC} \\ \hline 
53 & Learnedyourgender & 19.44\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourgenderPUBLIC} \\ \hline 
54 & Learnedthelanguageyouwerespeaking & 18.42\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedthelanguageyouwerespeakingPUBLIC} \\ \hline 
55 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 76.19\% & \includegraphics[width = 2cm, height = 0.5cm]{../trackedwhereyouareveryaccurately(whereyouareinaroom)PUBLIC} \\ \hline 
56 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 83.33\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)atrandomPUBLIC} \\ \hline 
57 & Recordedyourworkconversations & 96.67\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourworkconversationsPUBLIC} \\ \hline 
58 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookanincriminatingphotoofyoudoingsomethingembarrassingPUBLIC} \\ \hline 
59 & Learnedyoursocialsecuritynumber & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyoursocialsecuritynumberPUBLIC} \\ \hline 
60 & Learnedhowmuchmoneyyouhave & 100.0\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchmoneyyouhavePUBLIC} \\ \hline 
61 & Sharedvideosyoutookwhicharealreadyonyourdevice & 82.93\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedvideosyoutookwhicharealreadyonyourdevicePUBLIC} \\ \hline 
62 & Sharedphotosotherssenttoyousavedonyourdevice & 84.62\% & \includegraphics[width = 2cm, height = 0.5cm]{../sharedphotosotherssenttoyousavedonyourdevicePUBLIC} \\ \hline 
63 & Tookaphotoofyouunclothed & 91.67\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookaphotoofyouunclothedPUBLIC} \\ \hline 
64 & Tookavideoofyouintoxicated & 91.67\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookavideoofyouintoxicatedPUBLIC} \\ \hline 
65 & Recordedyourphoneconversations & 97.22\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourphoneconversationsPUBLIC} \\ \hline 
66 & Recordedyourpassingconversations & 85.29\% & \includegraphics[width = 2cm, height = 0.5cm]{../recordedyourpassingconversationsPUBLIC} \\ \hline 
67 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 75.61\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookvideosofpeople(withanoutward-facingcamera)atrandomPUBLIC} \\ \hline 
68 & Learnedwhenyouwerelyingnervousorstressed & 74.36\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedwhenyouwerelyingnervousorstressedPUBLIC} \\ \hline 
69 & Learnedhowmuchyouuseyourphone & 56.1\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchyouuseyourphonePUBLIC} \\ \hline 
70 & Learnedyourheartrate & 36.84\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedyourheartratePUBLIC} \\ \hline 
71 & Learnedhowmuchyouuseyourcomputer & 52.5\% & \includegraphics[width = 2cm, height = 0.5cm]{../learnedhowmuchyouuseyourcomputerPUBLIC} \\ \hline 
72 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 96.97\% & \includegraphics[width = 2cm, height = 0.5cm]{../tookphotosofyou(withaninward-facingcamera)athomePUBLIC} \\ \hline 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 tables-more/wearables-survey-paper-master/abstract.tex
started to look at results

--- 2015-01-08 wearables_survey.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
-\documentclass{acm_proc_article-sp}
-
-\usepackage{color}
-
-%%% still need to break urls
-
-\usepackage[hyphens]{url}
-
-\def\etal{{\it et al.~}}
-
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
-
-\begin{document}
-
-\title{Risk Perceptions for Wearable Devices}
-%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{Note
-%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}
-
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
-\numberofauthors{1}
-\author{
- \alignauthor Anonymous\\
-   \vspace{0.5em}
-   \affaddr{Some Place}
-}
-
-\maketitle
 \begin{abstract}
@@
 \keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
-
-%%%%%%%%%%%%%%%%%%%
-%%%         PAPER BODY         %%%
-%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing.
-Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking.
-Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-
-The market for wearable devices is currently in infancy.
-It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline.
-A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}.
-It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}.
-Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.
-
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns exposure of users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.
-
-To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
-
-We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
-This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
-
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
-
-%LL: this commented out for anonymity; can comment back in later.
-%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.
-
-%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here.
-The rest were put at the end of the paper, as you requested.
-
-\subsection{Methodology Motivation}
-\subsubsection{Smartphone Risk Scenarios}
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
-
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
-
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
-
-\subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
-\end{itemize}
-
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
-
-\subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
-
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
-
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
-
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{prompt.pdf}
-	\caption{An example of a wearable scenario question participants saw while taking the survey.}
-	\label{fig:prompt}
-\end{figure}
-
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
-\end{packed_item}
-
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
-
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
-
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
-
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
-
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
-
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
-
-\subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
-
-\subsection{Focus Group}
-We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
-Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
-
-\subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
-We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784.
-Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).
-
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
-The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
-We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission).
-Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-
-In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-In this section, we present our survey results.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device Type}
-Participants had unique VUR rates for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-\subsubsection{Demographic Factors}
-
-Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
-
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device Type & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device Type & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device Type & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device type (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device type was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Perceived Concerns for Wearable Devices}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
-
-\subsection{Future Research Directions}
-Wearables are still in infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-
-While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.
-
-\subsection{Limitations}
-One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo.
-We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
-
-\section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
-
-\subsection{Ubiquitous Sensing}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-
-\subsection{Smartphones and Wearables Concerns}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
-
-\subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-
-%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics.
-For this reason, people were heavily primed for the open-ended question.
-However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index.
-The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.
-
-%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-Participants rated how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
-
-%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
-
-%%%%%%%%%%%%%%%%%%%
-%%%            BIB & ACKS          %%%
-%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{abbrv}
-\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography
-
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
-(e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
-
-\textit{Do not consider the costs or risks associated with these items.
-It is true, for example, that sometimes swimmers can drown.
-But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least risky technology at 10 and assign higher numbers for the more risky technologies.
-(For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
-(e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
-
-\textit{Do not consider the costs or benefits associated with these items.
-It is true, for example, that electricity also creates a market for home appliances.
-But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
-
-\textit{Please rate the following technologies below with a number.
-We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
-Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies.
-(For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}
-
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
-%\section{Coding Label Definitions}
-%\label{sec:coding}
-%
-%Privacy: ``privacy,'' revealing personal information, spying. \\
-%Security:  ``security,'' compromise, malware, hacking. \\
-%GPS tracking: ``location,'' ``GPS,'' being monitored. 
-%
-%Unaware use: using data without permission or in a different way than understood by user. \\
-%Unaware collection: collecting data without permission. \\
-%Unaware access: disclosure of data without permission. \\
-%False information: inaccurate or maliciously false data.
-%
-%Health Risk: radiation, cancer, or long-term effects.\\
-%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-%Discomfort: eye strain, headache, obscured vision, irritation. \\
-%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-%Theft: the device getting stolen. 
-%
-%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-%Social Stigma: judgment, hate, or bystander discomfort.\\ 
-%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
-%
-%Miscellaneous: odd comments, uncommon concerns. \\
-%None: ``None,'' no threat, perceiving no big concerns \\
-%Don't know: ``do not know,'' hinting at confusion \\
-%Don't care: `` do not care,'' nonchalant answers
-
-%\section{Detailed Tech Rankings}
-
-\balancecolumns
-
-% That's all folks!
-\end{document}
-\\

### 2015-03-03 tables-more/wearables-survey-paper-master/results.tex
started to look at results

--- 2015-02-20 results.tex
@@
 \subsection{Concern Factors}
-In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
+Many factors impact participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
 We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
@@
 
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy}.
-This top concern surpassed all other concerns by about an order of magnitude or more (see Table \ref{openresponses}).
+Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy} (see Table \ref{openresponses}).
 Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).

### 2015-03-03 tex-inputs/results-recipient.tex
started to look at results

@@
 
-{\color {red} we're not saying that there is no distinction, just that there is more distinction between people and the app server."users make little distinction between sharing data with friends, co-workers, or the general public”: at first sight, this result is in conflict with privacy studies specifically in the social arena (e.g., Facebook).
-The authors may want to comment on this fact if they have any explanation.}
-
-{\color {red} add a discussion here about the variance between the recipients. Mention specific numbers. Was there a change in distribution just because we changed the recipient type?}
+{\color {red} We do not claim that there is no distinction between the friends, public, and work contact recipients, because people have been shown to behave differently, especially in the social arena (cite studies here).
+People are more comfortable sharing certain data types with certain recipients (refer to the table of all questions with ranks by each recipient here).
+There are other data types which are universally concerning, and universally unconcerning, and the magnitude of the sentiment varies by recipient.
+As you can see in Table (J still needs to do this table), the VUR rate for each recipient is negatively correlated with the standard deviation of the answers.
+Additionally, we see that there is greater distinction between sharing people and the app server--people are comfortable sharing data they would feel uncomfortable sharing with at human recipient, and the magnitude of concerns is might more significant compared to the other recipients.}

### 2015-03-03 tex-inputs/results-type.tex
sprinkled things to talk about inline
started to look at results

@@
 Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
+As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns, {\color {red} and are unanimously considered to be concerning}.
 Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
 
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
+Also regardless of the other factors, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
+{\color {red} As seen in Table \ref{top10}, participants had distributed opinions on how risky this information was to be shared.
+A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.}
+
+{\color {red} talk about the variance of the data types here, referring to the table in the appendix.
+Which were the highest in variance?
+Which were the unanimous?
+Which one had a spread?
+Were there any that were specifically polarized?
+J has yet to give me the table for this so I can talk about it.
+But the most unanimous ones seemed to be the highest-concerning ones, whereas the least concerning ones were more distributed.
+There are not any which are unanimously considered medium risk or to be not risky.}
 

### 2015-03-03 tables-more/untitled folder 2/excelp.py

@@ -1,0 +1,136 @@
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+from xlrd import open_workbook
+def parser(x):
+	x = open_workbook("data.xlsm")
+	sheet = x.sheet_by_index(3)
+	rtn = dict()
+	stat = dict()
+	temp = dict()
+	for j in range(312,323):
+		lst = []
+
+		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
+			for i in range(1,1785):
+				cat = sheet.cell_value(i,j)
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+				if arg > 100:
+					arg = 100
+				if str(sheet.cell_value(i,3) +" " +sheet.cell_value(0,j)) in rtn:
+					rtn[str(sheet.cell_value(i,3)) +" " + sheet.cell_value(0,j)].append(arg)
+				else:
+					rtn[str(sheet.cell_value(i,3)) + " " +sheet.cell_value(0,j)] = [arg]
+
+
+		else:
+			for i in range(1,1785):
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+					if arg > 100:
+						arg = 100
+					lst.append(int(arg))
+			if len(lst)!= 0:
+				check = sheet.cell_value(0,j)
+				if "Electricity" in check:
+					if "risk" in check:
+						check = "Electricity Risk"
+					else:
+						check = "Electricity Benefit"
+				elif "Motorcycle" in check:
+					if "risk" in check:
+						check = "Motorcycle Risk"
+					else:
+						check = "Motorcycle Benefit"
+				elif "Handgun" in check:
+					if "risk" in check:
+						check = "Handgun Risk"
+					else:
+						check = "Handgun Benefit"
+				elif "Lawnmower" in check:
+					if "risk" in check:
+						check = "Lawnmower Risk"
+					else:
+						check = "Lawnmower Benefit"
+				rtn[check] = lst
+	f = open("benefit.tex","w")
+	g = open("risk.tex","w")
[…]

### 2015-03-03 tex-inputs/results-type.tex
terrible 10 table

@@
 \small
-\begin{tabular}{| r | l | r |}
+\begin{tabular}{| r | l | r | l |c |}
 \hline
-Rank & Data &  VUR  \\
+Rank & Data & VUR & sd & Distribution \\
 \hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
+1 & a video of you unclothed & 95.97\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouunclothedcombined} \\
+2 & bank account information & 95.91\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourbankaccountinformationcombined}  \\
+3 & social security number & 94.84\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyoursocialsecuritynumbercombined}\\
+4 & video of you entering in your PIN & 92.67\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouenteringinyourPINatanATMcombined}\\
+5 & a photo of you unclothed & 92.59\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookaphotoofyouunclothedcombined}\\
+6 & an incriminating/embarrassing photo of you & 91.39\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined}\\
+7 & username and password for websites & 89.55\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourusernameandpasswordforwebsitescombined}\\
+8 & credit card information & 88.98\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourcreditcardinformationcombined}\\
+9 & an incriminating/embarrassing video of you & 88.41\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined}\\
+10 & a random (inward-facing) photo you at home & 87.50\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookphotosofyou(withaninward-facingcamera)athomecombined}\\
  & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
+64 & eye movement patterns (for eye tracking) & 40.51\%& number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\
+65 & when and how much you exercise  & 38.66\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenhowandhowmuchyouexercisecombined}\\
+66 & when you are happy or having fun  & 34.75\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouwerehappyorhavingfuncombined}\\
+67 & which television shows you watch & 30.20\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhattelevisionshowsyouwatchcombined}\\
+68 & when you are busy or interruptible  & 29.50\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouarebusyorinterruptiblecombined}\\
+69 & music from your device  & 28.06\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/copiedanduploadedmusicfromyourdevicecombined}\\
+70 & your heart rate & 27.50\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourheartratecombined} \\
+71 & your age & 24.29\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyouragecombined}\\
+72 & the language you speak & 15.86\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedthelanguageyouwerespeakingcombined}\\
+73 & your gender & 15.00\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourgendercombined}\\ 
 \hline

### 2015-03-03 tex-inputs/results-recipient.tex
bad recipient table

@@
 Additionally, we see that there is greater distinction between sharing people and the app server--people are comfortable sharing data they would feel uncomfortable sharing with at human recipient, and the magnitude of concerns is might more significant compared to the other recipients.}
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| r | l | r | l |c |}
+\hline
+Rank & Recipient & VUR & sd & Distribution \\
+\hline
+1 & Work Contacts & 75.16\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
+2 & Public & 72.41\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
+3 & Friends & 69.47\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
+4 & App's Server & 42.28\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
+\hline
+\end{tabular}
+\caption{The 10 most and least upsetting data types, across all recipients.}
+\label{recipient-table}
+\end{center}
+\end{table}
+
+%\begin{table}[t]
+%\begin{center}
+%\begin{tabular}{|l|r|r|r|r|}
+%\hline
+%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
+%\hline
+%Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
+%Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
+%Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
+%Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
+%Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
+%Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
+%\hline
+%\end{tabular}
+%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
+%\label{recipient}
+%\end{center}
+%\end{table}

### 2015-03-03 tex-inputs/results-type.tex
bad recipient table

@@
 Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns, {\color {red} and are unanimously considered to be concerning}.
+As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, {\color {red} and are unanimously considered to be concerning}.
 Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
@@
 Also regardless of the other factors, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-{\color {red} As seen in Table \ref{top10}, participants had distributed opinions on how risky this information was to be shared.
+{\color {red} As seen in Table \ref{top10-table}, participants had distributed opinions on how risky this information was to be shared.
 A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.}
@@
 \caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
+\label{top10-table}
 \end{center}

### 2015-03-03 Tables(2)/excelp.py
get rid of redundant files and confusing folders

@@ -1,199 +1,0 @@
-import csv
-import numpy as np
-import matplotlib.pyplot as plt
-from pylab import *
-from xlrd import open_workbook
-from numpy import median
-def parser(x):
-	x = open_workbook("data.xlsm")
-	sheet = x.sheet_by_index(3)
-	rtn = dict()
-	benefit_dic = dict()
-	risk_dic = dict()
-	final_dic = dict()
-	stat = dict()
-	temp = dict()
-	for j in range(312,323):
-		lst = []
-
-		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
-
-
-			for i in range(1,1785):
-				cat = sheet.cell_value(i,j)
-				arg = sheet.cell_value(i,j)
-				if arg != '':
-					if type(arg) != float:
-						print('error', i,j,arg)
-						return
-				if arg > 100:
-					arg = 100
-				if sheet.cell_value(0,j) == "ben":
-					ben_arg = str(sheet.cell_value(i,3)).replace(" ", "")
-					if ben_arg+ "ben" in benefit_dic:
-						benefit_dic[ben_arg+ "ben"].append(arg)
-					else:
-						benefit_dic[ben_arg + "ben"] = [arg]
-
-
-				if str(sheet.cell_value(i,3)  +sheet.cell_value(0,j)) in rtn:
-					rtn[str(sheet.cell_value(i,3))  + sheet.cell_value(0,j)].append(arg)
-				else:
-					rtn[str(sheet.cell_value(i,3))  +sheet.cell_value(0,j)] = [arg]
-
-
-		else:
-			for i in range(1,1785):
-				arg = sheet.cell_value(i,j)
-				if arg != '':
-					if type(arg) != float:
-						print('error', i,j,arg)
-						return
-					if arg > 100:
-						arg = 100
-					lst.append(int(arg))
-			if len(lst)!= 0:
-				check = sheet.cell_value(0,j)
-				if "Electricity" in check:
-					if "risk" in check:
-						check = "Electricity Risk"
-					else:
-						check = "Electricity Benefit"
-				elif "Motorcycle" in check:
-					if "risk" in check:
-						print("here it is")
-						check = "Motorcycle Risk"
-					else:
-						check = "Motorcycle Benefit"
-				elif "Handgun" in check:
-					if "risk" in check:
[…]

### 2015-03-03 Tables(2)/parser.py

@@ -1,381 +1,0 @@
-
-import numpy as np
-import matplotlib.pyplot as plt
-from pylab import *
-
-def parse(text):
-
-	f = open(text,'r')
-	# friends = open("friends.tex",'w')
-	# work = open("work.tex",'w')
-	# pub = open("pub.tex",'w')
-	# app = open("app.tex",'w')
-	collapsed = open("collapsed.tex",'w')
-	VUR_combined = open("VURcombined.tex",'w')
-	recipient = open("recipient.tex",'w')
-	x = """\\documentclass[a4paper,12pt]{article}
-\\usepackage[cm]{fullpage}
-\\usepackage{longtable}
-\\usepackage{graphicx}
-\\begin{document}
-\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
-
-\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
-\\endfirsthead
-
-\\multicolumn{3}{c}%
-{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
-\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
-\\endhead
-
-\\hline \\multicolumn{4}{|r|}{{Continued on next page}} \\\\ \\hline
-\\endfoot
-\\hline 
-\\endlastfoot\n"""
-	recipient.write("""\\begin{table}[t]
-\\begin{center}
-\\small
-\\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
-\\hline
-Rank & Recipient & VUR & Variance & Distribution\\\\
-\\hline\n""")
-	# friends.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
[…]

### 2015-03-03 Tables(2)/untitled folder 2/excelp.py

@@ -1,136 +1,0 @@
-import csv
-import numpy as np
-import matplotlib.pyplot as plt
-from pylab import *
-from xlrd import open_workbook
-def parser(x):
-	x = open_workbook("data.xlsm")
-	sheet = x.sheet_by_index(3)
-	rtn = dict()
-	stat = dict()
-	temp = dict()
-	for j in range(312,323):
-		lst = []
-
-		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
-			for i in range(1,1785):
-				cat = sheet.cell_value(i,j)
-				arg = sheet.cell_value(i,j)
-				if arg != '':
-					if type(arg) != float:
-						print('error', i,j,arg)
-						return
-				if arg > 100:
-					arg = 100
-				if str(sheet.cell_value(i,3) +" " +sheet.cell_value(0,j)) in rtn:
-					rtn[str(sheet.cell_value(i,3)) +" " + sheet.cell_value(0,j)].append(arg)
-				else:
-					rtn[str(sheet.cell_value(i,3)) + " " +sheet.cell_value(0,j)] = [arg]
-
-
-		else:
-			for i in range(1,1785):
-				arg = sheet.cell_value(i,j)
-				if arg != '':
-					if type(arg) != float:
-						print('error', i,j,arg)
-						return
-					if arg > 100:
-						arg = 100
-					lst.append(int(arg))
-			if len(lst)!= 0:
-				check = sheet.cell_value(0,j)
-				if "Electricity" in check:
-					if "risk" in check:
-						check = "Electricity Risk"
-					else:
-						check = "Electricity Benefit"
-				elif "Motorcycle" in check:
-					if "risk" in check:
-						check = "Motorcycle Risk"
-					else:
-						check = "Motorcycle Benefit"
-				elif "Handgun" in check:
-					if "risk" in check:
-						check = "Handgun Risk"
-					else:
-						check = "Handgun Benefit"
-				elif "Lawnmower" in check:
-					if "risk" in check:
-						check = "Lawnmower Risk"
-					else:
-						check = "Lawnmower Benefit"
-				rtn[check] = lst
-	f = open("benefit.tex","w")
-	g = open("risk.tex","w")
[…]

### 2015-03-03 tex-inputs/appendix/riskbenefit-table.tex
get rid of redundant files and confusing folders
added images for risk benefit table again

--- 2015-02-25 tables/riskbenefit.tex
@@
 \hline
-location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingben} \\
-speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextben} \\
-discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophoneben} \\
-smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesben} \\
-language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionben} \\
-laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsben} \\ 
-smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesben} \\ 
-google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassben} \\
-cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticben} \\ 
-gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionben} \\
-voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionben} \\
-voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionben} \\
-fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersben} \\
-age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionben} \\
-facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionben} \\
-email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailben} \\ 
-heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionben} \\
-discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocameraben} \\
-internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetben} \\ 
-facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\
+location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/locationtrackingben} \\
+speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/speechtotextben} \\
+discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetmicrophoneben} \\
+smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartwatchesben} \\
+language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/languagedetectionben} \\
+laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/laptopsben} \\
+smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/smartphonesben} \\
+google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/googleglassben} \\
+cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/cubetasticben} \\
+gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/genderdetectionben} \\
+voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicerecognitionben} \\
+voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/voicebasedemotiondetectionben} \\
+fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/fitnesstrackersben} \\
+age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/agedetectionben} \\
+facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialdetectionben} \\
+email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/emailben} \\
+heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/heartratedetectionben} \\
+discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/discreetvideocameraben} \\
+internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/internetben} \\
+facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/facialrecognitionben} \\
 
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/LawnmowerRisk} & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/LawnmowerBenefit} \\
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/ElectricityBenefit} \\
 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk}  & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/MotorcycleRisk}  & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/MotorcycleBenefit} \\
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/HandgunRisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/appendix/riskbenefit-images/HandgunBenefit} \\
 
@@
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
+\caption{Risks and benefit for all technologies.}
+\label{allriskben}
 \end{center}

### 2015-03-03 benefit.tex
risk/benefit
added tables folder and the parsers.

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 risk.tex
risk/benefit
added tables folder and the parsers.

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 riskbenefit.tex
risk/benefit
added tables folder and the parsers.

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
&\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
 \\hline
Technology &  Median & Q1 & Q3 & Distribution &  Median& Q1 & Q3 & Distribution   \\ 
\hline
location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
 & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrisk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../ben} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 excelp.py

@@ -1,0 +1,239 @@
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+from xlrd import open_workbook
+from numpy import median
+def parser(x):
+	x = open_workbook("data.xlsm")
+	sheet = x.sheet_by_index(3)
+	rtn = dict()
+	benefit_dic = dict()
+	risk_dic = dict()
+	final_dic = dict()
+	risk_fdic = dict()
+	benefit_fdic = dict()
+	stat = dict()
+	temp = dict()
+	for j in range(312,323):
+		lst = []
+
+		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
+
+
+			for i in range(1,1785):
+				cat = sheet.cell_value(i,j)
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+				if arg < 10:
+					arg = 10
+				if arg > 100:
+					arg = 100
+				if sheet.cell_value(0,j) == "ben":
+					ben_arg = str(sheet.cell_value(i,3)).replace(" ", "")
+					if ben_arg+ "ben" in benefit_dic:
+						benefit_dic[ben_arg+ "ben"].append(arg)
+					else:
+						benefit_dic[ben_arg + "ben"] = [arg]
+
+
+				if str(sheet.cell_value(i,3)  +sheet.cell_value(0,j)) in rtn:
+					rtn[str(sheet.cell_value(i,3))  + sheet.cell_value(0,j)].append(arg)
+				else:
+					rtn[str(sheet.cell_value(i,3))  +sheet.cell_value(0,j)] = [arg]
+
+
+		else:
+			for i in range(1,1785):
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+					if arg > 100:
+						arg = 100
+					if arg < 10:
+						arg = 10
+					lst.append(int(arg))
+			if len(lst)!= 0:
+				check = sheet.cell_value(0,j)
+				if "Electricity" in check:
+					if "risk" in check:
+						check = "Electricity Risk"
+					else:
+						check = "Electricity Benefit"
+				elif "Motorcycle" in check:
+					if "risk" in check:
+						print("here it is")
+						check = "Motorcycle Risk"
[…]

### 2015-03-03 parser.py

@@ -1,0 +1,416 @@
+
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+
+def parse(text):
+
+	f = open(text,'r')
+	# friends = open("friends.tex",'w')
+	# work = open("work.tex",'w')
+	# pub = open("pub.tex",'w')
+	# app = open("app.tex",'w')
+	collapsed = open("collapsed.tex",'w')
+	collapsed_std = open("collapsedstd.tex",'w')
+	VUR_combined = open("VURcombined.tex",'w')
+	recipient = open("recipient.tex",'w')
+	x = """\\documentclass[a4paper,12pt]{article}
+\\usepackage[cm]{fullpage}
+\\usepackage{longtable}
+\\usepackage{graphicx}
+\\begin{document}
+\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
+
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endfirsthead
+
+\\multicolumn{3}{c}%
+{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endhead
+
+\\hline \\multicolumn{4}{|r|}{{Continued on next page}} \\\\ \\hline
+\\endfoot
+\\hline 
+\\endlastfoot\n"""
+	recipient.write("""\\begin{table}[t]
+\\begin{center}
+\\small
+\\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
+\\hline
+Rank & Recipient & VUR & Variance & Distribution\\\\
+\\hline\n""")
+	# friends.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
[…]

### 2015-03-03 collapsed.tex
collapsed/collapsedstd/recipient, and images
title

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Standard Deviation}} &\multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} & \multicolumn{1}{c|}{\textbf{Standard Deviation}} & \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Tookavideoofyouunclothed & 95.97&0.3115 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouunclothedcombined} \\ 
2 & Learnedyourbankaccountinformation & 95.91&0.3539 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourbankaccountinformationcombined} \\ 
3 & Learnedyoursocialsecuritynumber & 94.84&0.26 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyoursocialsecuritynumbercombined} \\ 
4 & Tookavideoofyouenteringinyourpinatanatm & 92.67&0.475 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouenteringinyourPINatanATMcombined} \\ 
5 & Tookaphotoofyouunclothed & 92.59&0.4563 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookaphotoofyouunclothedcombined} \\ 
6 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39&0.5567 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
7 & Learnedyourusernameandpasswordforwebsites & 89.55&0.6167 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourusernameandpasswordforwebsitescombined} \\ 
8 & Learnedyourcreditcardinformation & 88.98&0.5625 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourcreditcardinformationcombined} \\ 
9 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41&0.5281 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5&0.6041 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
11 & Recordedyourworkconversations & 86.82&0.7602 & \includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyourworkconversationscombined} \\ 
12 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53&0.6227 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
13 & Recordedyourphoneconversations & 85.16&0.6079 & \includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyourphoneconversationscombined} \\ 
14 & Learnedhowmuchmoneyyouhave & 84.44&0.6142 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowmuchmoneyyouhavecombined} \\ 
15 & Tookavideoofyouintoxicated & 83.21&0.721 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouintoxicatedcombined} \\ 
16 & Learnedwhenandhowmuchyouhavesex & 81.95&0.8185 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenandhowmuchyouhavesexcombined} \\ 
17 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05&0.5999 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
18 & Tookaphotoofyouintoxicated & 78.95&0.8247 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookaphotoofyouintoxicatedcombined} \\ 
19 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76&0.8525 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
20 & Recordedyourpassingconversations & 78.13&0.8279 & \includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyourpassingconversationscombined} \\ 
21 & Learnedwhatmedicalconditionsyouhave & 77.7&0.8609 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatmedicalconditionsyouhavecombined} \\ 
22 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19&0.588 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
23 & Tookavideoofyouoff-Guard & 76.0&0.6274 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouoff-guardcombined} \\ 
24 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62&0.9035 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
25 & Learnedyourusernameforwebsites & 73.44&0.8255 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourusernameforwebsitescombined} \\ 
26 & Learnedyouraddress & 72.61&0.8625 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyouraddresscombined} \\ 
27 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55&0.7037 & \includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
28 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55&0.7037 & \includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
29 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81&0.9016 & \includegraphics[width = 2cm, height = 0.5cm]{tables/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
30 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63&1.034 & \includegraphics[width = 2cm, height = 0.5cm]{tables/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
31 & Sharedvideosotherssentyousavedonyourdevice & 70.59&0.8123 & \includegraphics[width = 2cm, height = 0.5cm]{tables/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
32 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54&0.899 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
33 & Learnedyourfingerprintsomehow & 70.12&0.8582 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourfingerprintsomehowcombined} \\ 
34 & Learnedwhenyouwerelyingnervousorstressed & 69.74&0.9105 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
35 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59&0.9115 & \includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
36 & Learnedwhatmedicationyoutake & 69.49&1.0051 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatmedicationyoutakecombined} \\ 
37 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89&0.8849 & \includegraphics[width = 2cm, height = 0.5cm]{tables/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
38 & Tookapictureofyoursignature & 68.07&0.8389 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookapictureofyoursignaturecombined} \\ 
39 & Learnedwhatwebsitesyougoto & 66.44&1.0101 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatwebsitesyougotocombined} \\ 
40 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21&1.0243 & \includegraphics[width = 2cm, height = 0.5cm]{tables/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
41 & Learnedwhereyoulivesomehow & 65.0&0.9769 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhereyoulivesomehowcombined} \\ 
42 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51&0.9892 & \includegraphics[width = 2cm, height = 0.5cm]{tables/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
43 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94&1.063 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
44 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49&1.0048 & \includegraphics[width = 2cm, height = 0.5cm]{tables/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
45 & Learnedwhenandhowmuchyouspendtimealone & 61.27&0.9872 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
46 & Trackedwhereyouare(Likeagps) & 61.24&1.0812 & \includegraphics[width = 2cm, height = 0.5cm]{tables/trackedwhereyouare(likeaGPS)combined} \\ 
47 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04&0.9495 & \includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
48 & Learnedwhereyouarecurrentlygoing & 60.87&0.9701 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhereyouarecurrentlygoingcombined} \\ 
49 & Recordedthesoundaroundyou & 60.45&0.9358 & \includegraphics[width = 2cm, height = 0.5cm]{tables/recordedthesoundaroundyoucombined} \\ 
50 & Learnedwhoyouwerespendingtimewith & 60.0&1.128 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhoyouwerespendingtimewithcombined} \\ 
51 & Learnedwhereyouworksomehow & 58.09&1.1581 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhereyouworksomehowcombined} \\ 
52 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4&1.2884 & \includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
53 & Learnedhowmuchyouuseyourphone & 51.95&1.2246 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowmuchyouuseyourphonecombined} \\ 
54 & Learnedwhatproductsyoubuy & 50.0&1.0937 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatproductsyoubuycombined} \\ 
55 & Learnedwhenyouaresickorhealthy & 48.17&1.271 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouaresickorhealthycombined} \\ 
56 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98&1.1241 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
57 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81&1.3063 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
58 & Learnedhowmuchyouuseyourcomputer & 44.93&1.1576 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowmuchyouuseyourcomputercombined} \\ 
59 & Learnedwhenhowmuchandwhatyouareeating & 42.86&1.2707 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
60 & Learnedyourname & 42.54&1.3974 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyournamecombined} \\ 
61 & Learnedwhenandhowwellyouaresleeping & 40.56&1.3424 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenandhowwellyouaresleepingcombined} \\ 
62 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51&1.2671 & \includegraphics[width = 2cm, height = 0.5cm]{tables/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
63 & Learnedwhenhowandhowmuchyouexercise & 38.66&1.2567 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenhowandhowmuchyouexercisecombined} \\ 
64 & Learnedwhenyouwerehappyorhavingfun & 34.75&1.2734 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouwerehappyorhavingfuncombined} \\ 
65 & Learnedwhattelevisionshowsyouwatch & 30.2&1.4009 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhattelevisionshowsyouwatchcombined} \\ 
66 & Learnedwhenyouarebusyorinterruptible & 29.5&1.2648 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouarebusyorinterruptiblecombined} \\ 
67 & Copiedanduploadedmusicfromyourdevice & 28.06&1.4257 & \includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedmusicfromyourdevicecombined} \\ 
68 & Learnedyourheartrate & 27.5&1.4026 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourheartratecombined} \\ 
69 & Learnedyourage & 24.29&1.4299 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyouragecombined} \\ 
70 & Learnedthelanguageyouwerespeaking & 15.86&1.485 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedthelanguageyouwerespeakingcombined} \\ 
71 & Learnedyourgender & 15.0&1.4577 & \includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourgendercombined} \\ 
\end{longtable}

\end{document}

### 2015-03-03 recipient.tex
collapsed/collapsedstd/recipient, and images
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
\hline
Rank & Recipient & VUR & Variance & Distribution\\
\hline
1& WORKCONTACTS & 75.16 & 0.879886356298& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_work}\\ 
2& PUBLIC & 72.41 & 0.96322375386& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_pub}\\ 
3& FRIENDS & 69.47 & 1.03749698795 & \includegraphics[width = 2cm, height = 2cm]{tables/recipient_friends}\\ 
4& ALL & 64.78 & 1.1105854312& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_total}\\ 
5& APPSERVER & 42.28 & 1.32348026053& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_app}\\ 
6\hline
\end{tabular}
\end{center}
\end{table}

### 2015-03-03 parser.py

@@ -49,7 +49,25 @@ Rank & Recipient & VUR & Variance & Distribution\\\\
 	# work.write(x)
 	# pub.write(x)
 	# app.write(x)
-	collapsed.write(x)
+	collapsed.write("""\\documentclass[a4paper,12pt]{article}
+\\usepackage[cm]{fullpage}
+\\usepackage{longtable}
+\\usepackage{graphicx}
+\\begin{document}
+\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}
+
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Standard Deviation}} &\\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endfirsthead
+
+\\multicolumn{3}{c}%
+{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} & \\multicolumn{1}{c|}{\\textbf{Standard Deviation}} & \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endhead
+
+\\hline \\multicolumn{4}{|r|}{{Continued on next page}} \\\\ \\hline
+\\endfoot
+\\hline 
+\\endlastfoot\n""")
 	collapsed_std.write("""\\documentclass[a4paper,12pt]{article}
 \\usepackage[cm]{fullpage}
 \\usepackage{longtable}
@@ -135,7 +153,7 @@ Rank & Recipient & VUR & Variance & Distribution\\\\
 			ax.set_autoscale_on(False)
 			plt.axis('off')
 
-			savefig(str(prev) + "combined", dpi=None, facecolor='w', edgecolor='w',
+			savefig("tables/" + str(prev) + "combined", dpi=None, facecolor='w', edgecolor='w',
 			orientation='portrait', papertype=None, format=None,
 			transparent=False, bbox_inches='tight', pad_inches=0,
 			frameon=None)
[…]

### 2015-03-03 benefit.tex
directory change in risk/benefit
title

@@
 \hline
-Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
-Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
-Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
-Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
-Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
-Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
-Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
-Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
-Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
-Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
-Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
-Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
-Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
-Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
-Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
-Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
-Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
-Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
-Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
-Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
-Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
-Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
-Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
-Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
+Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{genderdetectionben} \\ 
+Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{agedetectionben} \\ 
+Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetmicrophoneben} \\ 
+Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{cubetasticben} \\ 
+Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{fitnesstrackersben} \\ 
+Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicebasedemotiondetectionben} \\ 
+Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{facialdetectionben} \\ 
+Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetvideocameraben} \\ 
+Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{googleglassben} \\ 
+Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartwatchesben} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{HandgunBenefit} \\ 
+Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{facialrecognitionben} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{LawnmowerBenefit} \\ 
+Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{speechtotextben} \\ 
+Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicerecognitionben} \\ 
+Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{languagedetectionben} \\ 
+Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{heartratedetectionben} \\ 
+Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{locationtrackingben} \\ 
+Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{emailben} \\ 
+Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartphonesben} \\ 
+Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{laptopsben} \\ 
+Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{internetben} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{ElectricityBenefit} \\ 
+Ben & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{ben} \\ 
 \hline

### 2015-03-03 risk.tex
directory change in risk/benefit
title

@@
 \hline
-Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} \\ 
-Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} \\ 
-Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} \\ 
-Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} \\ 
-Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} \\ 
-Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} \\ 
-Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} \\ 
-Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} \\ 
-Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} \\ 
-Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} \\ 
-Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} \\ 
-Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} \\ 
-Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} \\ 
-Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} \\ 
-Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} \\ 
-Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} \\ 
-Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} \\ 
-Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} \\ 
-Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} \\ 
-Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} \\ 
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
+Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslocationtrackingrisk} \\ 
+Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesspeechtotextrisk} \\ 
+Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetmicrophonerisk} \\ 
+Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartwatchesrisk} \\ 
+Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslanguagedetectionrisk} \\ 
+Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslaptopsrisk} \\ 
+Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartphonesrisk} \\ 
+Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgoogleglassrisk} \\ 
+Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablescubetasticrisk} \\ 
+Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgenderdetectionrisk} \\ 
+Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicerecognitionrisk} \\ 
+Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicebasedemotiondetectionrisk} \\ 
+Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfitnesstrackersrisk} \\ 
+Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesagedetectionrisk} \\ 
+Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialdetectionrisk} \\ 
+Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesemailrisk} \\ 
+Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesheartratedetectionrisk} \\ 
+Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetvideocamerarisk} \\ 
+Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesinternetrisk} \\ 
+Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialrecognitionrisk} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesLawnmowerRisk} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesMotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesHandgunRisk} \\ 
+ & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tablesrisk} \\ 
 \hline

### 2015-03-03 riskbenefit.tex
directory change in risk/benefit
title

@@
 \hline
-location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\
-speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\
-discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\
-smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\
-language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\
-laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
-smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
-google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
-cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
-gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\
-voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\
-voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\
-fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\
-age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\
-facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\
-email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
-heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\
-discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\
-internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
-facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
-Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
-Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
-Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
-Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
- & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrisk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../ben} \\ 
+location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslocationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{locationtrackingben} \\
+speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesspeechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{speechtotextben} \\ 
+discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetmicrophoneben} \\
+smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartwatchesben} \\ 
+language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslanguagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{languagedetectionben} \\
+laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslaptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{laptopsben} \\ 
+smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartphonesben} \\ 
+google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgoogleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{googleglassben} \\ 
+cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablescubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{cubetasticben} \\ 
+gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgenderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{genderdetectionben} \\
+voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicerecognitionben} \\
+voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicebasedemotiondetectionben} \\
+fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{fitnesstrackersben} \\
+age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesagedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{agedetectionben} \\ 
+facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{facialdetectionben} \\
+email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesemailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{emailben} \\ 
+heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesheartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{heartratedetectionben} \\
+discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetvideocameraben} \\
+internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesinternetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{internetben} \\ 
+facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{facialrecognitionben} \\
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesLawnmowerRisk} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{HandgunBenefit} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{LawnmowerBenefit} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesMotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesHandgunRisk} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{ElectricityBenefit} \\ 
+ & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tablesrisk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{ben} \\ 
 \hline

### 2015-03-03 excelp.py

@@ -121,14 +121,14 @@ def parser(x):
 					ben_var[j] = "/"
 			ben_var = ''.join(ben_var)
 			quart2 = stat[ben_var]
-			final_string = str(i).replace("risk","") + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../tables" +arg+ "} & "+str(quart2[0]) + " & " + str(quart2[1]) + " & " + str(quart2[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../" + ben_var + "} \\\\ \n"
+			final_string = str(i).replace("risk","") + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables" +arg+ "} & "+str(quart2[0]) + " & " + str(quart2[1]) + " & " + str(quart2[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{" + ben_var + "} \\\\ \n"
 
 			if quart[0] in final_dic:
 				final_dic[quart[0]].append(final_string)
 			else:
 				final_dic[quart[0]] = [final_string]
 		#h.write(str(i).replace("risk","") + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../" +arg+ "} & "+str(quart2[0]) + " & " + str(quart2[1]) + " & " + str(quart2[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../" + ben_var + "} \\\\ \n")
-			thing = str(i).replace("risk","").title() + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../tables" + arg + "} \\\\ \n"
+			thing = str(i).replace("risk","").title() + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables" + arg + "} \\\\ \n"
 
 			if quart[0] in risk_fdic:
 				risk_fdic[quart[0]].append(thing)
@@ -136,13 +136,13 @@ def parser(x):
[…]

### 2015-03-03 benefit.tex
directory mistake
title

--- 2015-03-03 benefit.tex
@@
 \hline
-Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
-Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
-Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
-Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
-Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
-Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
-Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
-Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
-Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
-Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
-Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
-Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
-Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
-Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
-Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
-Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
-Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
-Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
-Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
-Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
-Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
-Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
-Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
-Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
+Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionben} \\ 
+Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionben} \\ 
+Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophoneben} \\ 
+Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticben} \\ 
+Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersben} \\ 
+Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionben} \\ 
+Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionben} \\ 
+Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocameraben} \\ 
+Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassben} \\ 
+Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesben} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\ 
+Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
+Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextben} \\ 
+Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionben} \\ 
+Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionben} \\ 
+Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionben} \\ 
+Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingben} \\ 
+Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailben} \\ 
+Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesben} \\ 
+Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsben} \\ 
+Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetben} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\ 
 \hline

### 2015-03-03 risk.tex
directory mistake
title

--- 2015-03-03 risk.tex
@@
 \hline
-Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} \\ 
-Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} \\ 
-Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} \\ 
-Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} \\ 
-Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} \\ 
-Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} \\ 
-Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} \\ 
-Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} \\ 
-Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} \\ 
-Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} \\ 
-Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} \\ 
-Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} \\ 
-Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} \\ 
-Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} \\ 
-Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} \\ 
-Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} \\ 
-Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} \\ 
-Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} \\ 
-Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} \\ 
-Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} \\ 
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
+Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingrisk} \\ 
+Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextrisk} \\ 
+Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophonerisk} \\ 
+Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesrisk} \\ 
+Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionrisk} \\ 
+Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsrisk} \\ 
+Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesrisk} \\ 
+Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassrisk} \\ 
+Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticrisk} \\ 
+Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionrisk} \\ 
+Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionrisk} \\ 
+Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionrisk} \\ 
+Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersrisk} \\ 
+Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionrisk} \\ 
+Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionrisk} \\ 
+Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailrisk} \\ 
+Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionrisk} \\ 
+Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocamerarisk} \\ 
+Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetrisk} \\ 
+Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} \\ 
 \hline

### 2015-03-03 riskbenefit.tex
directory mistake
title

@@
 \hline
-location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslocationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{locationtrackingben} \\
-speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesspeechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{speechtotextben} \\ 
-discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetmicrophoneben} \\
-smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartwatchesben} \\ 
-language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslanguagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{languagedetectionben} \\
-laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslaptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{laptopsben} \\ 
-smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartphonesben} \\ 
-google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgoogleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{googleglassben} \\ 
-cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablescubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{cubetasticben} \\ 
-gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgenderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{genderdetectionben} \\
-voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicerecognitionben} \\
-voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicebasedemotiondetectionben} \\
-fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{fitnesstrackersben} \\
-age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesagedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{agedetectionben} \\ 
-facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{facialdetectionben} \\
-email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesemailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{emailben} \\ 
-heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesheartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{heartratedetectionben} \\
-discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetvideocameraben} \\
-internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesinternetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{internetben} \\ 
-facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{facialrecognitionben} \\
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesLawnmowerRisk} \\ 
-Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{MotorcycleBenefit} \\ 
-Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{HandgunBenefit} \\ 
-Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{LawnmowerBenefit} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesElectricityRisk} \\ 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesMotorcycleRisk} \\ 
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesHandgunRisk} \\ 
-Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{ElectricityBenefit} \\ 
- & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tablesrisk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{ben} \\ 
+location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/locationtrackingben} \\
+speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/speechtotextben} \\
+discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetmicrophoneben} \\
+smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartwatchesben} \\
+language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/languagedetectionben} \\
+laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/laptopsben} \\ 
+smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/smartphonesben} \\ 
+google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/googleglassben} \\
+cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/cubetasticben} \\ 
+gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/genderdetectionben} \\
+voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicerecognitionben} \\
+voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/voicebasedemotiondetectionben} \\
+fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/fitnesstrackersben} \\
+age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/agedetectionben} \\
+facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialdetectionben} \\
+email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/emailben} \\ 
+heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/heartratedetectionben} \\
+discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/discreetvideocameraben} \\
+internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/internetben} \\ 
+facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\ 
+ & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tables/risk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tables/ben} \\ 
 \hline

### 2015-03-03 excelp.py

@@ -121,14 +121,14 @@ def parser(x):
 					ben_var[j] = "/"
 			ben_var = ''.join(ben_var)
 			quart2 = stat[ben_var]
-			final_string = str(i).replace("risk","") + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables" +arg+ "} & "+str(quart2[0]) + " & " + str(quart2[1]) + " & " + str(quart2[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{" + ben_var + "} \\\\ \n"
+			final_string = str(i).replace("risk","") + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables/" +arg+ "} & "+str(quart2[0]) + " & " + str(quart2[1]) + " & " + str(quart2[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables/" + ben_var + "} \\\\ \n"
 
 			if quart[0] in final_dic:
 				final_dic[quart[0]].append(final_string)
 			else:
 				final_dic[quart[0]] = [final_string]
 		#h.write(str(i).replace("risk","") + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../" +arg+ "} & "+str(quart2[0]) + " & " + str(quart2[1]) + " & " + str(quart2[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{../" + ben_var + "} \\\\ \n")
-			thing = str(i).replace("risk","").title() + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables" + arg + "} \\\\ \n"
+			thing = str(i).replace("risk","").title() + " & "+str(quart[0]) + " & " + str(quart[1]) + " & " + str(quart[2]) + " & " + "\\includegraphics[width = 2cm, height = 0.5cm]{tables/" + arg + "} \\\\ \n"
 
 			if quart[0] in risk_fdic:
 				risk_fdic[quart[0]].append(thing)
@@ -136,13 +136,13 @@ def parser(x):
[…]

### 2015-03-03 riskbenefit.tex
riskbenefit column fix
title

@@
 \begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
+\\hline
 &\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
@@
 facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tables/facialrecognitionben} \\
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk} \\ 
-Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\ 
-Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit} \\ 
-Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} \\ 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} \\ 
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk} \\ 
-Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit} \\ 
- & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tables/risk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tables/ben} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerRisk}  & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/LawnmowerBenefit}\\
+
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/ElectricityBenefit}  \\
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleRisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/MotorcycleBenefit} \\
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunRisk}& 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tables/HandgunBenefit}  \\ 
 \hline

### 2015-03-03 tex-inputs/benefit.tex
tables whoop whoop

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Gender Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
Age Detection & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
Discreet Microphone & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
Cubetastic & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
Fitness Trackers & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
Voice Based Emotion Detection & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
Facial Detection & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
Discreet Video Camera & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
Google Glass & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
Smartwatches & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit} \\ 
Facial Recognition & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit} \\ 
Speech To Text & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
Voice Recognition & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
Language Detection & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
Heart Rate Detection & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
Location Tracking & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
Email & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
Smartphones & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
Laptops & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
Internet & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 tex-inputs/long-tables/collapsedstd.tex
tables whoop whoop

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Standard Deviation}} &\multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} & \multicolumn{1}{c|}{\textbf{Standard Deviation}} & \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Learnedthelanguageyouwerespeaking & 15.86 & 1.485&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedthelanguageyouwerespeakingcombined} \\ 
2 & Learnedyourgender & 15.0 & 1.4577&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourgendercombined} \\ 
3 & Learnedyourage & 24.29 & 1.4299&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyouragecombined} \\ 
4 & Copiedanduploadedmusicfromyourdevice & 28.06 & 1.4257&\includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedmusicfromyourdevicecombined} \\ 
5 & Learnedyourheartrate & 27.5 & 1.4026&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourheartratecombined} \\ 
6 & Learnedwhattelevisionshowsyouwatch & 30.2 & 1.4009&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhattelevisionshowsyouwatchcombined} \\ 
7 & Learnedyourname & 42.54 & 1.3974&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyournamecombined} \\ 
8 & Learnedwhenandhowwellyouaresleeping & 40.56 & 1.3424&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenandhowwellyouaresleepingcombined} \\ 
9 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81 & 1.3063&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
10 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4 & 1.2884&\includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
11 & Learnedwhenyouwerehappyorhavingfun & 34.75 & 1.2734&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouwerehappyorhavingfuncombined} \\ 
12 & Learnedwhenyouaresickorhealthy & 48.17 & 1.271&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouaresickorhealthycombined} \\ 
13 & Learnedwhenhowmuchandwhatyouareeating & 42.86 & 1.2707&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
14 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & 1.2671&\includegraphics[width = 2cm, height = 0.5cm]{tables/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
15 & Learnedwhenyouarebusyorinterruptible & 29.5 & 1.2648&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouarebusyorinterruptiblecombined} \\ 
16 & Learnedwhenhowandhowmuchyouexercise & 38.66 & 1.2567&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenhowandhowmuchyouexercisecombined} \\ 
17 & Learnedhowmuchyouuseyourphone & 51.95 & 1.2246&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowmuchyouuseyourphonecombined} \\ 
18 & Learnedwhereyouworksomehow & 58.09 & 1.1581&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhereyouworksomehowcombined} \\ 
19 & Learnedhowmuchyouuseyourcomputer & 44.93 & 1.1576&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowmuchyouuseyourcomputercombined} \\ 
20 & Learnedwhoyouwerespendingtimewith & 60.0 & 1.128&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhoyouwerespendingtimewithcombined} \\ 
21 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98 & 1.1241&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
22 & Learnedwhatproductsyoubuy & 50.0 & 1.0937&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatproductsyoubuycombined} \\ 
23 & Trackedwhereyouare(Likeagps) & 61.24 & 1.0812&\includegraphics[width = 2cm, height = 0.5cm]{tables/trackedwhereyouare(likeaGPS)combined} \\ 
24 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94 & 1.063&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
25 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63 & 1.034&\includegraphics[width = 2cm, height = 0.5cm]{tables/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
26 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21 & 1.0243&\includegraphics[width = 2cm, height = 0.5cm]{tables/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
27 & Learnedwhatwebsitesyougoto & 66.44 & 1.0101&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatwebsitesyougotocombined} \\ 
28 & Learnedwhatmedicationyoutake & 69.49 & 1.0051&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatmedicationyoutakecombined} \\ 
29 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49 & 1.0048&\includegraphics[width = 2cm, height = 0.5cm]{tables/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
30 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51 & 0.9892&\includegraphics[width = 2cm, height = 0.5cm]{tables/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
31 & Learnedwhenandhowmuchyouspendtimealone & 61.27 & 0.9872&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
32 & Learnedwhereyoulivesomehow & 65.0 & 0.9769&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhereyoulivesomehowcombined} \\ 
33 & Learnedwhereyouarecurrentlygoing & 60.87 & 0.9701&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhereyouarecurrentlygoingcombined} \\ 
34 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04 & 0.9495&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
35 & Recordedthesoundaroundyou & 60.45 & 0.9358&\includegraphics[width = 2cm, height = 0.5cm]{tables/recordedthesoundaroundyoucombined} \\ 
36 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59 & 0.9115&\includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
37 & Learnedwhenyouwerelyingnervousorstressed & 69.74 & 0.9105&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
38 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62 & 0.9035&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
39 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81 & 0.9016&\includegraphics[width = 2cm, height = 0.5cm]{tables/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
40 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54 & 0.899&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
41 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89 & 0.8849&\includegraphics[width = 2cm, height = 0.5cm]{tables/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
42 & Learnedyouraddress & 72.61 & 0.8625&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyouraddresscombined} \\ 
43 & Learnedwhatmedicalconditionsyouhave & 77.7 & 0.8609&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhatmedicalconditionsyouhavecombined} \\ 
44 & Learnedyourfingerprintsomehow & 70.12 & 0.8582&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourfingerprintsomehowcombined} \\ 
45 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76 & 0.8525&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
46 & Tookapictureofyoursignature & 68.07 & 0.8389&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookapictureofyoursignaturecombined} \\ 
47 & Recordedyourpassingconversations & 78.13 & 0.8279&\includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyourpassingconversationscombined} \\ 
48 & Learnedyourusernameforwebsites & 73.44 & 0.8255&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourusernameforwebsitescombined} \\ 
49 & Tookaphotoofyouintoxicated & 78.95 & 0.8247&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookaphotoofyouintoxicatedcombined} \\ 
50 & Learnedwhenandhowmuchyouhavesex & 81.95 & 0.8185&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedwhenandhowmuchyouhavesexcombined} \\ 
51 & Sharedvideosotherssentyousavedonyourdevice & 70.59 & 0.8123&\includegraphics[width = 2cm, height = 0.5cm]{tables/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
52 & Tookaphotoofyouoff-Guard & 72.55 & 0.769&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookaphotoofyouoff-guardcombined} \\ 
53 & Recordedyourworkconversations & 86.82 & 0.7602&\includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyourworkconversationscombined} \\ 
54 & Tookavideoofyouintoxicated & 83.21 & 0.721&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouintoxicatedcombined} \\ 
55 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & 0.7037&\includegraphics[width = 2cm, height = 0.5cm]{tables/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
56 & Tookavideoofyouoff-Guard & 76.0 & 0.6274&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouoff-guardcombined} \\ 
57 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53 & 0.6227&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
58 & Learnedyourusernameandpasswordforwebsites & 89.55 & 0.6167&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourusernameandpasswordforwebsitescombined} \\ 
59 & Learnedhowmuchmoneyyouhave & 84.44 & 0.6142&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedhowmuchmoneyyouhavecombined} \\ 
60 & Recordedyourphoneconversations & 85.16 & 0.6079&\includegraphics[width = 2cm, height = 0.5cm]{tables/recordedyourphoneconversationscombined} \\ 
61 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & 0.6041&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
62 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05 & 0.5999&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
63 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19 & 0.588&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
64 & Learnedyourcreditcardinformation & 88.98 & 0.5625&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourcreditcardinformationcombined} \\ 
65 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & 0.5567&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
66 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & 0.5281&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
67 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & 0.475&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouenteringinyourPINatanATMcombined} \\ 
68 & Tookaphotoofyouunclothed & 92.59 & 0.4563&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookaphotoofyouunclothedcombined} \\ 
69 & Learnedyourbankaccountinformation & 95.91 & 0.3539&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyourbankaccountinformationcombined} \\ 
70 & Tookavideoofyouunclothed & 95.97 & 0.3115&\includegraphics[width = 2cm, height = 0.5cm]{tables/tookavideoofyouunclothedcombined} \\ 
71 & Learnedyoursocialsecuritynumber & 94.84 & 0.26&\includegraphics[width = 2cm, height = 0.5cm]{tables/learnedyoursocialsecuritynumbercombined} \\ 
\end{longtable}

\end{document}

### 2015-03-03 tex-inputs/results-recipient.tex
tables whoop whoop

@@
 \hline
-1 & Work Contacts & 75.16\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
-2 & Public & 72.41\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
-3 & Friends & 69.47\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
-4 & App's Server & 42.28\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
+1 & Work Contacts & 75.16\% & 0.880 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
+2 & Public & 72.41\% & 0.963 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
+3 & Friends & 69.47\% & 1.037 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
+4 & App's Server & 42.28\% & 1.323 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
 \hline

### 2015-03-03 tex-inputs/risk.tex
tables whoop whoop

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 tex-inputs/riskbenefit.tex
tables whoop whoop

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\\hline
&\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
 \\hline
Technology &  Median & Q1 & Q3 & Distribution &  Median& Q1 & Q3 & Distribution   \\ 
\hline
location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk}  & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit}\\

Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit}  \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk}& 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit}  \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-04 tex-inputs/intro.tex
started to look at results
intro redo

@@
 
-Because interactions with the wearables so frictionless, they are a popular choice for augmenting life with novel feedback and taking advantage of pre-existing applications more seamlessly.
-The constantly captured data from these devices has many benefits, ranging form a more natural, human-centered interface experience to healthier, fitness-data inspired lifestyle.
-It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits.
+The constantly captured data from these devices has many benefits, ranging from a more natural, human-centered interface experience to a healthier, fitness-data inspired lifestyle.
+It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits over traditional devices.
 
-Despite their popularity, the market is still in its infancy.
-It is hard to predict what device and applications will be most popular.
-Therefore, we use the current interest as a baseline.
-The most common wearables at the time of this study were in the form of fitness trackers and smart watches, with a survey of 3,956 wearables-enthusiastic respondents reporting the most popular devices as fitness bands (61\%), smart watches (45\%) and other health devices (17\%)~\cite{Nilsen}.
-However, there are also wearable glasses \cite{ 2_google_2014, 3_sony_global_2014}, rings \cite{4_ringly_2014}, bracelets \cite{5_intel_2014} and more.
-New wearables trends for 2015 include smart clothes made out fiber-optic fabrics which give information about workouts and UV technology hairslide which measures sun exposure \cite{1_digital_trends_2014, 2_arthur_2014}.
+Along with these benefits, wearable devices bring with them new potential privacy issues which expose users' activities without their awareness or consent.
+Fitbit allowed sex to be tracked as exercise while fitness profiles were public by default~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
+Public discomfort toward facial recognition was so strong that the capability was not even deployed for Google Glass \cite{GlassDetection}.
+Google Glass, an iconic wearable of today, has since disappeared \cite{13_google_2015}.
+Most suspect that the reason for its disappearance was because it was the ``straw the broke the back of the privacy camel's back'' \cite{14_dvorak_2014}.
+Some Glass wearers faced assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014}, while bystanders felt uncomfortable personal details, conversations, and photos possibly recorded.
 
-Wearable devices bring with them new potential security and privacy concerns.
-Many concerns expose users' activities without their awareness or consent.
-For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Additionally, public discomfort prevented Google from enabling capabilities such as facial detection on Google Glass \cite{GlassDetection}.
-
-Although Google Glass was most iconic wearable of its time, it has since disappeared due to complaints from the public\cite{13_google_2015}.
-No formal statement from Google addresses the states that the reason for its disappearance is due to negative social pressures.
-However, most suspect that this is the reason for its disappearance, rather than a shift in interest.
-One popular tech magazine called glass the ``straw the broke the back of the privacy camel's back \cite{14_dvorak_2014},'' and made bystanders feel uncomfortable with the possibility of recording personal details, conversations, and photos.
-Many instances of assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} on wearers were reported, resulting from a combination of privacy concerns and social tension\footnote{Google has come to represent gentrification in San Francisco ...
-[which] makes wearable device owners look and sound like one of the people whom residents of the city have come to feel oppressed by \cite{17_matyszczyk_2014}.
-The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers .
-The public was generally unsympathetic to the assults aggravated by social tension.
-Tweeting and comments included: ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.}.
-
-{\color {red} This calls for privacy research in this area!
-It's more important than ever!
-Or something along those lines.}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices to prevent negative social impact and breaches of privacy.
+{\color {red} We should warn people about such things.
+But we can't do that, since attention is a finite resource.
+This calls for privacy research in this area!}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices to prevent negative social impact and breaches of privacy.
 There has been extensive work on the need for showing users and bystanders how certain data is being captured so that they can have more control.
-We have an issue of showing everyone everything all the time, since attention is a finite resources.
+We have an issue of showing everyone everything all the time, since attention is a finite resource.
 We need to identify situations that people want to warn them about, and transparently access things that are benign.
@@
 The goal of this paper is to gain a better sense of what those concerns are.
+
+{\color {red} smart phone concerns. we haven't gotten it right for this yet! We need to do something for wearables before it's too late.}
 

### 2015-03-04 tex-inputs/intro.tex
put question generation into methodology; restructuring intro to the new outline (not done yet)

@@
 
-Wearable technologies, or ``wearables,'' are intimately related with both fields of ubiquitous computing and wearable computers.
-This \$700 million industry \cite{cmo} of electronically enhanced clothing items and accessories aims to interweave technological interaction into everyday life.
+Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} consisting of electronically enhanced clothing items and accessories aims to interweave technological interaction into everyday life.
 A top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
@@
 The constantly captured data from these devices has many benefits, ranging from a more natural, human-centered interface experience to a healthier, fitness-data inspired lifestyle.
+There will likely be many more applications in the future which take advantage of such data.
 It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits over traditional devices.
@@
 
+{\color {red} smart phone concerns. we haven't gotten it right for this yet! We need to do something for wearables before it's too late.}
+
 {\color {red} We should warn people about such things.
@@
 The goal of this paper is to gain a better sense of what those concerns are.
-
-{\color {red} smart phone concerns. we haven't gotten it right for this yet! We need to do something for wearables before it's too late.}
-
-To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study.
-At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}.
-These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.
 

### 2015-03-04 tex-inputs/methodology.tex
put question generation into methodology; restructuring intro to the new outline (not done yet)

@@
 \section{Methodology}
+To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study.
+At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}.
+These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.
 

### 2015-03-04 collapsedstd.tex
fixed standard deviation
title

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Standard Deviation}} &\multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} & \multicolumn{1}{c|}{\textbf{Standard Deviation}} & \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Learnedthelanguageyouwerespeaking & 15.86 & 1.485&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedthelanguageyouwerespeakingcombined} \\ 
2 & Learnedyourgender & 15.0 & 1.4577&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourgendercombined} \\ 
3 & Learnedyourage & 24.29 & 1.4299&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouragecombined} \\ 
4 & Copiedanduploadedmusicfromyourdevice & 28.06 & 1.4257&\includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedmusicfromyourdevicecombined} \\ 
5 & Learnedyourheartrate & 27.5 & 1.4026&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourheartratecombined} \\ 
6 & Learnedwhattelevisionshowsyouwatch & 30.2 & 1.4009&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhattelevisionshowsyouwatchcombined} \\ 
7 & Learnedyourname & 42.54 & 1.3974&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyournamecombined} \\ 
8 & Learnedwhenandhowwellyouaresleeping & 40.56 & 1.3424&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowwellyouaresleepingcombined} \\ 
9 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81 & 1.3063&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
10 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4 & 1.2884&\includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
11 & Learnedwhenyouwerehappyorhavingfun & 34.75 & 1.2734&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerehappyorhavingfuncombined} \\ 
12 & Learnedwhenyouaresickorhealthy & 48.17 & 1.271&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouaresickorhealthycombined} \\ 
13 & Learnedwhenhowmuchandwhatyouareeating & 42.86 & 1.2707&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowmuchandwhatyouareeatingcombined} \\ 
14 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & 1.2671&\includegraphics[width = 2cm, height = 0.5cm]{../tablesscannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
15 & Learnedwhenyouarebusyorinterruptible & 29.5 & 1.2648&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouarebusyorinterruptiblecombined} \\ 
16 & Learnedwhenhowandhowmuchyouexercise & 38.66 & 1.2567&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowandhowmuchyouexercisecombined} \\ 
17 & Learnedhowmuchyouuseyourphone & 51.95 & 1.2246&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourphonecombined} \\ 
18 & Learnedwhereyouworksomehow & 58.09 & 1.1581&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouworksomehowcombined} \\ 
19 & Learnedhowmuchyouuseyourcomputer & 44.93 & 1.1576&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourcomputercombined} \\ 
20 & Learnedwhoyouwerespendingtimewith & 60.0 & 1.128&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhoyouwerespendingtimewithcombined} \\ 
21 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98 & 1.1241&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
22 & Learnedwhatproductsyoubuy & 50.0 & 1.0937&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatproductsyoubuycombined} \\ 
23 & Trackedwhereyouare(Likeagps) & 61.24 & 1.0812&\includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouare(likeaGPS)combined} \\ 
24 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94 & 1.063&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
25 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63 & 1.034&\includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
26 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21 & 1.0243&\includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
27 & Learnedwhatwebsitesyougoto & 66.44 & 1.0101&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatwebsitesyougotocombined} \\ 
28 & Learnedwhatmedicationyoutake & 69.49 & 1.0051&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicationyoutakecombined} \\ 
29 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49 & 1.0048&\includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
30 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51 & 0.9892&\includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
31 & Learnedwhenandhowmuchyouspendtimealone & 61.27 & 0.9872&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouspendtimealonecombined} \\ 
32 & Learnedwhereyoulivesomehow & 65.0 & 0.9769&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyoulivesomehowcombined} \\ 
33 & Learnedwhereyouarecurrentlygoing & 60.87 & 0.9701&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouarecurrentlygoingcombined} \\ 
34 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04 & 0.9495&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
35 & Recordedthesoundaroundyou & 60.45 & 0.9358&\includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedthesoundaroundyoucombined} \\ 
36 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59 & 0.9115&\includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
37 & Learnedwhenyouwerelyingnervousorstressed & 69.74 & 0.9105&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerelyingnervousorstressedcombined} \\ 
38 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62 & 0.9035&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosatwork(withanoutward-facingcamera)combined} \\ 
39 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81 & 0.9016&\includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
40 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54 & 0.899&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosatwork(withanoutward-facingcamera)combined} \\ 
41 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89 & 0.8849&\includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
42 & Learnedyouraddress & 72.61 & 0.8625&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouraddresscombined} \\ 
43 & Learnedwhatmedicalconditionsyouhave & 77.7 & 0.8609&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicalconditionsyouhavecombined} \\ 
44 & Learnedyourfingerprintsomehow & 70.12 & 0.8582&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourfingerprintsomehowcombined} \\ 
45 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76 & 0.8525&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
46 & Tookapictureofyoursignature & 68.07 & 0.8389&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookapictureofyoursignaturecombined} \\ 
47 & Recordedyourpassingconversations & 78.13 & 0.8279&\includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourpassingconversationscombined} \\ 
48 & Learnedyourusernameforwebsites & 73.44 & 0.8255&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameforwebsitescombined} \\ 
49 & Tookaphotoofyouintoxicated & 78.95 & 0.8247&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouintoxicatedcombined} \\ 
50 & Learnedwhenandhowmuchyouhavesex & 81.95 & 0.8185&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouhavesexcombined} \\ 
51 & Sharedvideosotherssentyousavedonyourdevice & 70.59 & 0.8123&\includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosotherssentyousavedonyourdevicecombined} \\ 
52 & Tookaphotoofyouoff-Guard & 72.55 & 0.769&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouoff-guardcombined} \\ 
53 & Recordedyourworkconversations & 86.82 & 0.7602&\includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourworkconversationscombined} \\ 
54 & Tookavideoofyouintoxicated & 83.21 & 0.721&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouintoxicatedcombined} \\ 
55 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & 0.7037&\includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
56 & Tookavideoofyouoff-Guard & 76.0 & 0.6274&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouoff-guardcombined} \\ 
57 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53 & 0.6227&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
58 & Learnedyourusernameandpasswordforwebsites & 89.55 & 0.6167&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameandpasswordforwebsitescombined} \\ 
59 & Learnedhowmuchmoneyyouhave & 84.44 & 0.6142&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchmoneyyouhavecombined} \\ 
60 & Recordedyourphoneconversations & 85.16 & 0.6079&\includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourphoneconversationscombined} \\ 
61 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & 0.6041&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
62 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05 & 0.5999&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
63 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19 & 0.588&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
64 & Learnedyourcreditcardinformation & 88.98 & 0.5625&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourcreditcardinformationcombined} \\ 
65 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & 0.5567&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
66 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & 0.5281&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
67 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & 0.475&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinyourPINatanATMcombined} \\ 
68 & Tookaphotoofyouunclothed & 92.59 & 0.4563&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouunclothedcombined} \\ 
69 & Learnedyourbankaccountinformation & 95.91 & 0.3539&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourbankaccountinformationcombined} \\ 
70 & Tookavideoofyouunclothed & 95.97 & 0.3115&\includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouunclothedcombined} \\ 
71 & Learnedyoursocialsecuritynumber & 94.84 & 0.26&\includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyoursocialsecuritynumbercombined} \\ 
\end{longtable}

\end{document}

### 2015-03-04 parser.py

@@ -38,7 +38,7 @@ def parse(text):
 \\small
 \\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
 \\hline
-Rank & Recipient & VUR & Variance & Distribution\\\\
+Rank & Recipient & VUR & Standard Deviation & Distribution\\\\
 \\hline\n""")
 	# friends.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
 	# work.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
@@ -49,25 +49,7 @@ Rank & Recipient & VUR & Variance & Distribution\\\\
 	# work.write(x)
 	# pub.write(x)
 	# app.write(x)
-	collapsed.write("""\\documentclass[a4paper,12pt]{article}
-\\usepackage[cm]{fullpage}
-\\usepackage{longtable}
-\\usepackage{graphicx}
-\\begin{document}
-\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}
-
-\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Standard Deviation}} &\\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
-\\endfirsthead
-
-\\multicolumn{3}{c}%
-{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
-\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} & \\multicolumn{1}{c|}{\\textbf{Standard Deviation}} & \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
-\\endhead
-
[…]

### 2015-03-04 tex-inputs/results-regression.tex
Started modifying regression section, added codings for data types.

@@
 
-\begin{table}
+\begin{table}[t]
 \centering
@@
 \hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
+(Intercept) & 254.5 & 1 & 18,699.82\\
 \hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
+(Intercept) & 79.2 & 1 & 18,347.6\\
+Device & 391.0 & 1 & \\
 \hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
+(Intercept) & 232.1 & 1 & 17.897.0\\
 IUIPC (covariate) & 368.5 & 1 & \\
 \hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
+(Intercept) & 298.2 & 1 &17,606.5\\
+Data Recipient & 900.0 & 4 & \\
 \hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
+(Intercept) & 370.9 & 1 & 14,970.7\\
+Data Type & 1,898.4& 76 & \\
 \hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
+(Intercept) & 79.2 & 1 & 18,349.9\\
+Device & 391.0 & 1 & \\
 \hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
+(Intercept) & 29.2 & 1 & 14,114.8\\
+Device & 8.1 & 1 &  \\
+Data Recipient & 579.3 & 3 & \\
+Data Type & 1,765.4 & 76 &  \\
+\hline
+(Intercept) & 298.0 & 1 & 12,931.6 \\
+Device  & 10.4 & 1 &  \\
+Data Recipient & 626.2 & 3 & \\
+Data Type & 1,997.5 & 76 & \\
+IUIPC (covariate) & 374.8 & 1 & \\
 \hline
@@
 \caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
+The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
+Each parameter listed was statistically significant at $p<0.0005$.}
 \label{regression}
@@
 Thus, we opted to remove the other covariates from our analysis.
+Similarly, we observed no statistically significant interaction effects between any of these four variables, which is why we did not include them in our models.
 
@@
 Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
+This suggests that participants' biases towards specific wearable devices or wearable devices in general had a minimal effect on their results, and that they were primarily focused on the data type captured and how it will be shared.

### 2015-03-04 tex-inputs/results-type.tex
Started modifying regression section, added codings for data types.

@@
 
+The data types the we examined span several existing and future use cases.
+However, we do not necessarily believe they are comprehensive or cover all possible future use cases for how wearable devices might capture personal data.
+As such, we decided to code each data type in terms of both the capture medium (e.g., video, audio, text, etc.) and the type of risk to which it might expose the user.
+The purpose of this was to examine {\it why} participants viewed certain data types as more or less risky than others so that we can then generalize our results to other data types that were not covered by this particular survey instrument.
+To this end, two researchers agreed on a codebook and then independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.} in terms of the medium used for collection and in terms of the type of risk posed to the user.
+The mediums fell into six possible categories:
+
+\begin{enumerate}
+\item Photo
+\item Video
+\item Audio
+\item Behavioral Information
+\item Biometric Information
+\item Demographic Information
+\end{enumerate}
+
+The associated risks with each data type fell into the following five categories:
+
+\begin{enumerate}
+\item {\bf Financial:} The risk involves the loss of money or property.
+\item {\bf Image:} The risk involves loss of control over one's self-image (e.g., publicizing something embarrassing).
+\item {\bf Medical:} The risk involves disclosure of medical information.
+\item {\bf Physical:} The risk involves physical harm to the user.
+\item {\bf Relationships:} The risk involves damage to the user's inter-personal relationships.
+\end{enumerate}
+
+Upon independently coding each data type along these two axes, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity.
+Prior to this resolution, they agree on 83\% of the codings.
+Cohen's $\kappa$ was 0.75 for the risks and 0.81 for the mediums, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+
 %A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.

### 2015-03-04 tex-inputs/intro.tex
finished intro and did a bit of tweaks to related work

@@
 
-Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} consisting of electronically enhanced clothing items and accessories aims to interweave technological interaction into everyday life.
+Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} of electronically enhanced clothing items and accessories that interweaves technological interaction with everyday life.
 A top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
@@
 
-Along with these benefits, wearable devices bring with them new potential privacy issues which expose users' activities without their awareness or consent.
+Along with these benefits, wearable devices bring with them new potential privacy and security risks which expose users' activities without their awareness or consent.
 Fitbit allowed sex to be tracked as exercise while fitness profiles were public by default~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Public discomfort toward facial recognition was so strong that the capability was not even deployed for Google Glass \cite{GlassDetection}.
-Google Glass, an iconic wearable of today, has since disappeared \cite{13_google_2015}.
+Public discomfort toward facial recognition prevented the capability from being deployed to Google Glass \cite{GlassDetection}.
+Google Glass, the iconic wearable of its time, has since disappeared \cite{13_google_2015}.
 Most suspect that the reason for its disappearance was because it was the ``straw the broke the back of the privacy camel's back'' \cite{14_dvorak_2014}.
@@
 
-{\color {red} smart phone concerns. we haven't gotten it right for this yet! We need to do something for wearables before it's too late.}
+We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture with respect to smartphones.
+Mobile platforms have tried to address this by communicating data capture to users as the data is captured.
+However, many users are habituated to these notifications, because they see them all the time, often for things that they don't care about \cite{felt2012android}.
 
-{\color {red} We should warn people about such things.
-But we can't do that, since attention is a finite resource.
-This calls for privacy research in this area!}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices to prevent negative social impact and breaches of privacy.
-There has been extensive work on the need for showing users and bystanders how certain data is being captured so that they can have more control.
-We have an issue of showing everyone everything all the time, since attention is a finite resource.
-We need to identify situations that people want to warn them about, and transparently access things that are benign.
-A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns.
-The goal of this paper is to gain a better sense of what those concerns are.
+Human attention is a finite resource \cite{bohme2011security}.
+Given the additional capabilities of wearable devices and their increasing popularity, we need to study user concerns to warn users only about situations they are likely to care about.
+Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoid scandalous breaches of privacy.
 
-{\color {red} better intro to here} We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]
+The goal of this paper is to gain a better sense of user concerns for wearables.
+To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
+We surveyed 1,784 Internet users for their perceptions of wearable devices and contribute the following: \\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
-\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
-\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies.
-However, we suspect that this may be due to a lack of exposure to these newer technologies.
-%\item We report people's self-reported top concerns for wearable devices.
-Privacy, by far, is the top concern.
-Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms.
+\item Comparisons of users' perceptions of a range of privacy and security risks of wearables. We found that users care much more about the type of data than the recipient of the data.
+\item Insight into how users feel about various data recipients.
+We observed that users make less distinction between sharing data with friends, co-workers, and the general public, comparatively to sharing with an application's servers.
+\item Rankings of how data-collection capabilities of wearable devices compared to more familiar technologies.
+Most saw new capabilities as benign, but we suspect that this may be due to a lack of exposure to these newer technologies.
+\item A taxonomy and report of users' self-reported top concerns for wearable devices. Privacy is by far the top concern, along with security, health risks, financial risk, and social impact. 
 \end{itemize}

### 2015-03-04 tex-inputs/related_work.tex
finished intro and did a bit of tweaks to related work

--- 2015-02-20 related_work.tex
@@
+%!TEX root = ../paper.tex
+
 \section{Related Work}
-In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.
+We discuss related work that has examined users' perceptions surrounding security and privacy risks.
 
-\subsection{Ubiquitous Sensing}
+\subsection{Wearables Concerns}
+A small-scale interview of how bystanders feel about wearable devices \cite{denning2014situ} found that bystanders were predominantly split between having indifferent and negative reactions to the device.
+A variety of factors that make recording more or less acceptable, including what they are doing when the recording is being taken.
+Additionally, bystanders are expressed interest in being able to give permissions for the data being captured.
+We also investigate how the type and mechanism of data capture affects privacy concerns, but we examine the privacy concerns of wearables owners at a large-scale while their research examined the privacy concerns of wearables bystanders at a small-scale.
+
+\subsection{Ubiquitous Sensing Concerns}
 Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
@@
 However, none of these works attempted to quantify or rank user concern over different privacy risks.
+%one-sentence on takeaways from these sources and comment on them!
 
-\subsection{Smartphones and Wearables Concerns}
+\subsection{Smartphones Concerns}
 Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.  
-
-Recently Denning et.
-al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}.
-Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous).
-While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.
+%one-sentence on takeaways from these sources and comment on them!
 
@@
 Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
+%one-sentence on takeaways from these sources and comment on them!

### 2015-03-04 recipient.tex

@@
 \hline
-Rank & Recipient & VUR & Variance & Distribution\\
+Rank & Recipient & VUR & Standard Deviation & Distribution\\
 \hline
-1& WORKCONTACTS & 75.16 & 0.879886356298& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_work}\\ 
-2& PUBLIC & 72.41 & 0.96322375386& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_pub}\\ 
-3& FRIENDS & 69.47 & 1.03749698795 & \includegraphics[width = 2cm, height = 2cm]{tables/recipient_friends}\\ 
-4& ALL & 64.78 & 1.1105854312& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_total}\\ 
-5& APPSERVER & 42.28 & 1.32348026053& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_app}\\ 
-6\hline
+1& WORKCONTACTS & 75.16 & 0.938029850271& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_work}\\ 
+2& PUBLIC & 72.41 & 0.981427531711& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_pub}\\ 
+3& FRIENDS & 69.47 & 1.01857743937 & \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_friends}\\ 
+4& ALL & 64.78 & 1.05385008422& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_total}\\ 
+5& APPSERVER & 42.28 & 1.15043470045& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_app}\\ 
+\hline
 \end{tabular}

### 2015-03-04 tex-inputs/long-tables/collapsed.tex

\documentclass[a4paper,12pt]{article}
\usepackage[cm]{fullpage}
\usepackage{longtable}
\usepackage{graphicx}
\begin{document}
\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}

\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
\endhead

\hline \multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\hline 
\endlastfoot
1 & Tookavideoofyouunclothed & 95.97 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouunclothedcombined} \\ 
2 & Learnedyourbankaccountinformation & 95.91 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourbankaccountinformationcombined} \\ 
3 & Learnedyoursocialsecuritynumber & 94.84 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyoursocialsecuritynumbercombined} \\ 
4 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinyourPINatanATMcombined} \\ 
5 & Tookaphotoofyouunclothed & 92.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouunclothedcombined} \\ 
6 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
7 & Learnedyourusernameandpasswordforwebsites & 89.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameandpasswordforwebsitescombined} \\ 
8 & Learnedyourcreditcardinformation & 88.98 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourcreditcardinformationcombined} \\ 
9 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
11 & Recordedyourworkconversations & 86.82 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourworkconversationscombined} \\ 
12 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
13 & Recordedyourphoneconversations & 85.16 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourphoneconversationscombined} \\ 
14 & Learnedhowmuchmoneyyouhave & 84.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchmoneyyouhavecombined} \\ 
15 & Tookavideoofyouintoxicated & 83.21 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouintoxicatedcombined} \\ 
16 & Learnedwhenandhowmuchyouhavesex & 81.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouhavesexcombined} \\ 
17 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
18 & Tookaphotoofyouintoxicated & 78.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouintoxicatedcombined} \\ 
19 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
20 & Recordedyourpassingconversations & 78.13 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourpassingconversationscombined} \\ 
21 & Learnedwhatmedicalconditionsyouhave & 77.7 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicalconditionsyouhavecombined} \\ 
22 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
23 & Tookavideoofyouoff-Guard & 76.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouoff-guardcombined} \\ 
24 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosatwork(withanoutward-facingcamera)combined} \\ 
25 & Learnedyourusernameforwebsites & 73.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameforwebsitescombined} \\ 
26 & Learnedyouraddress & 72.61 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouraddresscombined} \\ 
27 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
28 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
29 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
30 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
31 & Sharedvideosotherssentyousavedonyourdevice & 70.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosotherssentyousavedonyourdevicecombined} \\ 
32 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosatwork(withanoutward-facingcamera)combined} \\ 
33 & Learnedyourfingerprintsomehow & 70.12 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourfingerprintsomehowcombined} \\ 
34 & Learnedwhenyouwerelyingnervousorstressed & 69.74 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerelyingnervousorstressedcombined} \\ 
35 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
36 & Learnedwhatmedicationyoutake & 69.49 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicationyoutakecombined} \\ 
37 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
38 & Tookapictureofyoursignature & 68.07 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookapictureofyoursignaturecombined} \\ 
39 & Learnedwhatwebsitesyougoto & 66.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatwebsitesyougotocombined} \\ 
40 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
41 & Learnedwhereyoulivesomehow & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyoulivesomehowcombined} \\ 
42 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
43 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
44 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
45 & Learnedwhenandhowmuchyouspendtimealone & 61.27 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouspendtimealonecombined} \\ 
46 & Trackedwhereyouare(Likeagps) & 61.24 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouare(likeaGPS)combined} \\ 
47 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
48 & Learnedwhereyouarecurrentlygoing & 60.87 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouarecurrentlygoingcombined} \\ 
49 & Recordedthesoundaroundyou & 60.45 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedthesoundaroundyoucombined} \\ 
50 & Learnedwhoyouwerespendingtimewith & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhoyouwerespendingtimewithcombined} \\ 
51 & Learnedwhereyouworksomehow & 58.09 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouworksomehowcombined} \\ 
52 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
53 & Learnedhowmuchyouuseyourphone & 51.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourphonecombined} \\ 
54 & Learnedwhatproductsyoubuy & 50.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatproductsyoubuycombined} \\ 
55 & Learnedwhenyouaresickorhealthy & 48.17 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouaresickorhealthycombined} \\ 
56 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
57 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
58 & Learnedhowmuchyouuseyourcomputer & 44.93 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourcomputercombined} \\ 
59 & Learnedwhenhowmuchandwhatyouareeating & 42.86 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowmuchandwhatyouareeatingcombined} \\ 
60 & Learnedyourname & 42.54 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyournamecombined} \\ 
61 & Learnedwhenandhowwellyouaresleeping & 40.56 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowwellyouaresleepingcombined} \\ 
62 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesscannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
63 & Learnedwhenhowandhowmuchyouexercise & 38.66 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowandhowmuchyouexercisecombined} \\ 
64 & Learnedwhenyouwerehappyorhavingfun & 34.75 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerehappyorhavingfuncombined} \\ 
65 & Learnedwhattelevisionshowsyouwatch & 30.2 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhattelevisionshowsyouwatchcombined} \\ 
66 & Learnedwhenyouarebusyorinterruptible & 29.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouarebusyorinterruptiblecombined} \\ 
67 & Copiedanduploadedmusicfromyourdevice & 28.06 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedmusicfromyourdevicecombined} \\ 
68 & Learnedyourheartrate & 27.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourheartratecombined} \\ 
69 & Learnedyourage & 24.29 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouragecombined} \\ 
70 & Learnedthelanguageyouwerespeaking & 15.86 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedthelanguageyouwerespeakingcombined} \\ 
71 & Learnedyourgender & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourgendercombined} \\ 
\end{longtable}

\end{document}

### 2015-03-04 tex-inputs/results-recipient.tex
paper cleanup

@@
-%!TEX root = paper.tex
+%!TEX root = ../paper.tex
 
@@
 \hline
-Rank & Recipient & VUR & sd & Distribution \\
+Rank & Recipient & VUR & sigma & Distribution \\
 \hline
-1 & Work Contacts & 75.16\% & 0.880 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
-2 & Public & 72.41\% & 0.963 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
-3 & Friends & 69.47\% & 1.037 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
-4 & App's Server & 42.28\% & 1.323 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
+1 & Work Contacts & 75.16\% & 0.938 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
+2 & Public & 72.41\% & 0.981 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
+3 & Friends & 69.47\% & 1.019 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
+4 & App's Server & 42.28\% & 1.150 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
 \hline

### 2015-03-04 tex-inputs/abstract.tex
abstract redo, intro tweaks, and much progress on data type results section

%!TEX root = ../paper.tex

\begin{abstract}
Along with great benefits, wearable devices, or ``wearables,'' bring new potential privacy and security risks which expose users' activities without their awareness or consent. With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture \cite{denning2014situ}, but human attention is a finite resource \cite{bohme2011security}. Therefore, user concerns should be investigated to to warn users only about situations they are likely to care about. Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy. To this end, we conducted the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,784 Internet users for their perceptions of wearable devices and contribute: relevant perceived risks for wearables, effects of data type and data recipient on perceived risk, users' self reported concerns, and an assessment of how wearable device capabilities compare to familiar technologies. We conclude with a discussion on future research directions for wearable devices. 
\end{abstract}

% A category with the (minimum) three required fields
\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

%\terms{Human Factors}{Measurement}{Security}

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings

### 2015-03-04 tex-inputs/intro.tex
abstract redo, intro tweaks, and much progress on data type results section

@@
 
-Along with these benefits, wearable devices bring with them new potential privacy and security risks which expose users' activities without their awareness or consent.
+Along with these benefits, wearable devices bring new potential privacy and security risks which expose users' activities without their awareness or consent.
 Fitbit allowed sex to be tracked as exercise while fitness profiles were public by default~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
@@
 
-Human attention is a finite resource \cite{bohme2011security}.
-Given the additional capabilities of wearable devices and their increasing popularity, we need to study user concerns to warn users only about situations they are likely to care about.
-Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoid scandalous breaches of privacy.
+With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture \cite{denning2014situ}, but human attention is a finite resource \cite{bohme2011security}.
+Therefore, user concerns should be investigated to to warn users only about situations they are likely to care about.
+Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy.
 
@@
 We observed that users make less distinction between sharing data with friends, co-workers, and the general public, comparatively to sharing with an application's servers.
+\item A taxonomy and report of users' self-reported top concerns for wearable devices. Privacy is by far the top concern, along with security, health risks, financial risk, and social impact. 
 \item Rankings of how data-collection capabilities of wearable devices compared to more familiar technologies.
 Most saw new capabilities as benign, but we suspect that this may be due to a lack of exposure to these newer technologies.
-\item A taxonomy and report of users' self-reported top concerns for wearable devices. Privacy is by far the top concern, along with security, health risks, financial risk, and social impact. 
 \end{itemize}

### 2015-03-04 tex-inputs/results-recipient.tex
abstract redo, intro tweaks, and much progress on data type results section

@@
 \hline
-1 & Work Contacts & 75.16\% & 0.938 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
-2 & Public & 72.41\% & 0.981 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
-3 & Friends & 69.47\% & 1.019 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
-4 & App's Server & 42.28\% & 1.150 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
+1 & Work Contacts & 75.16\% & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
+2 & Public & 72.41\% & 0.98 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
+3 & Friends & 69.47\% & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
+4 & App's Server & 42.28\% & 1.15 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
 \hline
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
+\caption{The overall upset rate for all recipients.}
 \label{recipient-table}
@@
 
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-%Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-%Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-%Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-%Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-%Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
+{\color {red} TODO: table of top and bottom 10 data types by recipient; refer to appendix; shoutout to when you were lying nervous or stressed work}

### 2015-03-04 tex-inputs/results-type.tex
abstract redo, intro tweaks, and much progress on data type results section

--- 2015-03-03 tex-inputs/results-type.tex
@@
+%!TEX root = ../paper.tex
+
 \subsubsection{Data Type}
@@
 We present various statistical models in section \ref{sec:regression} to support this conclusion.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
+The 10 most and 10 least concerning data types can be seen in Table \ref{top10-table}.
 
 Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, {\color {red} and are unanimously considered to be concerning}.
+As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, and are almost unanimously considered to be concerning.
 Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
@@
 Also regardless of the other factors, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-{\color {red} As seen in Table \ref{top10-table}, participants had distributed opinions on how risky this information was to be shared.
-A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.}
+As seen in Table \ref{top10-table}, participants had spread distributions in perceptions regarding such information.
+A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.
 
@@
 
-\begin{table}[t]
+\begin{table*}[t]
 \begin{center}
 \small
-\begin{tabular}{| r | l | r | l |c |}
+\begin{tabular}{| r | l | r | r |c |}
 \hline
-Rank & Data & VUR & sd & Distribution \\
+Rank & Data & VUR & $\sigma$ & Distribution \\
 \hline
-1 & a video of you unclothed & 95.97\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouunclothedcombined} \\
-2 & bank account information & 95.91\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourbankaccountinformationcombined}  \\
-3 & social security number & 94.84\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyoursocialsecuritynumbercombined}\\
-4 & video of you entering in your PIN & 92.67\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouenteringinyourPINatanATMcombined}\\
-5 & a photo of you unclothed & 92.59\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookaphotoofyouunclothedcombined}\\
-6 & an incriminating/embarrassing photo of you & 91.39\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined}\\
-7 & username and password for websites & 89.55\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourusernameandpasswordforwebsitescombined}\\
-8 & credit card information & 88.98\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourcreditcardinformationcombined}\\
-9 & an incriminating/embarrassing video of you & 88.41\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined}\\
-10 & a random (inward-facing) photo you at home & 87.50\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookphotosofyou(withaninward-facingcamera)athomecombined}\\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\%& number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\
-65 & when and how much you exercise  & 38.66\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenhowandhowmuchyouexercisecombined}\\
-66 & when you are happy or having fun  & 34.75\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouwerehappyorhavingfuncombined}\\
-67 & which television shows you watch & 30.20\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhattelevisionshowsyouwatchcombined}\\
-68 & when you are busy or interruptible  & 29.50\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouarebusyorinterruptiblecombined}\\
-69 & music from your device  & 28.06\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/copiedanduploadedmusicfromyourdevicecombined}\\
-70 & your heart rate & 27.50\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourheartratecombined} \\
-71 & your age & 24.29\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyouragecombined}\\
-72 & the language you speak & 15.86\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedthelanguageyouwerespeakingcombined}\\
-73 & your gender & 15.00\% & number & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourgendercombined}\\ 
+1 & video of you unclothed & 95.97\% & 0.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouunclothedcombined} \\
+2 & bank account information & 95.91\% & 0.35 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourbankaccountinformationcombined}  \\
+3 & social security number & 94.84\% & 0.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyoursocialsecuritynumbercombined}\\
+4 & video entering in a PIN at an ATM & 92.67\% & 0.47 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouenteringinyourPINatanATMcombined}\\
+5 & photo of you unclothed & 92.59\% & 0.46 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookaphotoofyouunclothedcombined}\\
+6 & photo of you that is very embarrassing & 91.39\% & 0.55 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined}\\
+7 & username and password for websites & 89.55\% & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourusernameandpasswordforwebsitescombined}\\
+8 & credit card information & 88.98\% & 0.56 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourcreditcardinformationcombined}\\
+9 & video of you that is very embarrassing & 88.41\% & 0.53 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined}\\
+10 & photo of you at home & 87.50\% & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookphotosofyou(withaninward-facingcamera)athomecombined}\\
+ & \vdots & & & \\
+64 & eye patterns (for eye tracking) & 40.51\%& 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\
+65 & exercise patterns  & 38.66\% & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenhowandhowmuchyouexercisecombined}\\
+66 & when you are happy or having fun  & 34.75\% & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouwerehappyorhavingfuncombined}\\
+67 & television shows watched & 30.20\% & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhattelevisionshowsyouwatchcombined}\\
+68 & when you are busy or interruptible  & 29.50\% & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouarebusyorinterruptiblecombined}\\
+69 & music on device  & 28.06\% & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/copiedanduploadedmusicfromyourdevicecombined}\\
+70 & your heart rate & 27.50\% & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourheartratecombined} \\
+71 & age & 24.29\% & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyouragecombined}\\
+72 & language spoken & 15.86\% & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedthelanguageyouwerespeakingcombined}\\
+73 & gender & 15.00\% & 1.45 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourgendercombined}\\ 
 \hline
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
+\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix [?].}
 \label{top10-table}
 \end{center}
-\end{table}
+\end{table*}
+
+The data types examined span several existing and future use cases.
+We do not believe they are comprehensive in coverage of how wearable devices might capture data nor for all possible future use cases of the data.
+Therefore, we coded each data type in two ways: firstly in terms in the data and how it was captured (e.g., video, audio, text, etc.), and  secondly in terms of the type of risks presented to the user.
+This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results.
+Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}
+
+The data captured fell into the following six possible categories:
+
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item Photo
+\item Video
+\item Audio
+\item Behavioral Information
+\item Biometric Information
+\item Demographic Information
+\end{enumerate}
+
+The associated risks data type fell into the following five categories:
+
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item {\bf Financial:} The risk involves the loss of money or property.
+\item {\bf Image:} The risk involves loss of control over one's self-image (e.g., publicizing something embarrassing).
+\item {\bf Medical:} The risk involves disclosure of medical information.
+\item {\bf Physical:} The risk involves physical harm to the user.
+\item {\bf Relationships:} The risk involves damage to the user's inter-personal relationships.
+\end{enumerate}
+
+After independently coding all data types with respect to these categories, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity.
+Prior to this resolution, there was  83\% agreement.
+Cohen's $\kappa$ is 0.81 for the data capture and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
 

### 2015-03-04 tex-inputs/results-type.tex
finished data type section

@@
 \subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
+Based on our data, we observed that the largest effect stemmed from the data being shared.
 We present various statistical models in section \ref{sec:regression} to support this conclusion.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10-table}.
+The 10 top and bottom concerning data can be seen in Table \ref{top10-table}, and the full list of data can be seen in Appendix [?].
 
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+Participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
 As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, and are almost unanimously considered to be concerning.
@@
 
-Also regardless of the other factors, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
+Participants were least concerned about data that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken) and information available to advertisers (e.g.
+TV shows watched, music on device).
 As seen in Table \ref{top10-table}, participants had spread distributions in perceptions regarding such information.
-A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.
+These may have appeared as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.
 
-{\color {red} talk about the variance of the data types here, referring to the table in the appendix.
-Which were the highest in variance?
-Which were the unanimous?
-Which one had a spread?
-Were there any that were specifically polarized?
-J has yet to give me the table for this so I can talk about it.
-But the most unanimous ones seemed to be the highest-concerning ones, whereas the least concerning ones were more distributed.
-There are not any which are unanimously considered medium risk or to be not risky.}
+For the complete ranked list of data considered in this study, see Appendix [?].
+Although certain data is considered unanimously upsetting to have shared, it is interesting to note that no data was considered unanimously non-upsetting to have shared, nor any data which evoked strong disagreement on how upsetting it was.
+Generally,  the rank of the data being shared is negatively correlated with the standard deviation of the answers.
 
@@
 This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results.
-Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}
+Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}.
 
-The data captured fell into the following six possible categories:
-
+The data fell into the following six possible categories:
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 
-The associated risks data type fell into the following five categories:
-
+The associated risks fell into the following five categories:
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]

### 2015-03-04 tex-inputs/long-tables/collapsed.tex
fixed long tables

@@
 \begin{document}
-\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
+\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} |p{1cm} | c |}
 
-\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
+\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Standard Deviation}} &\multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline
 \endfirsthead
@@
 {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
-\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} &  \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline 
+\hline \multicolumn{1}{|c|}{\textbf{Rank}} & \multicolumn{1}{c|}{\textbf{Question}} & \multicolumn{1}{c|}{\textbf{VUR}} & \multicolumn{1}{c|}{\textbf{Standard Deviation}} & \multicolumn{1}{c|}{\textbf{Distribution}} \\ \hline
 \endhead
@@
 \endlastfoot
-1 & Tookavideoofyouunclothed & 95.97 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouunclothedcombined} \\ 
-2 & Learnedyourbankaccountinformation & 95.91 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourbankaccountinformationcombined} \\ 
-3 & Learnedyoursocialsecuritynumber & 94.84 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyoursocialsecuritynumbercombined} \\ 
-4 & Tookavideoofyouenteringinyourpinatanatm & 92.67 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinyourPINatanATMcombined} \\ 
-5 & Tookaphotoofyouunclothed & 92.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouunclothedcombined} \\ 
-6 & Tookanincriminatingphotoofyoudoingsomethingembarrassing & 91.39 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
-7 & Learnedyourusernameandpasswordforwebsites & 89.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameandpasswordforwebsitescombined} \\ 
-8 & Learnedyourcreditcardinformation & 88.98 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourcreditcardinformationcombined} \\ 
-9 & Tookanincriminatingvideoofyoudoingsomethingembarrassing & 88.41 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
-10 & Tookphotosofyou(Withaninward-Facingcamera)Athome & 87.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
-11 & Recordedyourworkconversations & 86.82 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourworkconversationscombined} \\ 
-12 & Tookavideoofyouenteringinadigitalpasscodetoalockeddoor & 85.53 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
-13 & Recordedyourphoneconversations & 85.16 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourphoneconversationscombined} \\ 
-14 & Learnedhowmuchmoneyyouhave & 84.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchmoneyyouhavecombined} \\ 
-15 & Tookavideoofyouintoxicated & 83.21 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouintoxicatedcombined} \\ 
-16 & Learnedwhenandhowmuchyouhavesex & 81.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouhavesexcombined} \\ 
-17 & Tookvideosofyou(Withaninward-Facingcamera)Athome & 81.05 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
-18 & Tookaphotoofyouintoxicated & 78.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookaphotoofyouintoxicatedcombined} \\ 
-19 & Tookphotosofyou(Withaninward-Facingcamera)Atrandom & 78.76 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
-20 & Recordedyourpassingconversations & 78.13 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyourpassingconversationscombined} \\ 
-21 & Learnedwhatmedicalconditionsyouhave & 77.7 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicalconditionsyouhavecombined} \\ 
-22 & Tookvideosofyou(Withaninward-Facingcamera)Atrandom & 76.19 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
-23 & Tookavideoofyouoff-Guard & 76.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookavideoofyouoff-guardcombined} \\ 
-24 & Tookphotosatwork(Withanoutward-Facingcamera) & 74.62 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosatwork(withanoutward-facingcamera)combined} \\ 
-25 & Learnedyourusernameforwebsites & 73.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourusernameforwebsitescombined} \\ 
-26 & Learnedyouraddress & 72.61 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouraddresscombined} \\ 
-27 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
-28 & Copiedanduploadedaudiorecordingsyoumadeonyourdevice & 72.55 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
-29 & Sharedphotosyoudownloadedfromtheinternetsavedonyourdevice & 71.81 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
-30 & Sharedphotosotherssenttoyousavedonyourdevice & 71.63 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
-31 & Sharedvideosotherssentyousavedonyourdevice & 70.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosotherssentyousavedonyourdevicecombined} \\ 
-32 & Tookvideosatwork(Withanoutward-Facingcamera) & 70.54 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosatwork(withanoutward-facingcamera)combined} \\ 
-33 & Learnedyourfingerprintsomehow & 70.12 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourfingerprintsomehowcombined} \\ 
-34 & Learnedwhenyouwerelyingnervousorstressed & 69.74 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerelyingnervousorstressedcombined} \\ 
-35 & Recordedyoutalkingtoyourself(Makingvoicenotes) & 69.59 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
-36 & Learnedwhatmedicationyoutake & 69.49 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatmedicationyoutakecombined} \\ 
-37 & Sharedvideosyoutookwhicharealreadyonyourdevice & 68.89 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
-38 & Tookapictureofyoursignature & 68.07 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookapictureofyoursignaturecombined} \\ 
-39 & Learnedwhatwebsitesyougoto & 66.44 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatwebsitesyougotocombined} \\ 
-40 & Sharedphotosyoutookwhicharealreadyonyourdevice & 66.21 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
-41 & Learnedwhereyoulivesomehow & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyoulivesomehowcombined} \\ 
-42 & Trackedwhereyouareveryaccurately(Whereyouareinaroom) & 63.51 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
-43 & Tookphotosofpeople(Withanoutward-Facingcamera)Atrandom & 61.94 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
-44 & Sharedvideosyoudownloadedontheinternetsavedonyourdevice & 61.49 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
-45 & Learnedwhenandhowmuchyouspendtimealone & 61.27 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowmuchyouspendtimealonecombined} \\ 
-46 & Trackedwhereyouare(Likeagps) & 61.24 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestrackedwhereyouare(likeaGPS)combined} \\ 
-47 & Tookvideosofpeople(Withanoutward-Facingcamera)Atrandom & 61.04 & \includegraphics[width = 2cm, height = 0.5cm]{../tablestookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
-48 & Learnedwhereyouarecurrentlygoing & 60.87 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouarecurrentlygoingcombined} \\ 
-49 & Recordedthesoundaroundyou & 60.45 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrecordedthesoundaroundyoucombined} \\ 
-50 & Learnedwhoyouwerespendingtimewith & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhoyouwerespendingtimewithcombined} \\ 
-51 & Learnedwhereyouworksomehow & 58.09 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhereyouworksomehowcombined} \\ 
-52 & Copiedanduploadedsoundssavedonyourdevice(Notificationnoisesetc) & 54.4 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\
-53 & Learnedhowmuchyouuseyourphone & 51.95 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourphonecombined} \\ 
-54 & Learnedwhatproductsyoubuy & 50.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhatproductsyoubuycombined} \\ 
-55 & Learnedwhenyouaresickorhealthy & 48.17 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouaresickorhealthycombined} \\ 
-56 & Learnedhowcloseyouaretootherpeopleyouinteractwith & 46.98 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
-57 & Learnedhowyouwerefeelingbasedonheartratebreathingandortemperature & 46.81 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\
-58 & Learnedhowmuchyouuseyourcomputer & 44.93 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedhowmuchyouuseyourcomputercombined} \\ 
-59 & Learnedwhenhowmuchandwhatyouareeating & 42.86 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowmuchandwhatyouareeatingcombined} \\ 
-60 & Learnedyourname & 42.54 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyournamecombined} \\ 
-61 & Learnedwhenandhowwellyouaresleeping & 40.56 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenandhowwellyouaresleepingcombined} \\ 
-62 & Scannedyoureyetolearnyoureyepatterns(Foreyetracking) & 40.51 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesscannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
-63 & Learnedwhenhowandhowmuchyouexercise & 38.66 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenhowandhowmuchyouexercisecombined} \\ 
-64 & Learnedwhenyouwerehappyorhavingfun & 34.75 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouwerehappyorhavingfuncombined} \\ 
-65 & Learnedwhattelevisionshowsyouwatch & 30.2 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhattelevisionshowsyouwatchcombined} \\ 
-66 & Learnedwhenyouarebusyorinterruptible & 29.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedwhenyouarebusyorinterruptiblecombined} \\ 
-67 & Copiedanduploadedmusicfromyourdevice & 28.06 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescopiedanduploadedmusicfromyourdevicecombined} \\ 
-68 & Learnedyourheartrate & 27.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourheartratecombined} \\ 
-69 & Learnedyourage & 24.29 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyouragecombined} \\ 
-70 & Learnedthelanguageyouwerespeaking & 15.86 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedthelanguageyouwerespeakingcombined} \\ 
-71 & Learnedyourgender & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslearnedyourgendercombined} \\ 
+1 & video of you unclothed & 95.97 & 0.31 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouunclothedcombined} \\ 
+2 & bank account information & 95.91 & 0.35 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourbankaccountinformationcombined} \\ 
+3 & social security number & 94.84 & 0.26 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyoursocialsecuritynumbercombined} \\ 
+4 & video entering in a PIN at an ATM & 92.67 & 0.48 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouenteringinyourPINatanATMcombined} \\ 
+5 & photo of you unclothed & 92.59 & 0.45 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookaphotoofyouunclothedcombined} \\ 
+6 & photo of you that is very embarrassing & 91.39 & 0.56 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
+7 & username and password for websites & 89.55 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourusernameandpasswordforwebsitescombined} \\ 
+8 & credit card information & 88.98 & 0.56 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourcreditcardinformationcombined} \\ 
+9 & video of you that is very embarrassing & 88.41 & 0.53 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
+10 & photo of you at home & 87.5 &0.60 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
+11 & audio recording of work conversations & 86.82 & 0.76 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyourworkconversationscombined} \\ 
+12 & video of entering in a passcode to a door & 85.53 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
+13 & audio recording of phone conversations & 85.16 & 0.61 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyourphoneconversationscombined} \\ 
+14 & amount of money you have & 84.44 & 0.61 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowmuchmoneyyouhavecombined} \\ 
+15 & video of you intoxicated & 83.21 & 0.72 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouintoxicatedcombined} \\ 
+16 & when you have sex & 81.95 & 0.82 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenandhowmuchyouhavesexcombined} \\ 
+17 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
+18 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookaphotoofyouintoxicatedcombined} \\ 
+19 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
+20 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyourpassingconversationscombined} \\ 
+21 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
+22 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
+23 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookavideoofyouoff-guardcombined} \\ 
+24 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
+25 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourusernameforwebsitescombined} \\ 
+26 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyouraddresscombined} \\ 
+27 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
+28 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookaphotoofyouoff-guardcombined} \\ 
+29 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
+30 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
+31 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
+32 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
+33 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourfingerprintsomehowcombined} \\ 
+34 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
+35 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
+36 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatmedicationyoutakecombined} \\ 
+37 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
+38 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookapictureofyoursignaturecombined} \\ 
+39 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatwebsitesyougotocombined} \\ 
+40 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
+41 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhereyoulivesomehowcombined} \\ 
+42 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
+43 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
+44 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
+45 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
+46 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/trackedwhereyouare(likeaGPS)combined} \\ 
+47 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
+48 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
+49 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/recordedthesoundaroundyoucombined} \\ 
+50 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
+51 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhereyouworksomehowcombined} \\ 
+52 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
+53 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowmuchyouuseyourphonecombined} \\ 
+54 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhatproductsyoubuycombined} \\ 
+55 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouaresickorhealthycombined} \\ 
+56 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
+57 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
+58 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
+59 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
+60 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyournamecombined} \\ 
+61 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
+62 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
+63 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
+64 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
+65 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
+66 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
+67 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
+68 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourheartratecombined} \\ 
+69 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyouragecombined} \\ 
+70 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedthelanguageyouwerespeakingcombined} \\ 
+71 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{table-images/learnedyourgendercombined} \\ 
 \end{longtable}

### 2015-03-04 tex-inputs/collapsed.tex
got rid of longtables madness

%!TEX root = ../paper.tex
\begin{table*}[t]
\begin{center}
\small
\begin{tabular}{| l | r | r | r | r | r |}
\hline
Rank & Question & VUR & $\sigma$ & Distribution \\
\hline
1 & video of you unclothed & 95.97 & 0.31 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouunclothedcombined} \\ 
2 & bank account information & 95.91 & 0.35 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourbankaccountinformationcombined} \\ 
3 & social security number & 94.84 & 0.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyoursocialsecuritynumbercombined} \\ 
4 & video entering in a PIN at an ATM & 92.67 & 0.48 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouenteringinyourPINatanATMcombined} \\ 
5 & photo of you unclothed & 92.59 & 0.45 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouunclothedcombined} \\ 
6 & photo of you that is very embarrassing & 91.39 & 0.56 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined} \\ 
7 & username and password for websites & 89.55 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourusernameandpasswordforwebsitescombined} \\ 
8 & credit card information & 88.98 & 0.56 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourcreditcardinformationcombined} \\ 
9 & video of you that is very embarrassing & 88.41 & 0.53 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined} \\ 
10 & photo of you at home & 87.5 &0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofyou(withaninward-facingcamera)athomecombined} \\ 
11 & audio recording of work conversations & 86.82 & 0.76 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourworkconversationscombined} \\ 
12 & video of entering in a passcode to a door & 85.53 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouenteringinadigitalpasscodetoalockeddoorcombined} \\ 
13 & audio recording of phone conversations & 85.16 & 0.61 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourphoneconversationscombined} \\ 
14 & amount of money you have & 84.44 & 0.61 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchmoneyyouhavecombined} \\ 
15 & video of you intoxicated & 83.21 & 0.72 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouintoxicatedcombined} \\ 
16 & when you have sex & 81.95 & 0.82 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouhavesexcombined} \\ 
17 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
18 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouintoxicatedcombined} \\ 
19 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
20 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourpassingconversationscombined} \\ 
21 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
22 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
23 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouoff-guardcombined} \\ 
24 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
25 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourusernameforwebsitescombined} \\ 
26 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouraddresscombined} \\ 
27 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
28 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouoff-guardcombined} \\ 
29 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
30 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
31 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
32 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
33 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourfingerprintsomehowcombined} \\ 
34 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
35 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
36 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicationyoutakecombined} \\ 
37 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
38 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookapictureofyoursignaturecombined} \\ 
39 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatwebsitesyougotocombined} \\ 
40 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
41 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyoulivesomehowcombined} \\ 
42 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
43 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
44 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
45 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
46 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouare(likeaGPS)combined} \\ 
47 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
48 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
49 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedthesoundaroundyoucombined} \\ 
50 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
51 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouworksomehowcombined} \\ 
52 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\ 
53 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourphonecombined} \\ 
54 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatproductsyoubuycombined} \\ 
55 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouaresickorhealthycombined} \\ 
56 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
57 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\ 
58 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
59 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
60 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyournamecombined} \\ 
61 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
62 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
63 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
64 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
65 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
66 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
67 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
68 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourheartratecombined} \\ 
69 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouragecombined} \\ 
70 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedthelanguageyouwerespeakingcombined} \\ 
71 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourgendercombined} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix [?].}
\label{top10-table}
\end{center}
\end{table*}

### 2015-03-04 tex-inputs/results-demographics.tex
made it so every tex input file can compile the paper

--- 2015-03-03 tables-more/wearables-survey-paper-master/results.tex
@@
-\section{Results}
-We present our survey results and provide analyses of the data.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
-
-\subsection{Concern Factors}
-Many factors impact participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
-
-\subsubsection{Data Type}
-Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.
-
-Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
-
-Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken).
-It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| r | l | r |}
-\hline
-Rank & Data &  VUR  \\
-\hline
-1 & a video of you unclothed & 95.97\% \\
-2 & bank account information & 95.91\% \\
-3 & social security number & 94.84\% \\
-4 & video of you entering in your PIN & 92.67\% \\
-5 & a photo of you unclothed & 92.59\% \\
-6 & an incriminating/embarrassing photo of you & 91.39\% \\
-7 & username and password for websites & 89.55\% \\
-8 & credit card information & 88.98\% \\
-9 & an incriminating/embarrassing video of you & 88.41\% \\
-10 & a random (inward-facing) photo you at home & 87.50\% \\
- & \vdots & \\
-64 & eye movement patterns (for eye tracking) & 40.51\% \\
-65 & when and how much you exercise  & 38.66\% \\
-66 & when you are happy or having fun  & 34.75\% \\
-67 & which television shows you watch & 30.20\% \\
-68 & when you are busy or interruptible  & 29.50\% \\
-69 & music from your device  & 28.06\% \\
-70 & your heart rate & 27.50\% \\
-71 & your age & 24.29\% \\
-72 & the language you speak & 15.86\% \\
-73 & your gender & 15.00\% \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}
-
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
-
-\subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
-However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
-
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
-But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
-
-%Comment on differences between public/work, and end the subsection
-%SE: this needs to be rewritten below.
-
-We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans.
-We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]
-
-\begin{packed_enum}
-\item Bank account information
-\item A video of you unclothed
-\item Social security number
-\item Video of you entering your PIN
-\item An incriminating/embarrassing photo of you
-\item A photo of you unclothed \\[-.8cm]
-\end{packed_enum}
-
-While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed.
-For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%.
-This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|}
-%\hline
-%Recipients & VUR \\
-%\hline
-%App &  42.3\% \\
-%Friends & 69.5\% \\
-%Work & 75.2\% \\
-%Public & 72.4\% \\ 
-%\hline
-%\end{tabular}
-%\caption{generated for my presentation.}
-%\label{nouse}
-%\end{center}
-%\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-\hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
-\hline
-\end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-\label{recipient}
-\end{center}
-\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{|l|r|r|r|r|}
-%\hline
-%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
-%\hline
-%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
-%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
-%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
-%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
-%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
-%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
-%\hline
-%\end{tabular}
-%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
-%Work-App	& 564.318 & <0.0001 & 0.111\\
-%Public-App	& 479.980 & <0.0001 &  0.092\\
-%Friends-App & 380.000 & <0.0001 & 0.075\\
-%Friends-Work & 20.365 & <0.0001 &  0.004\\
-%Friends-Public & 5.349 & 0.0207 &  0.001\\
-%Work-Public&  5.054 & 0.0246 &  0.001\\
-%\end{tabular}
-%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
-%\label{recipient}
-%\end{center}
-%\end{table}
-
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%<data> & VUR  \\
-%social security number & 98.04\% \\ CC
-%a video of you unclothed & 97.44\% \\ CC
-%bank account information & 97.10\% \\ CC
-%recordings of your work conversations & 96.97\% \\ 
-%an incriminating/embarrassing photo of you & 96.36\% \\ CC
-%a photo of you unclothed & 96.30\% \\ CC
-%credit card information & 95.92\% \\ 
-%username and password for websites & 95.41\% \\ 
-%a video of you entering in your PIN & 93.91\% \\ CC
-%recordings of your phone conversations & 93.88\% \\ 
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%bank account information & 90.91\% \\ CC
-%a video of you unclothed & 90.62\% \\ CC
-%social security number  & 88.68\% \\ CC
-%video of you entering your PIN & 88.57\% \\ CC
-%an incriminating/embarrassing photo of you & 78.05\% \\ CC
-%a photo of you unclothed & 77.78\% \\ CC
-%a video of you entering a passcode to a door & 75.00\% \\ 
-%when and how much you have sex & 73.08\% \\ 
-%an incriminating/embarrassing video of you & 71.88\% \\ 
-%a random (inward-facing) photo of you at home & 66.67\% \\
-%\end{tabular}
-%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedtop10}
-%\end{center}
-%\end{table}
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%your name & 47.25\% \\
-%when and how much you exercise & 46.07\% \\
-%when you were happy or having fun & 38.10\% \\
-%what television shows you watch & 35.96\% \\
-%when you are busy or interruptible & 34.34\% \\
-%your heart rate & 32.28\% \\
-%music from your device & 31.87\% \\
-%your age & 29.67\% \\
-%the language you speak & 20.95\% \\
-%your gender & 16.81\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
-%\label{sharedbottom10}
-%\end{center}
-%\end{table}
-%
-%
-%\begin{table}[t]
-%\begin{center}
-%\begin{tabular}{| l | c |}
-%%starting from #63
-%<data> &  VUR  \\
-%when and how much you exercise & 16.67\% \\
-%how much you use your phone & 15.79\% \\
-%your age & 14.29\% \\
-%how much you like the people you interact with & 13.79\% \\
-%when, what, and how much you ate & 12.50\% \\
-%which television shows you watch & 11.43\% \\
-%your gender & 9.52\% \\
-%your heart rate & 9.09\% \\
-%eye movement patterns (for eye tracking) & 6.98\% \\
-%the language you speak & 2.50\% \\
-%\end{tabular}
-%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
-%\label{notsharedbottom10}
-%\end{center}
-%\end{table}
-%
-%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive.
-When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home.
-When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations.
-When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.
-%
-%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning.
-When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns.
-When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible.
-When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience.
-However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.
-
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Question &  Wearable VUR & Smartphone VUR \\
- \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
+%!TEX root = ../paper.tex
 \subsubsection{Demographic Factors}
@@
 Finally, we observed no correlation between education level and VUR.
-
-\subsubsection{Regression Models} 
-\label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
-
-\begin{table}
-\centering
-\begin{tabular}{|l| r| r| r|}
-\hline
-Parameters & $\chi^2$ & $df$ & QIC\\
-\hline
-\hline
-(Intercept) & 255.0 & 1 & 18,477.5\\
-\hline
-(Intercept) & 78.4 & 1 & 18,122.9\\
-Device & 400.3 & 1 & \\
-\hline
-(Intercept) & 289.1 & 1 & 17,667.5\\
-IUIPC (covariate) & 368.5 & 1 & \\
-\hline
-(Intercept) & 297.8 & 1 &17,383.6\\
-Data Recipient & 913.4 & 4 & \\
-\hline
-(Intercept) & 374.6 & 1 & 14,794.5\\
-Data Type & 1,866.5 & 77 & \\
-\hline
-(Intercept) & 303. & 1 & 13,942.9\\
-Device & 11.1 & 1 &  \\
-Data Recipient & 624.6 & 3 & \\
-Data Type & 1,961.2 & 76 &  \\
-\hline
-(Intercept) & 28.4 & 1 & 12,752.8 \\
-Device  & 8.8 & 1 &  \\
-Data Recipient & 577.8 & 3 & \\
-Data Type & 1,752.1 & 76 & \\
-IUIPC (covariate) & 378.7 & 1 & \\
-\hline
-\end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
-The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
-\label{regression}
-\end{table}
-
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
-
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
-
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
-
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
-
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy} (see Table \ref{openresponses}).
-Other significant secondary concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such distractions causing car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
-
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|l|r|r|}
-\hline
-Concern &  Responses &  Frequency   \\
-\hline
-Privacy & 452 & 25.32\% \\
-Being Unaware & 275 & 15.40\% \\
-%Unaware Use & 167 & (9.36\%)\\
-%Unaware Collection & 64 & (3.59\%)\\
-%Unaware Access & 44 & (2.46\%)\\
-Health Risk & 191 & 10.70\%\\
-Safety & 185 & 10.42\%\\
-Social Impact &	157 & 8.80\%\\
-Financial Cost & 151 & 8.46\%\\
-Security &	144 & 8.07\%\\
-Accidental Sharing &	69 & 3.87\%\\
-Miscellaneous &	57 & 3.19\%\\
-None	& 51 & 2.86\%\\
-Social Stigma &	39 & 2.18\%\\
-False Information & 33 & 1.85\%\\
-Don't know & 31 & 1.74\%\\
-Aesthetics 	& 19 & 1.06\%\\
-Don't care 	& 11 & 0.62\%\\
-\hline
-\end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
-\label{openresponses}
-\end{center}
-\end{table}

### 2015-03-04 tex-inputs/abstract.tex
tweaked abstract and intro, cleaned up tables and added appendix sections

@@
 Along with great benefits, wearable devices, or ``wearables,'' bring new potential privacy and security risks which expose users' activities without their awareness or consent.
-With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture \cite{denning2014situ}, but human attention is a finite resource \cite{bohme2011security}.
-Therefore, user concerns should be investigated to to warn users only about situations they are likely to care about.
+With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture, but human attention is a finite resource.
+Therefore, user concerns should be investigated to warn users only about situations they are likely to care about.
 Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy.

### 2015-03-04 tex-inputs/intro.tex
tweaked abstract and intro, cleaned up tables and added appendix sections

@@
 Google Glass, the iconic wearable of its time, has since disappeared \cite{13_google_2015}.
-Most suspect that the reason for its disappearance was because it was the ``straw the broke the back of the privacy camel's back'' \cite{14_dvorak_2014}.
-Some Glass wearers faced assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014}, while bystanders felt uncomfortable personal details, conversations, and photos possibly recorded.
+Most suspect that the reason for its disappearance was because it was not a shift in interest, but public concern over privacy issues \cite{14_dvorak_2014}.
+Some Glass wearers faced assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} from uncomfortable bystanders.
 
@@
 With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture \cite{denning2014situ}, but human attention is a finite resource \cite{bohme2011security}.
-Therefore, user concerns should be investigated to to warn users only about situations they are likely to care about.
+Therefore, user concerns should be investigated to warn users only about situations they are likely to care about.
 Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy.
@@
 We observed that users make less distinction between sharing data with friends, co-workers, and the general public, comparatively to sharing with an application's servers.
-\item A taxonomy and report of users' self-reported top concerns for wearable devices. Privacy is by far the top concern, along with security, health risks, financial risk, and social impact. 
+\item A report and categorization of users' self-reported top concerns for wearable devices.
+We give an sense of what broad concerns users have, which can be used to guide research in unexplored use cases.
 \item Rankings of how data-collection capabilities of wearable devices compared to more familiar technologies.

### 2015-03-04 tex-inputs/riskbenefit.tex
tweaked abstract and intro, cleaned up tables and added appendix sections

@@
+%!TEX root = ../paper.tex
+
+\section{Risk and Benefit Perceptions of Wearables Capabilities}
+\label{sec:riskben-appendix}
+
 \begin{table}[t]
@@
 \small
-\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
-\\hline
-&\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
- \\hline
-Technology &  Median & Q1 & Q3 & Distribution &  Median& Q1 & Q3 & Distribution   \\ 
+\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
 \hline
-location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\
-speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\
-discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\
-smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\
-language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\
-laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\
-smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\
-google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\
-cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\
-gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\
-voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\
-voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\
-fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\
-age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\
-facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\
-email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\
-heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\
-discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\
-internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\
-facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk}  & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit}\\
-
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit}  \\
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk}& 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit}  \\
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Gender Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
+Age Detection & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
+Discreet Microphone & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
+Cubetastic & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
+Fitness Trackers & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
+Voice Based Emotion Detection & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
+Facial Detection & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
+Discreet Video Camera & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
+Google Glass & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
+Smartwatches & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit} \\ 
+Facial Recognition & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit} \\ 
+Speech To Text & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
+Voice Recognition & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
+Language Detection & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
+Heart Rate Detection & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
+Location Tracking & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
+Email & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
+Smartphones & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
+Laptops & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
+Internet & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit} \\ 
 \hline
@@
 \end{table}
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
+\hline
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
+Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
+Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
+Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
+Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
+Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
+Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
+Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
+Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
+Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
+Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
+Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
+Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
+Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
+Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
+Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
+Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
+Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
+Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
+Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
+\hline
+\end{tabular}
+\caption{The 10 most and least upsetting data types, across all recipients.}
+\label{top10}
+\end{center}
+\end{table}

### 2015-03-04 tex-inputs/results-techrank.tex
sprinkled things to talk about inline
made it so every tex input file can compile the paper
tables inline and citing them

--- 2015-02-25 results-techrank.tex
@@
+%!TEX root = ../paper.tex
+
 \subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
+%	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
+%	\label{fig:techplot}
+%\end{figure}
 
@@
 We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
+Figures ~\ref{risk, benefit} depicts participants' median ratings.
 We found that the calibration technologies were all rated as the most risky.
@@
 People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+
+{\color {red} talk about the distributions and variance of the particular technologies, referring to the table in the appendix}
 
@@
 We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
+\hline
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
+Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
+Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
+Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
+Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
+Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
+Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
+Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
+Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
+Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
+Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
+Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
+Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
+Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
+Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
+Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
+Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
+Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
+Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
+Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
+\hline
+\end{tabular}
+\caption{Risk rankings in response to the Fischoff-style prompt for various technologies and capabilities.Most technologies are capabilities with respect to wearable devices.
+Calibration technologies were electricity, guns, lawnmowers, and motorcycles.
+Wearable technologies included the Google Glass and the Cubetastic3000.
+Other specific technologies, such as internet, email, laptops, and smartphones, were also asked.}
+\label{risk}
+\end{center}
+\end{table}
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
+\hline
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Gender Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
+Age Detection & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
+Discreet Microphone & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
+Cubetastic & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
+Fitness Trackers & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
+Voice Based Emotion Detection & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
+Facial Detection & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
+Discreet Video Camera & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
+Google Glass & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
+Smartwatches & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit} \\ 
+Facial Recognition & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit} \\ 
+Speech To Text & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
+Voice Recognition & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
+Language Detection & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
+Heart Rate Detection & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
+Location Tracking & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
+Email & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
+Smartphones & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
+Laptops & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
+Internet & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit} \\ 
+\hline
+\end{tabular}
+\caption{Benefit rankings in response to the Fischoff-style prompt for various technologies and capabilities.
+Most technologies are capabilities with respect to wearable devices.
+Calibration technologies were electricity, guns, lawnmowers, and motorcycles.
+Wearable technologies included the Google Glass and the Cubetastic3000.
+Other specific technologies, such as internet, email, laptops, and smartphones, were also asked.
+}
+\label{benefit}
+\end{center}
+\end{table}

### 2015-03-04 tex-inputs/discussion.tex
paper cleanup
tweaks to discussion section

@@
+%!TEX root = ../paper.tex
+
 \section{Discussion}
@@
 Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}.
-{\color {red} Any economics or behavioral papers to support our claims and elaborate on this would be great here.
-Maybe ones on perception, estimation, etc.}
 
@@
 
-Privacy concerns asked out of context differ from how users may react to these same concerns in real life.
+Privacy concerns asked out of context differ from how users may react to these same concerns in real life \cite{norberg2007privacy, jensen2005privacy}.
 This is an unavoidable, yet important consideration of any study of this nature.

### 2015-03-04 tex-inputs/methodology.tex
Corrected numbers

@@
 The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless.
-An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.
+There were a total of 288 questions in this set, from which we randomly 6 questions for each participant.
 
@@
 We presented participants with a second set of scenarios to control for the type of device being used.
-These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
 We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
@@
 \end{packed_enum}
+
+So that we could perform controlled comparisons based on device type, we also included a version of each of these questions in the wearable scenarios section that substituted ``Cubetastic3000'' for ``smartphone.'' Thus, there were a total of 293 Cubetastic3000 scenarios, from which each participant was randomly assigned 6.
 
@@
 We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654).
+Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344).
 Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
@@
 Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%.
+For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,782 responses, with an initial agreement rate of 89.7\%.
 The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.

### 2015-03-04 tex-inputs/results-devices.tex
sprinkled things to talk about inline
initial progress on results:devices

@@
+%!TEX root = ../paper.tex
+
 \subsubsection{Device}
+{\color {red} intro to this section}
+
+The five questions were:
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item Q1: How would you feel if an app on your <device> vibrated your phone without asking you first?
+\item Q2: How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
+\item Q3: How would you feel if an app on your <device> un-muted a phone call without asking you first?
+\item Q4: How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
+\item Q5: How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
+\end{enumerate}
+
 Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
+Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.
+The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
+{\color {red} talk about the standard deviation of the devices in general--was there more spread for the answers wrt smartphones, cubetastic, or were they kind of all the same?} However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
 Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
 The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
+Too few instances of participants answering both versions of questions occurred (34 in total for all 5 questions) to perform a sound within-subjects analysis.
 
@@
 \hline
- Question &  Wearable VUR & Smartphone VUR \\
+ Question &  Wearable VUR, $\sigma$ & Smartphone VUR, $\sigma$ \\
  \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
+ All & 58.79\%, \# & 46.64\%, \# \\
+Q1 & 14.81\%,  \# &  6.13\%, \# \\
+Q2 & 44.11\%, \# &  19.85\%, \# \\
+Q3 & 87.09\%, \# &  58.44\%, \# \\
+Q4 & 52.77\%, \# & 55.74\%, \# \\
+Q5 & 86.49\%, \# &  91.82\%, \# \\ 
 \hline

### 2015-03-04 tex-inputs/results-devices.tex
Redid stats and table

--- 2015-02-25 tex-inputs/results-devices.tex
@@
-\subsubsection{Device}
-Participants had unique VURs for scenarios only differing in device.
-Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}.
-However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}).
-Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.
-The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions.
-Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.
+%!TEX root = ../paper.tex
 
@@
 \hline
- Question &  Wearable VUR & Smartphone VUR \\
+ Misbehavior &  Cubetastic3000 & Smartphone \\
  \hline
- All & 58.79\% & 46.64\%\\
-Q1 & 14.81\%  &  6.13\%\\
-Q2 & 44.11\%  &  19.85\%\\
-Q3 & 87.09\%  &  58.44\%\\
-Q4 & 52.77\%  & 55.74\%\\
-Q5 & 86.49\%  &  91.82\%\\ 
+ \hline
+ All & 58.79\% & 46.67\%\\
+ \hline
+Vibration & 14.81\%  &  6.14\%\\
+Bluetooth & 44.12\%  &  19.86\%\\
+Unmuted Call & 87.10\%  &  58.44\%\\
+Screenshot & 52.78\%  & 55.74\%\\
+Premium Calls/Texts & 86.49\%  &  91.94\%\\ 
 \hline
 \end{tabular}
-\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
+\caption{VURs for the five questions about device misbehaviors described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
 \label{deviceVUR}
@@
 
-\begin{table}%[h]
-\begin{center}
-\begin{tabular}{|c|r|r|r|r|}
-%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
-%All	2.814	0.1395	No		3589		0.001\\
-%Q1	2.500	0.1139	No		714		0.004\\
-%Q2	17.333	<0.0001	Yes		708		0.024\\
-%Q3	0.020	0.8886	No		699		0.000\\
-%Q4	1.426	0.2324	No		731		0.002\\
-%Q5	1.611		0.2043	No		710		0.002\\
-\hline
-Question & $\chi^2$ & p-value & n & $\phi$ \\
-\hline
-All & 2.202 & <0.1378 & 3,588 & 0.001\\
-Q1 & 2.500 & <0.1139 & 714 & 0.004\\
-Q2 & 17.333 & <0.0001 & 708 &  0.024\\
-Q3 & 0.020 & <0.8886 & 699 &  0.000\\
-Q4 & 1.413 & <0.2345 & 730& 0.002\\
-Q5 & 1.604 & <0.2054 & 709 & 0.002\\
-\hline
-\end{tabular}
-\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
-\label{betweendevice}
-\end{center}
-\end{table}
+\subsubsection{Device}
+Recall that each participant answered 2 questions drawn from a set of 5 regarding their reactions to smartphone misbehaviors.
+To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same 5 questions amongst the pool of 293 Cubetastic3000 scenarios, only modifying the device type.
+In this manner, while all 1,782 participants received 2 smartphone questions, there were 159 participants who received at least one of these questions in relation to the Cubetastic 3000.
+Across all participants, the VUR was 46.7\% (of 1,782) when describing smartphones, whereas the VUR increased to 58.8\% (of 159) when describing these same misbehaviors on the Cubetastic3000.
+The VURs for both devices for all 5 questions are in Table ~\ref{deviceVUR}.
+
+To preserve data independence, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
+We found this difference to be statistically significant ($108,664.0$, $p<0.0005$), however, the effect size was incredibly small ($r=0.08$).
+Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors.
+As a result, we can conclude that in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible.
+Similarly, the entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.
+
+%{\color {red} talk about the variance of the devices in general--was there more spread for the answers wrt smartphones, cubetastic, or were they kind of all the same?}
 

### 2015-03-04 tex-inputs/results-regression.tex
made it so every tex input file can compile the paper
More data files

@@
+%!TEX root = ../paper.tex
 \subsubsection{Regression Models} 
 \label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
+In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
 We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
@@
 
-We created several models using our three dependent variables as factors: device (smartphone vs.
-wearable), data recipient, and data type.
+We created several models using two independent variables as predictors: data recipient and data type.
+Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients.
 We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
+For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
 Thus, we opted to remove the other covariates from our analysis.
-Similarly, we observed no statistically significant interaction effects between any of these four variables, which is why we did not include them in our models.
+Similarly, we observed no statistically significant interaction effects between any of our predictors, which is why we did not include them in our models.
 
@@
 This suggests that participants' biases towards specific wearable devices or wearable devices in general had a minimal effect on their results, and that they were primarily focused on the data type captured and how it will be shared.
+Because the data types were categorical, we did not include the full model here, instead showing the parameter weights for each data type in Appendix \ref{regression}.

### 2015-03-04 tex-inputs/results-devices.tex
oops

@@
 
-To preserve data independence, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
+To ensure independence of observations, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
 We found this difference to be statistically significant ($108,664.0$, $p<0.0005$), however, the effect size was incredibly small ($r=0.08$).

### 2015-03-04 tex-inputs/methodology.tex
ergh

@@
 Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]
+We randomly presented each participant with 2 of these 5 questions:
 
-\begin{packed_enum}
-\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
-\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
-\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
-\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
-\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
-\end{packed_enum}
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item How would you feel if an app on your <device> vibrated your phone without asking you first?
+\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
+\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
+\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
+\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
+\end{enumerate}
 

### 2015-03-04 tex-inputs/results-type.tex
Added reference

@@
 \subsubsection{Data Type}
+\label{sec:datatypes}
+
 Based on our data, we observed that the largest effect stemmed from the data being shared.
@@
 This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results.
-Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}.
+Two researchers agreed on a codebook and independently coded each of the 72 data types.\footnote{We excluded the data types that did not feature a data recipient, the five misbehaviors used to examine device types.}
 

### 2015-03-05 tex-inputs/results-regression.tex
Fixed regression

@@
 %!TEX root = ../paper.tex
+
 \subsubsection{Regression Models} 
@@
 \hline
-(Intercept) & 254.5 & 1 & 18,699.82\\
+(Intercept) & 423.96 & 1 & 13,209.1\\
 \hline
-(Intercept) & 79.2 & 1 & 18,347.6\\
-Device & 391.0 & 1 & \\
+(Intercept) & 207.07 & 1 & 12,551.49\\
+IUIPC (covariate) & 368.5 & 1 & \\
+Gender (covariate) & 6.30 & 1 & \\
 \hline
-(Intercept) & 232.1 & 1 & 17.897.0\\
-IUIPC (covariate) & 368.5 & 1 & \\
+(Intercept) & 411.66 & 1 &12,458.86\\
+Data Recipient & 599.72 & 3 & \\
 \hline
-(Intercept) & 298.2 & 1 &17,606.5\\
-Data Recipient & 900.0 & 4 & \\
+(Intercept) & 418.02 & 1 & 11,382.75\\
+Data Type & 1,141.40 & 71 & \\
 \hline
-(Intercept) & 370.9 & 1 & 14,970.7\\
-Data Type & 1,898.4& 76 & \\
+(Intercept) & 66.18 & 1 & 9,609.65 \\
+Data Recipient & 617.25 & 3 & \\
+Data Type & 1,288.51 & 71 & \\
+IUIPC (covariate) & 105.73 & 1 & \\
+Gender (covariate) & 9.74 & 1 & \\
+IUIPC $\times$ Gender & 8.33 & 1 &\\
 \hline
-(Intercept) & 79.2 & 1 & 18,349.9\\
-Device & 391.0 & 1 & \\
 \hline
-(Intercept) & 29.2 & 1 & 14,114.8\\
-Device & 8.1 & 1 &  \\
-Data Recipient & 579.3 & 3 & \\
-Data Type & 1,765.4 & 76 &  \\
+(Intercept) & 442.66 & 1 & 12,727.42\\
+Risk & 405.18 & 4 & \\
 \hline
-(Intercept) & 298.0 & 1 & 12,931.6 \\
-Device  & 10.4 & 1 &  \\
-Data Recipient & 626.2 & 3 & \\
-Data Type & 1,997.5 & 76 & \\
-IUIPC (covariate) & 374.8 & 1 & \\
+(Intercept) & 380.39 & 1 & 12,681.86\\
+Medium & 439.45 & 5 & \\
+\hline
+(Intercept) & 256.15 & 1 & 12,061.87\\
+Risk & 157.84 & 4 & \\
+Medium & 183.90 & 5 & \\
+Risk $\times$ Medium & 259.81 & 8 & \\
+\hline
+(Intercept) & 62.65 & 1 & 10,406.35\\
+Risk & 205.21 & 4 & \\
+Medium & 250.35 & 5 & \\
+Recipient & 546.89 & 3 & \\
+IUIPC (covariate) & 103.94 & 1 & \\
+Gender (covariate) & 9.80 & 1 & \\
+IUIPC $\times$ Gender & 8.21 & 1 & \\
+Risk $\times$ Medium & 303.44 & 8 & \\
+Recipient $\times$ Risk & 39.14 & 12 & \\
 \hline
@@
 The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
-Each parameter listed was statistically significant at $p<0.0005$.}
+Each parameter listed was statistically significant at $p<0.005$.}
 \label{regression}
@@
 We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores.
+For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other.
 Thus, we opted to remove the other covariates from our analysis.
-Similarly, we observed no statistically significant interaction effects between any of our predictors, which is why we did not include them in our models.
 
 Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor.
-Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).
-This suggests that participants' biases towards specific wearable devices or wearable devices in general had a minimal effect on their results, and that they were primarily focused on the data type captured and how it will be shared.
-Because the data types were categorical, we did not include the full model here, instead showing the parameter weights for each data type in Appendix \ref{regression}.
+As can be seen, the data type was the strongest predictor of VUR.
+One shortcoming of this approach is its generalizability: the data type predictor is categorically and obviously limited to the data types that we specifically chose for this study.
+While we believe these were relatively comprehensive, we have no doubt that future devices will be able to make use of data that goes well beyond the 72 data types captured in our module.
+As a result of this, we created a second set of models in which we replaced the data type with the risk types and mediums that we described in Section \ref{sec:datatypes}.
+Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit.
+What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect.
+When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.

### 2015-03-05 tex-inputs/results-regression.tex
Added full regression model to Appendix

@@
 \hline
+\end{tabular}
+\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
+The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
+Each parameter listed was statistically significant at $p<0.005$.}
+\label{regression}
+\end{table}
+
+We created several models using two independent variables as predictors: data recipient and data type.
+Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients.
+We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
+For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other.
+Thus, we opted to remove the other covariates from our analysis.
+Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
+As can be seen, the data type was the strongest predictor of VUR.
+
+While these models clearly illustrate  the relative weight that users might place on various types of information when determining whether a given privacy violation is truly upsetting, one shortcoming of this approach is its generalizability: the data type predictor is categorical and obviously limited to the data types that we specifically chose for this study.
+That is, it is not entirely clear how these models might apply to data types not among the 72 that we directly examined.
+Therefore, in an attempt to make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the data type (e.g., video, audio, etc.) and in terms of the type of risk it might present to the user.
+Two researchers agreed on a codebook and independently coded each of the 72 data types.\footnote{We excluded the data types that did not feature a data recipient, the five misbehaviors used to examine device types.}
+
+The data types fell into the following six possible categories:
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item Photo
+\item Video
+\item Audio
+\item Behavioral Information
+\item Biometric Information
+\item Demographic Information
+\end{enumerate}
+
+While the first three categories are self-explanatory, the latter three categories are all based on different user characteristics.
+We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} is defined as measurements of the user's body; and {\it demographic information} is defined as non-biometric information about the user's traits.
+The associated risks for each data type fell into the following five categories:
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item {\bf Financial:} the loss of money or property.
+\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing).
+\item {\bf Medical:} the disclosure of medical information.
+\item {\bf Physical:} physical harm to the user.
+\item {\bf Relationships:} damage to the user's inter-personal relationships.
+\end{enumerate}
+
+After independently coding all data types with respect to these categories, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity.
+Prior to this resolution, there was  83\% agreement.
+Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|l| r| r| r|}
+\hline
+Parameters & $\chi^2$ & $df$ & QIC\\
+\hline
 \hline
@@
 (Intercept) & 380.39 & 1 & 12,681.86\\
-Medium & 439.45 & 5 & \\
+Capture & 439.45 & 5 & \\
 \hline
@@
 \end{tabular}
-\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
+\caption{Goodness-of-fit metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures.
 The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
 Each parameter listed was statistically significant at $p<0.005$.}
-\label{regression}
+\label{regression2}
 \end{table}
 
-We created several models using two independent variables as predictors: data recipient and data type.
-Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other.
-Thus, we opted to remove the other covariates from our analysis.
-
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
-As can be seen, the data type was the strongest predictor of VUR.
-One shortcoming of this approach is its generalizability: the data type predictor is categorically and obviously limited to the data types that we specifically chose for this study.
-While we believe these were relatively comprehensive, we have no doubt that future devices will be able to make use of data that goes well beyond the 72 data types captured in our module.
-As a result of this, we created a second set of models in which we replaced the data type with the risk types and mediums that we described in Section \ref{sec:datatypes}.
+Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models.
 Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit.

### 2015-03-05 tex-inputs/results-type.tex
Added full regression model to Appendix

@@
 
-The data types examined span several existing and future use cases.
-We do not believe they are comprehensive in coverage of how wearable devices might capture data nor for all possible future use cases of the data.
-Therefore, we coded each data type in two ways: firstly in terms in the data and how it was captured (e.g., video, audio, text, etc.), and  secondly in terms of the type of risks presented to the user.
-This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results.
-Two researchers agreed on a codebook and independently coded each of the 72 data types.\footnote{We excluded the data types that did not feature a data recipient, the five misbehaviors used to examine device types.}
-
-The data fell into the following six possible categories:
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item Photo
-\item Video
-\item Audio
-\item Behavioral Information
-\item Biometric Information
-\item Demographic Information
-\end{enumerate}
-
-The associated risks fell into the following five categories:
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item {\bf Financial:} The risk involves the loss of money or property.
-\item {\bf Image:} The risk involves loss of control over one's self-image (e.g., publicizing something embarrassing).
-\item {\bf Medical:} The risk involves disclosure of medical information.
-\item {\bf Physical:} The risk involves physical harm to the user.
-\item {\bf Relationships:} The risk involves damage to the user's inter-personal relationships.
-\end{enumerate}
-
-After independently coding all data types with respect to these categories, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity.
-Prior to this resolution, there was  83\% agreement.
-Cohen's $\kappa$ is 0.81 for the data capture and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
-
 %A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.

### 2015-03-05 tex-inputs/results-techrank.tex
finished up rewording techranks

@@
 To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figures ~\ref{risk, benefit} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
+We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies.
+Figures ~\ref{risk, benefit} depicts participants' median, quartiles, and distributions of risks and benefit ratings.
+We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.
 
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+As a group, participants rated more familiar technologies as the more beneficial.
+We believe this is the result of exposure people have to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
+It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
+Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others.
+However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
 
-{\color {red} talk about the distributions and variance of the particular technologies, referring to the table in the appendix}
+Of the wearable technologies, privacy-invasive ones were perceived to be risky.
+Top risky technologies include facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal,  equivalent risk levels (i.e., a median of ``10'').
+The differences in risk that found between the different wearable-related technologies, are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.
+Interestingly, privacy risks and are comparative to real physical risks; for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
 
-{\color {red} people may have evaluated the risks only thinking of physical risk, not privacy risk.
-This might have happened because among the 5 presented options, the wearable-related one is the odd one out; all other options involve some physical risk scenario.
-These other options, by being the most prominent (4 versus 1), frame the risk perception in the user's mind as meaning "physical risk", and users may consequently ignore or downplay privacy risks.
-It would have been better to ask 4+4  questions (or 2+2 to keep the survey short) rather than the current 4+1.
-AND "with the exception of electricity, the calibration technologies were seen as lower benefit than the others".
-This is true for some, but not all of the others.
-Specifically, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
-AND The differences in risk that *are* found between the different wearable-related are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.}
-
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
-
-\begin{table}[t]
+\begin{table}[h!!!!]
 \begin{center}
@@
 
-\begin{table}[t]
+\begin{table}[h!!!!!]
 \begin{center}
@@
 \end{table}
+
+People prompted to rate with respect to all considerations (see ~\ref{sec:prompt}), including physical harm risk to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life, people may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
+Among the 5 presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk to the users.
+
+These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
+However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
+We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
+We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).

### 2015-03-05 tex-inputs/appendixes.tex
cleanup
sprinkled things to talk about inline
made it so every tex input file can compile the paper
Added full regression model to Appendix
Added more models to appendices

--- 2015-02-20 appendixes.tex
@@
+%!TEX root = ../paper.tex
 \appendix
+
 \section{Fischhoff Prompts}
@@
 
-%\section{Risk and Benefit Rankings}
-%\label{sec:techrank}
-%
-%BENEFIT: 
-%
-%technology 	median	25\%		75\% \\
-%electricity	87	50	100\\
-%internet	65	45	100\\
-%laptops	60	40	80\\
-%email	50	30	75\\
-%smartphones	50	32.5	75\\
-%location tracking	40	20	67.5\\
-%heart rate detection	40	28	62.5\\
-%language detection	35	15	60\\
-%voice recognition	25	15	40\\
-%speech to text	25	15	36.25\\
-%lawnmowers	24	15	40\\
-%facial recognition	22	13	40\\
-%guns	20	10	30\\
-%motrocycles	20	12	40\\
-%voice based emotion detection	20	10	30\\
-%facial detection	20	10	32\\
-%discrete camera	20	15	30\\
-%smartwatches	20	10	32.5\\
-%google glass	20	12	40\\
-%fitness trackers	19	10	30\\
-%cubetastic	18	10	30\\
-%discrete microphone	15	10	20\\
-%age detection	12	10	21\\
-%gender detection	10	10	15
-%
-%RISK: 
-%
-%technology 	median	25\%		75\%\\
-%guns	60	40	80\\
-%motrocycles	45	27	70\\
-%electricity	25	15	40\\
-%lawnmowers	20	12	30\\
-%facial recognition	17	12.5	30\\
-%internet	15	10	30\\
-%discrete camera	12	10	30\\
-%location tracking	10	10	20\\
-%age detection	10	10	15\\
-%gender detection	10	10	12\\
-%language detection	10	10	10\\
-%voice based emotion detection	10	10	15\\
-%facial detection	10	10	25\\
-%voice recognition	10	10	15\\
-%heart rate detection	10	10	10\\
-%email	10	10	16\\
-%speech to text	10	10	10\\
-%discrete microphone	10	10	20\\
-%smartphones	10	10	19\\
-%laptops	10	10	15\\
-%fitness trackers	10	10	10\\
-%smartwatches	10	10	10\\
-%google glass	10	10	20\\
-%cubetastic	10	10	30
-
 \section{Coding Label Definitions}
@@
 Don't care: `` do not care,'' nonchalant answers
+
+\onecolumn
+\section{Full Regression Model from Data Types}
+\label{sec:regression}
+%\begin{figure*}[t]
+\includegraphics[page=1,scale=0.8]{images/full-model.pdf}
+\includepdf[pages=2-3,scale=0.8]{images/full-model.pdf}
+
+%\caption{Full regression model, which includes all 72 data types, recipients, and covariates.}
+%\end{figure*}
+
+\section{Full Regression Model from Data Risks / Data Categories}
+\label{sec:regression}
+%\begin{figure*}[t]
+\includegraphics[page=1,scale=0.8]{images/full-model2.pdf}
+\includepdf[pages=2,scale=0.8]{images/full-model2.pdf}
+
+\twocolumn

### 2015-03-05 tex-inputs/results-regression.tex
Added more models to appendices

@@
 As can be seen, the data type was the strongest predictor of VUR.
+The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression}.
 
@@
 (Intercept) & 380.39 & 1 & 12,681.86\\
-Capture & 439.45 & 5 & \\
+Data Category & 439.45 & 5 & \\
 \hline
@@
 Risk & 157.84 & 4 & \\
-Medium & 183.90 & 5 & \\
-Risk $\times$ Medium & 259.81 & 8 & \\
+Data Category & 183.90 & 5 & \\
+Risk $\times$ Data Category & 259.81 & 8 & \\
 \hline
@@
 Risk & 205.21 & 4 & \\
-Medium & 250.35 & 5 & \\
+Data Category & 250.35 & 5 & \\
 Recipient & 546.89 & 3 & \\
@@
 IUIPC $\times$ Gender & 8.21 & 1 & \\
-Risk $\times$ Medium & 303.44 & 8 & \\
+Risk $\times$ Data Category & 303.44 & 8 & \\
 Recipient $\times$ Risk & 39.14 & 12 & \\

### 2015-03-05 tex-inputs/results-regression.tex
Added coding descriptions

@@
 Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+Applying this taxonomy to our collected data, we observed that average VURs were highest for financial risks (82.0\%) and lowest for medical data risks (47.4\%).
+In the middle were relationships (69.2\%), physical (66.4\%), and self-image (65.8\%) risks.
+One reason why medical risks were ranked relatively low is that this may be a misnomer: in addition to covering scenarios involving data about the user's health, it also covered basic demographics, such as age, gender, and emotional state.
+Similar to what we observed in Section \ref{sec:datatypes}, participants likely understood that many of these data types are publicly observable, which is why they were less concerned.
+
+With regard to the VURs of the broad categories of data that we coded, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%).
+Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data.
+In this case, we suspect that demographic data was more concerning than we expected because it included information that could be used to perpetuate fraud or identity theft, such as a Social Security Number, bank account information, and other financial information.
+We were very surprised that biometric information was seen as relatively benign (at least as compared to the other broad categories of data).
+One hypothesis is that since most home users do not use biometric authentication, they may have a poorer understanding of the types of systems that might be at risk if biometric data were to be stolen and then abused.
 
@@
 When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.
+The full model can be found in Appendix \ref{sec:regression2}.

### 2015-03-05 tex-inputs/results-demographics.tex
finished up rewording techranks
added in discussion of demographics in demographics section

@@
 Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$).
-Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
+We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggests that people's responses to questions were mostly based on their privacy preferences.
+Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
 We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
@@
 While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender.
-Finally, we observed no correlation between education level and VUR.
+60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$).
+The effect of a participant's gender also did not remain significant upon correcting for multiple testing.
+We observed no correlation between a participant's education level and VUR.

### 2015-03-05 tex-inputs/results-openended.tex
made it so every tex input file can compile the paper
reworded things in open-ended section

--- 2015-02-25 results-openended.tex
@@
+%!TEX root = ../paper.tex
 \subsection{Self-Reported Concerns for Wearables}
@@
 The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-\\
 
-Without a doubt, the most common self-reported concern of wearables for the average user is the \textit{possible loss of privacy} (see Table \ref{openresponses}).
-Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
+ Table \ref{openresponses} shows the most common user concerns related to wearable devices.
+Appendix \ref{sec:coding} details the responses categorized in each coding label.
+Most of these concerns are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users.
+This can be used to guide research in unexplored use cases.
+
+In addition to privacy in a general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
 

### 2015-03-05 tex-inputs/results-recipient.tex
initial progress on results:devices
reworded things in open-ended section

@@
 \subsubsection{Data Recipient}
-Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher.
-A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}).
+Across all scenarios, 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).
+A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}).
 However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
@@
 \caption{The overall upset rate for all recipients.}
-\label{recipient-table}
+\label{recipient-vur}
+\end{center}
+\end{table}
+
+\begin{table}[t]
+\begin{center}
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
+\hline
+Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
+Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
+Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
+Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
+Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
+Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
+\hline
+\end{tabular}
+\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
+\label{recipient-chi}
 \end{center}

### 2015-03-05 tex-inputs/results-recipient.tex
results recipient done

@@
 \subsubsection{Data Recipient}
-Across all scenarios, 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).
+There was a statistically significant difference in VUR for an application's servers comparatively to human data recipients.
+42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).
 A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}).
@@
 But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Similarly, we are unaware of a more appropriate test, given our data format; Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
+Similarly, we are unaware of a more appropriate test, given our data format.
+Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
 Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation.
-Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.
+Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.
 
-{\color {red} We do not claim that there is no distinction between the friends, public, and work contact recipients, because people have been shown to behave differently, especially in the social arena (cite studies here).
-People are more comfortable sharing certain data types with certain recipients (refer to the table of all questions with ranks by each recipient here).
-There are other data types which are universally concerning, and universally unconcerning, and the magnitude of the sentiment varies by recipient.
-As you can see in Table (J still needs to do this table), the VUR rate for each recipient is negatively correlated with the standard deviation of the answers.
-Additionally, we see that there is greater distinction between sharing people and the app server--people are comfortable sharing data they would feel uncomfortable sharing with at human recipient, and the magnitude of concerns is might more significant compared to the other recipients.}
+We do not claim that there are no distinctions between the friends, public, and work contact recipients.
+People are more comfortable sharing certain data types with certain human data recipients.
+For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.
+Participants were much more comfortable sharing phone use and products purchased with an application server than with human recipients.
+Appendix \ref{sec:recipient-appendix} shows the  complete VUR and rankings of all data types by recipient.
+
+%People have been shown to behave differently, especially in the social arena \cite{dwyer2007trust, gross2005information, fogel2009internet}.
 
@@
 \end{table}
-
-{\color {red} TODO: table of top and bottom 10 data types by recipient; refer to appendix; shoutout to when you were lying nervous or stressed work}

### 2015-03-05 tex-inputs/results-techrank.tex
results recipient done

--- 2015-02-25 results-techrank.tex
@@
+%!TEX root = ../paper.tex
+
 \subsection{Risk and Benefit Rankings} 
@@
 To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated familiar technologies and those related to wearables as being low-risk.
-Figure~\ref{fig:techplot} depicts participants' median ratings.
-We found that the calibration technologies were all rated as the most risky.
-At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.
+We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}).
+Appendix ~\ref{sec:riskben-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
+We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.
 
-As a group, participants rated the familiar technologies as the most beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily.
-Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10'').
-People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+As a group, participants rated more familiar technologies as the more beneficial.
+We believe this is the result of exposure people have to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
+It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
+Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others.
+However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
 
-{\color {red} people may have evaluated the risks only thinking of physical risk, not privacy risk.
-This might have happened because among the 5 presented options, the wearable-related one is the odd one out; all other options involve some physical risk scenario.
-These other options, by being the most prominent (4 versus 1), frame the risk perception in the user's mind as meaning "physical risk", and users may consequently ignore or downplay privacy risks.
-It would have been better to ask 4+4  questions (or 2+2 to keep the survey short) rather than the current 4+1.
-AND "with the exception of electricity, the calibration technologies were seen as lower benefit than the others".
-This is true for some, but not all of the others.
-Specifically, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
-AND The differences in risk that *are* found between the different wearable-related are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.}
+Of the wearable technologies, privacy-invasive ones were perceived to be risky.
+Top risky technologies include facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal,  equivalent risk levels (i.e., a median of ``10'').
+The differences in risk that found between the different wearable-related technologies, are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.
+Interestingly, privacy risks and are comparative to real physical risks; for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+
+People prompted to rate with respect to all considerations (see ~\ref{sec:prompt}), including physical harm risk to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life, people may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
+Among the 5 presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk to the users.
 

### 2015-03-05 tex-inputs/riskben.tex
results recipient done

--- 2015-03-04 tex-inputs/riskbenefit.tex
@@
 
-\section{Risk and Benefit Perceptions of Wearables Capabilities}
+\section{Risk Benefit Assessments of Various Technologies}
 \label{sec:riskben-appendix}
 
-\begin{table}[t]
+\begin{table}[h!!!!]
+\begin{center}
+\small
+\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
+\hline
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
+Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
+Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
+Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
+Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
+Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
+Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
+Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
+Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
+Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
+Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
+Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
+Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
+Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
+Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
+Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
+Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
+Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
+Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
+Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
+\hline
+\end{tabular}
+\caption{Risk rankings in response to the Fischoff-style prompt for various technologies and capabilities.Most technologies are capabilities with respect to wearable devices.
+Calibration technologies were electricity, guns, lawnmowers, and motorcycles.
+Wearable technologies included the Google Glass and the Cubetastic3000.
+Other specific technologies, such as internet, email, laptops, and smartphones, were also asked.}
+\label{risk}
+\end{center}
+\end{table}
+
+\begin{table}[h!!!!!]
 \begin{center}
@@
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
+\caption{Benefit rankings in response to the Fischoff-style prompt for various technologies and capabilities.
+Most technologies are capabilities with respect to wearable devices.
+Calibration technologies were electricity, guns, lawnmowers, and motorcycles.
+Wearable technologies included the Google Glass and the Cubetastic3000.
+Other specific technologies, such as internet, email, laptops, and smartphones, were also asked.
+}
+\label{benefit}
 \end{center}
 \end{table}
-
-\begin{table}[t]
-\begin{center}
-\small
-\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
-\hline
-Technology & Q1 &  Median & Q3 & Distribution  \\ 
-\hline
-Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
-Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
-Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
-Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
-Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
-Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
-Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
-Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
-Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
-Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
-Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
-Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
-Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
-Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
-Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
-Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
-Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
-Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
-Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
-Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
-\hline
-\end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
-\end{center}
-\end{table}

### 2015-03-05 tex-inputs/conclusion.tex
fixed little compiling bugs
rough draft done

--- 2015-02-24 untitled folder 2/wearables-survey-paper-master/conclusion.tex
@@
+%!TEX root = ../paper.tex
+
 \section{Conclusion}
 
-We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices.
-We examine how upset participants would in  304 scenarios, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns.
-We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model.
-An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology.
-We also state what users perceived as the most significant concerns with respect to wearable devices.
-We conclude by discussing future research directions in the wearables and user study space.
+Our 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices.
+We identify that participants are most concerned about protecting their financial information, photos, and videos and least concerned about demographic or biometric data.
+We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients, and also that certain data is more comfortably shared with certain recipients.
+Participants' self-reported concerns of categories and perceptions of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions.
+We perform two regression model analyses with respect to the type of data and the associated risks.
 

### 2015-03-05 tex-inputs/results-regression.tex
Fix multiply defined labels

@@
 As can be seen, the data type was the strongest predictor of VUR.
-The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression}.
+The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.
 
@@
 When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.
-The full model can be found in Appendix \ref{sec:regression2}.
+The full model can be found in Appendix \ref{sec:regression-apx2}.

### 2015-03-05 tex-inputs/abstract.tex
Major editing of abstract.

@@
 \begin{abstract}
-Along with great benefits, wearable devices, or ``wearables,'' bring new potential privacy and security risks which expose users' activities without their awareness or consent.
-With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture, but human attention is a finite resource.
-Therefore, user concerns should be investigated to warn users only about situations they are likely to care about.
-Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy.
-To this end, we conducted the first large-scale study to investigate user security and privacy concerns for wearable devices.
-We surveyed 1,784 Internet users for their perceptions of wearable devices and contribute: relevant perceived risks for wearables, effects of data type and data recipient on perceived risk, users' self reported concerns, and an assessment of how wearable device capabilities compare to familiar technologies.
-We conclude with a discussion on future research directions for wearable devices.
+Wearable devices bring great benefits but also new potential privacy and security risks that could expose users' activities without their awareness or consent.
+Effective design of notifications and security controls for wearable devices will require careful attention to prevent habituation and treat user as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
+In this paper, we conduct a large-scale survey to investigate user security and privacy concerns regarding wearable devices.
+We surveyed 1,784 Internet users for their perceptions of wearable devices and identify risks that are particularly concerning to users, measure the effect of data type and data recipient on perceived risk, study users' self-reported concerns, and compare wearable device risks to those of more familiar technologies.
+We hope that this work will inform design of future privacy and security controls for wearable devices.
 \end{abstract}

### 2015-03-05 tex-inputs/intro.tex
Some editing to intro, trimming down sentences and making it a little less pompous/formal

@@
 
-Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} of electronically enhanced clothing items and accessories that interweaves technological interaction with everyday life.
-A top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
-With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are transforming ubiquitous computing into a part of every day life.
-Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''
+Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
+With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
 
-The constantly captured data from these devices has many benefits, ranging from a more natural, human-centered interface experience to a healthier, fitness-data inspired lifestyle.
-There will likely be many more applications in the future which take advantage of such data.
-It is clear why wearable devices are becoming even more popular, especially as they have more capabilities and benefits over traditional devices.
+% Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''
 
-Along with these benefits, wearable devices bring new potential privacy and security risks which expose users' activities without their awareness or consent.
-Fitbit allowed sex to be tracked as exercise while fitness profiles were public by default~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Public discomfort toward facial recognition prevented the capability from being deployed to Google Glass \cite{GlassDetection}.
-Google Glass, the iconic wearable of its time, has since disappeared \cite{13_google_2015}.
-Most suspect that the reason for its disappearance was because it was not a shift in interest, but public concern over privacy issues \cite{14_dvorak_2014}.
-Some Glass wearers faced assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} from uncomfortable bystanders.
+Wearable devices offer many compelling opportunities for benefiting users.
+For instance, they could enable a more natural, human-centered interface experience and a healthier, fitness-data inspired lifestyle.
+There will likely be many more applications in the future which take advantage of data captured by wearable devices.
 
-We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture with respect to smartphones.
-Mobile platforms have tried to address this by communicating data capture to users as the data is captured.
+However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
+Even though wearable technology is currently in early stages, we have already seen instances of these risks.
+For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's withdrawal of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.
+
+We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture on smartphones.
+Mobile platforms have tried to address the risks by communicating data capture to users as the data is captured.
 However, many users are habituated to these notifications, because they see them all the time, often for things that they don't care about \cite{felt2012android}.

### 2015-03-06 tex-inputs/intro.tex
Edit contributions in intro

@@
 
-With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture \cite{denning2014situ}, but human attention is a finite resource \cite{bohme2011security}.
-Therefore, user concerns should be investigated to warn users only about situations they are likely to care about.
-Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy.
+With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data is captured \cite{denning2014situ}.
+However, human attention is a finite resource \cite{bohme2011security}, and bombarding users with notifications is likely to be counter-productive as it can lead to user frustration and habituation.
+Therefore, user concerns need to be investigated so that systems can warn users only about situations they are likely to care about.
 
-The goal of this paper is to gain a better sense of user concerns for wearables.
+The goal of this paper is to gain a better sense of user concerns about wearables.
 To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
-We surveyed 1,784 Internet users for their perceptions of wearable devices and contribute the following: \\[-0.8cm]
+We surveyed 1,784 Internet users about their perceptions of wearable devices and contribute the following: \\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item Comparisons of users' perceptions of a range of privacy and security risks of wearables. We found that users care much more about the type of data than the recipient of the data.
-\item Insight into how users feel about various data recipients.
-We observed that users make less distinction between sharing data with friends, co-workers, and the general public, comparatively to sharing with an application's servers.
-\item A report and categorization of users' self-reported top concerns for wearable devices.
-We give an sense of what broad concerns users have, which can be used to guide research in unexplored use cases.
-\item Rankings of how data-collection capabilities of wearable devices compared to more familiar technologies.
-Most saw new capabilities as benign, but we suspect that this may be due to a lack of exposure to these newer technologies.
+\item We compare users' perceptions of a range of privacy and security risks of wearables. We found that user concern is driven more by the type of data being captured than the recipient of the data.
+\item Our results shed light into how users feel about various data recipients.
+We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers.
+\item We analyze users' self-reported top concerns regarding wearable devices.
+The results give an sense of what broad concerns users have, which can be used to guide future research in unexplored use cases.
+\item We examine how serious users perceive the risks of wearables to be, compared to risks associated with more familiar technologies.
+Most of our participants saw wearables' new capabilities as benign, though we suspect that this could be due to a lack of exposure to these newer technologies.
 \end{itemize}

### 2015-03-06 tex-inputs/methodology.tex
Capitalize proper nouns (names of products)

@@
 To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study.
-At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}.
-These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.
+At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the Pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and Google Glass \cite{11_wikipedia_2015, 12_turi_2014}.
+We used these wearable devices, along with other comparable wearable devices on the market, as inspiration for the survey questions.
 

### 2015-03-06 tex-inputs/methodology.tex
Some editing of methodology

@@
 At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the Pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and Google Glass \cite{11_wikipedia_2015, 12_turi_2014}.
-We used these wearable devices, along with other comparable wearable devices on the market, as inspiration for the survey questions.
+We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.
 
+We then designed a survey to gauge how severe our participants consider these risks to be.
 Our survey contained two main sections.
@@
 This was intended to elicit their perception of the severity and impact of the risk.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
-Our survey design is based on two prior perception studies, as we describe next.
+The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices.
+In the other section, we asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
 %Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
@@
 Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action had occurred without permission.
+Participants were asked how upset they would be if a certain action occurred without their permission.
 Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.
+Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.
 
 \subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for those technologies.
+Fischhoff \etal performed a seminal study of the perceived risks of 30 widely used technologies~\cite{Fischhoff}.
+In their study, participants were asked to separately rate the risks and benefits for these technologies.
 They were told to think about all people affected by the technology, and to think about long-term vs.
@@
 Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.
+We apply their methodology to evaluate the perceived risks and benefits of several technologies related to wearable computing.
 %Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item 2 comprehension questions
+\item 2 reading comprehension questions
 \item 6 questions about wearable computing scenarios 
 \item 2 questions about smartphone scenarios 
-\item 2 risk/benefit questions 
+\item 2 Fischhoff-style risk/benefit questions 
 \item 15 demographic questions \\[-.8cm]
@@
 
-\subsubsection{Wearables Scenarios}
-We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}.
-Our questions were of the format:
+\subsubsection{Wearable Scenarios}
+We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first (see Figure \ref{fig:prompt}).
+Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
+Questions were of the form:
 
@@
 	\centering
-	\includegraphics[width=0.47\textwidth]{images/prompt.pdf}
+	\includegraphics[width=\columnwidth]{images/prompt.pdf}
 	\caption{An example of a wearable scenario question participants saw while taking the survey.}
@@
 
-The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared.
-There were a total of 288 questions in this set, from which we randomly 6 questions for each participant.
+The purpose of these questions was to determine how upset participants would be when data is inappropriately shared, and to understand how their reaction depends upon the type and recipient of the data that is shared.
+There were a total of 288 questions in this set, from which we randomly selected 6 questions for each participant.
 

### 2015-03-06 tex-inputs/methodology.tex
Small changes to methodology

@@
 The purpose of these questions was to determine how upset participants would be when data is inappropriately shared, and to understand how their reaction depends upon the type and recipient of the data that is shared.
-There were a total of 288 questions in this set, from which we randomly selected 6 questions for each participant.
+There were a total of 288 questions in this set.
 
@@
 We randomly presented each participant with 2 of these 5 questions:
-
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.
+We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
+These technologies were chosen to span varying levels of risks and benefits.
 
@@
 \subsubsection{Additional Questions}
-The exit portion of the survey firstly consisted of questions asking for age, gender, and education.
+The exit portion of the survey contained demographic questions asking for age, gender, and education.
 Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
+We ended with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
 
@@
 We recruited all of our focus group participants from Craigslist.
-Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).
+Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 ($\mu = 36.1$, $\sigma = 15.3$).
 Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
@@
 \subsection{Recruitment and Analysis Method}
-We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk.
+We recruited 2,250 participants over August 7--13, 2014 via Amazon's Mechanical Turk.
 We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.

### 2015-03-06 tex-inputs/methodology.tex
Capitalize Internet consistently

@@
 
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.
+Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
+We asked about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
 

### 2015-03-06 tex-inputs/abstract.tex
Edited to clean up language

@@
 \begin{abstract}
-Wearable devices bring great benefits but also new potential privacy and security risks that could expose users' activities without their awareness or consent.
-Effective design of notifications and security controls for wearable devices will require careful attention to prevent habituation and treat user as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
-In this paper, we conduct a large-scale survey to investigate user security and privacy concerns regarding wearable devices.
-We surveyed 1,784 Internet users for their perceptions of wearable devices and identify risks that are particularly concerning to users, measure the effect of data type and data recipient on perceived risk, study users' self-reported concerns, and compare wearable device risks to those of more familiar technologies.
-We hope that this work will inform design of future privacy and security controls for wearable devices.
+Wearable devices bring great benefits through their omnipresence and ability to capture new types of data.
+But they also create new privacy and security risks by potentially exposing users' activities without their awareness or consent.
+Effective design of notifications and security controls for wearable devices will require careful foresight to prevent habituation by treating user attention as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
+In this paper, we describe a large-scale survey that we conducted to investigate user security and privacy concerns regarding wearable devices.
+We surveyed 1,782 Internet users about their perceptions of wearable devices, in order to identify risks that are particularly concerning to users.
+We specifically controlled for the effects of data type and data recipient on the magnitude of perceived risks, while also collecting open-ended concerns.
+Finally, we compared wearable device risks to those of more familiar technologies.
+Our goal is for this work to inform the design of future privacy and security controls for wearable devices.
 \end{abstract}
@@
 % A category with the (minimum) three required fields
-\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
+%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
 

### 2015-03-06 tex-inputs/intro.tex
Tidied up intro, made habituation pieces a bit clearer

@@
 
-Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.
+Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
 With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
@@
 For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's withdrawal of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.
 
@@
 Mobile platforms have tried to address the risks by communicating data capture to users as the data is captured.
-However, many users are habituated to these notifications, because they see them all the time, often for things that they don't care about \cite{felt2012android}.
+However, many users are habituated to these notifications, because they see them all the time, often for things that they do not care about \cite{felt2012android}.
+Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.
 
 With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data is captured \cite{denning2014situ}.
-However, human attention is a finite resource \cite{bohme2011security}, and bombarding users with notifications is likely to be counter-productive as it can lead to user frustration and habituation.
-Therefore, user concerns need to be investigated so that systems can warn users only about situations they are likely to care about.
+However, the possible data types that these devices will be able to capture is likely to dwarf those currently captured by smartphones.
+Because human attention is a finite resource \cite{bohme2011security}, bombarding users with notifications for every conceivable data capture is likely to be counter-productive as it can lead to user frustration and habituation.
+Therefore, user concerns need to be investigated so that systems can warn users only about the situations they are likely to care about.
 
-The goal of this paper is to gain a better sense of user concerns about wearables.
+The goal of this paper is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications.
 To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
-We surveyed 1,784 Internet users about their perceptions of wearable devices and contribute the following: \\[-0.8cm]
+We surveyed 1,782 Internet users about their perceptions of wearable devices and contribute the following: %\\[-0.8cm]
 

### 2015-03-06 tex-inputs/methodology.tex
Modified Methodology, added more detail, fixed some errors

@@
 To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study.
-At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the Pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and Google Glass \cite{11_wikipedia_2015, 12_turi_2014}.
+At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns~\cite{6_fitbit_2014, 7_time_2014}; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}; and Google Glass~\cite{11_wikipedia_2015, 12_turi_2014}.
 We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.
 
-We then designed a survey to gauge how severe our participants consider these risks to be.
+We designed a survey to gauge how severe our participants consider these risks to be.
 Our survey contained two main sections.
@@
 This was intended to elicit their perception of the severity and impact of the risk.
-The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices.
+The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}.
 In the other section, we asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
@@
 \subsection{Motivation}
+In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of more general technology-based risk perceptions~\cite{Fischhoff}.
+
 \subsubsection{Smartphone Risk Scenarios}
@@
 
-\subsubsection{Technology Risk Perception}
-Fischhoff \etal performed a seminal study of the perceived risks of 30 widely used technologies~\cite{Fischhoff}.
+\subsubsection{Technology Risk Perceptions}
+Fischhoff \etal performed a seminal study of the perceived risks surrounding 30 widely used technologies~\cite{Fischhoff}.
 In their study, participants were asked to separately rate the risks and benefits for these technologies.
-They were told to think about all people affected by the technology, and to think about long-term vs.
-short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate the perceived risks and benefits of several technologies related to wearable computing.
+They told participants to think about all people affected by the technology, and to think about long-term versus short-term risks and benefits.
+Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10).
+We apply their methodology to evaluate the perceived risks and benefits of several technologies related to wearable computing and how these technologies compared to more familiar technologies.
 %Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
@@
 Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.
+We highlighted the capabilities of this device and described use cases:
+
+\begin{quotation}
+{\it Imagine that you are the proud owner of the Cubetastic3000, a new, high-tech computing device designed to be worn on your head.
+Imagine also that you wear this device all the time, because it is very lightweight, durable, and convenient.
+
+The Cubetastic3000 has the capability to capture video, photos, audio, and biometrics (biological data about you, such as heart rate).
+Just like other devices today, you can install third-party applications from an app store, and these applications can use the information that the Cubetastic3000 captures.
+
+With a wide range of applications and capabilities, your device can do all sorts of things, such as:\\
+
+\noindent---measuring heart rate, breathing, and other things to keep track of your fitness level and overall health\\
+
+\noindent---look at what you see to provide information about what's around you\\
+
+\noindent---allow you to take notes just by telling the device what you need to remember\\
+
+\noindent---take videos of you or what you see to share with others\\
+
+\noindent---automatically take photos or video so that you can replay events that previously happened\\
+
+\noindent---play music that you like for you when it detects that no one is around\\
+
+\noindent---infer information about you so you don't need to log in or search for the same thing over and over\\
+
+\noindent ...and much more!}
+\end{quotation}
+
+To ensure that participants had read and understood this device's capabilities, since it would form the basis for many of our survey questions, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn.
+We filtered out those who could not answer these questions.
 
 \subsubsection{Wearable Scenarios}
-We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first (see Figure \ref{fig:prompt}).
-Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
+We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
+Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
 Questions were of the form:
 
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.
+\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}
 
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]
+We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): \\[-.8cm]
 
@@
 The purpose of these questions was to determine how upset participants would be when data is inappropriately shared, and to understand how their reaction depends upon the type and recipient of the data that is shared.
-There were a total of 288 questions in this set.
+Thus, our question pool consisted of 293 questions: the 288 described here, plus 5 that we describe in the next section.
+In this section of the survey, participants received six questions, randomly drawn from this pool.
 
@@
 We presented participants with a second set of scenarios to control for the type of device being used.
-Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
+Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
 We randomly presented each participant with 2 of these 5 questions:
@@
 
-So that we could perform controlled comparisons based on device type, we also included a version of each of these questions in the wearable scenarios section that substituted ``Cubetastic3000'' for ``smartphone.'' Thus, there were a total of 293 Cubetastic3000 scenarios, from which each participant was randomly assigned 6.
+In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these five questions were among the pool of 293 questions from which participants were randomly assigned 6).
+In this section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
 
@@
 We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
+We compensated each participant with \$1.75 upon successfully completing the survey.
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
@@
 We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
-Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344).
+Additionally, most people are likely to be upset, at least a little, in all scenarios, because a device is taking action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344).
 Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
+However, one limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.
 

### 2015-03-06 tex-inputs/related_work.tex
Modified Methodology, added more detail, fixed some errors

@@
 %one-sentence on takeaways from these sources and comment on them!
+
+While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks is relatively nascent.
+For example, both Garg et al.\ and Blythe et al.\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
+While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted prior to examining risk communication.

### 2015-03-06 tex-inputs/abstract.tex
put Dave's changes back in

@@
 \begin{abstract}
-Wearable devices bring great benefits through their omnipresence and ability to capture new types of data.
-But they also create new privacy and security risks by potentially exposing users' activities without their awareness or consent.
+Wearable devices bring great benefits but also new potential privacy and security risks that could expose users' activities without their awareness or consent.
 Effective design of notifications and security controls for wearable devices will require careful foresight to prevent habituation by treating user attention as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
@@
 Finally, we compared wearable device risks to those of more familiar technologies.
-Our goal is for this work to inform the design of future privacy and security controls for wearable devices.
+We hope that this work will inform design of future privacy and security controls for wearable devices.
 \end{abstract}

### 2015-03-06 tex-inputs/intro.tex
incorporate colleagues' comments untp section 3

@@
 
-The goal of this paper is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications.
+The goal of this work is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications.
 To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.

### 2015-03-06 tex-inputs/methodology.tex
incorporate colleagues' comments untp section 3

@@
 \section{Methodology}
-To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study.
+To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
 At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns~\cite{6_fitbit_2014, 7_time_2014}; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}; and Google Glass~\cite{11_wikipedia_2015, 12_turi_2014}.
@@
 
-We designed a survey to gauge how severe our participants consider these risks to be.
+We designed a survey to gauge what risks users consider to be relevant.
 Our survey contained two main sections.
@@
 The exit portion of the survey contained demographic questions asking for age, gender, and education.
-Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
+We also asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
 We ended with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.

### 2015-03-06 tex-inputs/results-recipient.tex
continue incorporating comments, upto 4.2

@@
 \subsubsection{Data Recipient}
-There was a statistically significant difference in VUR for an application's servers comparatively to human data recipients.
+There was a statistically significant difference in VUR for data sent to an application's servers compared data sent to human data recipients.
 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).

### 2015-03-06 tex-inputs/results-type.tex
continue incorporating comments, upto 4.2

@@
 We present various statistical models in section \ref{sec:regression} to support this conclusion.
-The 10 top and bottom concerning data can be seen in Table \ref{top10-table}, and the full list of data can be seen in Appendix [?].
+The most and least concerning data are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.
 
 Participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
-As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, and are almost unanimously considered to be concerning.
+As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and are almost unanimously considered to be concerning.
 Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
@@
 As seen in Table \ref{top10-table}, participants had spread distributions in perceptions regarding such information.
-These may have appeared as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.
+These may have appeared as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this shared.
 
-For the complete ranked list of data considered in this study, see Appendix [?].
 Although certain data is considered unanimously upsetting to have shared, it is interesting to note that no data was considered unanimously non-upsetting to have shared, nor any data which evoked strong disagreement on how upsetting it was.
 Generally,  the rank of the data being shared is negatively correlated with the standard deviation of the answers.
+For the complete ranked list of data considered in this study, see Appendix \ref{sec:data-appendix}.
 
@@
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix [?].}
+\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix \ref{sec:data-appendix}.}
 \label{top10-table}

### 2015-03-06 tex-inputs/conclusion.tex
finish incorporating comments

@@
 
-Our 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices.
-We identify that participants are most concerned about protecting their financial information, photos, and videos and least concerned about demographic or biometric data.
+Our survey of 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices.
+We identify that participants are most concerned about protecting their financial information, photos, or videos and least concerned about demographic or biometric data.
 We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients, and also that certain data is more comfortably shared with certain recipients.
-Participants' self-reported concerns of categories and perceptions of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions.
-We perform two regression model analyses with respect to the type of data and the associated risks.
+Participants' self-reported concerns of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions.
+We perform two regression model analyses with respect to the type of data and the associated risks to verify our results.
 

### 2015-03-06 tex-inputs/discussion.tex
finish incorporating comments

@@
 \section{Discussion}
-Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.
+We discuss considerations when interpreting our results, the limitations of our work, and future work we hope to inspire.
 
@@
 These participants may have underestimated or overestimated the risk perceived in various scenarios.
-People may be overreacting to recent events for scenarios \footnote{During our study, there were many stories covering injuries from exploding batteries (http://www.bloomberg.com/news/articles/2014-08-11/exploding-lithium-batteries-riskier-to-planes-research), which were explicitly and repeated mentioned when self-reporting concerns.}.
+People may be overreacting to recent events for scenarios.\footnote{During our study, there were many stories covering injuries from exploding batteries (http://www.bloomberg.com/news/articles/2014-08-11/exploding-lithium-batteries-riskier-to-planes-research), which were explicitly mentioned in self-reported concerns.}.
 People may be underestimating the risk of sharing certain data due to unawareness of what can be inferred from the data, or not have an idea of how to rate a new technology with respect to familiar ones.
-Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}.
+Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}
 
@@
 We could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will also have its own biases and limitations, since this does not reflect the general population.
-At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, so our study reflective of the status quo.
+However, that will have its own biases and limitations, since this does not reflect the general population.
+At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, so our study is reflective of the current population.
 We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
@@
 Privacy concerns asked out of context differ from how users may react to these same concerns in real life \cite{norberg2007privacy, jensen2005privacy}.
-This is an unavoidable, yet important consideration of any study of this nature.
-This privacy paradox means that our findings may not be exactly representative of how upset users may be in real life, but do reflect their perceptions of wearable devices and various associated scenarios.
+This privacy paradox means that our findings may not be representative of how upset users may react to these scenarios in real life, but do reflect actual perceptions of wearable devices and various associated scenarios.
+This is an unavoidable, yet important distinction to make with of studies of our nature.
 
@@
 Investigating more fine-grained data types (e.g.
-investigating if various types of location data, versus just location data in general) would be a useful endeavor to gain further insight into user perception.
+investigating various types of location data, versus just location data in general) would be a useful endeavor to gain further insight into user perception.
 Adding more recipients, like ``advertisers'' or ``acquaintances'' may lead to more contrasting results.
@@
 
-Wearables are still in infancy.
+Wearables are still in their infancy.
 Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.

### 2015-03-06 tex-inputs/results-demographics.tex
finish incorporating comments

@@
 We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
-A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggests that people's responses to questions were mostly based on their privacy preferences.
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggests that responses to questions were mostly based on privacy preferences.
 Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).

### 2015-03-06 tex-inputs/results-openended.tex
finish incorporating comments

@@
 
-This question was asked along with demographics questions (but before any IUIPC questions to avoid biasing).
+This question was asked along with demographics questions (but before any IUIPC questions, which asked a lot of direct privacy-related questions, to avoid biasing the recipients).
 The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
@@
 
-In addition to privacy in a general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from emf waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
+In addition to privacy in a general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
 

### 2015-03-06 tex-inputs/results-techrank.tex
Use \columnwidth for figure width
finish incorporating comments

@@
 	\centering
-	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
+	\includegraphics[width=\columnwidth]{images/riskbenefit.pdf}
 	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
@@
 Top risky technologies include facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal,  equivalent risk levels (i.e., a median of ``10'').
-The differences in risk that found between the different wearable-related technologies, are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.
-Interestingly, privacy risks and are comparative to real physical risks; for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+The differences in risk between the different wearable-related technologies, are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.
+Interestingly, privacy risks and are comparable physical risks; for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
 
-People prompted to rate with respect to all considerations (see ~\ref{sec:prompt}), including physical harm risk to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life, people may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
-Among the 5 presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk to the users.
+People  were prompted to rate technologies with respect to all considerations (see ~\ref{sec:prompt}), including physical harm risk to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life, people may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
+Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk to the users.
 

### 2015-03-06 tex-inputs/intro.tex
Fixed some wrapping issues

@@
 Wearable devices offer many compelling opportunities for benefiting users.
-For instance, they could enable a more natural, human-centered interface experience and a healthier, fitness-data inspired lifestyle.
-There will likely be many more applications in the future which take advantage of data captured by wearable devices.
+For instance, they could enable more natural, human-centered interface experiences and healthier, fitness-data inspired lifestyles.
+There will likely be many more applications in the future that take advantage of data captured by wearable devices.
+However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
+Even though wearable technology is currently in early stages, we have already seen manifestations of these risks.
+For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.
 
-However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
-Even though wearable technology is currently in early stages, we have already seen instances of these risks.
-For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.
-
-We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture on smartphones.
-Mobile platforms have tried to address the risks by communicating data capture to users as the data is captured.
-However, many users are habituated to these notifications, because they see them all the time, often for things that they do not care about \cite{felt2012android}.
+Similar privacy~\cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues~\cite{enck2011study, felt2011survey} pervade smartphones.
+Mobile platforms have tried to address the risks by communicating data capture to users.
+However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}.
 Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.
@@
 \item We compare users' perceptions of a range of privacy and security risks of wearables. We found that user concern is driven more by the type of data being captured than the recipient of the data.
-\item Our results shed light into how users feel about various data recipients.
-We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers.
+\item We shed light on how users feel about various data recipients.
+We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers (the latter is viewed as less concerning).
 \item We analyze users' self-reported top concerns regarding wearable devices.
-The results give an sense of what broad concerns users have, which can be used to guide future research in unexplored use cases.
+The results give a sense of what broad concerns users have, which can be used to guide future research on unexplored use cases.
 \item We examine how serious users perceive the risks of wearables to be, compared to risks associated with more familiar technologies.

### 2015-03-06 tex-inputs/related_work.tex
incorporate colleagues' comments untp section 3
started related work; tweaked a couple words and merged 2.1 and 2.2

@@
 \section{Related Work}
-We discuss related work that has examined users' perceptions surrounding security and privacy risks.
+%%% better introduction, or take this out. This seems awkward. 
+%We discuss related work that has examined users' perceptions surrounding security and privacy risks.
 
+%%% turn these into paragraphs rather than subsections? Or maybe this will be a bad idea if I have too many sources. But try turning them into paragaphs.
 \subsection{Wearables Concerns}
@@
 
-\subsection{Ubiquitous Sensing Concerns}
+%%% There's a lot more work on risks associated with wearables and augmented reality.
+Look at work by  Franzi Roesner, David Molnar, and Apu Kapadia.
+I also think that this subsection can be merged with 2.2.
+
+%%% Smoothly merge the two paragraphs.
+
 Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
@@
 Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
-%one-sentence on takeaways from these sources and comment on them!
+
+%%% There's way more work in this area that needs to be cited (look at stuff by Janne Lindqvist, Norman Sadeh, Patrick Kelley, and Jason Hong).
+At the very least, if you don't add new citations, you absolutely need to say 2-3 sentences about the three papers that you did cite.
+Though I strongly urge you to add more.
 
@@
 Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
-%one-sentence on takeaways from these sources and comment on them!
 
-While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks is relatively nascent.
+While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
 For example, both Garg et al.\ and Blythe et al.\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.

### 2015-03-06 tex-inputs/related_work.tex
finished first subsection of relted work

@@
 
-%%% turn these into paragraphs rather than subsections? Or maybe this will be a bad idea if I have too many sources. But try turning them into paragaphs.
-\subsection{Wearables Concerns}
-A small-scale interview of how bystanders feel about wearable devices \cite{denning2014situ} found that bystanders were predominantly split between having indifferent and negative reactions to the device.
-A variety of factors that make recording more or less acceptable, including what they are doing when the recording is being taken.
-Additionally, bystanders are expressed interest in being able to give permissions for the data being captured.
-We also investigate how the type and mechanism of data capture affects privacy concerns, but we examine the privacy concerns of wearables owners at a large-scale while their research examined the privacy concerns of wearables bystanders at a small-scale.
+\subsection{Ubiquity and Wearable Devices}
+Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Many researchers have worked to study how privacy can be preserved in the presence ubiquitous devices.
+Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication {cornelius2008anonysense}, evaluation metrics for privacy ~\cite{scholtz2004toward}, and privacy models ~\cite{hong2004privacy, jiang2002approximate}.
+However, none of these works attempted to quantify or rank user concern over different privacy risks.
 
-%%% There's a lot more work on risks associated with wearables and augmented reality.
-Look at work by  Franzi Roesner, David Molnar, and Apu Kapadia.
-I also think that this subsection can be merged with 2.2.
+Roesner et al.\ urge the community to address potential concerns for wearable devices before the technologies become widespread \cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy \cite.{roesner2014augmented}.
+A small-scale interview of how bystanders feel about wearable devices found that bystanders were predominantly split between having indifferent and negative reactions to the device but expressed clear interest in being able to give permissions for the data being captured \cite{denning2014situ}.
+We hope our research furthers   work in communicating with users and bystanders.
 
-%%% Smoothly merge the two paragraphs.
-
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in such a future.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications.
-Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
-%one-sentence on takeaways from these sources and comment on them!
-
-\subsection{Smartphones Concerns}
+\subsection{Learning from Smartphones}
 Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.

### 2015-03-06 tex-inputs/methodology.tex

@@
 To ensure that participants had read and understood this device's capabilities, since it would form the basis for many of our survey questions, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn.
-We filtered out those who could not answer these questions.
+We filtered out responses from participants who could not answer these questions.
 
@@
 We presented participants with a second set of scenarios to control for the type of device being used.
-Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}.
-We randomly presented each participant with 2 of these 5 questions:
+Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 
-In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these five questions were among the pool of 293 questions from which participants were randomly assigned 6).
-In this section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
+In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6).
+In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
 

### 2015-03-06 tex-inputs/results-intro.tex
Added clarifications

@@
 \section{Results}
-We present our survey results and provide analyses of the data.
-We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived.
+In this section, we present participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to their risk perceptions.
 Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
@@
 Many factors impact participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.
+We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of the factors, including demographic traits.

### 2015-03-06 tex-inputs/results-type.tex
Added clarifications

@@
 
-Based on our data, we observed that the largest effect stemmed from the data being shared.
-We present various statistical models in section \ref{sec:regression} to support this conclusion.
-The most and least concerning data are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.
+Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect stemmed from the type of data being shared.
+The most and least concerning data types are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.
 
@@
 As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and are almost unanimously considered to be concerning.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.
+Information that could be used to impersonate someone (e.g., usernames/passwords for websites), or photos of someone at home, were also among the most concerning data types.
 
-Participants were least concerned about data that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken) and information available to advertisers (e.g.
-TV shows watched, music on device).
-As seen in Table \ref{top10-table}, participants had spread distributions in perceptions regarding such information.
-These may have appeared as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this shared.
+Participants were least concerned about data that could be collected through observations of public behavior, such as demographics (e.g., age, gender, language) or information available to advertisers (e.g., TV shows watched, music on device).
+As seen in Table \ref{top10-table}, participants' responses had a greater amount of variance.
+This greater variance and overall decreased concern may be because of uncertainty with how the data would be used, or because the financial, social, or physical consequences would be less immediate.
 
-Although certain data is considered unanimously upsetting to have shared, it is interesting to note that no data was considered unanimously non-upsetting to have shared, nor any data which evoked strong disagreement on how upsetting it was.
-Generally,  the rank of the data being shared is negatively correlated with the standard deviation of the answers.
-For the complete ranked list of data considered in this study, see Appendix \ref{sec:data-appendix}.
+Although certain data is considered unanimously upsetting to have shared, it is interesting to note that no data was considered unanimously non-upsetting to have shared, nor were there any data types that evoked strong disagreement between participants (i.e., bimodal).
+Generally, the average concern magnitude was inversely correlated with the standard deviation, which suggests the presence of ceiling effects for the most concerning data types.
+For the complete ranked list of data types in this study, see Appendix \ref{sec:data-appendix}.
 

### 2015-03-06 tex-inputs/related_work.tex
expanded the souces already in smartphones related work section

@@
 
-\subsection{Learning from Smartphones}
-Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.
+\subsection{Smartphones}
+Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones.
+Research shows that perceptions of risk change as computing systems change.
+Chin et.
+al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, and find that these attitudes differ significantly ~\cite{chin2012measuring}.
+How people use these devices had also changed.
+Palen et.
+al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}.
+People also perceive and behave without a realistic understanding of the risks they are taking.
+Felt et.
+al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.
 

### 2015-03-06 tex-inputs/related_work.tex
finished smartphone related work

@@
 
-\subsection{Ubiquity and Wearable Devices}
+\subsection{Ubiquitous and Wearable Devices}
 Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
@@
 Chin et.
-al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, and find that these attitudes differ significantly ~\cite{chin2012measuring}.
-How people use these devices had also changed.
+al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, finding that these attitudes differ significantly ~\cite{chin2012measuring}.
+How people use these smartphones was also unlike other computing systems.
 Palen et.
@@
 
-%%% There's way more work in this area that needs to be cited (look at stuff by Janne Lindqvist, Norman Sadeh, Patrick Kelley, and Jason Hong).
-At the very least, if you don't add new citations, you absolutely need to say 2-3 sentences about the three papers that you did cite.
-Though I strongly urge you to add more.
+Smartphones enabled new systems which used new types of data which were previously hard to measure.
+Users tend to use these applications for their benefit, but do not think of the privacy implications.
+Lindqvist et.
+al\  studies a popular location tracking application, and find that people share their location information for gaming, signaling availability to friends, and more withou concern for privacy implications of broadcasting this information \cite{lindqvist2011m}.
+Tsai et.
+al\ found that mobile users do get feedback about releasing data, such as who has viewed that you were at a certain location, greatly impacts user behaviors \cite{Tsai2009}.
+However, this type of feedback is not generally provided to users.
+There are still many unresolved concerns, such as the opaqueness which prevents knowledge of what applications are doing with given data, along with rogue applications which steal your data \cite{1_kane_2010, zhou2011taming}.
 

### 2015-03-06 tex-inputs/related_work.tex
fixed { error

@@
 Palen et.
-al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}.
+al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use \cite{palen2000going}.
 People also perceive and behave without a realistic understanding of the risks they are taking.

### 2015-03-06 tex-inputs/methodology.tex
methodology: made smartphone questions italics too.

@@
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item How would you feel if an app on your <device> vibrated your phone without asking you first?
+\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?
 \item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
@@
 \item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
-\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
+\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
 \end{enumerate}

### 2015-03-06 tex-inputs/appendixes.tex
Added coding descriptions
Fix multiply defined labels
reorder appendixes

@@
 Don't care: `` do not care,'' nonchalant answers
-
-\onecolumn
-\section{Full Regression Model from Data Types}
-\label{sec:regression}
-%\begin{figure*}[t]
-\includegraphics[page=1,scale=0.8]{images/full-model.pdf}
-\includepdf[pages=2-3,scale=0.8]{images/full-model.pdf}
-
-%\caption{Full regression model, which includes all 72 data types, recipients, and covariates.}
-%\end{figure*}
-
-\section{Full Regression Model from Data Risks / Data Categories}
-\label{sec:regression}
-%\begin{figure*}[t]
-\includegraphics[page=1,scale=0.8]{images/full-model2.pdf}
-\includepdf[pages=2,scale=0.8]{images/full-model2.pdf}
-
-\twocolumn

### 2015-03-06 tex-inputs/regression-model.tex
reorder appendixes

\onecolumn
\section{Full Regression Model from Data Types}
\label{sec:regression-apx}
%\begin{figure*}[t]
\includegraphics[page=1,scale=0.8]{images/full-model.pdf}
\includepdf[pages=2-3,scale=0.8]{images/full-model.pdf}

%\caption{Full regression model, which includes all 72 data types, recipients, and covariates.}
%\end{figure*}

\section{Full Regression Model from Data Risks / Data Categories}
\label{sec:regression-apx2}
%\begin{figure*}[t]
\includegraphics[page=1,scale=0.8]{images/full-model2.pdf}
\includepdf[pages=2,scale=0.8]{images/full-model2.pdf}

\twocolumn

### 2015-03-06 tex-inputs/results-recipient.tex

--- 2015-03-05 tex-inputs/results-recipient.tex
@@
 \subsubsection{Data Recipient}
-There was a statistically significant difference in VUR for an application's servers comparatively to human data recipients.
-42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).
+There was a statistically significant difference in VUR for data sent to an application's servers compared to data sent to human recipients.
+On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).
 A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}).

### 2015-03-06 tex-inputs/discussion.tex
pass through discussion

@@
 \section{Discussion}
-We discuss considerations when interpreting our results, the limitations of our work, and future work we hope to inspire.
+%We discuss considerations when interpreting our results, the limitations of our work, and future work we hope to inspire.
 
-\subsection{Interpreting the Survey Results}
-One of the main limitations of this work is that our participants might not have interest in or knowledge of wearables and their capabilities.
-83\% of our participants reported that they do not own a wearable device.
-These participants may have underestimated or overestimated the risk perceived in various scenarios.
-People may be overreacting to recent events for scenarios.\footnote{During our study, there were many stories covering injuries from exploding batteries (http://www.bloomberg.com/news/articles/2014-08-11/exploding-lithium-batteries-riskier-to-planes-research), which were explicitly mentioned in self-reported concerns.}.
-People may be underestimating the risk of sharing certain data due to unawareness of what can be inferred from the data, or not have an idea of how to rate a new technology with respect to familiar ones.
-Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}
+%\subsection{Limitations}
+One of the limitations is that our participants might not have interest in or knowledge of wearables and respective capabilities.
+83\% of our participants reported that they do not own a wearable.
+Participants may be over or underestimating the risk due to unawareness of what can be inferred from the data, not have an idea of how to rate a new technology with respect to familiar ones, or be greater influenced by recent events for scenarios.\footnote{Recently, stories  of  exploding batteries were in the news \cite{1_levin_2014}, which were explicitly self-reported as a concern.}.
+For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}.
 
-We believed that getting a representative survey base was a useful endeavor.
+We believed a representative survey base was a useful endeavor.
 We could have easily recruited only wearables owners or people specifically interested in wearables.
 However, that will have its own biases and limitations, since this does not reflect the general population.
-At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, so our study is reflective of the current population.
-We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
+At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, making our study is reflective of the current population.
 
@@
 
-\subsection{Future Research Directions}
+%\subsection{Future Research Directions}
 Further work can be done to expand various aspects of this study.
@@
 Adding more recipients, like ``advertisers'' or ``acquaintances'' may lead to more contrasting results.
-
-While privacy and security concerns were expected, consider the following self-reported user concerns as inspiration for future research: addressing the high financial costs of wearables, communicating the reality of health concerns from constant use, creating distraction-free interfaces to prevent safety issues, minimizing negative social impacts of wearable device use, and improving device aesthetics.
+Additionally, the following self-reported user concerns as inspiration for future research: addressing the high financial costs of wearables, communicating the reality of health concerns from constant use, creating distraction-free interfaces to prevent safety issues, minimizing negative social impacts of wearable device use, and improving device aesthetics.
 
@@
 Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies.
+However, videos and textual information are currently and significantly considered to be sensitive by our participants, along with past participants of smartphone user perception studies.
 Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

### 2015-03-06 tex-inputs/conclusion.tex
pass through conclusion

@@
 We identify that participants are most concerned about protecting their financial information, photos, or videos and least concerned about demographic or biometric data.
-We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients, and also that certain data is more comfortably shared with certain recipients.
+We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients.
 Participants' self-reported concerns of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions.

### 2015-03-06 tex-inputs/appendixes.tex
coding labels formatting

@@
 \label{sec:coding}
+Researchers coded the self reported answers in the following way.\\
 
-Privacy: ``privacy,'' revealing personal information, spying. \\
-Security:  ``security,'' compromise, malware, hacking. \\
-GPS tracking: ``location,'' ``GPS,'' being monitored.
-
-Unaware use: using data without permission or in a different way than understood by user. \\
-Unaware collection: collecting data without permission. \\
-Unaware access: disclosure of data without permission. \\
-False information: inaccurate or maliciously false data.
-
-Health Risk: radiation, cancer, or long-term effects.\\
-Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-Discomfort: eye strain, headache, obscured vision, irritation. \\
-Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
-Theft: the device getting stolen.
-
-Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
-Social Stigma: judgment, hate, or bystander discomfort.\\ 
-Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky.
-
-Miscellaneous: odd comments, uncommon concerns. \\
-None: ``None,'' no threat, perceiving no big concerns \\
-Don't know: ``do not know,'' hinting at confusion \\
-Don't care: `` do not care,'' nonchalant answers
+{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
+{\bf Security}:  ``security,'' mention of malware, hacking. \\
+{\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
+{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission or in a different way than understood by user. \\
+{\bf False information}: inaccurate or maliciously false data.\\
+{\bf Health Risk}: mention of radiation, cancer, or health effects.\\
+{\bf Safety}: mention of distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
+{\bf Discomfort}: mention of eye strain, headache, obscured vision, irritation. \\
+{\bf Financial cost}: mention of getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
+{\bf Theft}: mention of device theft. \\
+{\bf Social Impact}: mention of dependency, distance from friends and family, changes in decision making, social changes, etc. \\
+{\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
+{\bf Aesthetics}: mention of fashion, the device being ugly, looking dorky. \\
+{\bf Miscellaneous}: odd comments, uncommon concerns. \\
+{\bf None}: ``None,'' mention of no threat, or no real concerns \\
+{\bf Don't know}: ``do not know,'' general confusion \\
+{\bf Don't care}: `` do not care,'' nonchalant answers

### 2015-03-06 tex-inputs/related_work.tex

--- 2015-03-06 tex-inputs/related_work.tex
@@
 %We discuss related work that has examined users' perceptions surrounding security and privacy risks.
+In this section, we outline previous research that has examined privacy for ubiquitous and wearable computing environments, smartphone privacy and security, as well as user risk perceptions and behaviors.
 
-\subsection{Ubiquity and Wearable Devices}
+\subsection{Ubiquitous and Wearable Devices}
 Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Many researchers have worked to study how privacy can be preserved in the presence ubiquitous devices.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication {cornelius2008anonysense}, evaluation metrics for privacy ~\cite{scholtz2004toward}, and privacy models ~\cite{hong2004privacy, jiang2002approximate}.
+Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
+Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
 However, none of these works attempted to quantify or rank user concern over different privacy risks.
 
-Roesner et al.\ urge the community to address potential concerns for wearable devices before the technologies become widespread \cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy \cite.{roesner2014augmented}.
-A small-scale interview of how bystanders feel about wearable devices found that bystanders were predominantly split between having indifferent and negative reactions to the device but expressed clear interest in being able to give permissions for the data being captured \cite{denning2014situ}.
-We hope our research furthers   work in communicating with users and bystanders.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
+A small-scale interview of how bystanders feel about wearable devices found that bystanders were predominantly split between having indifference and negative reactions to the device, but expressed clear interest in being able to give permission for data to be captured~\cite{denning2014situ}.
+Our research furthers this goal of communicating risks to users and bystanders.
 
@@
 Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones.
-Research shows that perceptions of risk change as computing systems change.
-Chin et.
-al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, and find that these attitudes differ significantly ~\cite{chin2012measuring}.
-How people use these devices had also changed.
-Palen et.
-al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}.
+Research shows that perceptions of risk change based on the particular device being used.
+Chin {\it et al.}\ found that users' attitudes toward security and privacy for smarphones significantly differed from attitudes towards traditional computing systems~\cite{chin2012measuring}.
+How people used their smartphones also differed from how they used other computing systems.
+Palen {\it et al.}\ tracked smartphone users for six weeks and observed radical changes with respect to how they used their devices~\cite{palen2000going}.
 People also perceive and behave without a realistic understanding of the risks they are taking.
-Felt et.
-al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.
+Felt {\it et al.}\ examined the Android permission system and found that 17\% of participants paid attention to permission requests, and only 3\% comprehended what these permissions meant.
 
-%%% There's way more work in this area that needs to be cited (look at stuff by Janne Lindqvist, Norman Sadeh, Patrick Kelley, and Jason Hong).
-At the very least, if you don't add new citations, you absolutely need to say 2-3 sentences about the three papers that you did cite.
-Though I strongly urge you to add more.
+Smartphones allow applications to access new types of data.
+While this tends to benefit users, they do not think of the privacy implications.
+Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
+Tsai {\it et al.}\ found that when mobile users get feedback about releasing data, such as who has viewed location information, it greatly impacts future behaviors~\cite{Tsai2009}.
+However, this type of feedback is not generally provided to users.
+There are still many unresolved concerns, such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
 
 \subsection{User Perceptions and Behaviors}
-In this paper we focus on measuring people's perceptions of security and privacy risks.
-One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
+In this paper, we focus on measuring user perceptions of security and privacy risks, as they relate to wearable devices.
+One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and stated privacy preferences~\cite{spiekermann2001privacy}.
 
 While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
-For example, both Garg et al.\ and Blythe et al.\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
-While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted prior to examining risk communication.
+For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
+While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.

### 2015-03-06 tex-inputs/results-openended.tex
pass through open-ended

@@
 
- Table \ref{openresponses} shows the most common user concerns related to wearable devices.
+Table \ref{openresponses} shows common user concerns related to wearable devices.
 Appendix \ref{sec:coding} details the responses categorized in each coding label.
-Most of these concerns are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users.
+Most are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users.
 This can be used to guide research in unexplored use cases.
 
-In addition to privacy in a general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial), and information compromise (Security).
+In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware).
+Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).
 

### 2015-03-06 tex-inputs/methodology.tex
Killed orphans dead.

@@
 
-The purpose of these questions was to determine how upset participants would be when data is inappropriately shared, and to understand how their reaction depends upon the type and recipient of the data that is shared.
-Thus, our question pool consisted of 293 questions: the 288 described here, plus 5 that we describe in the next section.
-In this section of the survey, participants received six questions, randomly drawn from this pool.
+The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
+Each participant answered 6 questions that were randomly drawn from a pool of 293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).
 

### 2015-03-06 tex-inputs/results-demographics.tex
pass through demographics

@@
 Participants' responses were correlated with demographic factors.
-We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
-A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggests that responses to questions were mostly based on privacy preferences.
+The biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggest responses to questions were mostly based on privacy preferences.
 Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).

### 2015-03-06 tex-inputs/results-type.tex
Wordsmithed

@@
 
-Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect stemmed from the type of data being shared.
+Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect on participants' VURs stemmed from the type of data being shared; data recipient and device type had weaker impacts on overall VURs.
 The most and least concerning data types are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.

### 2015-03-06 tex-inputs/results-regression.tex
pass through regression section

--- 2015-03-05 tex-inputs/results-regression.tex
@@
 
-We created several models using two independent variables as predictors: data recipient and data type.
-Because the device type independent variable (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these 5 data types from our models, which resulted in a total of 72 data types shared between 4 possible recipients.
-We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
-For each model, we performed Wald's test to examine the model effects attributable to each of these parameters and observed that the only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other.
+We created several models using two independent variables as predictors: data and recipient.
+Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients.
+We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
+For each model, we performed Wald's test to examine the model effects attributable to each of these parameters.
+The only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other.
 Thus, we opted to remove the other covariates from our analysis.
@@
 As can be seen, the data type was the strongest predictor of VUR.
-The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression}.
+The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.
 
-While these models clearly illustrate  the relative weight that users might place on various types of information when determining whether a given privacy violation is truly upsetting, one shortcoming of this approach is its generalizability: the data type predictor is categorical and obviously limited to the data types that we specifically chose for this study.
-That is, it is not entirely clear how these models might apply to data types not among the 72 that we directly examined.
-Therefore, in an attempt to make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the data type (e.g., video, audio, etc.) and in terms of the type of risk it might present to the user.
-Two researchers agreed on a codebook and independently coded each of the 72 data types.\footnote{We excluded the data types that did not feature a data recipient, the five misbehaviors used to examine device types.}
+While these models illustrate the relative weights that users place on information when determining a scenario as truly upsetting, one shortcoming of this approach is its generalizability: the data predictor is categorical and limited to the data that we specifically chose for this study.
+To make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the type of data (e.g., video, audio, etc.) and the type of risk it presents.
+Two researchers agreed on a codebook and independently coded each of the 72 data types.
 
@@
 While the first three categories are self-explanatory, the latter three categories are all based on different user characteristics.
-We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} is defined as measurements of the user's body; and {\it demographic information} is defined as non-biometric information about the user's traits.
+We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.
+
 The associated risks for each data type fell into the following five categories:
@@
 
-After independently coding all data types with respect to these categories, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity.
-Prior to this resolution, there was  83\% agreement.
-Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the associated risks, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+After independently coding, the researchers met to resolve any disagreements, such that the results reflect unanimity.
+There was  83\% agreement prior to resolution.
+Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the  risks categories, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+
+With regard to data types, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%).
+Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data.
+We suspect that demographic data was more concerning than we expected because we included information such as a Social Security Number, bank account information, and other financial information.
+We chose to categorize them as such as they are not biological measurements of the user, nor the other types of data types in our categories.
+We were very surprised that biometric information was seen as relatively benign  compared to the other broad categories of data.
+One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data were to be stolen and abused.
+
+With regard to presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%).
+Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed next in VURs.
+VURs were lowest for medical information disclosure (47.4\%).
+One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also related basic information, such as age, gender, and emotional state.
+As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.
 
@@
 When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.
+The full model can be found in Appendix \ref{sec:regression-apx2}.

### 2015-03-06 tex-inputs/results-devices.tex
continue incorporating comments, upto 4.2

--- 2015-03-04 tex-inputs/results-devices.tex
@@
 \begin{table}[t]
+\small
 \begin{center}
@@
 Across all participants, the VUR was 46.7\% (of 1,782) when describing smartphones, whereas the VUR increased to 58.8\% (of 159) when describing these same misbehaviors on the Cubetastic3000.
-The VURs for both devices for all 5 questions are in Table ~\ref{deviceVUR}.
+The VURs for both devices for all 5 questions are in Table \ref{deviceVUR}.
 
-To preserve data independence, we performed a Mann-Whitney U test by comparing participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
-We found this difference to be statistically significant ($108,664.0$, $p<0.0005$), however, the effect size was incredibly small ($r=0.08$).
+To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
+This difference was statistically significant ($U=108,664.0$ with $p<0.0005$), however, the effect size was very small ($r=0.08$).
 Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors.
-As a result, we can conclude that in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible.
-Similarly, the entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.
+We conclude that while in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible.
+The entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.
 

### 2015-03-06 tex-inputs/results-recipient.tex

@@
 There was a statistically significant difference in VUR for data sent to an application's servers compared to data sent to human recipients.
-On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}).
+On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were almost double (Table \ref{recipient-vur}).
 A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}).
@@
 
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios.
+We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients.
 But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.

### 2015-03-06 tex-inputs/results-techrank.tex
Fixed grammar errors

@@
 
-As a group, participants rated more familiar technologies as the more beneficial.
-We believe this is the result of exposure people have to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
+As a group, participants rated more familiar technologies as more beneficial.
+We believe this is the result of exposure to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
 It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
@@
 Of the wearable technologies, privacy-invasive ones were perceived to be risky.
-Top risky technologies include facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal,  equivalent risk levels (i.e., a median of ``10'').
-The differences in risk between the different wearable-related technologies, are not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences are negligible.
-Interestingly, privacy risks and are comparable physical risks; for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.
+The riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
+The differences in risk between the different wearable-related technologies, were not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
+Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.
 
-People  were prompted to rate technologies with respect to all considerations (see ~\ref{sec:prompt}), including physical harm risk to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life, people may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
-Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk to the users.
+Participants were prompted to rate technologies with respect to all considerations (see ~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
+Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
+Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk.
 
 These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
+However, they do reflect the general public's exposure to these technologies and their perceptions, they also show that people perceive specific risks and benefits.
 We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.

### 2015-03-07 tex-inputs/riskben.tex
appendix formatting
appendix anger

--- 2015-03-03 tex-inputs/riskbenefit.tex
@@
+%!TEX root = ../paper.tex
+\onecolumn
+\section{Risk and Benefit Assessments of Various Technologies}
+\label{sec:riskben-appendix} 
+\twocolumn
 \begin{table}[t]
@@
 \small
-\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c | p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
-\\hline
-&\multicolumn{4}{ |c| }{Risk} & \multicolumn{4}{ c| }{Benefit}\\ 
- \\hline
-Technology &  Median & Q1 & Q3 & Distribution &  Median& Q1 & Q3 & Distribution   \\ 
+\begin{tabular}{| p{2.6cm} | p{.8cm} | p{.8cm} | p{.8cm} | c |}
 \hline
-location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\
-speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\
-discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\
-smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\
-language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\
-laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\
-smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\
-google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\
-cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\
-gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\
-voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\
-voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\
-fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\
-age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\
-facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\
-email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\
-heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\
-discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\
-internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\
-facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\
-Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk}  & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit}\\
-
-Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit}  \\
-Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\
-Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk}& 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit}  \\
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingrisk} \\ 
+Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextrisk} \\ 
+Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophonerisk} \\ 
+Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesrisk} \\ 
+Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionrisk} \\ 
+Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsrisk} \\ 
+Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesrisk} \\ 
+Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassrisk} \\ 
+Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticrisk} \\ 
+Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionrisk} \\ 
+Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionrisk} \\ 
+Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionrisk} \\ 
+Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersrisk} \\ 
+Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionrisk} \\ 
+Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionrisk} \\ 
+Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailrisk} \\ 
+Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionrisk} \\ 
+Discreet Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocamerarisk} \\ 
+Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetrisk} \\ 
+Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionrisk} \\ 
+Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerRisk} \\ 
+Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityRisk} \\ 
+Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleRisk} \\ 
+Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunRisk} \\ 
 \hline
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients.}
-\label{top10}
+\caption{Risk rankings of various technologies in response to the Fischoff-style prompt.}
+\label{risk}
 \end{center}
 \end{table}
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| p{2.6cm} | p{.8cm} | p{.8cm} | p{.8cm} | c |}
+\hline
+Technology & Q1 &  Median & Q3 & Distribution  \\ 
+\hline
+Gender Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/genderdetectionben} \\ 
+Age Detection & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/agedetectionben} \\ 
+Discreet Microphone & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetmicrophoneben} \\ 
+Cubetastic & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/cubetasticben} \\ 
+Fitness Trackers & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/fitnesstrackersben} \\ 
+Voice Based Emotion Detection & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicebasedemotiondetectionben} \\ 
+Facial Detection & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialdetectionben} \\ 
+Discreet Camera & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/discreetvideocameraben} \\ 
+Google Glass & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/googleglassben} \\ 
+Smartwatches & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartwatchesben} \\ 
+Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/MotorcycleBenefit} \\ 
+Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/HandgunBenefit} \\ 
+Facial Recognition & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/facialrecognitionben} \\ 
+Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/LawnmowerBenefit} \\ 
+Speech To Text & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/speechtotextben} \\ 
+Voice Recognition & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/voicerecognitionben} \\ 
+Language Detection & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/languagedetectionben} \\ 
+Heart Rate Detection & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/heartratedetectionben} \\ 
+Location Tracking & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/locationtrackingben} \\ 
+Email & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/emailben} \\ 
+Smartphones & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/smartphonesben} \\ 
+Laptops & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/laptopsben} \\ 
+Internet & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/internetben} \\ 
+Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/ElectricityBenefit} \\ 
+\hline
+\end{tabular}
+\caption{Benefit rankings of various technologies in response to the Fischoff-style prompt. }
+\label{benefit}
+\end{center}
+\end{table}

### 2015-03-07 tex-inputs/results-techrank.tex
Kills orphans dead.

@@
 
-Of the wearable technologies, privacy-invasive ones were perceived to be risky.
-The riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
-The differences in risk between the different wearable-related technologies, were not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
+Of the wearable technologies, the riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
+We did not test the differences in risk between the different wearable-related technologies for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
 Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.
 
-Participants were prompted to rate technologies with respect to all considerations (see ~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
+Participants were prompted to rate technologies with respect to all considerations (see Appendix~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
 Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
@@
 
-These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits.
-However, they do reflect the general public's exposure to these technologies and their perceptions, they also show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used.
-We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
+We examined participants' perceptions, and therefore responses may not be reflective of actual risks or benefits.
+However, they also reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
+We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities and that performing this experiment longitudinally may yield more interesting results, as these technologies become pervasive (and more familiar to participants).

### 2015-03-07 tex-inputs/results-demographics.tex
More dead orphans

@@
 
-Participants' responses were correlated with demographic factors.
-The biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
-A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggest responses to questions were mostly based on privacy preferences.
+The biggest demographic predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores and VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences.
 Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.
+We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.
 

### 2015-03-07 tex-inputs/results-openended.tex
More dead orphans

@@
 %!TEX root = ../paper.tex
-\subsection{Self-Reported Concerns for Wearables}
-We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:
+\subsection{Open-Ended Concerns for Wearables}
+We captured participants' general reactions to wearable devices as a whole by asking the following open-ended question:
 
@@
 Appendix \ref{sec:coding} details the responses categorized in each coding label.
-Most are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users.
+Most are related to privacy and security, but this open-ended data gives a sense of what broad categories of concerns are most relevant to users.
 This can be used to guide research in unexplored use cases.
@@
 In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware).
-Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).
+Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions that cause car accidents (Safety), resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).
 
@@
 \end{tabular}
-\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
+\caption{The most common open-ended risks associated with owning a wearable device.}
 \label{openresponses}

### 2015-03-07 tex-inputs/results-regression.tex
More orphans dead.

@@
 Thus, we opted to remove the other covariates from our analysis.
-Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit).
+Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection that also accounts for complexity (lower relative values indicate better fit).
 As can be seen, the data type was the strongest predictor of VUR.
@@
 
-The associated risks for each data type fell into the following five categories:
+The risks for each data type fell into the following categories:
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 There was  83\% agreement prior to resolution.
-Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the  risks categories, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the  risk categories, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
 
@@
 Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data.
-We suspect that demographic data was more concerning than we expected because we included information such as a Social Security Number, bank account information, and other financial information.
-We chose to categorize them as such as they are not biological measurements of the user, nor the other types of data types in our categories.
+We suspect that demographic data was more concerning because it included information such as a Social Security Number, bank account information, and other financial information.
+We chose to categorize them as such as they are non-biological descriptors of the user.
 We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data.
-One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data were to be stolen and abused.
+One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data are stolen and abused.
 
-With regard to presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%).
-Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed next in VURs.
+With regard to the presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%).
+Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed.
 VURs were lowest for medical information disclosure (47.4\%).
-One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also related basic information, such as age, gender, and emotional state.
+One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state.
 As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.
@@
 \end{tabular}
-\caption{Goodness-of-fit metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures.
+\caption{Metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures.
 The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.

### 2015-03-07 tex-inputs/discussion.tex
Cleaned up writing, killed orphans

@@
 %\subsection{Limitations}
-One of the limitations is that our participants might not have interest in or knowledge of wearables and respective capabilities.
-83\% of our participants reported that they do not own a wearable.
-Participants may be over or underestimating the risk due to unawareness of what can be inferred from the data, not have an idea of how to rate a new technology with respect to familiar ones, or be greater influenced by recent events for scenarios.\footnote{Recently, stories  of  exploding batteries were in the news \cite{1_levin_2014}, which were explicitly self-reported as a concern.}.
-For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}.
+One of the limitations is that our participants might not have interest in or knowledge of wearables and their respective capabilities, since 83\% of our participants reported that they do not own a wearable.
+Participants may be over or underestimating the risk due to unawareness of what can be inferred from the data, not have an idea of how to rate a new technology with respect to familiar ones, or be more influenced by recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
 
-We believed a representative survey base was a useful endeavor.
+We recruited both wearable users and non-users in order to yield a more representative sample of the general population.
 We could have easily recruited only wearables owners or people specifically interested in wearables.
-However, that will have its own biases and limitations, since this does not reflect the general population.
-At the time of this writing, about 85\% of the general population do not own wearable devices \cite{Nilsen,WearableStatNews}, making our study is reflective of the current population.
+However, that would have its own biases and limitations.
+At the time of this writing, about 85\% of the general population do not own wearable devices~\cite{Nilsen,WearableStatNews}, indicating our study is reflective of the current population.
 
-Privacy concerns asked out of context differ from how users may react to these same concerns in real life \cite{norberg2007privacy, jensen2005privacy}.
-This privacy paradox means that our findings may not be representative of how upset users may react to these scenarios in real life, but do reflect actual perceptions of wearable devices and various associated scenarios.
-This is an unavoidable, yet important distinction to make with of studies of our nature.
+Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}.
+At the same time, our results do reflect actual perceptions of wearable devices and the associated privacy scenarios involving them.
+This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and preferences, so that future systems can be designed with these in mind.
+We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over post hoc approaches (or ignoring user concerns altogether).
 
@@
 Further work can be done to expand various aspects of this study.
-Investigating more fine-grained data types (e.g.
-investigating various types of location data, versus just location data in general) would be a useful endeavor to gain further insight into user perception.
-Adding more recipients, like ``advertisers'' or ``acquaintances'' may lead to more contrasting results.
-Additionally, the following self-reported user concerns as inspiration for future research: addressing the high financial costs of wearables, communicating the reality of health concerns from constant use, creating distraction-free interfaces to prevent safety issues, minimizing negative social impacts of wearable device use, and improving device aesthetics.
+Investigating more fine-grained data types (e.g., investigating specific instances of location data, versus location data in general) would be a useful endeavor to gain further insight into user perceptions.
+Adding additional recipients, such as ``advertisers'' or ``acquaintances'' may lead to more nuanced results.
+Additionally, the open-ended concerns are inspiration for future research: addressing the high financial costs of wearables, communicating the reality of health concerns from constant use, creating distraction-free interfaces to prevent safety issues, minimizing negative social impacts of wearable device use, and improving device aesthetics.
 
@@
 Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, videos and textual information are currently and significantly considered to be sensitive by our participants, along with past participants of smartphone user perception studies.
+However, pursuant to previous studies of smartphone risk perceptions, our participants found embarrassing videos and risks involving financial losses to be the most sensitive, which suggests that these risks should be highlighted by platform developers.
 Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

### 2015-03-07 tex-inputs/appendixes.tex
small adjust
final version

@@
 \label{sec:coding}
-Researchers coded the self reported answers in the following way.\\
-
+Researchers coded the self reported answers as follows:\\
 {\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
@@
 {\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
-{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission or in a different way than understood by user. \\
+{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission. \\
 {\bf False information}: inaccurate or maliciously false data.\\
-{\bf Health Risk}: mention of radiation, cancer, or health effects.\\
-{\bf Safety}: mention of distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
-{\bf Discomfort}: mention of eye strain, headache, obscured vision, irritation. \\
-{\bf Financial cost}: mention of getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
+{\bf Health Risk}: mention of radiation, cancer, or other effects.\\
+{\bf Safety}: mention of distractions causing car crashes and injuries, violence due to the device, injuries from malfunctions.\\
+{\bf Discomfort}: mention of eye strain, headache, irritation. \\
+{\bf Financial cost}: cost of buying or using the device. \\
 {\bf Theft}: mention of device theft. \\
-{\bf Social Impact}: mention of dependency, distance from friends and family, changes in decision making, social changes, etc. \\
+{\bf Social Impact}: mention of dependency, distance from people, changes in decision making, etc. \\
 {\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
-{\bf Aesthetics}: mention of fashion, the device being ugly, looking dorky. \\
+{\bf Aesthetics}: mention of fashion or looking dorky. \\
 {\bf Miscellaneous}: odd comments, uncommon concerns. \\

### 2015-03-07 tex-inputs/collapsed.tex
tweaked abstract and intro, cleaned up tables and added appendix sections
Fix multiply defined label, and caption for the tables showing VUR rates for all data types (in appendix)
appendix formatting
Done!
final version

@@
 %!TEX root = ../paper.tex
+
+%\onecolumn
+\section{Concern Factors}
+\label{sec:concerns-appendix} 
+We show the full, fine-grained results of our survey in this appendix.
+This includes how participants had ranked each technology in response to the Fischhoff-style questions, the VUR rates for all seventy-two data types, across all recipients and by recipient, and the details of the full regression models used in our analyses.
+
 \begin{table*}[t]
@@
 \small
-\begin{tabular}{| l | r | r | r | r | r |}
+\begin{tabular}{| r | l | r | r | r | r |}
 \hline
@@
 16 & when you have sex & 81.95 & 0.82 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouhavesexcombined} \\ 
-17 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
-18 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouintoxicatedcombined} \\ 
-19 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
-20 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourpassingconversationscombined} \\ 
-21 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
-22 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
-23 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouoff-guardcombined} \\ 
-24 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
-25 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourusernameforwebsitescombined} \\ 
-26 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouraddresscombined} \\ 
-27 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
-28 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouoff-guardcombined} \\ 
-29 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
-30 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
-31 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
-32 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
-33 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourfingerprintsomehowcombined} \\ 
-34 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
-35 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
-36 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicationyoutakecombined} \\ 
-37 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
-38 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookapictureofyoursignaturecombined} \\ 
-39 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatwebsitesyougotocombined} \\ 
-40 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
-41 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyoulivesomehowcombined} \\ 
-42 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
-43 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
-44 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
-45 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
-46 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouare(likeaGPS)combined} \\ 
-47 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
-48 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
-49 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedthesoundaroundyoucombined} \\ 
-50 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
-51 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouworksomehowcombined} \\ 
-52 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\
-53 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourphonecombined} \\ 
-54 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatproductsyoubuycombined} \\ 
-55 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouaresickorhealthycombined} \\ 
-56 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
-57 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\
-58 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
-59 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
-60 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyournamecombined} \\ 
-61 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
-62 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
-63 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
-64 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
-65 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
-66 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
-67 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
-68 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourheartratecombined} \\ 
-69 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouragecombined} \\ 
-70 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedthelanguageyouwerespeakingcombined} \\ 
-71 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourgendercombined} \\ 
+17 & how much debt you have & 81.12  & 0.54 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouintoxicatedcombined} \\ %learnedhowmuchdebtyouhavecombined
+18 & video of you at home & 81.05 & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)athomecombined} \\ 
+19 & photo of you intoxicated & 78.95 & 0.82 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouintoxicatedcombined} \\ 
+20 & photo of you at random & 78.76 & 0.85 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofyou(withaninward-facingcamera)atrandomcombined} \\ 
+21 & audio recording of conversations & 78.13 & 0.83 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyourpassingconversationscombined} \\ 
+22 & medical conditions & 77.7 & 0.86 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicalconditionsyouhavecombined} \\ 
+23 & video of you at random & 76.19 & 0.59 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofyou(withaninward-facingcamera)atrandomcombined} \\ 
+24 & video of you off-guard & 76.0 & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookavideoofyouoff-guardcombined} \\ 
+25 & photo of your work or workplace & 74.62 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosatwork(withanoutward-facingcamera)combined} \\ 
+26 & username for websites & 73.44 & 0.83 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourusernameforwebsitescombined} \\ 
+27 & address & 72.61 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouraddresscombined} \\ 
+28 & audio recording you captured & 72.55  & 0.70 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedaudiorecordingsyoumadeonyourdevicecombined} \\ 
+29 & photo of you off-guard & 72.55 & 0.77 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookaphotoofyouoff-guardcombined} \\ 
+30 & photo downloaded from internet & 71.81 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoudownloadedfromtheinternetsavedonyourdevicecombined} \\ 
+31 & photo others sent you & 71.63 & 1.03 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosotherssenttoyousavedonyourdevicecombined} \\ 
+32 & video others sent you & 70.59 & 0.81 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosotherssentyousavedonyourdevicecombined} \\ 
+33 & video of your work or workplace & 70.54 & 0.90 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosatwork(withanoutward-facingcamera)combined} \\ 
+34 & fingerprint & 70.12 & 0.86 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourfingerprintsomehowcombined} \\ 
+35 & when you were lying nervous or stressed & 69.74 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerelyingnervousorstressedcombined} \\ 
+36 & audio recording of you (voice notes) & 69.59 & 0.91 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedyoutalkingtoyourself(makingvoicenotes)combined} \\ 
+& vdots & & & \\
 \hline
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix [?].}
-\label{top10-table}
+\caption{VUR for all data types, across all recipients.}
+\label{full-vur-table}
 \end{center}
 \end{table*}
+
+\begin{table*}[t]
+\begin{center}
+\small
+\begin{tabular}{| r | l | r | r | r | r |}
+\hline
+Rank & Question & VUR & $\sigma$ & Distribution \\
+\hline
+& \vdots & & & \\
+37 & medication taken & 69.49 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatmedicationyoutakecombined} \\ 
+38 & videos already on device & 68.89 & 0.88 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoutookwhicharealreadyonyourdevicecombined} \\ 
+39 & photo of your signature & 68.07 & 0.84 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookapictureofyoursignaturecombined} \\ 
+40 & web history & 66.44 & 1.01 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatwebsitesyougotocombined} \\ 
+41 & photos taken on device & 66.21 & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedphotosyoutookwhicharealreadyonyourdevicecombined} \\ 
+42 & home address & 65.0 & 0.97 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyoulivesomehowcombined} \\ 
+43 & fine-grained location tracking (+/- cm) & 63.51 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouareveryaccurately(whereyouareinaroom)combined} \\ 
+44 & photo of people at random & 61.94 & 1.06 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookphotosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
+45 & video downloaded from the internet & 61.49 & 1.00 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/sharedvideosyoudownloadedontheinternetsavedonyourdevicecombined} \\ 
+46 & when you are alone & 61.27 & 0.99 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowmuchyouspendtimealonecombined} \\ 
+47 & location tracking (+/- m) & 61.24 & 1.08 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/trackedwhereyouare(likeaGPS)combined} \\ 
+48 & videos of people at random & 61.04 & 0.95 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/tookvideosofpeople(withanoutward-facingcamera)atrandomcombined} \\ 
+49 & where you are currently going & 60.87 & 0.97 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouarecurrentlygoingcombined} \\ 
+50 & recording of sound around you & 60.45 & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/recordedthesoundaroundyoucombined} \\ 
+51 & people you spend time with & 60.0 & 1.13 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhoyouwerespendingtimewithcombined} \\ 
+52 & workplace address & 58.09 & 1.16 &\includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhereyouworksomehowcombined} \\ 
+53 & sounds on device (notifications, etc) & 54.4 & 1.29 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedsoundssavedonyourdevice(notificationnoisesetc)combined} \\
+54 & phone usage & 51.95 &1.22 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourphonecombined} \\ 
+55 & purchased products & 50.0 & 1.09 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhatproductsyoubuycombined} \\ 
+56 & when you are sick or healthy & 48.17  & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouaresickorhealthycombined} \\ 
+57 & how close you are to interacting people & 46.98 & 1.12 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowcloseyouaretootherpeopleyouinteractwithcombined} \\ 
+58 & feelings (based on biometrics) & 46.81 & 1.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowyouwerefeelingbasedonheartratebreathingandortemperaturecombined} \\
+59 & computer usage & 44.93 & 1.16 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedhowmuchyouuseyourcomputercombined} \\ 
+60 & eating patterns & 42.86 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowmuchandwhatyouareeatingcombined} \\ 
+61 & name & 42.54 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyournamecombined} \\ 
+62 & sleeping patterns & 40.56 & 1.34 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenandhowwellyouaresleepingcombined} \\ 
+63 & eye patterns (for eye tracking) & 40.51 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\ 
+64 & exercise patterns & 38.66 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenhowandhowmuchyouexercisecombined} \\ 
+65 & when you are happy or having fun & 34.75 & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouwerehappyorhavingfuncombined} \\ 
+66 & television shows watched & 30.2 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhattelevisionshowsyouwatchcombined} \\ 
+67 & when you are busy or interruptible & 29.5 & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedwhenyouarebusyorinterruptiblecombined} \\ 
+68 & music on device & 28.06 & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/copiedanduploadedmusicfromyourdevicecombined} \\ 
+69 & heart rate & 27.5 & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourheartratecombined} \\ 
+70 & age & 24.29 & 1.43 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyouragecombined} \\ 
+71 & language spoken & 15.86 & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedthelanguageyouwerespeakingcombined} \\ 
+72 & gender & 15.0 & 1.46 &  \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/table-images/learnedyourgendercombined} \\ 
+\hline
+\end{tabular}
+\caption{VUR for all data types, across all recipients.}
+\label{full-vur-table}
+\end{center}
+\end{table*}

### 2015-03-07 tex-inputs/results-techrank.tex
final version

@@
 We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}).
-Appendix ~\ref{sec:riskben-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
+Tables \ref{risk} and \ref{benefit} in Appendix ~\ref{sec:concerns-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
 We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.

### 2015-03-07 tex-inputs/results-type.tex
final version

@@
 Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect on participants' VURs stemmed from the type of data being shared; data recipient and device type had weaker impacts on overall VURs.
-The most and least concerning data types are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.
+The most and least concerning data types are listed in Table \ref{top10-table}, and the full list can be seen in Table \ref{full-vur-table} in Appendix \ref{sec:concerns-appendix}.
 

### 2015-04-13 tex-inputs/intro.tex
remove low-quality news citations/superfluous citations (there was almost two pages of citations..)

@@
 For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public backlash may have partly contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.
 
-Similar privacy~\cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues~\cite{enck2011study, felt2011survey} pervade smartphones.
+Similar privacy and security issues pervade smartphones.
 Mobile platforms have tried to address the risks by communicating data capture to users.

### 2015-04-13 tex-inputs/methodology.tex
remove low-quality news citations/superfluous citations (there was almost two pages of citations..)

@@
 To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
-At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns~\cite{6_fitbit_2014, 7_time_2014}; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}; and Google Glass~\cite{11_wikipedia_2015, 12_turi_2014}.
+At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
+%~\cite{6_fitbit_2014, 7_time_2014}
+the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
+and Google Glass %~\cite{11_wikipedia_2015, 12_turi_2014}. 
 We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.

### 2015-04-13 tex-inputs/abstract.tex
abstract readthrough and edits

@@
 \begin{abstract}
-Wearable devices bring great benefits but also new potential privacy and security risks that could expose users' activities without their awareness or consent.
-Effective design of notifications and security controls for wearable devices will require careful foresight to prevent habituation by treating user attention as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
-In this paper, we describe a large-scale survey that we conducted to investigate user security and privacy concerns regarding wearable devices.
-We surveyed 1,782 Internet users about their perceptions of wearable devices, in order to identify risks that are particularly concerning to users.
-We specifically controlled for the effects of data type and data recipient on the magnitude of perceived risks, while also collecting open-ended concerns.
-Finally, we compared wearable device risks to those of more familiar technologies.
+Wearable devices bring great benefits but also new potential risks that could expose users' activities without their awareness or consent.
+Effective design of notifications and security controls for wearable devices require careful foresight to prevent habituation and informing users about risks which are the most concerning.
+In this paper, we describe a large-scale survey conducted to investigate user security and privacy concerns regarding wearable devices.
+We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to users; these risks are inspired by the popular current wearable technologies' permissions and capabilities.
+During this experiment, we specifically control for the effects of data being shared and with whom the data is being shared with to determine their effects on the magnitude of perceived risks.
+We also investigate how these emergent threats compare to existent mobile threats, how upcoming capabilities and artifacts compare to existing technologies, and cover technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
 We hope that this work will inform design of future privacy and security controls for wearable devices.

### 2015-04-13 tex-inputs/intro.tex
use PETS formatting; little intro tweaks

@@
 
-Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
+Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} with a promising future.
+52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
 With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
+Wearable devices enable many benefits, ranging from interaction with virtual objects in an augmented reality world to healthier, fitness-data inspired lifestyles.
 
-% Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''
-
-Wearable devices offer many compelling opportunities for benefiting users.
-For instance, they could enable more natural, human-centered interface experiences and healthier, fitness-data inspired lifestyles.
-There will likely be many more applications in the future that take advantage of data captured by wearable devices.
 However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.

### 2015-04-13 tex-inputs/intro.tex
intro rewording

@@
 However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
-Even though wearable technology is currently in early stages, we have already seen manifestations of these risks.
-For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
-Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public backlash may have partly contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.
+Although wearable devices are still in their infancy, we have already seen manifestations of these risks.
+Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}; public backlash due to privacy concerns may have contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.
 
-Similar privacy and security issues pervade smartphones.
-Mobile platforms have tried to address the risks by communicating data capture to users.
+Similar issues pervade mobile platforms.
+Generally, risks are addressed by communicating data capture to users.
 However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}.
@@
 
-With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data is captured \cite{denning2014situ}.
-However, the possible data types that these devices will be able to capture is likely to dwarf those currently captured by smartphones.
-Because human attention is a finite resource \cite{bohme2011security}, bombarding users with notifications for every conceivable data capture is likely to be counter-productive as it can lead to user frustration and habituation.
-Therefore, user concerns need to be investigated so that systems can warn users only about the situations they are likely to care about.
+The data captured by powerful, ubiquitous, and increasingly popular wearables will dwarf data currently captured by smartphones.
+It is known that subjecting users with increased notifications for every conceivable data capture has shown to be negatively impactful on security, as it can lead to user frustration and habituation \cite{bohme2011security}.
+An understanding of user concerns allow for targeted, effective, and non-compromising communication with the user.
+Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured \cite{denning2014situ}.
+Our study focuses on the first-person user of wearable device rather than the bystander, and explores what users would like notifications about on a large scale.
 
-The goal of this work is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications.
+The goal of this work is to shape the still-malleable future of wearables platforms and interaction models with research on user-centric concerns.
 To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
-We surveyed 1,782 Internet users about their perceptions of wearable devices and contribute the following: %\\[-0.8cm]
+Our survey 1,782 Internet users and contributes the following: %\\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We compare users' perceptions of a range of privacy and security risks of wearables. We found that user concern is driven more by the type of data being captured than the recipient of the data.
-\item We shed light on how users feel about various data recipients.
-We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers (the latter is viewed as less concerning).
-\item We analyze users' self-reported top concerns regarding wearable devices.
-The results give a sense of what broad concerns users have, which can be used to guide future research on unexplored use cases.
-\item We examine how serious users perceive the risks of wearables to be, compared to risks associated with more familiar technologies.
-Most of our participants saw wearables' new capabilities as benign, though we suspect that this could be due to a lack of exposure to these newer technologies.
+\item We report how 72 types of data likely captured by wearable devices were perceived by our participants and rank them by relevance. 
+\item We repeat this across 4 possible recipients to also illustrate the contribution of the data recipient to the overall perceived risk. 
+\item We sketch a landscape of users' self-reported concerns regarding wearable devices, spanning concerns outside of security and privacy. 
+\item We compare emergent risks with existing risks to find that participants perceive risk in capabilities comparable to physical risk--for instance, facial detection was perceived as risky as a lawnmower.
 \end{itemize}

### 2015-04-13 tex-inputs/related_work.tex
related work

@@
 %We discuss related work that has examined users' perceptions surrounding security and privacy risks.
-In this section, we outline previous research that has examined privacy for ubiquitous and wearable computing environments, smartphone privacy and security, as well as user risk perceptions and behaviors.
+In this section, we outline previous research examining privacy in wearable computing environments, smartphone privacy and security, as well as user risk perceptions and behaviors.
 
-\subsection{Ubiquitous and Wearable Devices}
-Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+\subsection{Wearables and Privacy}
+We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
+
 Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
 Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
-However, none of these works attempted to quantify or rank user concern over different privacy risks.
+Our work aims to augment works like these with an understanding of what privacy means to the end user.
 
-Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
-A small-scale interview of how bystanders feel about wearable devices found that bystanders were predominantly split between having indifference and negative reactions to the device, but expressed clear interest in being able to give permission for data to be captured~\cite{denning2014situ}.
-Our research furthers this goal of communicating risks to users and bystanders.
+\subsection{Lessons form Smartphones}
+Research shows that perceptions of risk change based on the particular device being used.
+Chin {\it et al.}\ found that users' attitudes toward security and privacy for smarphones significantly differed from attitudes towards traditional computing systems, stemming from differences in how people used these systems ~\cite{chin2012measuring}.
+Undoubtedly, this will hold true for wearables as well as wearables have a sparse, world-driven interaction model.
 
-\subsection{Smartphones}
-Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones.
-Research shows that perceptions of risk change based on the particular device being used.
-Chin {\it et al.}\ found that users' attitudes toward security and privacy for smarphones significantly differed from attitudes towards traditional computing systems~\cite{chin2012measuring}.
-How people used their smartphones also differed from how they used other computing systems.
-Palen {\it et al.}\ tracked smartphone users for six weeks and observed radical changes with respect to how they used their devices~\cite{palen2000going}.
-People also perceive and behave without a realistic understanding of the risks they are taking.
-Felt {\it et al.}\ examined the Android permission system and found that 17\% of participants paid attention to permission requests, and only 3\% comprehended what these permissions meant.
+%% LL: None of this seems that relevant! :( I was just citing things to cite them.. find better things to say.
 
-Smartphones allow applications to access new types of data.
+%Palen {\it et al.}\ tracked smartphone users for six weeks and observed that people also perceive and behave without a realistic understanding of the risks they are taking ~\cite{palen2000going}; Felt {\it et al.}\ examined the Android permission system and found that 17\% of participants paid attention to permission requests, and only 3\% comprehended what these permissions meant.
+For these reasons, we need to
+
+%Smartphones allow applications to access new types of data.
 While this tends to benefit users, they do not think of the privacy implications.
 Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
+
+%There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
+
 Tsai {\it et al.}\ found that when mobile users get feedback about releasing data, such as who has viewed location information, it greatly impacts future behaviors~\cite{Tsai2009}.
-However, this type of feedback is not generally provided to users.
-There are still many unresolved concerns, such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
+Although this type of feedback is not provided to smartphone users, there is potential for impacting wearables users and shaping their behaviors so that they keep users safe.
 
-\subsection{User Perceptions and Behaviors}
-In this paper, we focus on measuring user perceptions of security and privacy risks, as they relate to wearable devices.
-One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and stated privacy preferences~\cite{spiekermann2001privacy}.
-
+\subsection{User Perceptions}
 While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
@@
 While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
+
+One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
+Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
+However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.

### 2015-04-13 tex-inputs/abstract.tex
discussion and conclusion redo

@@
 \begin{abstract}
-Wearable devices bring great benefits but also new potential risks that could expose users' activities without their awareness or consent.
+\indent\indent Wearable devices bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
 Effective design of notifications and security controls for wearable devices require careful foresight to prevent habituation and informing users about risks which are the most concerning.
@@
 We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to users; these risks are inspired by the popular current wearable technologies' permissions and capabilities.
-During this experiment, we specifically control for the effects of data being shared and with whom the data is being shared with to determine their effects on the magnitude of perceived risks.
-We also investigate how these emergent threats compare to existent mobile threats, how upcoming capabilities and artifacts compare to existing technologies, and cover technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
+During this experiment, we  determine the roles of the data being collected and with whom the data is being shared with through specifically controlling for these effects in our questions.
+We also investigate how these emergent threats compare to existent mobile threats, how upcoming capabilities and artifacts compare to existing technologies, and how users rank technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
 We hope that this work will inform design of future privacy and security controls for wearable devices.

### 2015-04-13 tex-inputs/conclusion.tex
discussion and conclusion redo

@@
 
-Our survey of 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices.
-We identify that participants are most concerned about protecting their financial information, photos, or videos and least concerned about demographic or biometric data.
-We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients.
-Participants' self-reported concerns of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions.
-We perform two regression model analyses with respect to the type of data and the associated risks to verify our results.
-
-%commented out for anonymity
-
-%\section{Research Ethics} 
-%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study.
-Survey data was collected in an anonymous manner.
-Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.
-
-%\section{Acknowledgments}
-%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research.
-Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings.
-Many thanks go out to the many generous colleagues who have provided feedback and encouragement.
+Wearables are still in their infancy.
+Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
+However, there is not much work done to determine which threats in the emerging threat landscape are pertinent to focus on.
+Our survey of 1,784 Internet users, is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
+Inspection of possible data concerns agree with previous studies of smartphone studies to find that video capture and financial data to be most sensitive.
+This suggests that these risks should be highlighted by platform developers.
+Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
+We calibrate our results with mobile devices and existing technologies; additionally, we verify with an open-ended question and find that privacy and security are at the top of user's overall concerns, over fashion, safety, and health concerns.
+We hope that this work has given a comprehensive overview of user concerns with respect to wearables, and inform designs of future privacy and security controls for wearable devices.

### 2015-04-13 tex-inputs/discussion.tex
discussion and conclusion redo

@@
 Adding additional recipients, such as ``advertisers'' or ``acquaintances'' may lead to more nuanced results.
-Additionally, the open-ended concerns are inspiration for future research: addressing the high financial costs of wearables, communicating the reality of health concerns from constant use, creating distraction-free interfaces to prevent safety issues, minimizing negative social impacts of wearable device use, and improving device aesthetics.
-
-Wearables are still in their infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, pursuant to previous studies of smartphone risk perceptions, our participants found embarrassing videos and risks involving financial losses to be the most sensitive, which suggests that these risks should be highlighted by platform developers.
-Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
+Additionally, the open-ended concerns illuminate areas of possible future research, such as communication and minimization of health effects from use, designing distraction-free interfaces to prevent safety issues, and minimizing negative social impacts during use.

### 2015-04-13 tex-inputs/methodology.tex
discussion and conclusion redo

@@
 To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
-At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
+At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
 %~\cite{6_fitbit_2014, 7_time_2014}
 the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
-and Google Glass %~\cite{11_wikipedia_2015, 12_turi_2014}. 
-We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.
+and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. %~\cite{11_wikipedia_2015, 12_turi_2014}. 
+These devices' capabilities and requested permissions as inspiration to develop a list of possible security and privacy risks that users will encounter in use.
 
-We designed a survey to gauge what risks users consider to be relevant.
+We designed a survey to gauge the relevancy of all these possible risks.
 Our survey contained two main sections.
-In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
+A set of questions presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
 This was intended to elicit their perception of the severity and impact of the risk.
 The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}.
-In the other section, we asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
+Another set asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
 %Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
@@
 \subsection{Motivation}
-In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of more general technology-based risk perceptions~\cite{Fischhoff}.
+In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of a wide range of general technology-based risk perceptions~\cite{Fischhoff}.
 
@@
 \subsection{Survey Questions}
-In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]
+\noindent Each participant answered 27 questions across 5 sections:   \\[-.5cm]
 

### 2015-04-13 tex-inputs/methodology.tex
look over methodology

@@
 \item 2 Fischhoff-style risk/benefit questions 
-\item 15 demographic questions \\[-.8cm]
+\item 15 demographic questions %\\[-.8cm]
 \end{itemize}
@@
 
-To ensure that participants had read and understood this device's capabilities, since it would form the basis for many of our survey questions, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn.
-We filtered out responses from participants who could not answer these questions.
+This device would form the basis for many of our survey questions.
+To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn.
+We filter out responses from participants who could not answer these questions.
 
 \subsubsection{Wearable Scenarios}
-We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
+We present scenarios involving data captured by the Cubetastic3000 and ask participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
 Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
@@
 
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): \\[-.8cm]
+We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): %\\[-.8cm]
 
@@
 \item The public
-\item The app's server (but didn't share it with anyone else)\\[-.8cm]
+\item The app's server (but didn't share it with anyone else) %\\[-.8cm]
 \end{packed_item}
@@
 Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
+
+\begin{quotation}
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 \end{enumerate}
+\end{quotation}
 
@@
 \subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
-These technologies were chosen to span varying levels of risks and benefits.
+In addition to investigating reactions to particular scenarios, we examine broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
+We model this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
+We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
+These technologies are chosen to span varying levels of risks and benefits.
 
-Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-We asked about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
-
-%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
-%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.
+Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
+To do this, we ask participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies.
+The 20 technologies are: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
 
@@
 
-\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]
+\begin{quotation}
+{\it \noindent Fill in your <risk/benefit> numbers for the following:\\
 
-\textit{Handguns}: \_\_\_\_\_\_\_ \\
-\textit{Motorcycles}: \_\_\_\_\_\_\_\\
-\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
-\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
-\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]
+\noindent Handguns: \_\_\_\_\_\_\_ \\
+Motorcycles: \_\_\_\_\_\_\_\\
+Lawnmowers: \_\_\_\_\_\_\_\\
+<Wearable Technology>: \_\_\_\_\_\_\_\\
+Electricity: \_\_\_\_\_\_\_\\ }
+\end{quotation}
 

### 2015-04-15 tex-inputs/results-intro.tex
small changes

@@
+%!TEX root = ../paper.tex
 \section{Results}
-In this section, we present participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to their risk perceptions.
-Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
+In this section, we present participants' responses to the various data-sharing scenarios, and discuss how and which various factors contributed to their risk perceptions.
+We also discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
 We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
@@
 \subsection{Concern Factors}
-Many factors impact participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of the factors, including demographic traits.
+Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question.
+We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of the above factors and additional demographic traits.

### 2015-04-15 tex-inputs/results-type.tex
broken link and caption fix
small changes

@@
 
-Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect on participants' VURs stemmed from the type of data being shared; data recipient and device type had weaker impacts on overall VURs.
+Based on our statistical models (later reported in Section \ref{sec:regression}), we observe that the largest effect on participants' VURs stemmed from the data being shared; with whom the data is shared and which device the user is interacting with had weaker impacts on overall VURs.
 The most and least concerning data types are listed in Table \ref{top10-table}, and the full list can be seen in Table \ref{full-vur-table} in Appendix \ref{sec:concerns-appendix}.
@@
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix \ref{sec:data-appendix}.}
+\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix \ref{sec:concerns-appendix}.}
 \label{top10-table}

### 2015-04-15 tex-inputs/results-devices.tex
small tweaks to device section

@@
 \subsubsection{Device}
-Recall that each participant answered 2 questions drawn from a set of 5 regarding their reactions to smartphone misbehaviors.
-To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same 5 questions amongst the pool of 293 Cubetastic3000 scenarios, only modifying the device type.
-In this manner, while all 1,782 participants received 2 smartphone questions, there were 159 participants who received at least one of these questions in relation to the Cubetastic 3000.
+Recall that each participant answered two questions drawn from a set of five smartphone misbehaviors.
+To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, only modifying the device in question.
+In this manner, while all 1,782 participants received two smartphone questions, there were 159 participants who received at least one of these questions in relation to the Cubetastic3000.
 Across all participants, the VUR was 46.7\% (of 1,782) when describing smartphones, whereas the VUR increased to 58.8\% (of 159) when describing these same misbehaviors on the Cubetastic3000.
@@
 To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
-This difference was statistically significant ($U=108,664.0$ with $p<0.0005$), however, the effect size was very small ($r=0.08$).
-Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the 5 misbehaviors.
-We conclude that while in general users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, the difference is likely negligible.
-The entire effect may be due to participants' increased familiarity with smartphones, and therefore may disappear as they increasingly encounter more wearable devices.
+This difference is statistically significant ($U=108,664.0$ with $p<0.0005$), however, the effect size is very small ($r=0.08$).
+Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the five misbehaviors.
+We conclude that users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, but thig difference is likely negligible.
+The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearable devices.
 

### 2015-04-15 tex-inputs/results-recipient.tex
final version
small tweaks to device section

@@
 \subsubsection{Data Recipient}
-There was a statistically significant difference in VUR for data sent to an application's servers compared to data sent to human recipients.
+A statistically significant difference in VUR exists between data shared with an application versus data shared with human recipients.
 On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were almost double (Table \ref{recipient-vur}).
@@
 Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.
+Our results motivate mechanisms which allow for data taint tracking or mechanisms which prevent accidental data sharing.
 
-We do not claim that there are no distinctions between the friends, public, and work contact recipients.
-People are more comfortable sharing certain data types with certain human data recipients.
+However, we do not claim that there are no distinctions between the friends, public, and work contact recipients.
+People are more comfortable sharing certain data types with certain human recipients.
 For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.
-Participants were much more comfortable sharing phone use and products purchased with an application server than with human recipients.
-Appendix \ref{sec:recipient-appendix} shows the  complete VUR and rankings of all data types by recipient.
+Table \ref{all-vur} Appendix \ref{sec:concerns-appendix} shows the  complete VUR and rankings of all data types by recipient.
 

### 2015-04-15 tex-inputs/abstract.tex
Cleaned up language

@@
 \indent\indent Wearable devices bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
-Effective design of notifications and security controls for wearable devices require careful foresight to prevent habituation and informing users about risks which are the most concerning.
+Effective design of notifications and security controls for wearable devices require careful foresight to prevent habituation and informing users about risks with which they are likely to be concerned.
 In this paper, we describe a large-scale survey conducted to investigate user security and privacy concerns regarding wearable devices.
-We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to users; these risks are inspired by the popular current wearable technologies' permissions and capabilities.
-During this experiment, we  determine the roles of the data being collected and with whom the data is being shared with through specifically controlling for these effects in our questions.
-We also investigate how these emergent threats compare to existent mobile threats, how upcoming capabilities and artifacts compare to existing technologies, and how users rank technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
-We hope that this work will inform design of future privacy and security controls for wearable devices.
+We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to them; these risks are inspired by the capabilities of popular wearable technologies.
+During this experiment, our questions controlled for the effects of what data was being accessed and with whom it was being shared.
+We also investigated how these emergent threats compared to existent mobile threats, how upcoming capabilities and artifacts compared to existing technologies, and how users ranked technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
+We hope that this work will inform the design of future privacy and security controls for wearable devices.
 \end{abstract}

### 2015-04-15 tex-inputs/results-techrank.tex
tweaks to riskben

@@
 
-We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits.
-We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we also asked about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We found that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}).
+We ask participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their  benefits and risk.
+We also ask them about technologies with which they were likely to be more familiar (e.g., smartphones and laptops) and two specific wearable devices, Google Glass and the fictitious Cubetastic3000.
+To calibrate our results, we  ask about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
+We find that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}).
 Tables \ref{risk} and \ref{benefit} in Appendix ~\ref{sec:concerns-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
-We found that the calibration technologies, which were more familiar to the participants, were all rated as the most risky.
-
-As a group, participants rated more familiar technologies as more beneficial.
-We believe this is the result of exposure to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
-It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
-Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others.
-However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
-
-Of the wearable technologies, the riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
-We did not test the differences in risk between the different wearable-related technologies for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
-Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.
 
@@
 We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities and that performing this experiment longitudinally may yield more interesting results, as these technologies become pervasive (and more familiar to participants).
+
+As a group, participants rated more familiar technologies as more beneficial.
+We believe this is the result of exposure to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
+It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
+Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others.
+However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
+
+We find that the more familiar a participant was with a technology, the more likely they were to rate it as risky.
+Again, we believe that this is due to the exposure to these technologies.
+Of the wearable technologies, the riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
+We did not test the differences in risk between the different wearable-related technologies for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
+Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.

### 2015-04-15 tex-inputs/results-openended.tex
tweaks to open-ended

@@
 \subsection{Open-Ended Concerns for Wearables}
-We captured participants' general reactions to wearable devices as a whole by asking the following open-ended question:
+We captured participants' reactions to wearable devices as a whole by asking the following open-ended question:
 
-\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]
+\begin{quotation}
+\noindent
+\textit{What do you think are the most likely risks associated with wearable devices?}
+\end{quotation}
 
@@
 In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware).
-Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions that cause car accidents (Safety), resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).
+Other orthogonal concerns included long-term health effects caused from wearing the device such as cancer from EMF waves (Health) and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).
+Interestingly, participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
 

### 2015-04-15 tex-inputs/results-openended.tex
more small changes

@@
 
-This question was asked along with demographics questions (but before any IUIPC questions, which asked a lot of direct privacy-related questions, to avoid biasing the recipients).
+This question was asked with demographics questions, but before any IUIPC questions (which asked a lot of direct privacy-related questions, to avoid biasing the recipients).
 The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

### 2015-04-15 tex-inputs/results-regression.tex
more small changes

@@
 \label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
-We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
+In order to examine the relative effect of each factor on participants' VURs, we construct several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
+We perform binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
 
@@
 
-We created several models using two independent variables as predictors: data and recipient.
-Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients.
+We create several models using two independent variables as predictors: data and recipient.
+Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) is only varied for the five smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients.
 We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
@@
 
-With regard to data types, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%).
-Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data.
+With regard to data types, the most concerning type of data is video (78.0\%), which was ranked similarly to photos (76.2\%).
+Next are audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data.
 We suspect that demographic data was more concerning because it included information such as a Social Security Number, bank account information, and other financial information.
@@
 We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data.
-One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data are stolen and abused.
+One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data is stolen and abused.
 
@@
 When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.
-The full model can be found in Appendix \ref{sec:regression-apx2}.
+%The full model can be found in Appendix \ref{sec:regression-apx2}.

### 2015-04-15 tex-inputs/intro.tex
Fixed more grammar

@@
 
-Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} with a promising future.
-52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
+Wearable technologies, or ``wearables,'' are a \$700 million industry with a promising future~\cite{cmo}.
+Recent surveys indicate that 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
 With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
@@
 Although wearable devices are still in their infancy, we have already seen manifestations of these risks.
-Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information.
+Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}.
 Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}; public backlash due to privacy concerns may have contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.
@@
 The data captured by powerful, ubiquitous, and increasingly popular wearables will dwarf data currently captured by smartphones.
-It is known that subjecting users with increased notifications for every conceivable data capture has shown to be negatively impactful on security, as it can lead to user frustration and habituation \cite{bohme2011security}.
+It is known that subjecting users with increased notifications for every conceivable data capture has shown to be negatively impactful on security, as it can lead to user frustration and habituation~\cite{bohme2011security}.
 An understanding of user concerns allow for targeted, effective, and non-compromising communication with the user.
-Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured \cite{denning2014situ}.
-Our study focuses on the first-person user of wearable device rather than the bystander, and explores what users would like notifications about on a large scale.
+Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured~\cite{denning2014situ}.
+Our study focuses on the users of wearable devices rather than bystanders, and explores what users would like notifications about on a large scale.
 
-The goal of this work is to shape the still-malleable future of wearables platforms and interaction models with research on user-centric concerns.
+The goal of this work is to shape the still-malleable future of wearable platforms and interaction models, with research on user-centric concerns.
 To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
-Our survey 1,782 Internet users and contributes the following: %\\[-0.8cm]
+Our survey of 1,782 Internet users contributes the following: %\\[-0.8cm]
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We report how 72 types of data likely captured by wearable devices were perceived by our participants and rank them by relevance. 
+\item We report how 72 types of data likely to be captured by wearable devices were perceived by our participants and rank them by relevance. 
 \item We repeat this across 4 possible recipients to also illustrate the contribution of the data recipient to the overall perceived risk. 
 \item We sketch a landscape of users' self-reported concerns regarding wearable devices, spanning concerns outside of security and privacy. 
-\item We compare emergent risks with existing risks to find that participants perceive risk in capabilities comparable to physical risk--for instance, facial detection was perceived as risky as a lawnmower.
+\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as a lawnmower.
 \end{itemize}

### 2015-04-15 tex-inputs/discussion.tex
add to discussion section

@@
 
-%\subsection{Limitations}
+\subsection{Limitations}
 One of the limitations is that our participants might not have interest in or knowledge of wearables and their respective capabilities, since 83\% of our participants reported that they do not own a wearable.
@@
 
-%\subsection{Future Research Directions}
+\subsection{Future Research Directions}
+We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications.
+We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourage work for contextual and user-input- independent permission models and access control schemes.
+
 Further work can be done to expand various aspects of this study.
@@
 Adding additional recipients, such as ``advertisers'' or ``acquaintances'' may lead to more nuanced results.
-Additionally, the open-ended concerns illuminate areas of possible future research, such as communication and minimization of health effects from use, designing distraction-free interfaces to prevent safety issues, and minimizing negative social impacts during use.
+Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impacts during use.

### 2015-04-15 tex-inputs/abstract.tex
intro rewording

@@
 \begin{abstract}
-\indent\indent Wearable devices bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
-Effective design of notifications and security controls for wearable devices require careful foresight to prevent habituation and informing users about risks with which they are likely to be concerned.
-In this paper, we describe a large-scale survey conducted to investigate user security and privacy concerns regarding wearable devices.
-We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to them; these risks are inspired by the capabilities of popular wearable technologies.
+\indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
+In this paper, we report findings from the first large-scale survey conducted to investigate user security and privacy concerns regarding wearables.
+We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to them; these risks are inspired by the sensor inputs and applications of popular wearable technologies.
 During this experiment, our questions controlled for the effects of what data was being accessed and with whom it was being shared.
 We also investigated how these emergent threats compared to existent mobile threats, how upcoming capabilities and artifacts compared to existing technologies, and how users ranked technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
-We hope that this work will inform the design of future privacy and security controls for wearable devices.
+We hope that this work will inform the design of future user notification, permission management, and access control schemes for wearables.
 \end{abstract}

### 2015-04-15 tex-inputs/appendixes.tex
intro rewording

@@
 (e.g.
-for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]
+for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.}
 
@@
 But evaluating such risks is not your present job.
-Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]
+Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.}
 
@@
 (e.g.
-for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]
+for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.}
 
@@
 But evaluating such benefits is not your present job.
-Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]
+Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.}
 

### 2015-04-15 tex-inputs/intro.tex
intro rewording

@@
 
-Wearable technologies, or ``wearables,'' are a \$700 million industry with a promising future~\cite{cmo}.
-Recent surveys indicate that 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
+Wearables are a \$700 million, growing industry~\cite{cmo}.
 With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
+This trend will likely continue, as 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
+
 Wearable devices enable many benefits, ranging from interaction with virtual objects in an augmented reality world to healthier, fitness-data inspired lifestyles.
-
 However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
@@
 Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}.
-Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}; public backlash due to privacy concerns may have contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.
+Google Glass has since been discontinued.
 
-Similar issues pervade mobile platforms.
-Generally, risks are addressed by communicating data capture to users.
+For smartphones, security and privacy risks are generally addressed by communicating data capture to users.
 However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}.
@@
 
-The data captured by powerful, ubiquitous, and increasingly popular wearables will dwarf data currently captured by smartphones.
-It is known that subjecting users with increased notifications for every conceivable data capture has shown to be negatively impactful on security, as it can lead to user frustration and habituation~\cite{bohme2011security}.
-An understanding of user concerns allow for targeted, effective, and non-compromising communication with the user.
+Wearables' sensor capabilities, continuous access, and ubiquitous presence will result in a firehose of familiar and unfamiliar types of data, at rate which will likely dwarf the amount of data currently captured by smartphones.
 Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured~\cite{denning2014situ}.
-Our study focuses on the users of wearable devices rather than bystanders, and explores what users would like notifications about on a large scale.
+However, subjecting people with increased notifications is not a sound option, as it has shown to lead to negatively impactful effects such as frustration and habituation~\cite{bohme2011security}.
+An understanding of user concerns may allow for targeted and effective communication with the user, inform design of future permission systems, or provide insight for access control mechanisms.
 

### 2015-04-15 tex-inputs/methodology.tex
killed an orphan

@@
 
-\subsection{Motivation}
+\subsection{Related Work}
 In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of a wide range of general technology-based risk perceptions~\cite{Fischhoff}.
@@
 \subsubsection{Technology Risk Perceptions}
-Fischhoff \etal performed a seminal study of the perceived risks surrounding 30 widely used technologies~\cite{Fischhoff}.
-In their study, participants were asked to separately rate the risks and benefits for these technologies.
-They told participants to think about all people affected by the technology, and to think about long-term versus short-term risks and benefits.
-Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate the perceived risks and benefits of several technologies related to wearable computing and how these technologies compared to more familiar technologies.
+Fischhoff \etal performed a seminal study of the perceived risks and benefits surrounding 30 widely used technologies~\cite{Fischhoff}.
+Participants were asked to separately think of the risks then benefits, considering all people affected, long-term effects, and short term effects.
+Then, the participants respectively rated these technologies on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10).
+We apply their methodology to evaluate perceived risks and benefits of technologies related to wearable computing with respect to more familiar technologies.
 %Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

### 2015-04-15 tex-inputs/methodology.tex
more orphans dead

@@
 
-This device would form the basis for many of our survey questions.
-To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn.
+Since this device is basis for many of our survey questions, we ensure that participants had understood this device's capabilities by asking them two multiple-choice comprehension questions about the device's.
 We filter out responses from participants who could not answer these questions.
@@
 \subsubsection{Wearable Scenarios}
-We present scenarios involving data captured by the Cubetastic3000 and ask participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
+We present scenarios involving data captured by the Cubetastic3000 and ask participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
 Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
@@
 
+\begin{quotation}
+\noindent
 \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}
+\end{quotation}
 

### 2015-04-15 tex-inputs/results-demographics.tex
more orphans dead

@@
 
-The biggest demographic predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}.
+We see that privacy is a main concern for wearables users.
+Additionally, we show that privacy preferences should also be a consideration for configuring a user's device.
+A participant's self-reported level of privacy concerns is the biggest demographic predictor of participants' VUR rate.
+This is determined by the IUIPC scale~\cite{malhotra2004internet}.
 A Spearman correlation yielded a statistically significant effect between average IUIPC scores and VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences.
-Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$).
-We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.
+Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$).
+Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.
 
-While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs.
+While we initially observed an effect on VURs based on whether or not participants claimed to already own wearables (57.0\% vs.
 60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$).

### 2015-04-15 tex-inputs/conclusion.tex
all orphans dead

@@
 
+ Our survey of 1,784 Internet users, is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices.
+We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
+We calibrate our results with mobile devices and existing technologies; additionally, we verify with an open-ended question and find that privacy and security are at the top of user's overall concerns.
 Wearables are still in their infancy.
@@
 However, there is not much work done to determine which threats in the emerging threat landscape are pertinent to focus on.
-Our survey of 1,784 Internet users, is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
 Inspection of possible data concerns agree with previous studies of smartphone studies to find that video capture and financial data to be most sensitive.
-This suggests that these risks should be highlighted by platform developers.
 Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-We calibrate our results with mobile devices and existing technologies; additionally, we verify with an open-ended question and find that privacy and security are at the top of user's overall concerns, over fashion, safety, and health concerns.
-We hope that this work has given a comprehensive overview of user concerns with respect to wearables, and inform designs of future privacy and security controls for wearable devices.
+We also find that users' self-reported privacy preferences are correlated with how participants may react, even with respect to situations that they are unfamiliar with.
+Permissions and access control mechanisms which do not depend on user inputs can still benefit from being informed by user preferences.
+We hope that this work has given a comprehensive overview of user concerns and inform designs of future privacy and security work for wearable devices.

### 2015-04-15 tex-inputs/discussion.tex
all orphans dead

@@
 \subsection{Limitations}
-One of the limitations is that our participants might not have interest in or knowledge of wearables and their respective capabilities, since 83\% of our participants reported that they do not own a wearable.
-Participants may be over or underestimating the risk due to unawareness of what can be inferred from the data, not have an idea of how to rate a new technology with respect to familiar ones, or be more influenced by recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
+One of the limitations of our experiment is that our participants might not have interest or knowledge in wearables and their respective capabilities; 83\% of our participants reported that they do not own a wearable.
+Because of this, our participants may be over or underestimating the risk, stemming form an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
+Our participants also did not differentiate between the benefits of risks of various new capabilities.
 
@@
 Adding additional recipients, such as ``advertisers'' or ``acquaintances'' may lead to more nuanced results.
-Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impacts during use.
+Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impact.

### 2015-04-16 tex-inputs/intro.tex
Minor edits:

@@
 
-Wearables' sensor capabilities, continuous access, and ubiquitous presence will result in a firehose of familiar and unfamiliar types of data, at rate which will likely dwarf the amount of data currently captured by smartphones.
+Wearables' sensor capabilities, continuous access, and ubiquitous presence will result in a firehose of familiar and unfamiliar types of data, at a rate which will likely dwarf the amount of data currently captured by smartphones.
 Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured~\cite{denning2014situ}.
-However, subjecting people with increased notifications is not a sound option, as it has shown to lead to negatively impactful effects such as frustration and habituation~\cite{bohme2011security}.
+However, subjecting people to increased notifications is not a sound option, as it has shown to lead to negative effects, such as frustration and habituation~\cite{bohme2011security}.
 An understanding of user concerns may allow for targeted and effective communication with the user, inform design of future permission systems, or provide insight for access control mechanisms.
@@
 \item We report how 72 types of data likely to be captured by wearable devices were perceived by our participants and rank them by relevance. 
-\item We repeat this across 4 possible recipients to also illustrate the contribution of the data recipient to the overall perceived risk. 
+\item We repeat this across 4 types of recipients to also illustrate the contribution of the data recipient to the overall perceived risk. 
 \item We sketch a landscape of users' self-reported concerns regarding wearable devices, spanning concerns outside of security and privacy. 
-\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as a lawnmower.
+\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as using a lawnmower.
 \end{itemize}

### 2015-04-16 tex-inputs/methodology.tex
Minor grammatical changes

@@
 and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. %~\cite{11_wikipedia_2015, 12_turi_2014}. 
-These devices' capabilities and requested permissions as inspiration to develop a list of possible security and privacy risks that users will encounter in use.
+These devices' capabilities and requested permissions were our inspiration to develop a list of possible security and privacy risks that users will encounter.
 
@@
 
-Since this device is basis for many of our survey questions, we ensure that participants had understood this device's capabilities by asking them two multiple-choice comprehension questions about the device's.
-We filter out responses from participants who could not answer these questions.
+Since this device is the basis for many of our questions, we ensured that participants had understood its capabilities by asking them two multiple-choice comprehension questions.
+We filtered out responses from participants who could not answer these questions.
 
 \subsubsection{Wearable Scenarios}
-We present scenarios involving data captured by the Cubetastic3000 and ask participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
+We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) was shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
 Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
@@
 
-We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): %\\[-.8cm]
+We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions: %\\[-.8cm]
 
@@
 
-\begin{quotation}
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?
-\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
-\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
-\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
-\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
+\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
+\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
+\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
+\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
+\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
 \end{enumerate}
-\end{quotation}
 
@@
 \subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examine broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We model this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
+In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
+We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
 We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
-These technologies are chosen to span varying levels of risks and benefits.
+These technologies were chosen to span varying levels of risks and benefits.
 
 Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
-To do this, we ask participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies.
-The 20 technologies are: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
+To do this, we asked participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies.
+The 20 technologies were: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
 

### 2015-04-16 tex-inputs/discussion.tex
grammar checks and orphan killing

@@
 \subsection{Limitations}
-One of the limitations of our experiment is that our participants might not have interest or knowledge in wearables and their respective capabilities; 83\% of our participants reported that they do not own a wearable.
+One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable.
 Because of this, our participants may be over or underestimating the risk, stemming form an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.

### 2015-04-16 tex-inputs/methodology.tex
grammar checks and orphan killing

@@
 The exit portion of the survey contained demographic questions asking for age, gender, and education.
-We also asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices.
-We ended with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.
+We then asked about wearables ownership so we could control for prior exposure.
+An open-ended question on what would be the most likely risks associated with wearable devices was included to catch user concerns more broadly.
+To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes.
 
@@
 We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey.
-Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear.
+The focus group began with participants taking the survey then giving feedback on the format and the content, noting any instructions or questions that were unclear.
 The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
@@
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
-We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and three participants who were under 18, leaving us with a total sample size of 1,782.
+We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and three participants for being under 18, leaving us with a total sample size of 1,782.
 Of these, 57.9\% were male (1,031), 41.0\% were female (731), and 20 participants declined to state their genders.
@@
 Additionally, most people are likely to be upset, at least a little, in all scenarios, because a device is taking action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344).
-Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.
-However, one limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.
+Thus, the distinguishing factor is whether a participant was maximally upset, rather than if they were upset.
+A limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.
 

### 2015-04-16 tex-inputs/results-devices.tex
grammar checks and orphan killing

@@
 \subsubsection{Device}
-Recall that each participant answered two questions drawn from a set of five smartphone misbehaviors.
-To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, only modifying the device in question.
-In this manner, while all 1,782 participants received two smartphone questions, there were 159 participants who received at least one of these questions in relation to the Cubetastic3000.
-Across all participants, the VUR was 46.7\% (of 1,782) when describing smartphones, whereas the VUR increased to 58.8\% (of 159) when describing these same misbehaviors on the Cubetastic3000.
-The VURs for both devices for all 5 questions are in Table \ref{deviceVUR}.
+Each participant answered two questions drawn from a set of five smartphone misbehaviors.
+To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, modifying the device in question.
+In this manner, all 1,782 participants received two smartphone questions, while 159 participants received at least one of these five Cubetastic3000 misbehavior questions.
+Across all participants, the VUR was 46.7\% (of 1,782) for smartphones, whereas the VUR increased to 58.8\% (of 159) for same misbehaviors on the Cubetastic3000.
+The VURs for both devices for these questions are in Table \ref{deviceVUR}.
 
 To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
-This difference is statistically significant ($U=108,664.0$ with $p<0.0005$), however, the effect size is very small ($r=0.08$).
-Because of this small effect size, we did not further reduce our statistical power by separately comparing each of the five misbehaviors.
-We conclude that users are likely to be more wary of misbehaviors occurring on wearable devices than smartphones, but thig difference is likely negligible.
-The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearable devices.
+This difference is statistically significant ($U=108,664.0$ with $p<0.0005$) but the effect size is very small ($r=0.08$).
+Because of this, we did not further reduce our statistical power by separately comparing the five misbehaviors.
+We conclude that users are likely more wary of misbehaviors on wearables than smartphones, but this difference is likely negligible.
+The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearables.
 

### 2015-04-16 tex-inputs/results-regression.tex
Fixed broken reference
grammar checks and orphan killing

--- 2015-03-07 tex-inputs/results-regression.tex
@@
 We created several models using two independent variables as predictors: data and recipient.
-Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients.
-We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
+Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) is only varied for the five smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, resulting in a total of 72 types of data shared with 4 possible recipients.
+We used the following demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
 For each model, we performed Wald's test to examine the model effects attributable to each of these parameters.
-The only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other.
+The only covariates that had an observable effect on our models were participants' gender and IUIPC scores, which also exhibited an interaction effect with each other.
 Thus, we opted to remove the other covariates from our analysis.
 Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection that also accounts for complexity (lower relative values indicate better fit).
-As can be seen, the data type was the strongest predictor of VUR.
-The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.
+As shown, the type of data being shared (data type) was found to be the strongest predictor of a high VUR.
 
@@
 
-The data types fell into the following six possible categories:
+The data types fell into these six categories:
+
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 
-The risks for each data type fell into the following categories:
+The risks for data types fell into these five categories:
+
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]

### 2015-12-07 paper.tex
linda's push
formatting tweaks
restructuring latex and some discussion work
cleanup
started background and scoping; finished up a couple sections
redoing the intro
get rid of redundant files and confusing folders
started to work on VURcombined.pdf
tables whoop whoop
paper cleanup
abstract redo, intro tweaks, and much progress on data type results section
got rid of longtables madness
one table in appendix is still cut off.. give up for today.
tables inline and citing them
Added full regression model to Appendix
rough draft done
continue incorporating comments, upto 4.2
reorder appendixes
final

@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate-hotpets15}
 \usepackage{color}
 \usepackage[hyphens]{url}
+\usepackage{longtable}
+\usepackage{graphicx}
+\usepackage{enumitem}
+\usepackage{pdfpages}
 
@@
 \begin{document}
+\title{Risk Perceptions for Wearable Devices}
+%\numberofauthors{1}
+%\author{
+% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
+%   \vspace{0.5em}
+%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
+%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+%}
 
-\input{title.tex}
-\input{abstract.tex}
-\input{intro.tex}
-\input{methodology.tex}
-\input{results.tex}
-\input{discussion.tex} 
-\input{related_work.tex} 
-\input{conclusion.tex} 
+\numberofauthors{1}
+\author{
+ \alignauthor Anonymous\\
+   \vspace{0.5em}
+   \affaddr{Some Place}
+}
+\maketitle
+
+\begin{abstract}
+\indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
+In this paper, we report findings from the first large-scale survey conducted to investigate user security and privacy concerns regarding wearables.
+We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to them; these risks are inspired by the sensor inputs and applications of popular wearable technologies.
+During this experiment, our questions controlled for the effects of what data was being accessed and with whom it was being shared.
+We also investigated how these emergent threats compared to existent mobile threats, how upcoming capabilities and artifacts compared to existing technologies, and how users ranked technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
+We hope that this work will inform the design of future user notification, permission management, and access control schemes for wearables.
+\end{abstract}
+
+% A category with the (minimum) three required fields
+%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
+
+%\terms{Human Factors}{Measurement}{Security}
+
+\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
+
+\section{Introduction}
+
+Wearables are a \$700 million, growing industry~\cite{cmo}.
+With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
+This trend will likely continue, as 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
+
+Wearable devices enable many benefits, ranging from interaction with virtual objects in an augmented reality world to healthier, fitness-data inspired lifestyles.
+However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
+Although wearable devices are still in their infancy, we have already seen manifestations of these risks.
+Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.
+Google Glass has since been discontinued.
+
+For smartphones, security and privacy risks are generally addressed by communicating data capture to users.
+However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}.
+Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.
+
+Wearables' sensor capabilities, continuous access, and ubiquitous presence will result in a firehose of familiar and unfamiliar types of data, at a rate which will likely dwarf the amount of data currently captured by smartphones.
+Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured~\cite{denning2014situ}.
+However, subjecting people to increased notifications is not a sound option, as it has shown to lead to negative effects, such as frustration and habituation~\cite{bohme2011security}.
+An understanding of user concerns may allow for targeted and effective communication with the user, inform design of future permission systems, or provide insight for access control mechanisms.
+
+The goal of this work is to shape the still-malleable future of wearable platforms and interaction models, with research on user-centric concerns.
+To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
+Our survey of 1,782 Internet users contributes the following: %\\[-0.8cm]
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item We report how 72 types of data likely to be captured by wearable devices were perceived by our participants and rank them by relevance. 
+\item We repeat this across 4 types of recipients to also illustrate the contribution of the data recipient to the overall perceived risk. 
+\item We sketch a landscape of users' self-reported concerns regarding wearable devices, spanning concerns outside of security and privacy. 
+\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as using a lawnmower.
+\end{itemize}
+
+\section{Methodology}
+To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
+At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
+%~\cite{6_fitbit_2014, 7_time_2014}
+the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
+and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. %~\cite{11_wikipedia_2015, 12_turi_2014}. 
+These devices' capabilities and requested permissions were our inspiration to develop a list of possible security and privacy risks that users will encounter.
+
+We designed a survey to gauge the relevancy of all these possible risks.
+Our survey contained two main sections.
+A set of questions presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
+This was intended to elicit their perception of the severity and impact of the risk.
+The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}.
+Another set asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
+%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
+
+\subsection{Related Work}
+In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of a wide range of general technology-based risk perceptions~\cite{Fischhoff}.
+
+\subsubsection{Smartphone Risk Scenarios}
+Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
+Their survey asked 3,115 smartphone users about 99 risk scenarios.
+Participants were asked how upset they would be if a certain action occurred without their permission.
+Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
+Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.
+
+\subsubsection{Technology Risk Perceptions}
+Fischhoff \etal performed a seminal study of the perceived risks and benefits surrounding 30 widely used technologies~\cite{Fischhoff}.
+Participants were asked to separately think of the risks then benefits, considering all people affected, long-term effects, and short term effects.
+Then, the participants respectively rated these technologies on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10).
+We apply their methodology to evaluate perceived risks and benefits of technologies related to wearable computing with respect to more familiar technologies.
+%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+
+\subsection{Survey Questions}
+\noindent Each participant answered 27 questions across 5 sections:   \\[-.5cm]
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item 2 reading comprehension questions
+\item 6 questions about wearable computing scenarios 
+\item 2 questions about smartphone scenarios 
+\item 2 Fischhoff-style risk/benefit questions 
+\item 15 demographic questions %\\[-.8cm]
+\end{itemize}
+
+We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
+
+\subsubsection{Comprehension Questions}
+Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
+Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
+We highlighted the capabilities of this device and described use cases:
+
+\begin{quotation}
+{\it Imagine that you are the proud owner of the Cubetastic3000, a new, high-tech computing device designed to be worn on your head.
+Imagine also that you wear this device all the time, because it is very lightweight, durable, and convenient.
+
+The Cubetastic3000 has the capability to capture video, photos, audio, and biometrics (biological data about you, such as heart rate).
+Just like other devices today, you can install third-party applications from an app store, and these applications can use the information that the Cubetastic3000 captures.
+
+With a wide range of applications and capabilities, your device can do all sorts of things, such as:\\
+
+\noindent---measuring heart rate, breathing, and other things to keep track of your fitness level and overall health\\
+
+\noindent---look at what you see to provide information about what's around you\\
+
+\noindent---allow you to take notes just by telling the device what you need to remember\\
+
+\noindent---take videos of you or what you see to share with others\\
+
+\noindent---automatically take photos or video so that you can replay events that previously happened\\
+
+\noindent---play music that you like for you when it detects that no one is around\\
+
+\noindent---infer information about you so you don't need to log in or search for the same thing over and over\\
+
+\noindent ...and much more!}
+\end{quotation}
+
+Since this device is the basis for many of our questions, we ensured that participants had understood its capabilities by asking them two multiple-choice comprehension questions.
+We filtered out responses from participants who could not answer these questions.
+
+\subsubsection{Wearable Scenarios}
+We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) was shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
+Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
+Questions were of the form:
+
+\begin{quotation}
+\noindent
+\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}
+\end{quotation}
+
+We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions: %\\[-.8cm]
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{images/prompt.pdf}
+	\caption{An example of a wearable scenario question participants saw while taking the survey.}
+	\label{fig:prompt}
+\end{figure}
+
+\begin{packed_item}
+\item Your work contacts
+\item Your friends
+\item The public
+\item The app's server (but didn't share it with anyone else) %\\[-.8cm]
+\end{packed_item}
+
+The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
+Each participant answered 6 questions that were randomly drawn from a pool of 293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).
+
+\subsubsection{Smartphone Scenarios}
+\label{sec:smartphones}
+We presented participants with a second set of scenarios to control for the type of device being used.
+Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
+
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
+\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
+\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
+\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
+\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
+\end{enumerate}
+
+In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6).
+In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
+
+\subsubsection{Risk and Benefit Assessment}
+In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
+We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
+We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
+These technologies were chosen to span varying levels of risks and benefits.
+
+Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
+To do this, we asked participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies.
+The 20 technologies were: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
+
+To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
+We randomized whether they performed the ranking for risks or benefits first.
+The prompt is listed in Appendix \ref{sec:prompt}.
+The question format was as follows:
+
+\begin{quotation}
+{\it \noindent Fill in your <risk/benefit> numbers for the following:\\
+
+\noindent Handguns: \_\_\_\_\_\_\_ \\
+Motorcycles: \_\_\_\_\_\_\_\\
+Lawnmowers: \_\_\_\_\_\_\_\\
+<Wearable Technology>: \_\_\_\_\_\_\_\\
+Electricity: \_\_\_\_\_\_\_\\ }
+\end{quotation}
+
+\subsubsection{Additional Questions}
+The exit portion of the survey contained demographic questions asking for age, gender, and education.
+We then asked about wearables ownership so we could control for prior exposure.
+An open-ended question on what would be the most likely risks associated with wearable devices was included to catch user concerns more broadly.
+To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes.
+
+\subsection{Focus Group}
+We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
+The focus group began with participants taking the survey then giving feedback on the format and the content, noting any instructions or questions that were unclear.
+The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
+Finally, we compensated participants with \$30 in cash.
+We recruited all of our focus group participants from Craigslist.
+Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 ($\mu = 36.1$, $\sigma = 15.3$).
+Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.
+
+\subsection{Recruitment and Analysis Method}
+We recruited 2,250 participants over August 7--13, 2014 via Amazon's Mechanical Turk.
+We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
+We compensated each participant with \$1.75 upon successfully completing the survey.
+Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
+We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and three participants for being under 18, leaving us with a total sample size of 1,782.
+Of these, 57.9\% were male (1,031), 41.0\% were female (731), and 20 participants declined to state their genders.
+Ages ranged from 18 to 73, with a mean of 32.1 ($\sigma$ = 10.37).
+Almost half of our participants had completed a college degree or more (49.2\% of 1,782), which includes the 219 (12.3\% of 1,782) who reported graduate degrees.
+While our sample was younger and more educated than the U.S.
+population as a whole, we believe it is still consistent with the U.S.
+Internet-using population.
+
+In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
+The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
+We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced.
+Additionally, most people are likely to be upset, at least a little, in all scenarios, because a device is taking action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344).
+Thus, the distinguishing factor is whether a participant was maximally upset, rather than if they were upset.
+A limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.
+
+We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+Rather, we report medians and quartiles, which are not impacted by outliers.
+For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,782 responses, with an initial agreement rate of 89.7\%.
+The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
+
+\section{Results}
+In this section, we present participants' responses to the various data-sharing scenarios, and discuss how and which various factors contributed to their risk perceptions.
+We also discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
+We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
+
+\subsection{Concern Factors}
+Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question.
+We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of the above factors and additional demographic traits.
+
+\subsubsection{Data Type}
+\label{sec:datatypes}
+
+Based on our statistical models (later reported in Section \ref{sec:regression}), we observe that the largest effect on participants' VURs stemmed from the data being shared; with whom the data is shared and which device the user is interacting with had weaker impacts on overall VURs.
+The most and least concerning data types are listed in Table \ref{top10-table}, and the full list can be seen in Table \ref{full-vur-table} in Appendix \ref{sec:concerns-appendix}.
+
+Participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and are almost unanimously considered to be concerning.
+Information that could be used to impersonate someone (e.g., usernames/passwords for websites), or photos of someone at home, were also among the most concerning data types.
+
+Participants were least concerned about data that could be collected through observations of public behavior, such as demographics (e.g., age, gender, language) or information available to advertisers (e.g., TV shows watched, music on device).
+As seen in Table \ref{top10-table}, participants' responses had a greater amount of variance.
+This greater variance and overall decreased concern may be because of uncertainty with how the data would be used, or because the financial, social, or physical consequences would be less immediate.
+
+Although certain data is considered unanimously upsetting to have shared, it is interesting to note that no data was considered unanimously non-upsetting to have shared, nor were there any data types that evoked strong disagreement between participants (i.e., bimodal).
+Generally, the average concern magnitude was inversely correlated with the standard deviation, which suggests the presence of ceiling effects for the most concerning data types.
+For the complete ranked list of data types in this study, see Appendix \ref{sec:concerns-appendix}.
+
+\begin{table*}[t]
+\begin{center}
+\small
+\begin{tabular}{| r | l | r | r |c |}
+\hline
+Rank & Data & VUR & $\sigma$ & Distribution \\
+\hline
+1 & video of you unclothed & 95.97\% & 0.31 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouunclothedcombined} \\
+2 & bank account information & 95.91\% & 0.35 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourbankaccountinformationcombined}  \\
+3 & social security number & 94.84\% & 0.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyoursocialsecuritynumbercombined}\\
+4 & video entering in a PIN at an ATM & 92.67\% & 0.47 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookavideoofyouenteringinyourPINatanATMcombined}\\
+5 & photo of you unclothed & 92.59\% & 0.46 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookaphotoofyouunclothedcombined}\\
+6 & photo of you that is very embarrassing & 91.39\% & 0.55 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingphotoofyoudoingsomethingembarrassingcombined}\\
+7 & username and password for websites & 89.55\% & 0.62 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourusernameandpasswordforwebsitescombined}\\
+8 & credit card information & 88.98\% & 0.56 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourcreditcardinformationcombined}\\
+9 & video of you that is very embarrassing & 88.41\% & 0.53 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookanincriminatingvideoofyoudoingsomethingembarrassingcombined}\\
+10 & photo of you at home & 87.50\% & 0.60 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/tookphotosofyou(withaninward-facingcamera)athomecombined}\\
+ & \vdots & & & \\
+64 & eye patterns (for eye tracking) & 40.51\%& 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/scannedyoureyetolearnyoureyepatterns(foreyetracking)combined} \\
+65 & exercise patterns  & 38.66\% & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenhowandhowmuchyouexercisecombined}\\
+66 & when you are happy or having fun  & 34.75\% & 1.27 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouwerehappyorhavingfuncombined}\\
+67 & television shows watched & 30.20\% & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhattelevisionshowsyouwatchcombined}\\
+68 & when you are busy or interruptible  & 29.50\% & 1.26 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedwhenyouarebusyorinterruptiblecombined}\\
+69 & music on device  & 28.06\% & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/copiedanduploadedmusicfromyourdevicecombined}\\
+70 & your heart rate & 27.50\% & 1.40 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourheartratecombined} \\
+71 & age & 24.29\% & 1.43 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyouragecombined}\\
+72 & language spoken & 15.86\% & 1.49 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedthelanguageyouwerespeakingcombined}\\
+73 & gender & 15.00\% & 1.45 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/data10/learnedyourgendercombined}\\ 
+\hline
+\end{tabular}
+\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix \ref{sec:concerns-appendix}.}
+\label{top10-table}
+\end{center}
+\end{table*}
+
+%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
+We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
+
+\subsubsection{Data Recipient}
+A statistically significant difference in VUR exists between data shared with an application versus data shared with human recipients.
+On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were almost double (Table \ref{recipient-vur}).
+A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}).
+However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
+
+We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients.
+But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
+Similarly, we are unaware of a more appropriate test, given our data format.
+Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
+Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation.
+Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.
+Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.
+
+However, we do not claim that there are no distinctions between the friends, public, and work contact recipients.
+People are more comfortable sharing certain data types with certain human recipients.
+For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.
+Table \ref{all-vur} Appendix \ref{sec:concerns-appendix} shows the  complete VUR and rankings of all data types by recipient.
+
+%People have been shown to behave differently, especially in the social arena \cite{dwyer2007trust, gross2005information, fogel2009internet}.
+
+\begin{table}[t]
+\begin{center}
+\small
+\begin{tabular}{| r | l | r | l |c |}
+\hline
+Rank & Recipient & VUR & sigma & Distribution \\
+\hline
+1 & Work Contacts & 75.16\% & 0.94 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_work} \\
+2 & Public & 72.41\% & 0.98 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_pub}  \\
+3 & Friends & 69.47\% & 1.02 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_friends}\\
+4 & App's Server & 42.28\% & 1.15 & \includegraphics[width = 2cm, height = 0.5cm]{tex-inputs/recipient4/recipient_app}\\
+\hline
+\end{tabular}
+\caption{The overall upset rate for all recipients.}
+\label{recipient-vur}
+\end{center}
+\end{table}
+
+\begin{table}[t]
+\small
+\begin{center}
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
+\hline
+Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
+Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
+Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
+Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
+Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
+Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
+\hline
+\end{tabular}
+\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
+\label{recipient-chi}
+\end{center}
+\end{table}
+
+\begin{table}[t]
+\small
+\begin{center}
+\begin{tabular}{| c | r | r |}
+\hline
+ Misbehavior &  Cubetastic3000 & Smartphone \\
+ \hline
+ \hline
+ All & 58.79\% & 46.67\%\\
+ \hline
+Vibration & 14.81\%  &  6.14\%\\
+Bluetooth & 44.12\%  &  19.86\%\\
+Unmuted Call & 87.10\%  &  58.44\%\\
+Screenshot & 52.78\%  & 55.74\%\\
+Premium Calls/Texts & 86.49\%  &  91.94\%\\ 
+\hline
+\end{tabular}
+\caption{VURs for the five questions about device misbehaviors described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
+\label{deviceVUR}
+\end{center}
+\end{table}
+
+\subsubsection{Device}
+Each participant answered two questions drawn from a set of five smartphone misbehaviors.
+To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, modifying the device in question.
+In this manner, all 1,782 participants received two smartphone questions, while 159 participants received at least one of these five Cubetastic3000 misbehavior questions.
+Across all participants, the VUR was 46.7\% (of 1,782) for smartphones, whereas the VUR increased to 58.8\% (of 159) for same misbehaviors on the Cubetastic3000.
+The VURs for both devices for these questions are in Table \ref{deviceVUR}.
+
+To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
+This difference is statistically significant ($U=108,664.0$ with $p<0.0005$) but the effect size is very small ($r=0.08$).
+Because of this, we did not further reduce our statistical power by separately comparing the five misbehaviors.
+We conclude that users are likely more wary of misbehaviors on wearables than smartphones, but this difference is likely negligible.
+The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearables.
+
+%{\color {red} talk about the variance of the devices in general--was there more spread for the answers wrt smartphones, cubetastic, or were they kind of all the same?}
+
+%\begin{table}%[h]
+%\begin{center}
+%\begin{tabular}{| c | c | c | c |}
+%Question & $\chi^2$ &	2-tail P & Effect Size \\
+%All & 0.444  & 0.505 & 0.006\\
+%Q1 & 0 & 1 & 0 \\
+%Q2 & 0 & 1 & 0\\
+%Q3 & 0 & 1 & 0\\
+%Q4 & 0 & 1 & 0\\
+%Q5 & 0 & 1 & 0\\
+%\end{tabular}
+%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
+%\label{withindevice}
+%\end{center}
+%\end{table}
+
+%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
+Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
+The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
+For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
+
+\subsection{Risk and Benefit Rankings} 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{images/riskbenefit.pdf}
+	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
+	\label{fig:techplot}
+\end{figure}
+
+We ask participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their  benefits and risk.
+We also ask them about technologies with which they were likely to be more familiar (e.g., smartphones and laptops) and two specific wearable devices, Google Glass and the fictitious Cubetastic3000.
+To calibrate our results, we  ask about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
+We find that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}).
+Tables \ref{risk} and \ref{benefit} in Appendix ~\ref{sec:concerns-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
+
+Participants were prompted to rate technologies with respect to all considerations (see Appendix~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
+Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
+Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk.
+
+We examined participants' perceptions, and therefore responses may not be reflective of actual risks or benefits.
+However, they also reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
+We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities and that performing this experiment longitudinally may yield more interesting results, as these technologies become pervasive (and more familiar to participants).
+
+As a group, participants rated more familiar technologies as more beneficial.
+We believe this is the result of exposure to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
+It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
+Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others.
+However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
+
+We find that the more familiar a participant was with a technology, the more likely they were to rate it as risky.
+Again, we believe that this is due to the exposure to these technologies.
+Of the wearable technologies, the riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
+We did not test the differences in risk between the different wearable-related technologies for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
+Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.
+
+\subsection{Open-Ended Concerns for Wearables}
+We captured participants' reactions to wearable devices as a whole by asking the following open-ended question:
+
+\begin{quotation}
+\noindent
+\textit{What do you think are the most likely risks associated with wearable devices?}
+\end{quotation}
+
+This question was asked with demographics questions, but before any IUIPC questions (which asked a lot of direct privacy-related questions, to avoid biasing the recipients).
+The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
+
+Table \ref{openresponses} shows common user concerns related to wearable devices.
+Appendix \ref{sec:coding} details the responses categorized in each coding label.
+Most are related to privacy and security, but this open-ended data gives a sense of what broad categories of concerns are most relevant to users.
+This can be used to guide research in unexplored use cases.
+
+In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware).
+Other orthogonal concerns included long-term health effects caused from wearing the device such as cancer from EMF waves (Health) and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).
+Interestingly, participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
+
+\begin{table}[t]
+\begin{center}
+\begin{tabular}{|l|r|r|}
+\hline
+Concern &  Responses &  Frequency   \\
+\hline
+Privacy & 452 & 25.32\% \\
+Being Unaware & 275 & 15.40\% \\
+%Unaware Use & 167 & (9.36\%)\\
+%Unaware Collection & 64 & (3.59\%)\\
+%Unaware Access & 44 & (2.46\%)\\
+Health Risk & 191 & 10.70\%\\
+Safety & 185 & 10.42\%\\
+Social Impact &	157 & 8.80\%\\
+Financial Cost & 151 & 8.46\%\\
+Security &	144 & 8.07\%\\
+Accidental Sharing &	69 & 3.87\%\\
+Miscellaneous &	57 & 3.19\%\\
+None	& 51 & 2.86\%\\
+Social Stigma &	39 & 2.18\%\\
+False Information & 33 & 1.85\%\\
+Don't know & 31 & 1.74\%\\
+Aesthetics 	& 19 & 1.06\%\\
+Don't care 	& 11 & 0.62\%\\
+\hline
+\end{tabular}
+\caption{The most common open-ended risks associated with owning a wearable device.}
+\label{openresponses}
+\end{center}
+\end{table}
+
+\subsubsection{Demographic Factors}
+
+We see that privacy is a main concern for wearables users.
+Additionally, we show that privacy preferences should also be a consideration for configuring a user's device.
+A participant's self-reported level of privacy concerns is the biggest demographic predictor of participants' VUR rate.
+This is determined by the IUIPC scale~\cite{malhotra2004internet}.
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores and VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences.
+Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$).
+Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.
+
+While we initially observed an effect on VURs based on whether or not participants claimed to already own wearables (57.0\% vs.
+60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$).
+The effect of a participant's gender also did not remain significant upon correcting for multiple testing.
+We observed no correlation between a participant's education level and VUR.
+
+\subsubsection{Regression Models} 
+\label{sec:regression}
+In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
+We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|l| r| r| r|}
+\hline
+Parameters & $\chi^2$ & $df$ & QIC\\
+\hline
+\hline
+(Intercept) & 423.96 & 1 & 13,209.1\\
+\hline
+(Intercept) & 207.07 & 1 & 12,551.49\\
+IUIPC (covariate) & 368.5 & 1 & \\
+Gender (covariate) & 6.30 & 1 & \\
+\hline
+(Intercept) & 411.66 & 1 &12,458.86\\
+Data Recipient & 599.72 & 3 & \\
+\hline
+(Intercept) & 418.02 & 1 & 11,382.75\\
+Data Type & 1,141.40 & 71 & \\
+\hline
+(Intercept) & 66.18 & 1 & 9,609.65 \\
+Data Recipient & 617.25 & 3 & \\
+Data Type & 1,288.51 & 71 & \\
+IUIPC (covariate) & 105.73 & 1 & \\
+Gender (covariate) & 9.74 & 1 & \\
+IUIPC $\times$ Gender & 8.33 & 1 &\\
+\hline
+\end{tabular}
+\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures.
+The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
+Each parameter listed was statistically significant at $p<0.005$.}
+\label{regression}
+\end{table}
+
+We created several models using two independent variables as predictors: data and recipient.
+Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) is only varied for the five smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, resulting in a total of 72 types of data shared with 4 possible recipients.
+We used the following demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
+For each model, we performed Wald's test to examine the model effects attributable to each of these parameters.
+The only covariates that had an observable effect on our models were participants' gender and IUIPC scores, which also exhibited an interaction effect with each other.
+Thus, we opted to remove the other covariates from our analysis.
+Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection that also accounts for complexity (lower relative values indicate better fit).
+As shown, the type of data being shared (data type) was found to be the strongest predictor of a high VUR.
+
+While these models illustrate the relative weights that users place on information when determining a scenario as truly upsetting, one shortcoming of this approach is its generalizability: the data predictor is categorical and limited to the data that we specifically chose for this study.
+To make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the type of data (e.g., video, audio, etc.) and the type of risk it presents.
+Two researchers agreed on a codebook and independently coded each of the 72 data types.
+
+The data types fell into these six categories:
+
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item Photo
+\item Video
+\item Audio
+\item Behavioral Information
+\item Biometric Information
+\item Demographic Information
+\end{enumerate}
+
+While the first three categories are self-explanatory, the latter three categories are all based on different user characteristics.
+We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.
+
+The risks for data types fell into these five categories:
+
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\item {\bf Financial:} the loss of money or property.
+\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing).
+\item {\bf Medical:} the disclosure of medical information.
+\item {\bf Physical:} physical harm to the user.
+\item {\bf Relationships:} damage to the user's inter-personal relationships.
+\end{enumerate}
+
+After independently coding, the researchers met to resolve any disagreements, such that the results reflect unanimity.
+There was  83\% agreement prior to resolution.
+Cohen's $\kappa$ was 0.81 for the data categories and 0.75 for the  risk categories, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
+
+With regard to data types, the most concerning type of data is video (78.0\%), which was ranked similarly to photos (76.2\%).
+Next are audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data.
+We suspect that demographic data was more concerning because it included information such as a Social Security Number, bank account information, and other financial information.
+We chose to categorize them as such as they are non-biological descriptors of the user.
+We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data.
+One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data is stolen and abused.
+
+With regard to the presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%).
+Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed.
+VURs were lowest for medical information disclosure (47.4\%).
+One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state.
+As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|l| r| r| r|}
+\hline
+Parameters & $\chi^2$ & $df$ & QIC\\
+\hline
+\hline
+(Intercept) & 442.66 & 1 & 12,727.42\\
+Risk & 405.18 & 4 & \\
+\hline
+(Intercept) & 380.39 & 1 & 12,681.86\\
+Data Category & 439.45 & 5 & \\
+\hline
+(Intercept) & 256.15 & 1 & 12,061.87\\
+Risk & 157.84 & 4 & \\
+Data Category & 183.90 & 5 & \\
+Risk $\times$ Data Category & 259.81 & 8 & \\
+\hline
+(Intercept) & 62.65 & 1 & 10,406.35\\
+Risk & 205.21 & 4 & \\
+Data Category & 250.35 & 5 & \\
+Recipient & 546.89 & 3 & \\
+IUIPC (covariate) & 103.94 & 1 & \\
+Gender (covariate) & 9.80 & 1 & \\
+IUIPC $\times$ Gender & 8.21 & 1 & \\
+Risk $\times$ Data Category & 303.44 & 8 & \\
+Recipient $\times$ Risk & 39.14 & 12 & \\
+\hline
+\end{tabular}
+\caption{Metrics for additional binary logistic models of our data using general estimating equations to account for repeated measures.
+The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
+Each parameter listed was statistically significant at $p<0.005$.}
+\label{regression2}
+\end{table}
+
+Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models.
+Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit.
+What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect.
+When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.
+%The full model can be found in Appendix \ref{sec:regression-apx2}.
+
+\section{Discussion}
+%We discuss considerations when interpreting our results, the limitations of our work, and future work we hope to inspire.
+
+\subsection{Limitations}
+One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable.
+Because of this, our participants may be over or underestimating the risk, stemming form an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
+Our participants also did not differentiate between the benefits of risks of various new capabilities.
+
+We recruited both wearable users and non-users in order to yield a more representative sample of the general population.
+We could have easily recruited only wearables owners or people specifically interested in wearables.
+However, that would have its own biases and limitations.
+At the time of this writing, about 85\% of the general population do not own wearable devices~\cite{Nilsen,WearableStatNews}, indicating our study is reflective of the current population.
+
+Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}.
+At the same time, our results do reflect actual perceptions of wearable devices and the associated privacy scenarios involving them.
+This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and preferences, so that future systems can be designed with these in mind.
+We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over post hoc approaches (or ignoring user concerns altogether).
+
+\subsection{Future Research Directions}
+We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications.
+We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourage work for contextual and user-input- independent permission models and access control schemes.
+
+Further work can be done to expand various aspects of this study.
+Investigating more fine-grained data types (e.g., investigating specific instances of location data, versus location data in general) would be a useful endeavor to gain further insight into user perceptions.
+Adding additional recipients, such as ``advertisers'' or ``acquaintances'' may lead to more nuanced results.
+Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impact.
+
+\section{Additional Related Work}
+%%% better introduction, or take this out. This seems awkward. 
+%We discuss related work that has examined users' perceptions surrounding security and privacy risks.
+%In this section, we outline previous research examining privacy in wearable computing environments, smartphone privacy and security, as well as user risk perceptions and behaviors.
+
+\subsection{Wearables and Privacy}
+We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
+
+Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
+Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
+Our work aims to augment works like these with an understanding of what privacy means to the end user.
+
+\subsection{Lessons form Smartphones}
+Research shows that perceptions of risk change based on the particular device being used.
+Chin {\it et al.}\ found that users' attitudes toward security and privacy for smarphones significantly differed from attitudes towards traditional computing systems, stemming from differences in how people used these systems ~\cite{chin2012measuring}.
+Undoubtedly, this will hold true for wearables as well as wearables have a sparse, world-driven interaction model.
+
+%% LL: None of this seems that relevant! :( I was just citing things to cite them.. find better things to say.
+
+%Palen {\it et al.}\ tracked smartphone users for six weeks and observed that people also perceive and behave without a realistic understanding of the risks they are taking ~\cite{palen2000going}; Felt {\it et al.}\ examined the Android permission system and found that 17\% of participants paid attention to permission requests, and only 3\% comprehended what these permissions meant.
+For these reasons, we need to
+
+%Smartphones allow applications to access new types of data.
+While this tends to benefit users, they do not think of the privacy implications.
+Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
+
+%There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
+
+Tsai {\it et al.}\ found that when mobile users get feedback about releasing data, such as who has viewed location information, it greatly impacts future behaviors~\cite{Tsai2009}.
+Although this type of feedback is not provided to smartphone users, there is potential for impacting wearables users and shaping their behaviors so that they keep users safe.
+
+\subsection{User Perceptions}
+While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
+For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
+While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
+
+One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
+Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
+However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
+
+\section{Conclusion}
+
+ Our survey of 1,784 Internet users, is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices.
+We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
+We calibrate our results with mobile devices and existing technologies; additionally, we verify with an open-ended question and find that privacy and security are at the top of user's overall concerns.
+Wearables are still in their infancy.
+Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
+However, there is not much work done to determine which threats in the emerging threat landscape are pertinent to focus on.
+Inspection of possible data concerns agree with previous studies of smartphone studies to find that video capture and financial data to be most sensitive.
+Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
+We also find that users' self-reported privacy preferences are correlated with how participants may react, even with respect to situations that they are unfamiliar with.
+Permissions and access control mechanisms which do not depend on user inputs can still benefit from being informed by user preferences.
+We hope that this work has given a comprehensive overview of user concerns and inform designs of future privacy and security work for wearable devices.
+
 \bibliographystyle{abbrv}
 \bibliography{bibliography.bib}
-\input{appendixes.tex}
+
+\input{tex-inputs/appendixes.tex}
+\input{tex-inputs/collapsed.tex}
+\input{tex-inputs/riskben.tex}
+\input{tex-inputs/VURcombined.tex}
+
+%%% REGRESSION MODEL
+
+%\onecolumn
+%\section{Full Regression Model from Data Types}
+%\label{sec:regression-apx}
+%%\begin{figure*}[t]
+%\includegraphics[page=1,scale=0.8]{images/full-model.pdf}
+%\includepdf[pages=2-3,scale=0.8]{images/full-model.pdf}
+%
+%%\caption{Full regression model, which includes all 72 data types, recipients, and covariates.}
+%%\end{figure*}
+%
+%\section{Full Regression Model from Data Risks / Data Categories}
+%\label{sec:regression-apx2}
+%%\begin{figure*}[t]
+%\includegraphics[page=1,scale=0.8]{images/full-model2.pdf}
+%\includepdf[pages=2,scale=0.8]{images/full-model2.pdf}
+%
+%\twocolumn
 

### 2015-12-07 paper.tex
comment out things about fischoff study

@@
 
-\subsubsection{Technology Risk Perceptions}
-Fischhoff \etal performed a seminal study of the perceived risks and benefits surrounding 30 widely used technologies~\cite{Fischhoff}.
+%\subsubsection{Technology Risk Perceptions}
+%Fischhoff \etal performed a seminal study of the perceived risks and benefits surrounding 30 widely used technologies~\cite{Fischhoff}.
 Participants were asked to separately think of the risks then benefits, considering all people affected, long-term effects, and short term effects.
@@
 
-\subsection{Risk and Benefit Rankings} 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\columnwidth]{images/riskbenefit.pdf}
-	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-	\label{fig:techplot}
-\end{figure}
-
-We ask participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their  benefits and risk.
+%\subsection{Risk and Benefit Rankings} 
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=\columnwidth]{images/riskbenefit.pdf}
+%	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
+%	\label{fig:techplot}
+%\end{figure}
+%
+%We ask participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their  benefits and risk.
 We also ask them about technologies with which they were likely to be more familiar (e.g., smartphones and laptops) and two specific wearable devices, Google Glass and the fictitious Cubetastic3000.
@@
 Tables \ref{risk} and \ref{benefit} in Appendix ~\ref{sec:concerns-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
-
-Participants were prompted to rate technologies with respect to all considerations (see Appendix~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
+%
+%Participants were prompted to rate technologies with respect to all considerations (see Appendix~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
 Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
 Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk.
-
-We examined participants' perceptions, and therefore responses may not be reflective of actual risks or benefits.
+%
+%We examined participants' perceptions, and therefore responses may not be reflective of actual risks or benefits.
 However, they also reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
 We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities and that performing this experiment longitudinally may yield more interesting results, as these technologies become pervasive (and more familiar to participants).
-
-As a group, participants rated more familiar technologies as more beneficial.
+%
+%As a group, participants rated more familiar technologies as more beneficial.
 We believe this is the result of exposure to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
@@
 However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
-
-We find that the more familiar a participant was with a technology, the more likely they were to rate it as risky.
+%
+%We find that the more familiar a participant was with a technology, the more likely they were to rate it as risky.
 Again, we believe that this is due to the exposure to these technologies.
@@
 \section{Additional Related Work}
-%%% better introduction, or take this out. This seems awkward. 
-%We discuss related work that has examined users' perceptions surrounding security and privacy risks.
-%In this section, we outline previous research examining privacy in wearable computing environments, smartphone privacy and security, as well as user risk perceptions and behaviors.
 
@@
 Undoubtedly, this will hold true for wearables as well as wearables have a sparse, world-driven interaction model.
-
-%% LL: None of this seems that relevant! :( I was just citing things to cite them.. find better things to say.
-
-%Palen {\it et al.}\ tracked smartphone users for six weeks and observed that people also perceive and behave without a realistic understanding of the risks they are taking ~\cite{palen2000going}; Felt {\it et al.}\ examined the Android permission system and found that 17\% of participants paid attention to permission requests, and only 3\% comprehended what these permissions meant.
-For these reasons, we need to
 

### 2015-12-07 tex-inputs/appendixes.tex
also comment out appendix part of fischoff study

@@
 
-\section{Fischhoff Prompts}
-\label{sec:prompt}
-
-\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
-
-{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
+%\section{Fischhoff Prompts}
+%\label{sec:prompt} 
+%
+%\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}
+%
+%{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations.
 (e.g.
 for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.}
-
-\textit{Do not consider the costs or risks associated with these items.
+%
+%\textit{Do not consider the costs or risks associated with these items.
 It is true, for example, that sometimes swimmers can drown.
@@
 Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.}
-
-\textit{Please rate the following technologies below with a number.
+%
+%\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.
@@
 (For instance, a technology rated 14 is half as risky as a technology rated 28.)}
-
-{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
+%
+%{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on.
 (e.g.
 for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.}
-
-\textit{Do not consider the costs or benefits associated with these items.
+%
+%\textit{Do not consider the costs or benefits associated with these items.
 It is true, for example, that electricity also creates a market for home appliances.
@@
 Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.}
-
-\textit{Please rate the following technologies below with a number.
+%
+%\textit{Please rate the following technologies below with a number.
 We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you.

### 2015-12-07 paper.tex
take out tables associated with commented out sections
more cleanup

@@
 \item We sketch a landscape of users' self-reported concerns regarding wearable devices, spanning concerns outside of security and privacy. 
-\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as using a lawnmower.
+%\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as using a lawnmower.
 \end{itemize}
@@
 
-\subsubsection{Risk and Benefit Assessment}
-In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
+%\subsubsection{Risk and Benefit Assessment}
+%In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
 We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
@@
 These technologies were chosen to span varying levels of risks and benefits.
-
-Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
+%
+%Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
 To do this, we asked participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies.
 The 20 technologies were: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-
-To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
+%
+%To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
 We randomized whether they performed the ranking for risks or benefits first.
@@
 The question format was as follows:
-
-\begin{quotation}
-{\it \noindent Fill in your <risk/benefit> numbers for the following:\\
-
-\noindent Handguns: \_\_\_\_\_\_\_ \\
-Motorcycles: \_\_\_\_\_\_\_\\
-Lawnmowers: \_\_\_\_\_\_\_\\
-<Wearable Technology>: \_\_\_\_\_\_\_\\
-Electricity: \_\_\_\_\_\_\_\\ }
-\end{quotation}
+%
+%\begin{quotation}
+%{\it \noindent Fill in your <risk/benefit> numbers for the following:\\
+%
+%\noindent Handguns: \_\_\_\_\_\_\_ \\
+%Motorcycles: \_\_\_\_\_\_\_\\
+%Lawnmowers: \_\_\_\_\_\_\_\\
+%<Wearable Technology>: \_\_\_\_\_\_\_\\
+%Electricity: \_\_\_\_\_\_\_\\ }
+%\end{quotation}
 
@@
 \input{tex-inputs/appendixes.tex}
-\input{tex-inputs/collapsed.tex}
-\input{tex-inputs/riskben.tex}
+%\input{tex-inputs/collapsed.tex}
+%\input{tex-inputs/riskben.tex}
 \input{tex-inputs/VURcombined.tex}

### 2015-12-07 paper.tex
merged the related work sections

@@
 \subsection{Related Work}
-In this section, we describe the two prior works on which we based our survey format: Felt {\it et al.}'s survey of smartphone-based risks~\cite{Felt} and Fischhoff {\it et al.}'s survey of a wide range of general technology-based risk perceptions~\cite{Fischhoff}.
+{\color{red} some intro here}\\
 
-\subsubsection{Smartphone Risk Scenarios}
+\noindent {\bfseries Ubiquitous Sensing}
+
+We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
+
+Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
+Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
+Our work aims to augment works like these with an understanding of what privacy means to the end user.
+\\
+
+\noindent {\bfseries Lessons form Smartphones}
+
+Smartphones allow applications to access new types of data.
+While this tends to benefit users, they do not think of the privacy implications.
+Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
+There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
+
 Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
@@
 Participants were asked how upset they would be if a certain action occurred without their permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
-Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.
+Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.
 
-%\subsubsection{Technology Risk Perceptions}
-%Fischhoff \etal performed a seminal study of the perceived risks and benefits surrounding 30 widely used technologies~\cite{Fischhoff}.
-Participants were asked to separately think of the risks then benefits, considering all people affected, long-term effects, and short term effects.
-Then, the participants respectively rated these technologies on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with a risk rating of 20 is considered twice as risky as compared to a technology with a risk rating of 10).
-We apply their methodology to evaluate perceived risks and benefits of technologies related to wearable computing with respect to more familiar technologies.
-%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
+Tsai {\it et al.}\ found that when mobile users get feedback about releasing data, such as who has viewed location information, it greatly impacts future behaviors~\cite{Tsai2009}.
+Although this type of feedback is not provided to smartphone users, there is potential for impacting wearables users and shaping their behaviors so that they keep users safe.
+\\
+
+\noindent {\bfseries User Perceptions}
+
+While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
+For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
+While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
+
+One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
+Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
+However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
 
@@
 
-\section{Additional Related Work}
-
-\subsection{Wearables and Privacy}
-We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
-
-Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
-Our work aims to augment works like these with an understanding of what privacy means to the end user.
-
-\subsection{Lessons form Smartphones}
-Research shows that perceptions of risk change based on the particular device being used.
-Chin {\it et al.}\ found that users' attitudes toward security and privacy for smarphones significantly differed from attitudes towards traditional computing systems, stemming from differences in how people used these systems ~\cite{chin2012measuring}.
-Undoubtedly, this will hold true for wearables as well as wearables have a sparse, world-driven interaction model.
-
-%Smartphones allow applications to access new types of data.
-While this tends to benefit users, they do not think of the privacy implications.
-Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
-
-%There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
-
-Tsai {\it et al.}\ found that when mobile users get feedback about releasing data, such as who has viewed location information, it greatly impacts future behaviors~\cite{Tsai2009}.
-Although this type of feedback is not provided to smartphone users, there is potential for impacting wearables users and shaping their behaviors so that they keep users safe.
-
-\subsection{User Perceptions}
-While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
-For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
-While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
-
-One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
-Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
-However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
-
 \section{Conclusion}

### 2015-12-07 paper.tex
commented out comparison with smartphones

@@
 \noindent---measuring heart rate, breathing, and other things to keep track of your fitness level and overall health\\
-
 \noindent---look at what you see to provide information about what's around you\\
-
 \noindent---allow you to take notes just by telling the device what you need to remember\\
-
-\noindent---take videos of you or what you see to share with others\\
-
+\noindent---take videos of you or what you see to share\\
 \noindent---automatically take photos or video so that you can replay events that previously happened\\
-
 \noindent---play music that you like for you when it detects that no one is around\\
-
-\noindent---infer information about you so you don't need to log in or search for the same thing over and over\\
-
+\noindent---infer information about you so you don't need to log in or search for things\\
 \noindent ...and much more!}
@@
 The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
-Each participant answered 6 questions that were randomly drawn from a pool of 293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).
+Each participant answered 6 questions that were randomly drawn from this pool.
+%293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).
 
-\subsubsection{Smartphone Scenarios}
-\label{sec:smartphones}
-We presented participants with a second set of scenarios to control for the type of device being used.
+%\subsubsection{Smartphone Scenarios}
+%\label{sec:smartphones}
+%We presented participants with a second set of scenarios to control for the type of device being used.
 Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
-
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
-\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
-\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
-\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
-\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
-\end{enumerate}
-
-In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6).
+%
+%\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+%\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
+%\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
+%\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
+%\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
+%\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
+%\end{enumerate}
+%
+%
+%In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6).
 In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
@@
 
-We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
+%We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
 Rather, we report medians and quartiles, which are not impacted by outliers.
@@
 
-\subsection{Concern Factors}
-Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question.
+%\subsection{Concern Factors}
+%Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question.
 We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of the above factors and additional demographic traits.
@@
 
-\subsubsection{Device}
-Each participant answered two questions drawn from a set of five smartphone misbehaviors.
+%\subsubsection{Device}
+%Each participant answered two questions drawn from a set of five smartphone misbehaviors.
 To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, modifying the device in question.
@@
 The VURs for both devices for these questions are in Table \ref{deviceVUR}.
-
-To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
+%
+%To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
 This difference is statistically significant ($U=108,664.0$ with $p<0.0005$) but the effect size is very small ($r=0.08$).

### 2015-12-11 paper.tex
removed commentedout sections (I have git anyway)
finished rough draft

@@
 \indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
-In this paper, we report findings from the first large-scale survey conducted to investigate user security and privacy concerns regarding wearables.
-We surveyed 1,782 Internet users in order to identify risks that are particularly concerning to them; these risks are inspired by the sensor inputs and applications of popular wearable technologies.
-During this experiment, our questions controlled for the effects of what data was being accessed and with whom it was being shared.
-We also investigated how these emergent threats compared to existent mobile threats, how upcoming capabilities and artifacts compared to existing technologies, and how users ranked technical and non-technical concerns to sketch a concrete and broad view of the wearable device landscape.
-We hope that this work will inform the design of future user notification, permission management, and access control schemes for wearables.
+We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning.
+Our study  relatively ranks a range of potential wearables data capture scenarios, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable).
+To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables.
+We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
 \end{abstract}
@@
 
-Wearable devices enable many benefits, ranging from interaction with virtual objects in an augmented reality world to healthier, fitness-data inspired lifestyles.
+Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to an virtual-object filled augmented reality.
 However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
@@
 Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.
-Google Glass has since been discontinued.
-
-For smartphones, security and privacy risks are generally addressed by communicating data capture to users.
-However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}.
-Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.
 
@@
 
-The goal of this work is to shape the still-malleable future of wearable platforms and interaction models, with research on user-centric concerns.
-To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices.
+The goal of this work is to motivate research on the still-malleable future of wearable interaction models to preserve privacy and security, which we found are the top user perceived risk associated with wearable devices.
 Our survey of 1,782 Internet users contributes the following: %\\[-0.8cm]
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We report how 72 types of data likely to be captured by wearable devices were perceived by our participants and rank them by relevance. 
-\item We repeat this across 4 types of recipients to also illustrate the contribution of the data recipient to the overall perceived risk. 
-\item We sketch a landscape of users' self-reported concerns regarding wearable devices, spanning concerns outside of security and privacy. 
-%\item We compare emergent risks with existing risks and find that participants perceive risks similarly to physical risks---for instance, facial detection was perceived as risky as using a lawnmower.
+\item We give a relative ranking of 72 potential wearables capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
+\item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient.
+\item We sketch a landscape of users' self-reported concerns regarding wearable devices and analyze responses using logistic regression models. 
 \end{itemize}
@@
 \section{Methodology}
-To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
-At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
-%~\cite{6_fitbit_2014, 7_time_2014}
-the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
-and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. %~\cite{11_wikipedia_2015, 12_turi_2014}. 
-These devices' capabilities and requested permissions were our inspiration to develop a list of possible security and privacy risks that users will encounter.
-
-We designed a survey to gauge the relevancy of all these possible risks.
-Our survey contained two main sections.
-A set of questions presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
+We designed a survey for our IRB-approved study to capture the general public's perception of wearables risks.
+To determine which of the current data capture scenarios were most concerning to users, we asked them to rate their level of concern for a handful of scenarios from a list of possible scenarios.
 This was intended to elicit their perception of the severity and impact of the risk.
 The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}.
-Another set asked participants to compare the risks and benefits of wearable technologies to those of better-understood technologies, following the same methodology from Fischhoff {\it et al.}'s seminal study in risk perception~\cite{Fischhoff}.
-%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.
+To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we ask our participants an open-ended question.
 
-\subsection{Related Work}
-{\color{red} some intro here}\\
-
-\noindent {\bfseries Ubiquitous Sensing}
-
-We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
-
-Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
-Our work aims to augment works like these with an understanding of what privacy means to the end user.
-\\
-
-\noindent {\bfseries Lessons form Smartphones}
-
-Smartphones allow applications to access new types of data.
-While this tends to benefit users, they do not think of the privacy implications.
-Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
-There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
-
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
-Their survey asked 3,115 smartphone users about 99 risk scenarios.
-Participants were asked how upset they would be if a certain action occurred without their permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.
-
-Tsai {\it et al.}\ found that when mobile users get feedback about releasing data, such as who has viewed location information, it greatly impacts future behaviors~\cite{Tsai2009}.
-Although this type of feedback is not provided to smartphone users, there is potential for impacting wearables users and shaping their behaviors so that they keep users safe.
-\\
-
-\noindent {\bfseries User Perceptions}
-
-While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
-For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
-While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
-
-One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
-Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
-However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
+To obtain a representative list of scenarios, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
+At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc.
+These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today.
 
@@
 \item 2 reading comprehension questions
-\item 6 questions about wearable computing scenarios 
-\item 2 questions about smartphone scenarios 
-\item 2 Fischhoff-style risk/benefit questions 
-\item 15 demographic questions %\\[-.8cm]
+\item 6 questions regarding possible wearables scenarios
+\item 1 open-ended wearables risk question
+\item 14 demographic questions %\\[-.8cm]
 \end{itemize}
 
-We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.
+To assist in user fatigue, gave our participants a randomly selected subset of wearables scenarios.
+The average survey completion time was 11.5 minutes, which includes time for answering questions that are omitted from this paper due to lack of participants' familiarity with specific wearables devices and a misguided attempt to directly compare smartphones and wearables.
+See Appendix \ref{sec:noquestions} for details.
 
 \subsubsection{Comprehension Questions}
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable.
-Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
+The beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
+Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios on a fictitious wearable.
 We highlighted the capabilities of this device and described use cases:
@@
 {\it Imagine that you are the proud owner of the Cubetastic3000, a new, high-tech computing device designed to be worn on your head.
-Imagine also that you wear this device all the time, because it is very lightweight, durable, and convenient.
+Imagine that you wear this device all the time, because it is very lightweight, durable, and convenient.
 
 The Cubetastic3000 has the capability to capture video, photos, audio, and biometrics (biological data about you, such as heart rate).
-Just like other devices today, you can install third-party applications from an app store, and these applications can use the information that the Cubetastic3000 captures.
+Just like other devices, you can install third-party applications from an app store, and these applications can use the information from the Cubetastic3000.
 
-With a wide range of applications and capabilities, your device can do all sorts of things, such as:\\
+With a wide range of applications, your device can do all sorts of things, such as:\\
 
@@
 
-Since this device is the basis for many of our questions, we ensured that participants had understood its capabilities by asking them two multiple-choice comprehension questions.
-We filtered out responses from participants who could not answer these questions.
+To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.
 
 \subsubsection{Wearable Scenarios}
-We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) was shared without permission with a particular data recipient (see Figure \ref{fig:prompt}).
-Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}.
-Questions were of the form:
+We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts).
+The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
+Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset'')..
+Figure \ref{fig:prompt}) shows an example.
+Specifically, questions were of the form:
 
@@
 
-We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions: %\\[-.8cm]
-
 \begin{figure}[t]
 	\centering
-	\includegraphics[width=\columnwidth]{images/prompt.pdf}
+	\includegraphics[width=\columnwidth]{images/prompt.png}
 	\caption{An example of a wearable scenario question participants saw while taking the survey.}
@@
 
-\begin{packed_item}
-\item Your work contacts
-\item Your friends
-\item The public
-\item The app's server (but didn't share it with anyone else) %\\[-.8cm]
-\end{packed_item}
-
-The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
+We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions.We randomly pick 6 wearables scenarios from a list of 288 scenarios, and also display them to the user in a random order.
+Our 288 scenarios are the result of permuting 72 scenarios with 4 recipients, which can be seen in Table \ref{all-vur}.
+We clarified for our participants that ``app'' meant the the app's server, and that the data was not shared with anyone else.
 Each participant answered 6 questions that were randomly drawn from this pool.
-%293: the 288 described here, plus 5 that we describe in the next section (Section \ref{sec:smartphones}).
-
-%\subsubsection{Smartphone Scenarios}
-%\label{sec:smartphones}
-%We presented participants with a second set of scenarios to control for the type of device being used.
-Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
-%
-%\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-%\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
-%\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
-%\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
-%\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
-%\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
-%\end{enumerate}
-%
-%
-%In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6).
-In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
-
-%\subsubsection{Risk and Benefit Assessment}
-%In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies.
-We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society.
-We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.
-These technologies were chosen to span varying levels of risks and benefits.
-%
-%Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.
-To do this, we asked participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies.
-The 20 technologies were: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
-%
-%To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved.
-We randomized whether they performed the ranking for risks or benefits first.
-The prompt is listed in Appendix \ref{sec:prompt}.
-The question format was as follows:
-%
-%\begin{quotation}
-%{\it \noindent Fill in your <risk/benefit> numbers for the following:\\
-%
-%\noindent Handguns: \_\_\_\_\_\_\_ \\
-%Motorcycles: \_\_\_\_\_\_\_\\
-%Lawnmowers: \_\_\_\_\_\_\_\\
-%<Wearable Technology>: \_\_\_\_\_\_\_\\
-%Electricity: \_\_\_\_\_\_\_\\ }
-%\end{quotation}
 
@@
 To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes.
+However, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks.
+We talk about this more in Section 4.
 
@@
 
-%We followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses.
-Rather, we report medians and quartiles, which are not impacted by outliers.
-For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,782 responses, with an initial agreement rate of 89.7\%.
-The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.
-
 \section{Results}
 In this section, we present participants' responses to the various data-sharing scenarios, and discuss how and which various factors contributed to their risk perceptions.
-We also discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies.
-We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.
+We had at least 141 responses per data type, 2,779 per recipient, and 35 responses per each unique data type/recipient combination.
+We conclude the section with participants' self-reported wearables concerns.\\
 
-%\subsection{Concern Factors}
-%Many factors can potentially impact participants' concern levels:  the data being shared, with whom the data is shared, and device in question.
-We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of the above factors and additional demographic traits.
-
-\subsubsection{Data Type}
-\label{sec:datatypes}
-
-Based on our statistical models (later reported in Section \ref{sec:regression}), we observe that the largest effect on participants' VURs stemmed from the data being shared; with whom the data is shared and which device the user is interacting with had weaker impacts on overall VURs.
-The most and least concerning data types are listed in Table \ref{top10-table}, and the full list can be seen in Table \ref{full-vur-table} in Appendix \ref{sec:concerns-appendix}.
+\noindent {\bfseries Data Type}
+Based on our statistical models (later reported in Section \ref{sec:regression}), we observe that the largest effect on participants' VURs stemmed from the data being shared, rather than  with whom the data is shared.
+The most and least concerning data types are listed in Table \ref{top10-table}.
 
@@
 Generally, the average concern magnitude was inversely correlated with the standard deviation, which suggests the presence of ceiling effects for the most concerning data types.
-For the complete ranked list of data types in this study, see Appendix \ref{sec:concerns-appendix}.
+For the complete ranked list of data types in this study, see Table \ref{all-vur}.\\
 
@@
 \end{tabular}
-\caption{The 10 most and least upsetting data types, across all recipients. For the complete list of all data types across all recipients, see Appendix \ref{sec:concerns-appendix}.}
+\caption{The 10 most and least upsetting data types, across all recipients.}
 \label{top10-table}
@@
 
-\subsubsection{Data Recipient}
-A statistically significant difference in VUR exists between data shared with an application versus data shared with human recipients.
+\noindent {\bfseries Data Recipient}
+A statistically significant difference in VUR exists between data shared with an application versus human recipients.
 On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were almost double (Table \ref{recipient-vur}).
@@
 However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
+
+The statistical significance arises for two distinct reasons.
+Firstly, sharing data only with an application's server carries less social impact.
+And for our participants, it may seem that it is shared with less people.
+Additionally, there is a class of data which may be considered odd for a human to know, but completely normal for a wearable device to know (e.g., it's okay if your fitbit knows when you sleep, but maybe less so for your friends).
 
@@
 People are more comfortable sharing certain data types with certain human recipients.
-For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.
-Table \ref{all-vur} Appendix \ref{sec:concerns-appendix} shows the  complete VUR and rankings of all data types by recipient.
-
-%People have been shown to behave differently, especially in the social arena \cite{dwyer2007trust, gross2005information, fogel2009internet}.
+For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.Table \ref{all-vur} shows the  complete VUR and rankings of all data types by recipient.\\
 
@@
 
-\begin{table}[t]
-\small
-\begin{center}
-\begin{tabular}{| c | r | r |}
-\hline
- Misbehavior &  Cubetastic3000 & Smartphone \\
- \hline
- \hline
- All & 58.79\% & 46.67\%\\
- \hline
-Vibration & 14.81\%  &  6.14\%\\
-Bluetooth & 44.12\%  &  19.86\%\\
-Unmuted Call & 87.10\%  &  58.44\%\\
-Screenshot & 52.78\%  & 55.74\%\\
-Premium Calls/Texts & 86.49\%  &  91.94\%\\ 
-\hline
-\end{tabular}
-\caption{VURs for the five questions about device misbehaviors described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
-\label{deviceVUR}
-\end{center}
-\end{table}
-
-%\subsubsection{Device}
-%Each participant answered two questions drawn from a set of five smartphone misbehaviors.
-To compare these misbehaviors with misbehaviors on the Cubetastic3000, we included these same five questions amongst the pool of 293 Cubetastic3000 scenarios, modifying the device in question.
-In this manner, all 1,782 participants received two smartphone questions, while 159 participants received at least one of these five Cubetastic3000 misbehavior questions.
-Across all participants, the VUR was 46.7\% (of 1,782) for smartphones, whereas the VUR increased to 58.8\% (of 159) for same misbehaviors on the Cubetastic3000.
-The VURs for both devices for these questions are in Table \ref{deviceVUR}.
-%
-%To ensure independence of observations, we performed a Mann-Whitney U test to compare participants' average VURs for the Cuebtastic3000 scenarios (i.e., 159 participants) to the remaining participants' average VURs for the smartphone scenarios (i.e., 1,623 participants).
-This difference is statistically significant ($U=108,664.0$ with $p<0.0005$) but the effect size is very small ($r=0.08$).
-Because of this, we did not further reduce our statistical power by separately comparing the five misbehaviors.
-We conclude that users are likely more wary of misbehaviors on wearables than smartphones, but this difference is likely negligible.
-The entire effect may be due to participants' familiarity with smartphones, and therefore this effect may disappear as they increasingly encounter more wearables.
-
-%{\color {red} talk about the variance of the devices in general--was there more spread for the answers wrt smartphones, cubetastic, or were they kind of all the same?}
-
-%\begin{table}%[h]
-%\begin{center}
-%\begin{tabular}{| c | c | c | c |}
-%Question & $\chi^2$ &	2-tail P & Effect Size \\
-%All & 0.444  & 0.505 & 0.006\\
-%Q1 & 0 & 1 & 0 \\
-%Q2 & 0 & 1 & 0\\
-%Q3 & 0 & 1 & 0\\
-%Q4 & 0 & 1 & 0\\
-%Q5 & 0 & 1 & 0\\
-%\end{tabular}
-%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
-%\label{withindevice}
-%\end{center}
-%\end{table}
-
-%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test.
-Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone).
-The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid.
-For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
-
-%\subsection{Risk and Benefit Rankings} 
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=\columnwidth]{images/riskbenefit.pdf}
-%	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
-%	\label{fig:techplot}
-%\end{figure}
-%
-%We ask participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their  benefits and risk.
-We also ask them about technologies with which they were likely to be more familiar (e.g., smartphones and laptops) and two specific wearable devices, Google Glass and the fictitious Cubetastic3000.
-To calibrate our results, we  ask about four well-established technologies studied by Fischhoff \etal\cite{Fischhoff}.
-We find that participants generally rated technologies related to wearables as being low-risk comparatively to other technologies (Figure \ref{fig:techplot}).
-Tables \ref{risk} and \ref{benefit} in Appendix ~\ref{sec:concerns-appendix} shows participants' median, quartiles, and distributions of risks and benefit ratings for all technologies.
-%
-%Participants were prompted to rate technologies with respect to all considerations (see Appendix~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life.
-Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk.
-Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk.
-%
-%We examined participants' perceptions, and therefore responses may not be reflective of actual risks or benefits.
-However, they also reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits.
-We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities and that performing this experiment longitudinally may yield more interesting results, as these technologies become pervasive (and more familiar to participants).
-%
-%As a group, participants rated more familiar technologies as more beneficial.
-We believe this is the result of exposure to these technologies---most people use these technologies daily and therefore see what the benefits of these technologies are.
-It is true that people perceive unfamiliar technologies as less beneficial at the moment, but this will change as the use of these technologies evolve and adoption increases.
-Most calibration technologies, with the exception of electricity, were seen as lower benefit than the others.
-However, Google glass and Cubetastic3000 were about equally beneficial, and gender and age recognition were less beneficial.
-%
-%We find that the more familiar a participant was with a technology, the more likely they were to rate it as risky.
-Again, we believe that this is due to the exposure to these technologies.
-Of the wearable technologies, the riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10'').
-We did not test the differences in risk between the different wearable-related technologies for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible.
-Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.
-
-\subsection{Open-Ended Concerns for Wearables}
+\noindent {\bfseries Open-ended Concerns}
 We captured participants' reactions to wearable devices as a whole by asking the following open-ended question:
@@
 
-This question was asked with demographics questions, but before any IUIPC questions (which asked a lot of direct privacy-related questions, to avoid biasing the recipients).
-The participants were presented with a blank box to write in, with no character limit to their open-ended responses.
-
+The participants were presented with a blank box to write in, with no particular suggestion on what to talk about, and with no character limit to their open-ended responses.
 Table \ref{openresponses} shows common user concerns related to wearable devices.
 Appendix \ref{sec:coding} details the responses categorized in each coding label.
-Most are related to privacy and security, but this open-ended data gives a sense of what broad categories of concerns are most relevant to users.
-This can be used to guide research in unexplored use cases.
+Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible privacy and security risks.
 
-In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware).
-Other orthogonal concerns included long-term health effects caused from wearing the device such as cancer from EMF waves (Health) and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).
-Interestingly, participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
+\begin{quotation}
+\noindent
+\textit{P246: ``Privacy and security of your data, particularly for eg, stored financial/payment or medical information''}\\
+
+\noindent
+\textit{P1256: ``They can be hacked and then your security will be compromised.''}
+\end{quotation}
+
+Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).
+
+\begin{quotation}
+\noindent
+\textit{P1742: Capturing and sharing data and information that you are unaware of.}\\
+
+\noindent
+\textit{P670: ``Are there microwaves or some such type of waves that can pass through the brain and harm the brain?  Wearing something all day can hurt that area of the body after a while.''}\\
+
+\noindent
+\textit{P1038: ``Becoming distracted by the devices while doing other activities that require concentration such as driving.''}\\
+
+Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
+
+\noindent
+\textit{P1425: I think the biggest risk is how they may effect society as a whole...
+a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}
+\end{quotation}
+
+The landscape of users' perceived risks associated with wearable devices are broad, encompassing concepts such as privacy and security, but also non-technical aspects such as health, safety, and change in social behaviors.
+We hope that this motivates researchers to investigate these aforementioned risks.
+\\
 
@@
 
-\subsubsection{Demographic Factors}
-
+\noindent {\bfseries Demographics Factors}
 We see that privacy is a main concern for wearables users.
@@
 The effect of a participant's gender also did not remain significant upon correcting for multiple testing.
-We observed no correlation between a participant's education level and VUR.
+We observed no correlation between a participant's education level and VUR.\\
 
-\subsubsection{Regression Models} 
+\noindent {\bfseries Regression Models}
 \label{sec:regression}
-In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
+To examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes).
 We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).
@@
 We created several models using two independent variables as predictors: data and recipient.
-Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) is only varied for the five smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, resulting in a total of 72 types of data shared with 4 possible recipients.
-We used the following demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
+This resulted in a total of 72 types of data shared with 4 possible recipients.
+Demographic factors used as covariates are: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score.
 For each model, we performed Wald's test to examine the model effects attributable to each of these parameters.
@@
 To make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the type of data (e.g., video, audio, etc.) and the type of risk it presents.
-Two researchers agreed on a codebook and independently coded each of the 72 data types.
+Two researchers agreed on a codebook and independently coded each of the 72 data types.\\
 
@@
 We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.
+\\
 
@@
 When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type.
-%The full model can be found in Appendix \ref{sec:regression-apx2}.
 
 \section{Discussion}
-%We discuss considerations when interpreting our results, the limitations of our work, and future work we hope to inspire.
 
-\subsection{Limitations}
+\noindent {\bfseries Limitations}
 One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable.
@@
 
-\subsection{Future Research Directions}
+Although we presented with our participants with a prompt illustrating all the benefits of a wearable, the questions we asked isolated from the risk from the benefits of sharing data with a particular recipient.
+We sacrificed context due to the complexity of the question necessary for the participant to answer correctly.
+Users are willing to tolerate risks if there is enough benefit associated with that risk.
+We do believe that since all of our questions were out of context, our study does represent what data people ambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\
+
+\noindent {\bfseries Future Research Directions}
 We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications.
@@
 Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impact.
+
+\section{Related Work}
+\noindent {\bfseries Ubiquitous Sensing} We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
+Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
+Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
+Our work aims to augment works like these with an understanding of what privacy means to the end user.
+\\
+
+\noindent {\bfseries Lessons form Smartphones} Smartphones allow applications to access new types of data.
+While this tends to benefit users, they do not think of the privacy implications.
+Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
+There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
+
+Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
+Their survey asked 3,115 smartphone users about 99 risk scenarios.
+Participants were asked how upset they would be if a certain action occurred without their permission.
+Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.\\
+
+\noindent {\bfseries User Perceptions} While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
+For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
+While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
+
+One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
+Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
+However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
 
@@
 \input{tex-inputs/appendixes.tex}
-%\input{tex-inputs/collapsed.tex}
-%\input{tex-inputs/riskben.tex}
 \input{tex-inputs/VURcombined.tex}
 
-%%% REGRESSION MODEL
-
-%\onecolumn
-%\section{Full Regression Model from Data Types}
-%\label{sec:regression-apx}
-%%\begin{figure*}[t]
-%\includegraphics[page=1,scale=0.8]{images/full-model.pdf}
-%\includepdf[pages=2-3,scale=0.8]{images/full-model.pdf}
-%
-%%\caption{Full regression model, which includes all 72 data types, recipients, and covariates.}
-%%\end{figure*}
-%
-%\section{Full Regression Model from Data Risks / Data Categories}
-%\label{sec:regression-apx2}
-%%\begin{figure*}[t]
-%\includegraphics[page=1,scale=0.8]{images/full-model2.pdf}
-%\includepdf[pages=2,scale=0.8]{images/full-model2.pdf}
-%
-%\twocolumn
-
 \end{document}

### 2015-12-11 tex-inputs/appendixes.tex
finished rough draft

@@
 
+\section{Omitted Survey Questions}
+\label{sec:noquestions}
+Our participants answered four additional question which are not detailed in this paper.
+Two questions compared smartphones to wearable devices, to investigate if participants inherently saw wearables as threatening due to its unfamiliarity.
+The questions were not particularly well suited for this task, and our results showed no significant difference between smartphone and wearables perceptions.
+The other two questions asked our participants to numerically rate the risks and benefits of common, familiar technologies versus wearables (e.g., an airplane versus a wearable).
+In addition to the fact that these comparisons were unsound to make, our results largely highlighted our participants' unfamiliarity with wearables or other less common devices; participants rated more familiar technologies as more beneficial or risky.
+
 \section{Coding Label Definitions}

### 2015-12-19 paper.tex
Fix broken section reference (it was a ref to start of Sec 3)
Took full pass, fixed a lot of typos

@@
 \title{Risk Perceptions for Wearable Devices}
-%\numberofauthors{1}
-%\author{
-% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-%   \vspace{0.5em}
-%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
-%}
-
 \numberofauthors{1}
 \author{
- \alignauthor Anonymous\\
+ \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
    \vspace{0.5em}
-   \affaddr{Some Place}
+   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
+   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
 }
+
 \maketitle
@@
 We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning.
-Our study  relatively ranks a range of potential wearables data capture scenarios, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable).
+Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape of users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable).
 To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables.
@@
 
-Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to an virtual-object filled augmented reality.
+Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to a virtual-object filled augmented reality.
 However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
@@
 
-The goal of this work is to motivate research on the still-malleable future of wearable interaction models to preserve privacy and security, which we found are the top user perceived risk associated with wearable devices.
+The goal of this work is to motivate research on the still-malleable future of wearable interaction models to preserve privacy and security, which we found are the top user perceived risks associated with wearable devices.
 Our survey of 1,782 Internet users contributes the following: %\\[-0.8cm]
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We give a relative ranking of 72 potential wearables capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
+\item We give a relative ranking of 72 potential capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
 \item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient.
@@
 The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}.
-To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we ask our participants an open-ended question.
+To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we asked our participants an open-ended question.
 
 To obtain a representative list of scenarios, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
-At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc.
+At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc.
 These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today.
@@
 \subsection{Survey Questions}
-\noindent Each participant answered 27 questions across 5 sections:  \\[-.5cm]
+\noindent We report on participants' responses to 23 questions across 4 survey sections:  \\[-.5cm]
 
@@
 
-To assist in user fatigue, gave our participants a randomly selected subset of wearables scenarios.
-The average survey completion time was 11.5 minutes, which includes time for answering questions that are omitted from this paper due to lack of participants' familiarity with specific wearables devices and a misguided attempt to directly compare smartphones and wearables.
+To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios.
+The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables.
 See Appendix \ref{sec:noquestions} for details.
@@
 The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
-Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset'')..
-Figure \ref{fig:prompt}) shows an example.
+Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset'').
+Figure \ref{fig:prompt} shows an example.
 Specifically, questions were of the form:
@@
 
-We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions.We randomly pick 6 wearables scenarios from a list of 288 scenarios, and also display them to the user in a random order.
-Our 288 scenarios are the result of permuting 72 scenarios with 4 recipients, which can be seen in Table \ref{all-vur}.
-We clarified for our participants that ``app'' meant the the app's server, and that the data was not shared with anyone else.
-Each participant answered 6 questions that were randomly drawn from this pool.
+We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form a pool of 288 scenarios (Table \ref{all-vur}).
+Each participant answered 6 questions that were randomly drawn from this pool, displayed in random order.
+We clarified for our participants that ``app'' meant the app's server, and that the data was not shared with anyone else.
 
 \subsubsection{Additional Questions}
-The exit portion of the survey contained demographic questions asking for age, gender, and education.
-We then asked about wearables ownership so we could control for prior exposure.
-An open-ended question on what would be the most likely risks associated with wearable devices was included to catch user concerns more broadly.
+The exit portion of the survey contained demographic questions (age, gender, and education), and then asked about wearable device ownership so we could control for prior exposure.
+An open-ended question on what would be the most likely risks associated with wearable devices was included to capture user concerns more broadly.
 To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes.
@@
 
-In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.
+In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario~\cite{Felt}.
 The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
@@
 Additionally, most people are likely to be upset, at least a little, in all scenarios, because a device is taking action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344).
-Thus, the distinguishing factor is whether a participant was maximally upset, rather than if they were upset.
+Thus, the distinguishing factor is whether a participant was maximally upset.
 A limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.
@@
 Firstly, sharing data only with an application's server carries less social impact.
-And for our participants, it may seem that it is shared with less people.
-Additionally, there is a class of data which may be considered odd for a human to know, but completely normal for a wearable device to know (e.g., it's okay if your fitbit knows when you sleep, but maybe less so for your friends).
+And for our participants, it may seem that it is shared with fewer people.
+Additionally, there is a class of data which may be considered odd for a human to know, but completely normal for a wearable device to know (e.g., it's okay if your Fitbit knows when you sleep, but maybe less so for your friends).
 
@@
 People are more comfortable sharing certain data types with certain human recipients.
-For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.Table \ref{all-vur} shows the  complete VUR and rankings of all data types by recipient.\\
+For instance, participants were significantly more uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.
+Table \ref{all-vur} shows the complete VURs and rankings of all data types by recipient.\\
 
@@
 Appendix \ref{sec:coding} details the responses categorized in each coding label.
-Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible privacy and security risks.
+Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of privacy-related scenarios, which may have heightened their awareness of the possible privacy and security risks.
 
@@
 \noindent
-\textit{P246: ``Privacy and security of your data, particularly for eg, stored financial/payment or medical information''}\\
+\textit{P246: ``Privacy and security of your data, particularly for eg, [sic] stored financial/payment or medical information''}\\
 
@@
 
+\end{quotation}
+
 Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
 
+\begin{quotation}
 \noindent
@@
 
-The landscape of users' perceived risks associated with wearable devices are broad, encompassing concepts such as privacy and security, but also non-technical aspects such as health, safety, and change in social behaviors.
+The landscape of users' perceived risks associated with wearable devices is broad, encompassing concepts such as privacy and security, but also non-technical aspects such as health, safety, and change in social behaviors.
 We hope that this motivates researchers to investigate these aforementioned risks.
@@
 We see that privacy is a main concern for wearables users.
-Additionally, we show that privacy preferences should also be a consideration for configuring a user's device.
-A participant's self-reported level of privacy concerns is the biggest demographic predictor of participants' VUR rate.
-This is determined by the IUIPC scale~\cite{malhotra2004internet}.
-A Spearman correlation yielded a statistically significant effect between average IUIPC scores and VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences.
+Additionally, we show that privacy preferences should also be a consideration when configuring a user's device.
+A participant's self-reported level of privacy concern---as determined by the IUIPC scale~\cite{malhotra2004internet}---is the biggest demographic predictor of VURs.
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences.
 Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$).
@@
 One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state.
-As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.
+As mentioned earlier, participants saw these as publicly observable and therefore unconcerning.
 
@@
 One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable.
-Because of this, our participants may be over or underestimating the risk, stemming form an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
-Our participants also did not differentiate between the benefits of risks of various new capabilities.
+Because of this, our participants may be over or underestimating the risk, stemming from an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
+Our participants also did not differentiate between the benefits and risks of various new capabilities.
 
@@
 This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and preferences, so that future systems can be designed with these in mind.
-We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over post hoc approaches (or ignoring user concerns altogether).
+We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over {\it post hoc} approaches (or ignoring user concerns altogether).
 
-Although we presented with our participants with a prompt illustrating all the benefits of a wearable, the questions we asked isolated from the risk from the benefits of sharing data with a particular recipient.
+Although we presented our participants with a prompt illustrating all the benefits of a wearable device, the questions we asked isolated the risk from the benefits of sharing data with a particular recipient.
 We sacrificed context due to the complexity of the question necessary for the participant to answer correctly.
@@
 We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications.
-We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourage work for contextual and user-input- independent permission models and access control schemes.
+We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work for contextual and user-input-independent permission models and access control schemes.
 
@@
 
-\noindent {\bfseries Lessons form Smartphones} Smartphones allow applications to access new types of data.
+\noindent {\bfseries Lessons from Smartphones} Smartphones allow applications to access new types of data.
 While this tends to benefit users, they do not think of the privacy implications.
@@
 
- Our survey of 1,784 Internet users, is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices.
+ Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices.
 We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
-We calibrate our results with mobile devices and existing technologies; additionally, we verify with an open-ended question and find that privacy and security are at the top of user's overall concerns.
-Wearables are still in their infancy.
-Perceptions of situations and capabilities will change rapidly with advancements and increased exposure.
-However, there is not much work done to determine which threats in the emerging threat landscape are pertinent to focus on.
-Inspection of possible data concerns agree with previous studies of smartphone studies to find that video capture and financial data to be most sensitive.
+Our open-ended responses show that privacy and security are at the top of user's overall concerns.
+While wearables are still in their infancy, perceptions of situations and capabilities are likely to change rapidly with advancements and increased exposure.
+However, there has not been much prior work done to determine which threats in the emerging threat landscape are pertinent to focus on.
+Our examination of possible data concerns agree with previous studies of smartphone users that found that video capture and financial data are the most sensitive data types.
 Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
-We also find that users' self-reported privacy preferences are correlated with how participants may react, even with respect to situations that they are unfamiliar with.
-Permissions and access control mechanisms which do not depend on user inputs can still benefit from being informed by user preferences.
-We hope that this work has given a comprehensive overview of user concerns and inform designs of future privacy and security work for wearable devices.
+We also found that users' self-reported privacy preferences are correlated with how they may react, even with respect to situations that they are unfamiliar with.
+Our results may be used by system designers to create permissions and access control mechanisms that do not directly depend on users' inputs.
+We hope that this work has given a comprehensive overview of user concerns and informs designs of future privacy and security work for wearable devices.
 

### 2016-01-29 data-files/excelp.py
organization

@@ -1,0 +1,239 @@
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+from xlrd import open_workbook
+from numpy import median
+def parser(x):
+	x = open_workbook("data.xlsm")
+	sheet = x.sheet_by_index(3)
+	rtn = dict()
+	benefit_dic = dict()
+	risk_dic = dict()
+	final_dic = dict()
+	risk_fdic = dict()
+	benefit_fdic = dict()
+	stat = dict()
+	temp = dict()
+	for j in range(312,323):
+		lst = []
+
+		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
+
+
+			for i in range(1,1785):
+				cat = sheet.cell_value(i,j)
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+				if arg < 10:
+					arg = 10
+				if arg > 100:
+					arg = 100
+				if sheet.cell_value(0,j) == "ben":
+					ben_arg = str(sheet.cell_value(i,3)).replace(" ", "")
+					if ben_arg+ "ben" in benefit_dic:
+						benefit_dic[ben_arg+ "ben"].append(arg)
+					else:
+						benefit_dic[ben_arg + "ben"] = [arg]
+
+
+				if str(sheet.cell_value(i,3)  +sheet.cell_value(0,j)) in rtn:
+					rtn[str(sheet.cell_value(i,3))  + sheet.cell_value(0,j)].append(arg)
+				else:
+					rtn[str(sheet.cell_value(i,3))  +sheet.cell_value(0,j)] = [arg]
+
+
+		else:
+			for i in range(1,1785):
+				arg = sheet.cell_value(i,j)
+				if arg != '':
+					if type(arg) != float:
+						print('error', i,j,arg)
+						return
+					if arg > 100:
+						arg = 100
+					if arg < 10:
+						arg = 10
+					lst.append(int(arg))
+			if len(lst)!= 0:
+				check = sheet.cell_value(0,j)
+				if "Electricity" in check:
+					if "risk" in check:
+						check = "Electricity Risk"
+					else:
+						check = "Electricity Benefit"
+				elif "Motorcycle" in check:
+					if "risk" in check:
+						print("here it is")
[…]

### 2016-01-29 old-stuff/parser.py

@@ -1,0 +1,399 @@
+
+import numpy as np
+import matplotlib.pyplot as plt
+from pylab import *
+
+def parse(text):
+
+	f = open(text,'r')
+	# friends = open("friends.tex",'w')
+	# work = open("work.tex",'w')
+	# pub = open("pub.tex",'w')
+	# app = open("app.tex",'w')
+	collapsed = open("collapsed.tex",'w')
+	collapsed_std = open("collapsedstd.tex",'w')
+	VUR_combined = open("VURcombined.tex",'w')
+	recipient = open("recipient.tex",'w')
+	x = """\\documentclass[a4paper,12pt]{article}
+\\usepackage[cm]{fullpage}
+\\usepackage{longtable}
+\\usepackage{graphicx}
+\\begin{document}
+\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
+
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endfirsthead
+
+\\multicolumn{3}{c}%
+{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
+\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
+\\endhead
+
+\\hline \\multicolumn{4}{|r|}{{Continued on next page}} \\\\ \\hline
+\\endfoot
+\\hline 
+\\endlastfoot\n"""
+	recipient.write("""\\begin{table}[t]
+\\begin{center}
+\\small
+\\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
+\\hline
+Rank & Recipient & VUR & Standard Deviation & Distribution\\\\
+\\hline\n""")
+	# friends.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
[…]

### 2016-01-29 excelp.py
.

@@ -1,239 +1,0 @@
-import csv
-import numpy as np
-import matplotlib.pyplot as plt
-from pylab import *
-from xlrd import open_workbook
-from numpy import median
-def parser(x):
-	x = open_workbook("data.xlsm")
-	sheet = x.sheet_by_index(3)
-	rtn = dict()
-	benefit_dic = dict()
-	risk_dic = dict()
-	final_dic = dict()
-	risk_fdic = dict()
-	benefit_fdic = dict()
-	stat = dict()
-	temp = dict()
-	for j in range(312,323):
-		lst = []
-
-		if sheet.cell_value(0,j) == "ben" or sheet.cell_value(0,j) == "risk":
-
-
-			for i in range(1,1785):
-				cat = sheet.cell_value(i,j)
-				arg = sheet.cell_value(i,j)
-				if arg != '':
-					if type(arg) != float:
-						print('error', i,j,arg)
-						return
-				if arg < 10:
-					arg = 10
-				if arg > 100:
-					arg = 100
-				if sheet.cell_value(0,j) == "ben":
-					ben_arg = str(sheet.cell_value(i,3)).replace(" ", "")
-					if ben_arg+ "ben" in benefit_dic:
-						benefit_dic[ben_arg+ "ben"].append(arg)
-					else:
-						benefit_dic[ben_arg + "ben"] = [arg]
-
-
-				if str(sheet.cell_value(i,3)  +sheet.cell_value(0,j)) in rtn:
-					rtn[str(sheet.cell_value(i,3))  + sheet.cell_value(0,j)].append(arg)
-				else:
-					rtn[str(sheet.cell_value(i,3))  +sheet.cell_value(0,j)] = [arg]
-
-
-		else:
-			for i in range(1,1785):
-				arg = sheet.cell_value(i,j)
-				if arg != '':
-					if type(arg) != float:
-						print('error', i,j,arg)
-						return
-					if arg > 100:
-						arg = 100
-					if arg < 10:
-						arg = 10
-					lst.append(int(arg))
-			if len(lst)!= 0:
-				check = sheet.cell_value(0,j)
-				if "Electricity" in check:
-					if "risk" in check:
-						check = "Electricity Risk"
-					else:
-						check = "Electricity Benefit"
-				elif "Motorcycle" in check:
-					if "risk" in check:
-						print("here it is")
[…]

### 2016-01-29 old-stuff/parser.py
.

@@ -1,399 +1,0 @@
-
-import numpy as np
-import matplotlib.pyplot as plt
-from pylab import *
-
-def parse(text):
-
-	f = open(text,'r')
-	# friends = open("friends.tex",'w')
-	# work = open("work.tex",'w')
-	# pub = open("pub.tex",'w')
-	# app = open("app.tex",'w')
-	collapsed = open("collapsed.tex",'w')
-	collapsed_std = open("collapsedstd.tex",'w')
-	VUR_combined = open("VURcombined.tex",'w')
-	recipient = open("recipient.tex",'w')
-	x = """\\documentclass[a4paper,12pt]{article}
-\\usepackage[cm]{fullpage}
-\\usepackage{longtable}
-\\usepackage{graphicx}
-\\begin{document}
-\\begin{longtable}{| p{0.5cm} | p{7cm} | p{1cm} | c |}
-
-\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
-\\endfirsthead
-
-\\multicolumn{3}{c}%
-{{\\bfseries \\tablename\ \\thetable{} -- continued from previous page}} \\\\
-\\hline \\multicolumn{1}{|c|}{\\textbf{Rank}} & \\multicolumn{1}{c|}{\\textbf{Question}} & \\multicolumn{1}{c|}{\\textbf{VUR}} &  \\multicolumn{1}{c|}{\\textbf{Distribution}} \\\\ \\hline 
-\\endhead
-
-\\hline \\multicolumn{4}{|r|}{{Continued on next page}} \\\\ \\hline
-\\endfoot
-\\hline 
-\\endlastfoot\n"""
-	recipient.write("""\\begin{table}[t]
-\\begin{center}
-\\small
-\\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
-\\hline
-Rank & Recipient & VUR & Standard Deviation & Distribution\\\\
-\\hline\n""")
-	# friends.write("\\begin{table}[t]\n\\begin{center}\n\\small\n\\begin{tabular}{| p{0.5cm} | p{7cm} | p{1cm} | c |}\n\\hline\n Rank & Q &  VUR & Distribution  \\\\ \n\\hline\n")
[…]

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
camera ready version with template

--- 2015-12-19 paper.tex
@@
-\documentclass{sig-alternate-hotpets15}
+%% Modified for USEC 2016 on 2015/10/06
+
+\documentclass[conference]{IEEEtran}
 \usepackage{color}
@@
 \usepackage{pdfpages}
+\pagestyle{plain}
 
-\def\etal{{\it et al.~}}
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
+% not currently provide for hyperlinked citations.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
 
 \begin{document}
+%
+% paper title
+% can use linebreaks \\ within to get better formatting as desired
 \title{Risk Perceptions for Wearable Devices}
-\numberofauthors{1}
-\author{
- \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
-   \vspace{0.5em}
-   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
-   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+\author{\IEEEauthorblockN{Linda Lee, JoongHwa Lee, Serge Egelman, David Wagner}
+\IEEEauthorblockA{University of California, Berkeley\\
+\{lnl@,dlwndghk94,egelman,daw\}@cs.berkeley.edu}}
+%\and
+%\IEEEauthorblockN{JoongHwa Lee}
+%\IEEEauthorblockA{University of California, Berkeley\\
+%dlwndghk94@berkeley.edu }
+%\and
+%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
+%\IEEEauthorblockA{Starfleet Academy\\
+%someemail@somedomain.com}}
+
+\IEEEoverridecommandlockouts
+\makeatletter\def\@IEEEpubidpullup{9\baselineskip}\makeatother
+\IEEEpubid{\parbox{\columnwidth}{Permission to freely reproduce all or part
+    of this paper for noncommercial purposes is granted provided that
+    copies bear this notice and the full citation on the first
+    page. Reproduction for commercial purposes is strictly prohibited
+    without the prior written consent of the Internet Society, the
+    first-named author (for reproduction of an entire paper only), and
+    the author's employer if the paper was prepared within the scope
+    of employment.  \\
+    USEC '16, 21 February 2016, San Diego, CA, USA\\
+    Copyright 2016 Internet Society, ISBN 1-891562-42-8\\
+    http://dx.doi.org/10.14722/usec.2016.23006
 }
+\hspace{\columnsep}\makebox[\columnwidth]{}}
 
+% make the title area
 \maketitle
@@
 \begin{abstract}
-\indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
+\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
 We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning.
@@
 \end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]
-
-%\terms{Human Factors}{Measurement}{Security}
-
-\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings
 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{images/prompt.png}
+	\includegraphics[width=\columnwidth]{prompt.png}
 	\caption{An example of a wearable scenario question participants saw while taking the survey.}
@@
 
-Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
+Felt {\it et al.} previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
 Their survey asked 3,115 smartphone users about 99 risk scenarios.
@@
 
+% that's all folks
 \end{document}

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
updated the related work section

@@
 \section{Related Work}
-\noindent {\bfseries Ubiquitous Sensing} We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique and difficult problems these devices present in terms for law and policy~\cite{roesner2014augmented}.
-Many researchers have worked to study how privacy can be preserved in the presence of ubiquitous devices.
-Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
-Our work aims to augment works like these with an understanding of what privacy means to the end user.
+\noindent {\bfseries User Perceptions} 
+While risk communication for the physical world has been examined for several decades (e.g.,~\cite{slovic2000perception, Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
+For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
+While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users'  information risk acceptance in this domain is warranted prior to examining risk communication.
+
+Our study is limited to owners of general consumer wearable devices.
+Denning {\it et al.}\ study the effect of wearables on bystanders, to find that bystanders have a range of indifferent to negative reactions which depend on the how acceptable users find the recording to be.
+Nasir {\it et al.}\ specifically explore medical wearables, to find that perceived risk determines physician and user acceptance of wearable health technologies.
+
+One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
+Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
+Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
+However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
 \\
 
-\noindent {\bfseries Lessons from Smartphones} Smartphones allow applications to access new types of data.
+\noindent {\bfseries Ubiquitous Sensing} We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique problems present in terms for law and policy~\cite{roesner2014augmented}.
+Privacy preservation research in this age of ubiquitous sensing include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
+Our work aims to guide these efforts with an insight into user acceptance of common information risks.
+\\
+
+\noindent {\bfseries Lessons from Smartphones} Not long ago, smartphones revolutionized applications' access to  data.
 While this tends to benefit users, they do not think of the privacy implications.
-Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}.
-There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.
+There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}, which are applicable to wearables.
 
@@
 Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.\\
-
-\noindent {\bfseries User Perceptions} While risk communication for the physical world has been examined for several decades (e.g.,~\cite{Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
-For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
-While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users' risk perceptions in this domain is warranted, prior to examining risk communication.
-
-One limitation of user perceptions is that people do not always have enough information to make privacy-sensitive decisions.
-Even if users did have this information, it has been shown that users often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}.
-Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
-However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
 

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
change title and abstract to discuss information disclosure

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Risk Perceptions for Wearable Devices}
+\title{Perceptions of Information Disclosure Risks for Wearable Devices}
 
@@
 \begin{abstract}
-\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent.
-We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning.
-Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape of users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable).
-To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables.
-We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
+\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential information disclosure risks that could expose users' activities without their awareness or consent.
+We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify which users find most concerning if disclosed.
+Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data disclosure, and concludes with a survey of users' risks perceptions associated with wearable devices.
+Users perceive associate risks of owning a wearable with compromised privacy and security, but also consider factors such as safety risk, changes in social behaviors, and how wearable devices are unfashionable.
+To our knowledge, this is the largest user-based experiment concerning information disclosure regarding wearables.
+We hope that this work will aid in the design of future user notification, permission management, and access control schemes for wearables.
 \end{abstract}

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
fix < and > errors

@@
 \noindent
-\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}
+\textit{``How would you feel if an app on your Cubetastic3000 learned (data) and shared it with (recipient), without asking you first?''}
 \end{quotation}
@@
 
-We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form a pool of 288 scenarios (Table \ref{all-vur}).
+We combined 72 data types, ({\it data}), with 4 data recipients, ({\it recipient}), to form a pool of 288 scenarios (Table \ref{all-vur}).
 Each participant answered 6 questions that were randomly drawn from this pool, displayed in random order.
@@
 
-%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper.
-We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
+%A statistical analysis regarding the significance and confidence of data types with respect to all 72 was not performed due to the space constraints of the paper.
+We do consider all data categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.
 
@@
 \hline
-Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
-Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
-Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
-Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
-Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
-Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
+Work-App	& 565.910 & \textless0.0001 & 5,083 & 0.111\\
+Public-App	& 481.776 & \textless0.0001 & 5,1988& 0.093\\
+Friends-App & 381.653 & \textless0.0001 & 5,096 & 0.075\\
+Friends-Work & 20.39 & \textless0.0001 & 5,037 & 0.004\\
+Friends-Public & 5.41 & \textless0.0200 & 5,142 & 0.001\\
+Work-Public&  5.00 & \textless0.0253 & 5,129	& 0.001\\
 \hline
@@
 A participant's self-reported level of privacy concern---as determined by the IUIPC scale~\cite{malhotra2004internet}---is the biggest demographic predictor of VURs.
-A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences.
-Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$).
+A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p\textless0.0005$), which suggests responses to questions were mostly based on privacy preferences.
+Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p\textless0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p\textless0.0005$).
 Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.
@@
 While we initially observed an effect on VURs based on whether or not participants claimed to already own wearables (57.0\% vs.
-60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$).
+60.8\%, respectively; Mann-Whitney $U=202,896$, $p\textless0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$).
 The effect of a participant's gender also did not remain significant upon correcting for multiple testing.
@@
 The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
-Each parameter listed was statistically significant at $p<0.005$.}
+Each parameter listed was statistically significant at $p\textless0.005$.}
 \label{regression}
@@
 The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.
-Each parameter listed was statistically significant at $p<0.005$.}
+Each parameter listed was statistically significant at $p\textless0.005$.}
 \label{regression2}

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
fixing ugly formatting from template transition

@@
 The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables.
-See Appendix \ref{sec:noquestions} for details.
+See Appendix \ref{sec:noquestions} for details.\\
 
-\subsubsection{Comprehension Questions}
+\noindent {\bfseries Comprehension Questions}
 The beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
@@
 
-To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.
+To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.\\
 
-\subsubsection{Wearable Scenarios}
+\noindent {\bfseries Wearable Scenarios}
 We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts).
@@
 Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of privacy-related scenarios, which may have heightened their awareness of the possible privacy and security risks.
+\\
 
@@
 \noindent
-\textit{P1256: ``They can be hacked and then your security will be compromised.''}
+\textit{P1256: ``They can be hacked and then your security will be compromised.''}\\
 \end{quotation}
 
-Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).
+Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\
 
@@
 
-Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
+Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\
 
@@
 \textit{P1425: I think the biggest risk is how they may effect society as a whole...
-a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}
+a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}\\
 \end{quotation}

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
final wordsmith and orphankilling passthrough

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Perceptions of Information Disclosure Risks for Wearable Devices}
+\title{Information Disclosure Concerns in The Age of Wearable Computing}
 
@@
 We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify which users find most concerning if disclosed.
-Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data disclosure, and concludes with a survey of users' risks perceptions associated with wearable devices.
-Users perceive associate risks of owning a wearable with compromised privacy and security, but also consider factors such as safety risk, changes in social behaviors, and how wearable devices are unfashionable.
+Our study relatively ranks a potential data capture scenarios enabled by wearables and investigates the impact of the recipient of the data on the perceived risk of data disclosure.
+We conclude with a brief survey of users' perception of  general risks associated with wearable devices, which includes factors such as safety, changes in social behaviors, and impact on fashion.
 To our knowledge, this is the largest user-based experiment concerning information disclosure regarding wearables.
@@
 Wearables are a \$700 million, growing industry~\cite{cmo}.
-With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.
-This trend will likely continue, as 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
+With 20\% of the population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, ubiquitous computing is becoming a reality.
+This trend will continue, as 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.
 
@@
 \item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient.
-\item We sketch a landscape of users' self-reported concerns regarding wearable devices and analyze responses using logistic regression models. 
+\item We sketch a landscape of users' self-reported general risks regarding wearable devices and analyze responses using logistic regression models. 
 \end{itemize}
@@
 \section{Methodology}
-We designed a survey for our IRB-approved study to capture the general public's perception of wearables risks.
-To determine which of the current data capture scenarios were most concerning to users, we asked them to rate their level of concern for a handful of scenarios from a list of possible scenarios.
+We designed a survey for our IRB-approved study to capture the general public's perception of information disclosure risks associated with wearables.
+To determine the most concerning data disclosure scenarios, we asked them to rate their level of concern for a 6 of scenarios from a list of 72 possible scenarios.
 This was intended to elicit their perception of the severity and impact of the risk.
@@
 
-To obtain a representative list of scenarios, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
-At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc.
+To obtain a representative list of scenarios, 4 researchers examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market.
+At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks.
 These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today.
+For a scenario to be included in this study, the scenario was required to be understandable to a user, possible to happen with today's wearable devices, and capture unique information not in other scenarios.
 
 \subsection{Survey Questions}
-\noindent We report on participants' responses to 23 questions across 4 survey sections:  \\[-.5cm]
+\noindent We report on participants' responses to 23 questions across 4 survey sections:  \\
 
@@
 \item 1 open-ended wearables risk question
-\item 14 demographic questions %\\[-.8cm]
+\item 14 demographic questions \\
 \end{itemize}
@@
 \noindent {\bfseries Comprehension Questions}
-The beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
+The survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
 Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios on a fictitious wearable.
-We highlighted the capabilities of this device and described use cases:
+We highlighted the capabilities of this device and described use cases:\\
 
@@
 \noindent---infer information about you so you don't need to log in or search for things\\
-\noindent ...and much more!}
+\noindent ...and much more!}\\
 \end{quotation}
@@
 We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts).
-The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient.
+The purpose for using this question format was to determine how upset participants would be if data were inappropriately disclosed, and the extent to which their reactions were based on the data type and recipient.
 Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset'').
 Figure \ref{fig:prompt} shows an example.
-Specifically, questions were of the form:
+Specifically, questions were of the form: \\
 
@@
 \noindent
-\textit{``How would you feel if an app on your Cubetastic3000 learned (data) and shared it with (recipient), without asking you first?''}
+\textit{``How would you feel if an app on your Cubetastic3000 learned (data) and shared it with (recipient), without asking you first?''}\\
 \end{quotation}
@@
 
-We combined 72 data types, ({\it data}), with 4 data recipients, ({\it recipient}), to form a pool of 288 scenarios (Table \ref{all-vur}).
-Each participant answered 6 questions that were randomly drawn from this pool, displayed in random order.
-We clarified for our participants that ``app'' meant the app's server, and that the data was not shared with anyone else.
+We combined 72 data types ({\it data}) with 4 recipients ({\it recipient}) to form 288 scenarios (Table \ref{all-vur}).
+Each participant answered 6 randomly drawn questions, displayed in random order.
+We clarified that ``app'' meant that the data was not shared with anyone else but a server.
+\\
 
-\subsubsection{Additional Questions}
-The exit portion of the survey contained demographic questions (age, gender, and education), and then asked about wearable device ownership so we could control for prior exposure.
-An open-ended question on what would be the most likely risks associated with wearable devices was included to capture user concerns more broadly.
+\noindent {\bfseries Additional Questions}
+The exit portion of the survey collected demographics (age, gender, and education) and wearable device ownership so we could control for prior exposure.
+An open-ended question the most likely risks associated with wearable devices was included to capture user concerns more broadly.
 To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes.
-However, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks.
+However, we realize that we asked this open-ended question after exposing participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks.
 We talk about this more in Section 4.
@@
 We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group began with participants taking the survey then giving feedback on the format and the content, noting any instructions or questions that were unclear.
-The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include.
-Finally, we compensated participants with \$30 in cash.
-We recruited all of our focus group participants from Craigslist.
+The focus group participants took the survey, gave feedback on the format and the content, and noted any confusions.
+The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional information disclosure scenarios.
+The Craigslist-recruited participants received \$30 in cash for their time.
 Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 ($\mu = 36.1$, $\sigma = 15.3$).
@@
 We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above.
-We compensated each participant with \$1.75 upon successfully completing the survey.
+We compensated each participant with \$1.75 upon completing the survey.
 Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants.
@@
 A limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.
+This metric is commonly used in marketing research.
 
 \section{Results}
-In this section, we present participants' responses to the various data-sharing scenarios, and discuss how and which various factors contributed to their risk perceptions.
 We had at least 141 responses per data type, 2,779 per recipient, and 35 responses per each unique data type/recipient combination.
-We conclude the section with participants' self-reported wearables concerns.\\
+In this section, we present participants' responses to the various data disclosure scenarios and discuss various factors contributed to their risk perceptions.
+We conclude the section with self-reported general wearables concerns.\\
 
@@
 
-Participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information.
+Participants were most concerned about photos and videos, especially if they contained embarrassing content, personal content, nudity, financial information, or information that can be used to impersonate someone (e.g., usernames/passwords for websites).
 As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and are almost unanimously considered to be concerning.
-Information that could be used to impersonate someone (e.g., usernames/passwords for websites), or photos of someone at home, were also among the most concerning data types.
 
@@
 The statistical significance arises for two distinct reasons.
-Firstly, sharing data only with an application's server carries less social impact.
-And for our participants, it may seem that it is shared with fewer people.
+Firstly, sharing data only with a server carries less social impact.
+For our participants, it may seem that it is shared with fewer people.
 Additionally, there is a class of data which may be considered odd for a human to know, but completely normal for a wearable device to know (e.g., it's okay if your Fitbit knows when you sleep, but maybe less so for your friends).
@@
 Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
-Nonetheless, we repeated our analysis using only one randomly-selected data point per participant and found that our selected test was robust to this violation.
-Therefore, we conclude that participants were significantly more concerned about having their data seen by a human versus an application, though differences between specific human groups such as the public, friends, and work contacts were not as significant.
+Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation.
+Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were not as significant.
 Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.
@@
 For instance, participants were significantly more uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.
+We believe a more fine-grained study is required to measure these effects accurately, although we have insight into the existence of these trends.
 Table \ref{all-vur} shows the complete VURs and rankings of all data types by recipient.\\
@@
 \noindent
-\textit{What do you think are the most likely risks associated with wearable devices?}
+\textit{What do you think are the most likely risks associated with wearable devices?}\\
 \end{quotation}
 
-The participants were presented with a blank box to write in, with no particular suggestion on what to talk about, and with no character limit to their open-ended responses.
+Participants were asked to write in a blank box, with no particular suggestion on what to talk about or a character limit to their responses.
 Table \ref{openresponses} shows common user concerns related to wearable devices.
-Appendix \ref{sec:coding} details the responses categorized in each coding label.
-Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of privacy-related scenarios, which may have heightened their awareness of the possible privacy and security risks.
+Appendix \ref{sec:coding} details which responses were categorized in a coding label.
+Note that participants were especially concerned with privacy and security.
+Many answers mention scenarios not included in the study, but prior exposure to our questions may have heightened sensitivity to information disclosure risks.
 \\
@@
 
-Other significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\
+Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\
 
@@
 
-The landscape of users' perceived risks associated with wearable devices is broad, encompassing concepts such as privacy and security, but also non-technical aspects such as health, safety, and change in social behaviors.
-We hope that this motivates researchers to investigate these aforementioned risks.
+The landscape of users' perceived risks associated with wearables is broad, encompassing concepts outside of privacy and security.
+We hope that this frames our research to be just one aspect of risks associated with wearables, and motivates researchers to investigate these other risks.
 \\
@@
 \noindent {\bfseries Demographics Factors}
-We see that privacy is a main concern for wearables users.
-Additionally, we show that privacy preferences should also be a consideration when configuring a user's device.
 A participant's self-reported level of privacy concern---as determined by the IUIPC scale~\cite{malhotra2004internet}---is the biggest demographic predictor of VURs.
 A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p\textless0.0005$), which suggests responses to questions were mostly based on privacy preferences.
-Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p\textless0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p\textless0.0005$).
+Age was another significant predictor of VUR ($\rho=0.121$, $p\textless0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p\textless0.0005$).
 Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.
@@
 For each model, we performed Wald's test to examine the model effects attributable to each of these parameters.
-The only covariates that had an observable effect on our models were participants' gender and IUIPC scores, which also exhibited an interaction effect with each other.
+The covariates that had an observable effect on our models were participants' gender and IUIPC scores, which exhibited an interaction effect with each other.
 Thus, we opted to remove the other covariates from our analysis.
@@
 
-The data types fell into these six categories:
+The data types fell into these six categories:\\
 
@@
 \item Biometric Information
-\item Demographic Information
+\item Demographic Information\\
 \end{enumerate}
 
-While the first three categories are self-explanatory, the latter three categories are all based on different user characteristics.
+While the first three categories are self-explanatory, the latter three categories are based on user characteristics.
 We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.
@@
 
-The risks for data types fell into these five categories:
+The risks for data types fell into these five categories:\\
 
@@
 \item {\bf Physical:} physical harm to the user.
-\item {\bf Relationships:} damage to the user's inter-personal relationships.
+\item {\bf Relationships:} damage to the user's inter-personal relationships.\\
 \end{enumerate}
 
-After independently coding, the researchers met to resolve any disagreements, such that the results reflect unanimity.
+After independently coding,  researchers met to resolve any disagreements such that the results reflect unanimity.
 There was  83\% agreement prior to resolution.
@@
 We chose to categorize them as such as they are non-biological descriptors of the user.
-We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data.
-One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data is stolen and abused.
+We were surprised that biometric information was seen as  benign.
+We suspect most users today may have an inaccurate understanding of the risks if biometric data is stolen and abused.
 
@@
 One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state.
-As mentioned earlier, participants saw these as publicly observable and therefore unconcerning.
 
@@
 Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models.
-Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit.
+Because these risk categories and mediums are less likely to change over time, models that take these into account are likely more useful and less likely to be overfit.
 What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect.
@@
 One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable.
-Because of this, our participants may be over or underestimating the risk, stemming from an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}.
+Because of this, our participants may be over or underestimating the risk, stemming from an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  Biometrics were generally not a concern for our participants, although there are security and privacy implications~\cite{prabhakar2003biometric}.
 Our participants also did not differentiate between the benefits and risks of various new capabilities.
 
-We recruited both wearable users and non-users in order to yield a more representative sample of the general population.
+We recruited both wearable users and non-users to yield a representative sample of the general population.
 We could have easily recruited only wearables owners or people specifically interested in wearables.
@@
 Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}.
-At the same time, our results do reflect actual perceptions of wearable devices and the associated privacy scenarios involving them.
-This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and preferences, so that future systems can be designed with these in mind.
+At the same time, our results do reflect actual perceptions of wearable devices and the associated information disclosure scenarios.
+This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and acceptance so that future systems can be designed with these in mind.
 We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over {\it post hoc} approaches (or ignoring user concerns altogether).
@@
 \noindent {\bfseries Future Research Directions}
-We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications.
-We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work for contextual and user-input-independent permission models and access control schemes.
+Further work can be done to expand various aspects of this study.
+A study designed to highlight the differences in information disclosure acceptance, privacy preferences, or technical fluency between wearables owners and non-owners will compliment this work.
+Investigating more fine-grained data (e.g., investigating specific instances of location data, versus location data in general),  additional recipients (e.g., ``advertisers'' or ``acquaintances'') may lead to more nuanced results.
+Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impact.
 
-Further work can be done to expand various aspects of this study.
-Investigating more fine-grained data types (e.g., investigating specific instances of location data, versus location data in general) would be a useful endeavor to gain further insight into user perceptions.
-Adding additional recipients, such as ``advertisers'' or ``acquaintances'' may lead to more nuanced results.
-Additionally, the open-ended concerns illuminate areas of possible future research, such as the design of a distraction-free interface to prevent safety issues, and how to minimize negative social impact.
+We find that although people have opinions on applications which are familiar, users are still unfamiliar with particular data types or capabilities.
+We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work broadly in contextual and user-input-independent permission models and access control schemes.
 
@@
 Furthermore, actual behavior may deviate from stated privacy preferences~\cite{spiekermann2001privacy}.
-However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures in general against breaches of privacy and security in a new threat landscape.
+However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures against breaches of privacy and security in a new threat landscape.
 \\
@@
 
- Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices.
+ Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric information disclosure concerns int he age of wearable computing.
 We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
@@
 While wearables are still in their infancy, perceptions of situations and capabilities are likely to change rapidly with advancements and increased exposure.
-However, there has not been much prior work done to determine which threats in the emerging threat landscape are pertinent to focus on.
-Our examination of possible data concerns agree with previous studies of smartphone users that found that video capture and financial data are the most sensitive data types.
+Our examination of possible data concerns agree with previous studies of smartphone users that found that video capture and financial data are the most sensitive data types, and least acceptable to be disclosed without user consent.
 Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
@@
 Our results may be used by system designers to create permissions and access control mechanisms that do not directly depend on users' inputs.
-We hope that this work has given a comprehensive overview of user concerns and informs designs of future privacy and security work for wearable devices.
+We hope that this work has given an insight into user acceptability in information disclosure and general user concerns about wearable devices, and that this study motivates privacy and security work for wearable devices.
 

### 2016-01-29 USEC2016-camera-ready/tex-inputs/appendixes.tex
final wordsmith and orphankilling passthrough

--- 2015-12-11 tex-inputs/appendixes.tex
@@
-%!TEX root = ../paper.tex
+%!TEX root = ../camera-ready.tex
 \appendix
@@
 
-\section{Omitted Survey Questions}
+\noindent {\bfseries Omitted Survey Questions}
 \label{sec:noquestions}
@@
 The questions were not particularly well suited for this task, and our results showed no significant difference between smartphone and wearables perceptions.
+
 The other two questions asked our participants to numerically rate the risks and benefits of common, familiar technologies versus wearables (e.g., an airplane versus a wearable).
-In addition to the fact that these comparisons were unsound to make, our results largely highlighted our participants' unfamiliarity with wearables or other less common devices; participants rated more familiar technologies as more beneficial or risky.
+This was to mimic the methodology in Fischhoff's seminal study on attitudes toward technological risks and benefits.In Fischhoff's study, all technologies were concerning with physical risk, while ours mixed information disclosure risks with physical risks.
+These comparisons were unsound to make.
+Nonetheless, our results largely highlighted our participants' unfamiliarity with wearables or other less common devices; generally, participants rated more familiar technologies as more beneficial or risky.
+\\
 
-\section{Coding Label Definitions}
+\noindent {\bfseries Coding Label Definitions}
 \label{sec:coding}
-Researchers coded the self reported answers as follows:\\
-{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
+We realize that coding answers ranging from 1 to 1,400+ words into a single, one-word category is tricky.
+To give some transparency into how we coded the answers, we provide the coding outline we used.
+If an answer mentioned multiple concerns, the answer was given multiple coding labels\\
+
+\noindent {\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
 {\bf Security}:  ``security,'' mention of malware, hacking. \\

### 2016-01-29 USEC2016-camera-ready/tex-inputs/appendixes.tex
added a missing period
fixed errors in appendix

--- 2015-12-07 tex-inputs/appendixes.tex
@@
 
-\section{Coding Label Definitions}
+\noindent {\bfseries Omitted Survey Questions}
+\label{sec:noquestions}
+Our participants answered four additional questions not detailed in this paper.
+Two questions compared smartphones to wearable devices, to investigate if participants inherently saw wearables as threatening due to its unfamiliarity.
+The questions were not particularly well suited for this task, and our results showed no significant difference between smartphone and wearables perceptions.
+
+The other two questions asked participants to numerically rate risks and benefits of familiar technologies versus wearables (e.g., an airplane versus a wearable).
+This was to mimic the methodology in Fischhoff's seminal study on attitudes toward technological risks and benefits.
+In Fischhoff's study \cite{fischhoff1978safe}, all technologies were concerning with physical risk, while ours mixed information disclosure risks with physical risks.
+These comparisons were unsound to make.
+Nonetheless, our results largely highlighted participants' unfamiliarity with devices; generally, participants rated more familiar technologies as more beneficial or risky.
+\\
+
+\noindent {\bfseries Coding Label Definitions}
 \label{sec:coding}
-Researchers coded the self reported answers as follows:\\
-{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
+To give some transparency into how we coded the answers (ranging from 1 to 1,400+ words), we provide the coding outline we used.
+An answer mentioning multiple concerns was given multiple coding labels.
+\\
+
+\noindent {\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
 {\bf Security}:  ``security,'' mention of malware, hacking. \\

### 2016-02-02 USEC2016-camera-ready/camera-ready.tex
Fixed various typos and grammatical errors, used correct reference format

@@
 \noindent Wearable devices, or ``wearables,'' bring great benefits but also potential information disclosure risks that could expose users' activities without their awareness or consent.
-We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify which users find most concerning if disclosed.
-Our study relatively ranks a potential data capture scenarios enabled by wearables and investigates the impact of the recipient of the data on the perceived risk of data disclosure.
+We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify the data disclosure scenarios that users find most concerning.
+Our study relatively ranks potential data capture scenarios enabled by wearables and investigates the impact of the recipient of the data on the perceived risk of data disclosure.
 We conclude with a brief survey of users' perception of general risks associated with wearable devices, which includes factors such as safety, changes in social behaviors, and impact on fashion.
-To our knowledge, this is the largest user-based experiment concerning information disclosure regarding wearables.
-We hope that this work will aid in the design of future user notification, permission management, and access control schemes for wearables.
+To our knowledge, this is the largest user-based experiment concerning information disclosure surrounding wearables.
+We hope that this work will aid in the design of future user notifications, permission management, and access control schemes for wearables.
 \end{abstract}
@@
 
-Wearables are a \$700 million, growing industry~\cite{cmo}.
+Wearables are a growing \$700 million industry~\cite{cmo}.
 With 20\% of the population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, ubiquitous computing is becoming a reality.
@@
 
-Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to a virtual-object filled augmented reality.
+Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to virtual-object filled augmented reality.
 However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent.
@@
 Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}.
-Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.
+Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users~\cite{1_russell_2014,16_gross_2014}.
 
-Wearables' sensor capabilities, continuous access, and ubiquitous presence will result in a firehose of familiar and unfamiliar types of data, at a rate which will likely dwarf the amount of data currently captured by smartphones.
-Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured~\cite{denning2014situ}.
+Wearables' sensor capabilities, continuous access, and ubiquity will result in a firehose of familiar and unfamiliar types of data, at a rate which will likely dwarf the amount of data currently captured by smartphones.
+Bystanders in the proximity of wearable devices have already expressed interest in being notified before data about them is captured~\cite{denning2014situ}.
 However, subjecting people to increased notifications is not a sound option, as it has shown to lead to negative effects, such as frustration and habituation~\cite{bohme2011security}.
-An understanding of user concerns may allow for targeted and effective communication with the user, inform design of future permission systems, or provide insight for access control mechanisms.
+An understanding of user concerns may allow for targeted and effective user communication, inform design of future permission systems, or provide insights for access control mechanisms.
 
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item We give a relative ranking of 72 potential capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
+\item We relatively rank 72 potential capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
 \item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient.
@@
 We designed a survey for our IRB-approved study to capture the general public's perception of information disclosure risks associated with wearables.
-To determine the most concerning data disclosure scenarios, we asked them to rate their level of concern for a 6 of scenarios from a list of 72 possible scenarios.
+To determine the most concerning data disclosure scenarios, we asked participants to rate their level of concern for 6 scenarios drawn from a list of 72 possible scenarios.
 This was intended to elicit their perception of the severity and impact of the risk.
@@
 At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks.
-These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today.
+These devices' capabilities and requested permissions were the basis for the list of possible data capture scenarios used in this study, which we feel will be representative of what users are likely to encounter today.
 For a scenario to be included in this study, the scenario was required to be understandable to a user, possible to happen with today's wearable devices, and capture unique information not in other scenarios.
@@
 To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios.
-The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables.
-See Appendix \ref{sec:noquestions} for details.\\
+The average survey completion time was 11.5 minutes, which included four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables.
+See the appendix for details.\\
 
 \noindent {\bfseries Comprehension Questions}
+Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios around a fictitious wearable.
 The survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios on a fictitious wearable.
 We highlighted the capabilities of this device and described use cases:\\
@@
 
-To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.\\
+To guarantee that participants understood its capabilities, we asked two multiple-choice comprehension questions and removed participants who did not answer both correctly.\\
 
@@
 The exit portion of the survey collected demographics (age, gender, and education) and wearable device ownership so we could control for prior exposure.
-An open-ended question the most likely risks associated with wearable devices was included to capture user concerns more broadly.
-To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes.
+We included an open-ended question about the most likely risks associated with wearable devices to capture user concerns more broadly.
+To avoid biasing the open-ended question, we asked it before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which we used to control for participants' general privacy attitudes.
 However, we realize that we asked this open-ended question after exposing participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks.
@@
 We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue.
-The focus group participants took the survey, gave feedback on the format and the content, and noted any confusions.
+The focus group participants took the survey, gave feedback on the format and the content, and noted any confusion.
 The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional information disclosure scenarios.
@@
 We had at least 141 responses per data type, 2,779 per recipient, and 35 responses per each unique data type/recipient combination.
-In this section, we present participants' responses to the various data disclosure scenarios and discuss various factors contributed to their risk perceptions.
-We conclude the section with self-reported general wearables concerns.\\
+In this section, we present participants' responses to the various data disclosure scenarios and discuss how various factors contributed to their risk perceptions.
+We conclude with self-reported general wearables concerns.\\
 
 \noindent {\bfseries Data Type}
-Based on our statistical models (later reported in Section \ref{sec:regression}), we observe that the largest effect on participants' VURs stemmed from the data being shared, rather than  with whom the data is shared.
-The most and least concerning data types are listed in Table \ref{top10-table}.
+Based on our statistical models (reported later), we observed that the largest effect on participants' VURs stemmed from the data being shared, rather than with whom the data is shared.
+Table \ref{top10-table} lists the most and least concerning data types.
 
-Participants were most concerned about photos and videos, especially if they contained embarrassing content, personal content, nudity, financial information, or information that can be used to impersonate someone (e.g., usernames/passwords for websites).
-As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and are almost unanimously considered to be concerning.
+Participants were most concerned about photos and videos, especially those containing personal or embarrassing content, nudity, financial information, or information that can be used for impersonation (e.g., usernames/passwords).
+As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and were almost unanimously concerning.
 
@@
 But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
-Similarly, we are unaware of a more appropriate test, given our data format.
+Similarly, we are unaware of a more appropriate test (beyond using mixed effects modeling), given our data format.
 Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
@@
 \end{tabular}
-\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
+\caption{Chi-square tests to examine VUR based on data recipient.}
 \label{recipient-chi}
@@
 
-\noindent {\bfseries Open-ended Concerns}
-We captured participants' reactions to wearable devices as a whole by asking the following open-ended question:
+\noindent {\bfseries Open-Ended Concerns}
+We asked participants the following open-ended question:
 
@@
 
-Participants were asked to write in a blank box, with no particular suggestion on what to talk about or a character limit to their responses.
+Participants did not receive any additional prompts and responded using a text box that did not have a character limit.
 Table \ref{openresponses} shows common user concerns related to wearable devices.
-Appendix \ref{sec:coding} details which responses were categorized in a coding label.
-Note that participants were especially concerned with privacy and security.
-Many answers mention scenarios not included in the study, but prior exposure to our questions may have heightened sensitivity to information disclosure risks.
-\\
+The appendix details the coding of responses.
+Note that participants were especially concerned with privacy and security; many answers mentioned scenarios not included in the study, but prior exposure to our questions may have heightened sensitivity to information disclosure risks:\\
 
@@
 
-Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\
+Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EM waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\
 
@@
 
-Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\
+Interestingly, a few participants were concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\
 
@@
 The landscape of users' perceived risks associated with wearables is broad, encompassing concepts outside of privacy and security.
-We hope that this frames our research to be just one aspect of risks associated with wearables, and motivates researchers to investigate these other risks.
+We therefore hope this motivates other researchers to investigate these other risks.
 \\
@@
 
-While these models illustrate the relative weights that users place on information when determining a scenario as truly upsetting, one shortcoming of this approach is its generalizability: the data predictor is categorical and limited to the data that we specifically chose for this study.
+While these models illustrate the relative weights that users place on information when determining whether a scenario is truly upsetting, one shortcoming is this approach's generalizability: data types are limited to what we specifically chose for this study.
 To make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the type of data (e.g., video, audio, etc.) and the type of risk it presents.
-Two researchers agreed on a codebook and independently coded each of the 72 data types.\\
-
-The data types fell into these six categories:\\
+Two researchers agreed on a codebook and independently coded each of the 72 data types.
+The data types fell into six categories:
 
@@
 \item Biometric Information
-\item Demographic Information\\
+\item Demographic Information
 \end{enumerate}
@@
 We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.
-\\
 
-The risks for data types fell into these five categories:\\
+The risks for data types fell into five categories:
 
 \begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-\item {\bf Financial:} the loss of money or property.
-\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing).
-\item {\bf Medical:} the disclosure of medical information.
-\item {\bf Physical:} physical harm to the user.
-\item {\bf Relationships:} damage to the user's inter-personal relationships.\\
+\item {\bf Financial:} the loss of money or property
+\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing)
+\item {\bf Medical:} the disclosure of medical information
+\item {\bf Physical:} physical harm to the user
+\item {\bf Relationships:} damage to inter-personal relationships
 \end{enumerate}
@@
 \noindent {\bfseries Limitations}
-One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable.
-Because of this, our participants may be over or underestimating the risk, stemming from an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  Biometrics were generally not a concern for our participants, although there are security and privacy implications~\cite{prabhakar2003biometric}.
-Our participants also did not differentiate between the benefits and risks of various new capabilities.
+One of the limitations of our experiment is that our participants might not have knowledge of or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable device.
+Because of this, our participants may be overestimating or underestimating risk due to an unawareness of what can be inferred from the data collected by these devices.
+Our participants may not have clear understandings of new technologies with respect to familiar ones, and may also have a higher likelihood of being influenced by reports of recent events relevant to these unfamiliar devices.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  We also noted that biometrics were generally not a concern for our participants, although they have security and privacy implications~\cite{prabhakar2003biometric}.
+Our participants also did not differentiate between the benefits and risks of various new capabilities made possible by wearable devices.
 
@@
 At the same time, our results do reflect actual perceptions of wearable devices and the associated information disclosure scenarios.
-This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and acceptance so that future systems can be designed with these in mind.
+This is an unavoidable, yet important distinction to make with studies of this nature: our primary goal was to examine perceptions and acceptance so that future systems can be designed with these in mind.
 We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over {\it post hoc} approaches (or ignoring user concerns altogether).
@@
 Users are willing to tolerate risks if there is enough benefit associated with that risk.
-We do believe that since all of our questions were out of context, our study does represent what data people ambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\
+We do believe that since all of our questions were out of context, our study does represent what data people unambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\
 
@@
 
-We find that although people have opinions on applications which are familiar, users are still unfamiliar with particular data types or capabilities.
+We find that although people have opinions on applications which are familiar, users are still unfamiliar with particular data types and capabilities.
 We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work broadly in contextual and user-input-independent permission models and access control schemes.
@@
 Our study is limited to owners of general consumer wearable devices.
-Denning {\it et al.}\ study the effect of wearables on bystanders, to find that bystanders have a range of indifferent to negative reactions which depend on the how acceptable users find the recording to be.
-Nasir {\it et al.}\ specifically explore medical wearables, to find that perceived risk determines physician and user acceptance of wearable health technologies.
+Denning {\it et al.}\ study the effect of wearables on bystanders, to find that bystanders have a range of indifferent to negative reactions which depend on how acceptable users find the recording to be~\cite{Denning2014}.
+Nasir {\it et al.}\ specifically explore medical wearables, to find that perceived risk determines physician and user acceptance of wearable health technologies~\cite{nasir2015consumers}.
 
@@
 \noindent {\bfseries Ubiquitous Sensing} We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}.
-Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique problems present in terms for law and policy~\cite{roesner2014augmented}.
+Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique problems present in terms of law and policy~\cite{roesner2014augmented}.
 Privacy preservation research in this age of ubiquitous sensing include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}.
@@
 \noindent {\bfseries Lessons from Smartphones} Not long ago, smartphones revolutionized applications' access to  data.
-While this tends to benefit users, they do not think of the privacy implications.
+While this tends to benefit users, they often do not think of the privacy implications.
 There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}, which are applicable to wearables.
@@
 
- Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric information disclosure concerns int he age of wearable computing.
+ Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric information disclosure concerns in the age of wearable computing.
 We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients.
-Our open-ended responses show that privacy and security are at the top of user's overall concerns.
+Our open-ended responses show that privacy and security are at the top of users' overall concerns.
 While wearables are still in their infancy, perceptions of situations and capabilities are likely to change rapidly with advancements and increased exposure.
-Our examination of possible data concerns agree with previous studies of smartphone users that found that video capture and financial data are the most sensitive data types, and least acceptable to be disclosed without user consent.
+Our examination of possible data concerns corroborate previous studies of smartphone users that found that video capture and financial data are the most sensitive data types, and least acceptable to be disclosed without user consent.
 Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.
@@
 Our results may be used by system designers to create permissions and access control mechanisms that do not directly depend on users' inputs.
-We hope that this work has given an insight into user acceptability in information disclosure and general user concerns about wearable devices, and that this study motivates privacy and security work for wearable devices.
+We hope that this work has given an insight into user acceptability in information disclosure and general user concerns about wearable devices, and that this study motivates future privacy and security work for wearable devices.
 
-\bibliographystyle{abbrv}
+\bibliographystyle{IEEEtran}
 \bibliography{bibliography.bib}

### 2016-02-02 USEC2016-camera-ready/camera-ready.tex
Made title wrap better
used official IEEE template (rather than implicit)

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Information Disclosure Concerns in The Age of Wearable Computing}
+\title{Information Disclosure Concerns\\in The Age of Wearable Computing}
 
@@
 \subsection{Survey Questions}
-\noindent We report on participants' responses to 23 questions across 4 survey sections:  \\
+\noindent We report on participants' responses to 23 questions across 4 survey sections:
 
@@
 \item 1 open-ended wearables risk question
-\item 14 demographic questions \\
+\item 14 demographic questions 
 \end{itemize}
@@
 The average survey completion time was 11.5 minutes, which included four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables.
-See the appendix for details.\\
+See the appendix for details.
 
@@
 The survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks.
-We highlighted the capabilities of this device and described use cases:\\
+We highlighted the capabilities of this device and described use cases:
 
@@
 
-To guarantee that participants understood its capabilities, we asked two multiple-choice comprehension questions and removed participants who did not answer both correctly.\\
+To guarantee that participants understood its capabilities, we asked two multiple-choice comprehension questions and removed participants who did not answer both correctly.
 
@@
 Figure \ref{fig:prompt} shows an example.
-Specifically, questions were of the form: \\
+Specifically, questions were of the form:
 
@@
 \noindent
-\textit{``How would you feel if an app on your Cubetastic3000 learned (data) and shared it with (recipient), without asking you first?''}\\
+\textit{``How would you feel if an app on your Cubetastic3000 learned (data) and shared it with (recipient), without asking you first?''}
 \end{quotation}
@@
 We clarified that ``app'' meant that the data was not shared with anyone else but a server.
-\\
 
@@
 In this section, we present participants' responses to the various data disclosure scenarios and discuss how various factors contributed to their risk perceptions.
-We conclude with self-reported general wearables concerns.\\
+We conclude with self-reported general wearables concerns.
 
@@
 Generally, the average concern magnitude was inversely correlated with the standard deviation, which suggests the presence of ceiling effects for the most concerning data types.
-For the complete ranked list of data types in this study, see Table \ref{all-vur}.\\
+For the complete ranked list of data types in this study, see Table \ref{all-vur}.
 
@@
 Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation.
-Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were not as significant.
-Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.
+Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application; differences between human recipients were not as significant.
+Our results motivate mechanisms for tracking data flow and preventing accidental data sharing.
 
@@
 We believe a more fine-grained study is required to measure these effects accurately, although we have insight into the existence of these trends.
-Table \ref{all-vur} shows the complete VURs and rankings of all data types by recipient.\\
+Table \ref{all-vur} shows the complete VURs and rankings of all data types by recipient.
 
@@
 \noindent
-\textit{P1256: ``They can be hacked and then your security will be compromised.''}\\
+\textit{P1256: ``They can be hacked and then your security will be compromised.''}
 \end{quotation}
 
-Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EM waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\
+Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EM waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).
 
@@
 \noindent
-\textit{P1038: ``Becoming distracted by the devices while doing other activities that require concentration such as driving.''}\\
+\textit{P1038: ``Becoming distracted by the devices while doing other activities that require concentration such as driving.''}
 
@@
 
-Interestingly, a few participants were concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\
+Interestingly, a few participants were concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact).
 
@@
 \textit{P1425: I think the biggest risk is how they may effect society as a whole...
-a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}\\
+a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}
 \end{quotation}
@@
 We therefore hope this motivates other researchers to investigate these other risks.
-\\
 
@@
 The effect of a participant's gender also did not remain significant upon correcting for multiple testing.
-We observed no correlation between a participant's education level and VUR.\\
+We observed no correlation between a participant's education level and VUR.
 
@@
 We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.
-
 The risks for data types fell into five categories:
@@
 Users are willing to tolerate risks if there is enough benefit associated with that risk.
-We do believe that since all of our questions were out of context, our study does represent what data people unambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\
+We do believe that since all of our questions were out of context, our study does represent what data people unambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.
 
@@
 While risk communication for the physical world has been examined for several decades (e.g.,~\cite{slovic2000perception, Fischhoff,Morgan2001}), research into effectively communicating computer-based risks has only recently been researched.
-For example, both Garg {\it et al.}\ and Blythe {\it et al.}\ show that due to varying perceptions and abilities that correlate with demographic factors, computer-based risk communication should employ some degree of demographic targeting~\cite{Garg2012,Blythe2011}.
-While this work is likely applicable to wearable computing risk communication, we believe that a better understanding of users'  information risk acceptance in this domain is warranted prior to examining risk communication.
+For example, Garg {\it et al.}\ and Blythe {\it et al.}\ show that computer-based risk communication should employ some degree of demographic targeting due to varying perceptions and abilities that correlate with demographic factors~\cite{Garg2012,Blythe2011}.
+This work is likely applicable to wearable computing risk communication, a more thorough understanding of users'  information risk acceptance in this domain is warranted prior to examining risk communication.
 
@@
 However, understanding user concerns is a necessary first step not only for risk communication, but preventative measures against breaches of privacy and security in a new threat landscape.
-\\
 
@@
 Our work aims to guide these efforts with an insight into user acceptance of common information risks.
-\\
 
 \noindent {\bfseries Lessons from Smartphones} Not long ago, smartphones revolutionized applications' access to  data.
-While this tends to benefit users, they often do not think of the privacy implications.
-There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}, which are applicable to wearables.
+While this tends to benefit users, users often do not think of the privacy implications.
+Many unresolved concerns, such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}, are applicable to wearables.
 
-Felt {\it et al.} previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}.
+Felt {\it et al.} previously studied the security concerns of smartphone users through large-scale online survey~\cite{Felt}.
 Their survey asked 3,115 smartphone users about 99 risk scenarios.
 Participants were asked how upset they would be if a certain action occurred without their permission.
-Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.\\
+Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our methodology closely follows that study, but with scenarios chosen to shed light on the security and privacy risks of wearable devices.
 
@@
 
+\newpage
 \input{tex-inputs/appendixes.tex}

### 2016-02-02 USEC2016-camera-ready/camera-ready.tex
Fixed

--- 2016-02-02 USEC2016-camera-ready/camera-ready.tex
@@
 \usepackage{graphicx}
-\usepackage{enumitem}
+%\usepackage{enumitem}
 \usepackage{pdfpages}
@@
 \IEEEauthorblockA{University of California, Berkeley\\
-\{lnl@,dlwndghk94,egelman,daw\}@cs.berkeley.edu}}
+\{lnl,dlwndghk94,egelman,daw\}@cs.berkeley.edu}}
 %\and
@@
 
-We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients.
+This chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients.
 But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results.
 Similarly, we are unaware of a more appropriate test (beyond using mixed effects modeling), given our data format.
-Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed).
+Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality.
 Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation.
-Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were not as significant.
-Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.
+Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were negligible.
 
@@
 \end{tabular}
-\caption{Chi-square tests to examine VUR based on data recipient.}
+\caption{Chi-square tests to examine VUR based on data recipient, across all data points.}
 \label{recipient-chi}
@@
 \noindent {\bfseries Open-Ended Concerns}
-We asked participants the following open-ended question:
+To examine privacy and security concerns that may have otherwise not been captured by our scenarios, we asked participants an open-ended question:
 
@@
 \noindent
-\textit{What do you think are the most likely risks associated with wearable devices?}\\
+\textit{What do you think are the most likely risks associated with wearable devices?}
 \end{quotation}
@@
 
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\begin{enumerate}%[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
 \item Photo
@@
 
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\begin{enumerate}%[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
 \item {\bf Financial:} the loss of money or property
@@
 
-\bibliographystyle{IEEEtran}
+\section*{Acknowledgements}
+
+We would like to thank the National Science Foundation (NSF) for supporting the first author through a Graduate Research Fellowship.
+This work was also made possible by the Intel Science and Technology Center for Secure Computing and NSF awards CNS-1514211 and CNS-1514457.
+
+\bibliographystyle{IEEEtranS}
 \bibliography{bibliography.bib}
